### 2016-12-17 Latex/article.tex
First commit

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997 Cambridge University Press

\NeedsTeXFormat{LaTeX2e}

\documentclass{jfm}
%\documentclass[referee]{jfm} %for double spaced output for submission

\usepackage{graphicx}
\usepackage{natbib}

\usepackage{color}
\usepackage{soul}

\pdfoptionpdfminorversion 4

% \pdfcompresslevel0

% See if the author has AMS Euler fonts installed: If they have, attempt2
% to use the 'upmath' package to provide upright math.
\ifCUPmtlplainloaded \else
  \checkfont{eurm10}
  \iffontfound
    \IfFileExists{upmath.sty}
      {\typeout{^^JFound AMS Euler Roman fonts on the system,
                   using the 'upmath' package.^^J}%
       \usepackage{upmath}}
      {\typeout{^^JFound AMS Euler Roman fonts on the system, but you
                   dont seem to have the}%
       \typeout{'upmath' package installed. JFM.cls can take advantage
                 of these fonts,^^Jif you use 'upmath' package.^^J}%
       \providecommand\upi{\pi}%
      }
  \else
    \providecommand\upi{\pi}%
  \fi
\fi

% See if the author has AMS symbol fonts installed: If they have, attempt
% to use the 'amssymb' package to provide the AMS symbol characters.

\ifCUPmtlplainloaded \else
  \checkfont{msam10}
  \iffontfound
    \IfFileExists{amssymb.sty}
      {\typeout{^^JFound AMS Symbol fonts on the system, using the
                'amssymb' package.^^J}%
       \usepackage{amssymb}%
       \let\le=\leqslant  \let\leq=\leqslant
       \let\ge=\geqslant  \let\geq=\geqslant
      }{}
  \fi
\fi

% See if the author has the AMS 'amsbsy' package installed: If they have,
% use it to provide better bold math support (with \boldsymbol).

\ifCUPmtlplainloaded \else
  \IfFileExists{amsbsy.sty}
    {\typeout{^^JFound the 'amsbsy' package on the system, using it.^^J}%
     \usepackage{amsbsy}}
    {\providecommand\boldsymbol[1]{\mbox{\boldmath $##1$}}}
\fi

%%% Example macros (some are not used in this sample file) %%%

% For units of measure
\newcommand\dynpercm{\nobreak\mbox{$\;$dyn\,cm$^{-1}$}}
\newcommand\cmpermin{\nobreak\mbox{$\;$cm\,min$^{-1}$}}

% Various bold symbols
\providecommand\bnabla{\boldsymbol{\nabla}}
\providecommand\bcdot{\boldsymbol{\cdot}}
\newcommand\biS{\boldsymbol{S}}
\newcommand\etb{\boldsymbol{\eta}}

% For multiletter symbols
\newcommand\Real{\mbox{Re}} % cf plain TeX's \Re and Reynolds number
\newcommand\Imag{\mbox{Im}} % cf plain TeX's \Im
\newcommand\Rey{\mbox{\textit{Re}}}  % Reynolds number
\newcommand\Pran{\mbox{\textit{Pr}}} % Prandtl number, cf TeX's \Pr product
\newcommand\Pen{\mbox{\textit{Pe}}}  % Peclet number
\newcommand\Ai{\mbox{Ai}}            % Airy function
\newcommand\Bi{\mbox{Bi}}            % Airy function

% For sans serif characters:
% The following macros are setup in JFM.cls for sans-serif fonts in text
% and math.  If you use these macros in your article, the required fonts
% will be substitued when you article is typeset by the typesetter.
%
% \textsfi, \mathsfi   : sans-serif slanted
% \textsfb, \mathsfb   : sans-serif bold
% \textsfbi, \mathsfbi : sans-serif bold slanted (doesnt exist in CM fonts)
%
% For san-serif roman use \textsf and \mathsf as normal.
%
\newcommand\ssC{\mathsf{C}}    % for sans serif C
\newcommand\sfsP{\mathsfi{P}}  % for sans serif sloping P
\newcommand\slsQ{\mathsfbi{Q}} % for sans serif bold-sloping Q

% Hat position
\newcommand\hatp{\skew3\hat{p}}      % p with hat
\newcommand\hatR{\skew3\hat{R}}      % R with hat
\newcommand\hatRR{\skew3\hat{\hatR}} % R with 2 hats
\newcommand\doubletildesigma{\skew2\tilde{\skew2\tilde{\Sigma}}}
%       italic Sigma with double tilde

% array strut to make delimiters come out right size both ends
\newsavebox{\astrutbox}
\sbox{\astrutbox}{\rule[-5pt]{0pt}{20pt}}
\newcommand{\astrut}{\usebox{\astrutbox}}

\newcommand\GaPQ{\ensuremath{G_a(P,Q)}}
\newcommand\GsPQ{\ensuremath{G_s(P,Q)}}
\newcommand\p{\ensuremath{\partial}}
\newcommand\tti{\ensuremath{\rightarrow\infty}}
\newcommand\kgd{\ensuremath{k\gamma d}}
\newcommand\shalf{\ensuremath{{\scriptstyle\frac{1}{2}}}}
\newcommand\sh{\ensuremath{^{\shalf}}}
\newcommand\smh{\ensuremath{^{-\shalf}}}
\newcommand\squart{\ensuremath{{\textstyle\frac{1}{4}}}}
\newcommand\thalf{\ensuremath{{\textstyle\frac{1}{2}}}}
\newcommand\Gat{\ensuremath{\widetilde{G_a}}}
\newcommand\ttz{\ensuremath{\rightarrow 0}}
\newcommand\ndq{\ensuremath{\frac{\mbox{$\partial$}}{\mbox{$\partial$} n_q}}}
\newcommand\sumjm{\ensuremath{\sum_{j=1}^{M}}}
\newcommand\pvi{\ensuremath{\int_0^{\infty}%
  \mskip \ifCUPmtlplainloaded -30mu\else -33mu\fi -\quad}}

\newcommand\etal{\mbox{\textit{et al.}}}
\newcommand\etc{etc.\ }
\newcommand\eg{e.g.\ }

\newcommand{\uu}{\textbf{u}}
\newcommand{\xx}{\textbf{x}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\JJ}{\textbf{J}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ff}{\textbf{f}}
\newcommand{\FF}{\textbf{F}}
\newcommand{\baa}{\textbf{a}}
\newcommand{\bb}{\textbf{b}}
\newcommand{\NN}{\textbf{N}}

\newcommand{\eps}{\varepsilon}

\newcommand{\ErtelPV}{\mathcal{Q}}

\newcommand{\fdiss}{f_{\mbox{\scriptsize diss}}}

\newcommand{\D}{\mbox{D}}

\newcommand{\eez}{\boldsymbol{e_z}}
\newcommand{\scalarprod}[2]{\big( #1 \, , \ #2 \big)_{\kk}}

\newcommand{\mean}[1]{\langle #1 \rangle}

\newcommand{\meane}[1]{\langle #1 \rangle}
% \newcommand{\meane}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}e}}}

\newcommand{\meanx}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}\mbox{\scriptsize$\xx$}}}}

\newcommand{\meant}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}\theta}}}

\newcommand{\means}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}s}}}

\newcommand{\shocks}{ {\mbox{\tiny shocks}} }

\newcommand{\kmax}{k_{\mbox{\scriptsize max}}}
\newcommand{\kdiss}{k_{\mbox{\scriptsize diss}}}

\newcommand{\mA}{\mathcal{A}}

\newlength{\halfwidth}
\setlength{\halfwidth}{66mm}

\newcommand{\PA}[1]{{\color{green}#1}}

\newcommand{\Add}[1]{{\color{blue}#1}}
% \newcommand{\Add}[1]{#1}
\newcommand{\Remove}[1]{{\color{red}\st{#1}}}
% \newcommand{\Remove}[1]{}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\title[Wave energy cascade in shallow-water flows]%
{Wave energy cascade in forced-dissipative one-layer shallow-water flows}

\author[P. Augier and E. Lindborg]%
{Pierre Augier$^{1,2}$%
  \thanks{Email address for correspondence: p.augier@damtp.cam.ac.uk},\ns
and Erik Lindborg$^1$}

\affiliation{$^1$Linn\'e Flow Centre, KTH Mechanics,
SE-100 44 Stockholm, Sweden\\[\affilskip]
$^2$Department of Applied Mathematics and Theoretical Physics,
University of Cambridge, Cambridge CB3 0WA, United Kingdom}

\pubyear{2013}
\volume{???}
\pagerange{???--???}
% Do not enter received and revised dates. These will be entered by
% the editorial office.
\date{?; revised ?; accepted ?. - To be entered by editorial office}
%\setcounter{page}{1}
\begin{document}

\maketitle

% \baselineskip 8mm
\begin{abstract}
The dynamics of one-layer shallow-water flows forced in medium-scale
wave modes and dissipation acting at small scales is investigated by
means of theoretical analysis and numerical simulations with
resolutions up to $7680^2$.
%
We first focus on the non-rotating case for which a statistically
stationary regime is obtained for all resolutions and Froude numbers
$F_f = \eps/(k_f c)$, where $\eps$ is the energy dissipation rate,
$k_f$ the forcing wave number and $c$ the wave speed.
%
All the injected energy goes into a downscale energy
cascade. Consequently, the spectral energy flux is constant and
positive between the forcing wave number and the wave numbers where
dissipation is active.  The spectral energy flux is exactly
equipartioned between kinetic and potential energy.  An exact third
order structure function law of Kolmogorov type is derived and
numerically verified.  However, the downscale cascade is less
efficient than in three-dimensional Navier-Stokes turbulence, since
the mean energy of the statistically stationary flow scales as
$\sqrt{\eps c /k_f}$ and varies with the dissipative scale.
%
Moreover, the spectra scale as $k^{-2}$ and the structure functions of
order larger than two scale approximately as $r$.
%
%
This intermittent scaling is explained by a simple model based on the
assumption that the statistics is totally determined by shocks.
%
It is verified that the dynamics is not drastically modified by system
rotation as long as the forcing wave number is larger than the
deformation wave number $k_d = f/c$, where $f$ is the Coriolis
parameter.
\end{abstract}

% \begin{keywords}
% \end{keywords}

\section{Introduction}

The shallow-water models have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
These models are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere \Add{and on which are based the so-called
primitive equations}.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. \Add{However,
as long as there is no overturning, the shallow-water model in the
limit of a large number of layers and the primitive equations describe
the same dynamics. In the opposite limit, two models are particularly
important from the theoretical point of view.} The two-layer
shallow-water model captures the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The equations of the one-layer shallow-water model are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
one-layer model does not capture the baroclinic instability but it is
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega = \pm \omega_l = \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the wave speed and $k
= |\kk|$ the wave number.
%

For geophysical applications, it is convenient to consider the limits
for which the linear frequency $\omega_{l}$ is much larger than the
characteristic nonlinear frequency $\omega_{nl} = U k$, where $U$ is a
characteristic velocity.  In the limit $f/\omega_{nl} \sim
ck/\omega_{nl} \rightarrow \infty$, one can obtain a quasi-geostrophic
one-layer shallow-water model, i.e. derive self-consistent evolution
equations for the 0-linear-frequency variable, the Charney potential
vorticity.  In this limit, the dynamics of the 0-linear-frequency
variable is totally decorrelated from the fast waves.
%
For finite rotation and wave speed, there are slow balanced motions,
which are associated with relatively weak non-zero linear frequency
modes.
%
When $\omega_{nl}(k) \ll \omega_{l}(k) $, there is only a weak
interaction between waves and the balanced modes.
%
Due to its relative simplicity, the one-layer shallow-water model has
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}. \Add{In this study, we consider the
same model in order to address a related but different issue.}

Balanced flows have a dynamics which is very similar to
two-dimensional turbulence.
%
In the quasi-geostrophic limit, the space-averaged energy and the
space-averaged potential enstrophy are conserved, positive definite
and proportional in Fourier space. This leads\Add{, as in
two-dimensional turbulence,} to an upscale energy cascade and a
downscale enstrophy cascade.
%
Thus, the small-scale dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989, YuanHamilton1994}.  The mechanism of a wave cascade
has been proposed to explain the attraction towards the balanced flows
\cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
statistically stationary shallow-water flows can be obtained forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales.
%
\Add{They propose that the $k^{-5/3}$ spectra that are observed at the
atmospheric meso-scales} \cite[]{NastromGage1985, FrehlichSharman2010}
\Add{and reproduced by some atmospheric models based on the primitive
equations} \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008} \Add{could be reproduced by the one-layer
shallow-water model by a downscale energy cascade of waves.}

However, few studies have investigated the dynamics of the downscale
energy cascade of waves in shallow-water models.
%
Most numerical studies have investigated decaying flows and have not
focused on the cascade \cite[]{FargeSadourny1989,
LarichevMcWilliams1991, SpallMcWilliams1992,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
%
Moreover, there are strong discrepancies between different numerical
results and between these results and available theoretical results.
%
\cite{FargeSadourny1989} reported spectra scaling like $k^{-4}$
whereas those shown by \cite{LahayeZeitlin2012} scale like $k^{-6}$.

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}.  In the case of
inertial-gravity waves, \cite{FalkovichMedvedev1992} showed that the
exact solutions of the kinetic equation corresponding to a constant
downscale energy flux is associated with a spectrum scaling like $E(k)
\sim P^{2/3} k^{-8/3}$.
%
However, as pointed out by \cite{FalkovichMeyer1996} when the
dispersion is small enough, waves moving in the same direction have
the same velocity and interact strongly, which can lead to the
formation of shocks. \Add{In this case, the weak wave turbulence
formalism is unable to give valuable results.}  Such sharp and long
structures have been observed in many simulations
\cite[]{FargeSadourny1989, PolvaniMcWilliamsSpallFord1994,
LahayeZeitlin2012} but \Add{their effects} are not well understood.
%
\cite{Kuznetsov2004} predicted that a flow dominated by shocks should
be associated with spectra scaling like $E(k) \sim k^{-2}$.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks 
and reported spectra in agreement with this theoretical prediction.
%
The shocks also lead to very strong intermittency, as demonstrated by
\cite{BouchaudMezardParisi1995} and \cite{WeinanKhaninMazelSinai1997}
in the case of Burgers turbulence.
%

The dynamics of waves in complex shallow-water flows is not well
understood.  \Add{Our long-term goal is to understand this dynamics
which involves interactions between balance and unbalance parts of the
flow. However, even the wave cascade without balance flow is not well
understood.} A statistically stationary wave cascade has never been
simulated at high resolution.
%
Is it possible to obtain a statistically stationary state in the very
fast wave regime, and how does the mean energy in this hypothetical
regime depends on the forcing and the wave speed?  
% What is the slope of 
\Add{How does} the energy spectra \Add{scale as a function of the
input parameters}?
%
All these questions are open and straightforward simulations may
provide the answers.

\cite{YuanHamilton1994} and \cite{FalkovichMeyer1996} carried out
forced dissipated simulation of the one-layer shallow water model and
acoustic turbulence, respectively.
% 
However, the resolution in both studies was quite coarse \Add{($386^2$
and $101^2$ grid points, respectively)} so that the inertial range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing \Add{with waves in only one
direction} while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

In this paper, we investigate the dynamics of one-layer shallow-water
flows forced in the wave modes by means of high resolution numerical
simulations \Add{with up the  $7680^2$ grid points}.
%
The model is described in section~\ref{section_basic_theory}.
%
We then derive some new theoretical results for this model and for
turbulence dominated by shocks
(section~\ref{section_advanced_theory}).
%
The numerical methods and the forcing are described in
section~\ref{section_methods}.
%
The main numerical results corresponding to the simple case without
global rotation are presented in
section~\ref{section_wave_cascade_f=0}.
%
We investigate the sensibility of the non-rotating results to a
moderate rotation (section~\ref{section_rotation}).

\section{The one-layer shallow-water model}
\label{section_basic_theory}
% \input{section_basic_theory}

\section{Theoretical analysis}
\label{section_advanced_theory}
% \input{section_advanced_theory}

\section{Numerical methods}
\label{section_methods}
% \input{section_methods}

\section{Wave cascade without global rotation}
\label{section_wave_cascade_f=0}
% \input{section_wave_cascade_f=0}

\section{Effects of global rotation}
\label{section_rotation}
% \input{section_rotation}

\section{Conclusions}

We have numerically investigated one-layer shallow-water flows forced
with medium-scale waves and dissipated at small scales.
%
First, we have focused on the non-rotating case and varied the
resolution and the wave speed over a wide range.
%
The spectral energy budget for the full non-quadratic energy has been
derived and has allowed us to show that the KE and the APE fluxes are
constant and equal over a wide range of wave numbers.
%
The KE and APE spatio-temporal spectra present equal and very strong
peaks at the linear wave frequency.
%
These two results show that there is a downscale energy cascade of
non-dispersive waves, explaining the generation of statistically
stationary flows.
%
We have derived an exact Kolmogorov law for the one-layer
shallow-water flow based on the assumption that there is a constant
energy flux due to a purely divergent flow and verified that the
numerical results are in agreement with this theoretical law.

The time- and spaced-averaged energy scales like $E = C_n \sqrt{\eps
L_f c}$ and increases with the resolution at least up to $n = 5760$.
The spectra scale like the Zakharov-Sagdeev spectrum $k^{-3/2}
\sqrt{\eps c}$ at relatively small wave numbers $k \lesssim 2 k_f$ and
like $k^{-2} c^{1/3} \eps^{5/9} k_f^{4/9}$ over the inertial range.
We stress that we lack any convincing theoretical explanations for
these scaling laws and we hope our results will motivate theoretical
investigations on these challenging issues.

Nevertheless, the $k^{-2}$ scaling can be explained by the presence of
discontinuities \cite[]{Kuznetsov2004}.  The snapshots indeed show
very sharp hydraulic jumps, which are the equivalent of shocks in
compressible flows.
%
Following \cite{BouchaudMezardParisi1995} and
\cite{WeinanKhaninMazelSinai1997}, we have built a simple model based
on the assumption that the structure functions are determined only by
shocks.
%
Using only this hypothesis, we explain the extreme intermittent
characteristics of the flows, i.e.\ the $r^1$-scaling of the structure
functions of order larger than 2 and the $r^{-1}$-scaling of the
flatness.
%
Adding a simple hypothesis on the structure of the velocity field
across the shocks, namely $\delta u_L = \delta u \sin\theta$ and
$\delta u_T = \delta u \cos\theta$, where $\theta$ is the angle
between the shock line and the separation vector, we have predicted
the values of ratios of structure functions $R_p(r) \equiv
\mean{|\delta u_L|^p}/\mean{|\delta u_T|^p}$ and of the flatness
factors $F_T/F_L = 1.5$.
%
% Very interestingly, the flatness factors computed from atmospheric
% data \cite[]{Lindborg1999} are also very large with a slope close to
% $-1$ and a ratio $F_T/F_L$ equal to $1.5 \pm 0.1$.
%
Finally, we have shown that as long as $k_f>k_d$, the dispersion added
by the rotation does not prevent the production of the regime studied
in the non-rotating case and only weakly modify the results on the
wave cascade.

% In order to draw conclusions on the interpretation of turbulent
% measurements in geophysical flows, we first have to stress that the
% one-layer shallow-water model can only give insights on some
% mechanisms important for geophysical fluids but is not suitable for
% simulate the oceans and atmosphere.
% %
% Most of the simulations of theses systems are performed solving the
% so-called primitive equations, which are (or in the atmospheric case
% are very similar to) the Navier-Stokes equations under the Boussinesq
% and the hydrostatic approximations.
% %
% We focus on the non-rotating case since it is a reasonable
% approximation for the medium scales for which an energy cascade seems
% to strongly influence the dynamics of geophysical flows, namely the
% mesoscales in the atmosphere and the sub-mesoscales in the oceans.
% %
% The dominant balance for the primitive equations in the strongly
% stratified and high Reynolds number limits corresponds to flows
% structured in thin layers \cite[]{BillantChomaz2001}.
% %
% This layering, which has been widely observed in nature, is of course
% inconsistent with the one-layer shallow-water model.
% %
% Another aspect of the dominant balance in the strongly stratified and
% high Reynolds number case is that the energetic waves are not fast
% compared to the balanced flows ($\omega_l \sim \omega_{nl}$), which is
% very different from the case of the studied one-layer shallow-water
% flows.
% %
% Moreover, the strongly stratified and high Reynolds number dominant
% balance would corresponds in terms of the shallow-water Froude number
% to $Fr \sim 1$.  This limit can not be correctly simulated even with a
% multi-layer shallow-water model since when $Fr \sim 1$ the thickness
% of the layers tends to reach the value 0 for which the shallow-water
% models cease to be well defined.
% %
% Therefore, the shallow-water models are not suitable for simulating
% the geophysical medium scales where the cascade is important.

Our results on the dynamics of the wave energy cascade in the
one-layer shallow-water model can yet give interesting informations on
the interpretation of turbulent measurements in geophysical fluids.
%
Since we have shown in this case that many statistical results are
dominated by the effects of the discontinuities due to shocks, we can
conjecture that the discontinuities or front in the atmosphere can
significantly influence the cascade processes and the statistical
results.
%
It would be interesting in the future to quantity the effects of the
processes of frontogenesis in terms of downscale energy cascade in
geophysical flows.

\section*{Acknowledgements}

The authors thank Gregory Falkovich and Sergey Nazarenko for valuable
comments and suggestions regarding the interpretation of the
simulations.

\appendix

\section{Kinetic energy dissipation and forcing rates}
\label{app_comp}
% \input{appendix_dissip_forcing}

\bibliographystyle{jfm}
\bibliography{biblio}

\end{document}

### 2016-12-17 Latex/section_advanced_theory.tex
First commit

\subsection{Analysis of the wave energy cascade}

\subsubsection{Formulation of the spectral energy budget for
non-quadratic energy}

In order to analyze the flux of energy, we derive the spectral energy
budget, i.e.\ the governing equations for spectral KE and APE
functions.
%
This is not as straightforward as in incompressible turbulence since
the expression of the kinetic energy $E_K = \JJ\cdot\uu/2$ is not
quadratic.
%
In order to define the spectral KE function, we use the relation
\begin{equation}
\meanx{ E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
\end{equation}
where
\begin{equation}
\scalarprod{\baa}{\bb} \equiv \Re\{ \hat \baa(\kk)^* \cdot \hat \bb(\kk) \},
\end{equation}
where $\Re$ denotes the real part, $\kk$ is the wave number and the
hat denotes the Fourier transform.
%
The spectral KE function can therefore be defined as
\begin{equation}
E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2, 
\end{equation}
such as $\meanx{ E_K } = \sum_\kk E_K(\kk)$.
%
Similarly, the PE can be written as the sum over all wave numbers of
the spectral PE function $E_P(\kk) = c^2 |\hat h|^2/2 = c^2
\scalarprod{h}{h}/2$, where, by definition,
\begin{equation}
\scalarprod{a}{b} \equiv \Re\{ \hat a(\kk)^* \hat b(\kk) \}.
\end{equation}

The equation for the spectral KE and PE functions can be written as
\begin{eqnarray}
\p_t E_K(\kk) &=& T_K(\kk) + C_K(\kk),\\
\p_t E_P(\kk) &=& T_P(\kk) - C_P(\kk),
\end{eqnarray}
where
\begin{equation}
C_K(\kk) 
= -\scalarprod{\uu}{\bnabla E_P}/2 - c^2 \scalarprod{\JJ}{\bnabla h}/2,
\end{equation}
\begin{equation}
C_P(\kk) = c^2 \scalarprod{h}{hd} /2,
\end{equation}
\begin{equation}
T_P(\kk) = -c^2 \scalarprod{h}{\uu \cdot \bnabla h + hd/2}
\end{equation}
and
\begin{equation}
T_K(\kk) 
= -\scalarprod{\uu}{\uu \cdot \bnabla \JJ}/2
-\scalarprod{\JJ}{\uu \cdot \bnabla \uu}/2
-\scalarprod{\uu}{d\JJ}/2.
\end{equation}
The mean conversion from potential energy to kinetic energy can be
computed from the two conversion spectral functions as $C = \sum_\kk
C_K(\kk) = \sum_\kk C_P(\kk)$.

\subsubsection{Exact Kolmogorov law for irrotational flows}

As in incompressible homogeneous isotropic turbulence, an exact
Kolmogorov law for irrotational flows can be derived.
%
It is convenient to start from the following form of the governing
equations
\begin{eqnarray}
\p_t \uu &=& -\bnabla \cdot (|\uu|^2/2) - c^2 \bnabla h  
- \zeta_a \eez \wedge \uu, \\
\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
\p_t h   &=& -\bnabla \cdot \JJ.
\end{eqnarray}
Assuming that the flow is irrotational and that there is no global
rotation ($\zeta_a=0$), it can be shown that
\begin{equation}
\p_t ( J_i' u_i ) = - \p_i( J_i'|\uu|^2/2) - \p_i'(u_j J_j' u_i')
-\p_i (J_i' c^2 h)  - \p_i' (u_i E_p')
\end{equation}
and
\begin{equation}
\p_t ( h' h ) = - \p_i( h'J_i ) - \p_i'( hJ_i' ),
\end{equation}
which gives
\begin{eqnarray}
\p_t ( \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h )
&=& - \p_i( J_i'|\uu|^2/2) - \p_i'( J_i|\uu'|^2/2) %\nonumber \\&& 
- \p_i'(u_j J_j' u_i') - \p_i(u_j' J_j u_i) \nonumber\\
&& -c^2\p_i (J_i'h) - c^2\p_i' (J_ih') %\nonumber\\&& 
- \p_i' (u_i E_p') - \p_i (u_i' E_p) \nonumber\\
&& -2c^2\p_i' (J_i'h) - 2c^2\p_i (J_ih').
\end{eqnarray}
We then assume homogeneity and take the ensemble average denoted by
$\meane{}$.  The separation vector is noted $\rr = \xx' - \xx$.  For
every function $g(\xx, \xx')$, we have $\p_i' \meane{g} =
-\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We obtain
\begin{eqnarray}
\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
&=& + \bnabla_{\rr}\cdot\meane{ \JJ'|\uu|^2/2 - \JJ|\uu'|^2/2 } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ u_j J_j' \uu' - u_j' J_j \uu } \nonumber\\
&& - \bnabla_{\rr}\cdot\meane{ \uu E_p'- \uu' E_p } \nonumber\\
&& -c^2\bnabla_{\rr}\cdot\meane{ \JJ'h - \JJ h' }
\end{eqnarray}
%
We then introduce the structure functions and the operator $\delta$
returning the increment of a variable between two points separated by $\rr$, 
for example $\delta h (\xx, \rr) = h(\xx+\rr)- h(\xx)$.
%
Using again homogeneity, we get
\begin{equation}
\meane{ (\delta h)^2 \delta\uu } = 
-\meane{ h'^2 \uu } + \meane{ h^2 \uu' }
+2\meane{ hh' \uu } - 2\meane{ hh' \uu' }
\end{equation}
and 
\begin{equation}
\meane{ |\delta \uu|^2 \delta\JJ } = 
\meane{  |\uu|^2 \JJ' } - \meane{ |\uu'|^2\JJ }
+\meane{ u_ju_j' \JJ' } - \meane{  u_ju_j' \JJ },
\end{equation}
which gives
\begin{equation}
2\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
= \bnabla_{\rr} \cdot ( \meane{ |\delta \uu|^2 \delta\JJ } 
+ c^2\meane{ (\delta h)^2 \delta\uu } ).
\end{equation}
Using isotropy and integrating yield an exact Kolmogorov law for
one-layer shallow water irrotational turbulence
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L } 
+ c^2\meane{ (\delta h)^2 \delta u_L } = -4 \varepsilon r, \label{eq_Kolmo}
\end{equation}
where $\eps$ is the energy dissipation rate and $J_L \equiv
\JJ\cdot\rr / |\rr|$ and $u_L \equiv \uu\cdot\rr / |\rr|$ are
longitudinal increments.

\subsection{Simple model for structure functions determined by a
random set of shocks}
\label{subsection_shock_model}

\cite{BouchaudMezardParisi1995} and \cite{Kuznetsov2004} showed that
the presence of discontinuities can strongly influence the statistics
and in particular lead to very strong intermittency.
%
We now present an extremely simple model based on the assumption that
shocks totally dominate the flow.  The structure functions are
calculated by averaging increments over the total surface of the
domain $\mA$.  Considering that the increments are produced only by
discontinuity lines, we get
\begin{eqnarray}
\meane{|\delta h|^p} 
&=& \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p \nonumber\\
&\simeq& \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
\end{eqnarray}
where $\theta$ is the angle between the shock line and the separation
vector $\rr$ %
and $\Delta h (s)$ is the step in $h$ at a shock.
%
Assuming isotropy, the integral can be split and we get
\begin{equation}
\meane{|\delta h|^p} 
\simeq 
r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h (s)|^p}
=
r \frac{L_s}{\mA} \frac{2}{\pi} \means{|\Delta h (s)|^p},
\end{equation}
where $\meant{}$ denotes the mean over $\theta$, %
$L_s$ is the total length of the shocks in the domain %
and $\means{}$ denotes the mean over all shocks.

For velocity increments, we can also use a characteristic of the
velocity singularities.  The step in velocity is only in the component
perpendicular to the shocks, which implies that the longitudinal and
transverse increments are related by $\delta u_L = \delta u
\sin\theta$, $\delta u_T = \delta u \cos\theta$.
%
Applying the same averaging method, we obtain
\begin{equation}
\meane{|\delta u_L|^p} 
\simeq 
r \frac{L_s}{\mA} 
\meant{|\sin\theta|^{1+p}}
\means{|\Delta u (s)|^p}
\end{equation}
and
\begin{equation}
\meane{|\delta u_T|^p} 
\simeq 
r \frac{L_s}{\mA} 
\meant{|\sin\theta||\cos\theta|^{p}}
\means{|\Delta u (s)|^p},
\end{equation}
where $\Delta u (s)$ is the velocity step at a shock.
%
These assumptions completely determine the ratio between the
longitudinal and transverse structure functions, which can be
analytically computed as
\begin{eqnarray}
R_p(r) \equiv \frac{\meane{|\delta u_L|^p}}{\meane{|\delta u_T|^p}} = 
\frac{\meant{|\sin\theta|^{1+p}}}{\meant{|\sin\theta||\cos\theta|^p}},
\end{eqnarray}
giving the numerical values $R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.

Interestingly, for an isotropic and purely divergent flow ($\zeta =
0$), the longitudinal and transverse second order structure functions
are exactly related by $\meane{(\delta u_L)^2} = \p_r( r\meane{(\delta
u_T)^2} )$ \cite[]{Lindborg2007jas}.
%
If we further assume than both second order structure functions follow
the same scaling law $\meane{ (\delta u_L)^2} \propto \meane{ (\delta
u_T)^2} \propto r^\alpha$, then we have $\meane{ (\delta u_L)^2} =
(1+\alpha) \meane{ (\delta u_T)^2} $, which gives $ R_2 = 2
\Leftrightarrow \alpha = 1$.

The shock model also provides predictions of the flatness factors of
the velocity increments
\begin{eqnarray}
F_L &=&  \frac{\meane{|\delta u_L|^4}}{\meane{|\delta u_L|^2}^2} 
= r^{-1} \frac{\means{|\Delta u|^4}}{\means{|\Delta u|^2}^2} 
\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2},\\
F_T &=&  \frac{\meane{|\delta u_T|^4}}{\meane{|\delta u_T|^2}^2} 
= r^{-1} \frac{\means{|\Delta u|^4}}{\means{|\Delta u|^2}^2} 
\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2},
\end{eqnarray}
and on the ratio of the two flatness factors, which is simply equal to
$F_T/F_L = 1.5$ according to the model.

### 2016-12-17 Latex/section_wave_cascade_f=0.tex
First commit

\subsection{Downscale energy cascade of waves}
\label{subsection_cascade}

\begin{figure}
\centerline{
\includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
\caption{Spectral energy fluxes averaged over a long simulation for $c
= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
and plotted versus $k/k_f$.  }
\label{fig_seb}
\end{figure}

The spectral energy fluxes of total energy, KE and APE are plotted in
figure~\ref{fig_seb} as functions of $k/k_f$.
%
The fluxes are approximately zero at the wave numbers smaller than the
forced wave numbers.  They increase sharply at the forced wave numbers
to values close to $\eps$ for the total energy flux and to $0.5\eps$
for the KE and APE fluxes.  The fluxes then decrease to zero over the
dissipation range.
%
The energy is transferred from the forced wave numbers to the
dissipation wave numbers with a constant flux equal to the mean
forcing and dissipation rates.
%
There is an inertial range where the flux is constant and
equipartitioned between equal KE and APE fluxes.
%
However, at wave numbers $k \simeq 2 k_f$, the flux is not exactly
equal to $\eps$.  This is very likely related to the energy injection
at wave numbers for which the force is zero, which is due to the
non-quadraticity of the kinetic energy (see appendix~\ref{app_comp}).
%
Nevertheless this effect is non-negligible only for wave number of the
order of $k\simeq 2 k_f$, i.e.\ at the first harmonics of the forced
wave numbers, such that there is a clear and wide inertial range
between $k\gtrsim 3 k_f$ to the dissipation range starting at wave
number of the order of $k \sim 70 k_f$.

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
\caption{
Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo}) 
averaged over a long simulation for $c = 20$ and $n = 3840$.
%
The structure functions are normalized by $4 \eps r$.
%
Black thick line, $\mean{ \delta J_L|\delta \uu|^2 } 
+ c^2\mean{\delta u_L(\delta h)^2}$;
light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
%
The dotted straight line shows $4 \eps_q r$, 
where $\eps_q$ is the quadratic energy dissipation rate.
}
\label{fig_Kolmo}
\end{figure}

Figure~\ref{fig_Kolmo} shows the quantity $\mean{\delta J_L|\delta
\uu|^2 } + c^2\mean{\delta u_L(\delta h)^2 }$ (black thick line)
normalized by $4 \eps r$ for $c = 20$ and $n = 1920$.
%
In this section, the brackets $\mean{}$ denote the average over space
and time.
%
The dotted straight line shows the quantity $4 \eps_q r$, where
$\eps_q$ is the quadratic energy dissipation rate (see
appendix~\ref{app_comp}) which takes place at small scales.
%
We see that the Kolmogorov law (\ref{eq_Kolmo}) is well satisfied
between \Add{$r \simeq 0.02L_f$ and $r \simeq 0.1 L_f$}.  The dark and
light thin continuous lines correspond to the quantities $\mean{\delta
J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta h)^2}$,
respectively.
%
These two quantities are nearly equal over the inertial and
dissipation ranges, which is consistent with a wave cascade when
$f=0$.
%
The agreement with the Kolmogorov law and the equality between
$\mean{\delta J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta
h)^2}$ are the equivalents in the separation space of the plateau in
the total energy flux and the equality between $\Pi_K$ and $\Pi_A$,
respectively.

\begin{figure}
\centerline{
\includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
= 12$, 27, 62, 143, 327, and 746.  }
\label{fig_spatiotemp_spectra}
\end{figure}

Figure~\ref{fig_spatiotemp_spectra} presents the spatio-temporal
spectra plotted as a function of the normalized frequency
$\omega/\omega_l$.
%\PA{Explain how these spectra have been calculated.}  
In order to calculate these spectra, we have saved well-resolved time
series of $\hat d(\kk)$ and $\hat a(\kk)$ for wave numbers inside
particular shells such as $k\leqslant \kk<k+\delta k$, computed the
temporal spectrum of each signal and averaged over the wave numbers
inside each shell.
%
The spectra are strongly dominated by large peaks at $\omega =
\omega_l$ indicating that the characteristic frequency for each wave
number is the linear frequency.  However, the widening of the peaks
can be explained only by nonlinear effects.  \Add{The equipartition
between kinetic and potential energies is expected since the flow only
consists of gravity waves and the total energy is nearly equal to the
quadratic energy which is equal to the sum over all waves of their
equipartitioned quadratic energy.}

\subsection{Time- and space-averaged energy as a function of $c$}

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
\includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
}
\caption{Time- and space-averaged energy 
$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ 
of the statistically stationary flows.
%
In (\textit{a}), the energy is divided by 
$\sqrt{\eps}$ and plotted versus $c$ for 3 resolutions:
$n = 960$, dotted lines; 
$n = 1920$, continuous lines and 
$n = 3840$, dashed lines. 
The cyan curves show the law $C_n \sqrt{\eps L_f c}$, 
with $C_n$ a fit coefficient.
%
In (\textit{b}), the energy is divided by 
$\sqrt{\eps L_f c}$ and plotted versus $n$
for six values of $c$ as indicated in the legend.
}
\label{fig_Evsc}
\end{figure}

Figure~\ref{fig_Evsc}(\textit{a}) shows the time- and space-averaged
energy for the statistically stationary flows divided by the square
root of the mean energy dissipation rate as a function of $c$ and for
three resolutions: $n = 960$, dotted lines; $n = 1920$, continuous
lines and $n = 3840$, dashed lines.
%
For all resolutions, the energy increases with $c$.  More precisely,
the curves can be well fitted to a law $E = C_n \sqrt{\eps L_f c}$
(blue lines).  However, the coefficient $C_n$ varies with the
resolution, i.e.\ with the effective Reynolds number.
%
This is very different from the case of isotropic turbulence where the
energy scales as $E \sim (\eps L_f)^{2/3}$ and does not vary with the
Reynolds number in the limit of very large Reynolds number.
%
Weak wave turbulence theory predicts an energy-flux law of the form $E
\propto \eps^{1/(N-1)}$, where $N$ is the number of waves involved
in the nonlinear interactions \cite[]{Nazarenko2011}.  Therefore, the
scaling $E = C_n \sqrt{\eps L_f c}$ would correspond to interactions
involving three waves.
%
However, the hypothesis needed for applying the weak wave turbulence
formulation are not fulfilled.

This effect of the increase of the energy with the resolution is
investigated in figure~\ref{fig_Evsc}(\textit{b}) where the quantity
$C_n = E/\sqrt{\eps L_f c}$ is plotted as a function of the
resolution.
%
For $c = 10$ (dotted line), the waves are not very fast and the
variation with the resolution is weak.
%
However, in the limit of very fast waves ($c>100$), the curves for the
different wave speeds nearly collapse and increase at least up to $n =
5760$.  The increase tends to saturate but it is difficult to know
from our results what is the scaling of $C_n$ as a function of the
resolution and if it really saturates for very large $n$ and $c$.
%
In order to decide on this issue, we would need to run simulations in
the very-fast-wave regime, $c>100$, and at very large resolutions $n >
5760$.  In this regime the energy fluctuations are large so
that the simulations would have to be carried out for very long time
in order to get a good convergence for the mean energy.  Since the
time step has to be extremely small in this regime, such simulations
would be too costly.

\subsection{Energy spectra}

We now turn to the study of the energy spectra.  A dimensional
analysis based on the assumption that the spectra only depend on
$\eps$, $c$ and $k_f$ gives the following general expression
\begin{equation}
E_{\alpha, \beta}(k) = k^{-\alpha} \eps^\beta   c^{2- 3\beta} 
{k_f}^{\alpha -1 - \beta}, \label{eq_E_alpha_beta}
\end{equation}
where $\alpha$ and $\beta$ are two free parameters.

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
}
\caption{
Compensated energy spectra versus $k/k_f$ for different wave speeds $c$.
%
The spectra are compensated by $k^{-3/2}\sqrt{\varepsilon c} $ 
in (\textit{a,b})
and by $k^{-2}c^{1/3} \eps^{5/9} k_f^{4/9} $ 
in (\textit{c,d}).
%
The resolution is 
$n = 1920$ in (\textit{a,c}) and 
$n = 3840$ in (\textit{b,d}).
%
In (\textit{a,c}), the wave speed goes from 10 to 1000
and 
in (\textit{b,d}) from 10 to 200 
(for the precise values, see figure~\ref{fig_Evstime}).
}
\label{fig_spectra_c}
\end{figure}

The scaling of the energy as $\sqrt{\eps L_f c}$ suggests that the
spectra should scale like the Zakharov-Sagdeev spectrum, $E(k) \sim
k^{-3/2}\sqrt{\eps c}$, which is the prediction of weak wave
turbulence theory for three-dimensional acoustic turbulence
\cite[]{Nazarenko2011}.
%
The compensated spectra $E(k) / ( k^{-3/2}\sqrt{\eps c})$ are plotted
in figure~\ref{fig_spectra_c}(\textit{a}) for $n = 1920$ and in
figure~\ref{fig_spectra_c}(\textit{b}) for $n = 3840$.  The different
curves correspond to different wave speeds, going from $c=10$ to
$c=1000$ for $n = 1920$ and from $c=10$ to $c=200$ for $n = 3840$.
%
For both resolutions, the compensated spectra collapse at the
energy-dominating small wave numbers.
%
However, these compensated spectra are not flat in the inertial range
and do not collapse in the inertial and dissipation ranges, i.e. for
$k\gtrsim 2k_f$.  In the inertial range, they follow a clear $k^{-2}$
scaling law and there is a bottleneck in the dissipation range where
the slope is close to $-3/2$.
%
\cite{Kuznetsov2004} showed that $k^{-2}$ spectra can be explained by
singularities and this scaling has already been observed in
two-dimensional acoustic turbulence \cite[]{FalkovichMeyer1996}.
%

Inserting $\alpha = 2$ in the spectrum (\ref{eq_E_alpha_beta}) gives
\begin{equation}
E_\beta(k) = k^{-2} {k_f}^{1-\beta} c^{2-3\beta} \eps^\beta  
\end{equation}
and we have found that the numerical spectra are very close to the
spectrum $E_\beta(k)$ with $\beta = 5/9$.
%
The compensated spectra $E(k) / ( k^{-2} c^{1/3} \eps^{5/9} k_f^{4/9}
)$ are plotted in figure~\ref{fig_spectra_c}(\textit{c}) for $n =
1920$ and in figure~\ref{fig_spectra_c}(\textit{d}) for $n = 3840$.
The collapse is very good in the inertial range but we stress that we
are not aware of any theory predicting the empirical spectrum $k^{-2}
c^{1/3} \eps^{5/9} k_f^{4/9}$.

\begin{figure}
\centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
\caption{Compensated spectra
of total energy (thick black line)
kinetic energy (thin dark line) and
available potential energy (thin light line)
for $c = 40$ and $n = 7680$.}
\label{fig_spectra_c40}
\end{figure}

Figure~\ref{fig_spectra_c40} shows the compensated spectra $E(k) / (
k^{-2} c^{1/3} \eps^{5/9} k_f^{4/9} )$ of total energy (black line),
KE (red line) and APE (blue line) for $c = 40$ and $n = 7680$.  For
all wave numbers, we have $E(k) = 2E_K(k) = 2E_A(k)$ since the flow
only consists of \Add{gravity} waves.
%
The spectra are very close to $k^{-2}$ in the inertial range over more
than one decade and the shallowing to a slope close to $-3/2$ is
clearly confined to the dissipation range.  This confirms that this
bump is due to a dissipation effect and that there is no wide
$k^{-3/2}$ spectrum even at very large resolutions.

% \begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_resol_c=10}
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_resol_c=40}
% }
% \caption{Compensated energy spectra $E(k) / ( k^{-3/2}\sqrt{\eps c})$
% for different resolutions.  In (\textit{a}), $c = 10$ and in
% (\textit{a}), $c = 40$.}
% \label{fig_spectra_resol}
% \end{figure}

% The compensated spectra $E(k) / ( k^{-3/2}\sqrt{\eps c})$ are plotted
% for different resolutions %
% in figure~\ref{fig_spectra_resol}(\textit{a}) for $c=10$ and 
% in figure~\ref{fig_spectra_resol}(\textit{b}) for $c=40$.
% %
% We see that an inertial range with a $k^{-2}$ scaling starts to appear
% for $n\gtrsim 960$.
% %
% As seen in figure~\ref{fig_Evsc}, the ratio $E/\sqrt{\eps L_f c}$ only
% weakly varies for $c=10$ but increases in the fast-waves regime for
% $c=40$.  This effect can be seen here at the energy-containing wave
% numbers $k<2 k_f$.  However, the variation with the resolution is much
% weaker in the inertial range at $k>2 k_f$.

In subsection~\ref{subsection_cascade}, we have shown that third-order
structure functions scale like $r$ since there is a downscale energy
cascade.
%
The Kolmogorov method predicts $k^{-5/3}$-spectra but the numerical
spectra are much steeper in the inertial range, with a slope equal to
-2.  The fact that third-order and second-order quantities can not be
simply related by the Kolmogorov scaling implies that the cascade is
very intermittent.

\subsection{Effect of the shocks and intermittency}

\begin{figure}
\setlength{\halfwidth}{69mm}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
\hspace{-4mm}
\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
\hspace{-4mm}
\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
}
\caption{
Snapshots for $n = 1920$ and two values of the wave speed 
$c= 20$ (\textit{a,c}) and $c= 200$ (\textit{b,d}).
The colors represent the thickness in (\textit{a,b}) and
the $y$-component of the velocity in (\textit{c,d}).
The arrows represent the velocity field.
%
The coordinates are nondimensionalized by the characteristic scale of
the forcing $L_f = 3.57$.  }
\label{fig_phys}
\end{figure}

Figure~\ref{fig_phys} shows %
the normalized thickness $h$ %
(figures~\ref{fig_phys}\textit{a,b}) %
and the $y$-component of the velocity $u_y$ %
(figures~\ref{fig_phys}\textit{c,d}) %
for $c = 20$ (figures~\ref{fig_phys}\textit{a,c}) and %
$c = 200$ (figures~\ref{fig_phys}\textit{b,d}).
%
These wave speeds correspond %
to a moderate forcing Froude number $F_f \sim 0.05$ and %
to a very small forcing Froude number $F_f \sim 0.005$, respectively.
The normalized surface displacement $\eta = h - 1$ is of order 0.3 for
$c = 20$ and one order of magnitude smaller, 0.03, for $c = 200$.
%
The typical velocity is also much smaller than the wave speed, %
with $u_y/c \sim 0.2$ for $c = 20$ %
and $u_y/c \sim 0.03$ for $c = 200$. %
This confirms that the flows are in a fast-wave regime, especially for
$c = 200$.
%
However, many discontinuities can be seen in both fields $h$ and
$u_y$.  These discontinuities are hydraulic jumps, which are the
equivalent to shocks in a compressible flows.
%
\Add{Baines (1998) provides a theoretical prediction for the velocity
of the hydraulic jumps is one-layer shallow-water flow:
\begin{equation}
c_s = c \sqrt{\frac{h_+}{h_-} \frac{h_+ + h_-}{2}},
\end{equation}
where $h_+$ and $h_-$ are the dimensionless thickness before and after
the jump.
%
We have verified that the velocity of the discontinuities in the
simulations is consistent with this theoretical prediction, implying
that the associated Froude number (or Mach number) is of the order
unity.}

\nocite{Baines1998}

% We have verified that these shocks are very fast and travel at a
% velocity of the order of the wave speed \Add{(more precisely, Baines 1998)}
% , implying
% that their associated Froude number (or Mach number) is of the order
% unity.
%el (This is not necessarily true...)
% The existence of shocks implies that there is a strong coherence
% between small and large wave numbers and indicates nonlocal
% interactions between wave numbers.
%
In between the shocks, the flow is very smooth for $c=20$ and slightly
more irregular for $c = 200$.

Figures~\ref{fig_phys}(\textit{c,d}) display the $y$-component of the
velocity.  There are less discontinuities in this quantity than in the
thickness. More precisely, the $h$-discontinuity lines that are along
the $y$-axis are not associated with corresponding discontinuities of
the $y$-component of the velocity. This can be seen for example for
the shock at $x/L_f\simeq 0.4$ and $y/L_f\simeq 2.1$ in
figures~\ref{fig_phys}(\textit{a}) and \ref{fig_phys}(\textit{c}).
%
This illustrates that the singularity in the velocity is in the
component perpendicular to the shock line, which is the assumption on
the structure of the velocity discontinuities used in the model
presented in \S~\ref{subsection_shock_model}.

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_ux}
\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_uy}
}
\caption{
Compensated fifth-order structure functions $\mean{|\delta u_L|^5}/r$ 
of (\textit{a}) the longitudinal increments and (\textit{b}) the
transverse increments. %
The crosses indicate the range of separation $r$ where the exponent
$\zeta_p$ is computed. %
The dashed lines correspond to the Kolmogorov scaling laws $r^{p/3}$
and $\zeta_p = p/3$.  The wave speed and the resolution are $c = 40$
and $n = 7680$.  }
\label{fig_strfct5}
\end{figure}

The shock model derived in subsection~\ref{subsection_shock_model}
predicts that structure functions of all orders should scale linearly
with $r$.
%
Figure~\ref{fig_strfct5} presents fifth-order structure functions
compensated by $r$.
%
Figures~\ref{fig_strfct5}(\textit{a}) and
\ref{fig_strfct5}(\textit{b}) correspond to the structure functions
computed from the longitudinal increments and the transverse
increments, respectively.  The structure functions compensated by $r$
are nearly flat between $r \simeq 0.012 L_f$ and $r \simeq 0.06 L_f$,
showing that they scale like $r$ on this relatively narrow range of
scale compared to the inertial range.
%
The $r$-scaling is very different from the slope of the fifth-order
structure functions calculated from the Kolmogorov scaling $\zeta_5 =
p/3 \simeq 1.66$ (dashed straight line).  This shows that the wave
cascade is strongly intermittent and that this intermittency can be
explained by the presence of discontinuities related to the shocks.

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_interm_ux}
\includegraphics[width=\halfwidth]{../Figs/fig_interm_uy}
}
\caption{
Exponents $\zeta_p$ of the structure functions 
of (\textit{a}) the longitudinal increments 
and (\textit{b}) the transverse increments versus the order $p$.
%
The dashed lines correspond to 
the Kolmogorov scaling laws $r^{p/3}$ and $\zeta_p = p/3$.
The wave speed and the resolution are $c = 40$ and $n = 7680$.
}
\label{fig_interm}
\end{figure}

The slope of the structure functions of order $p$ over the range
$0.012 L_f\leqslant r \leqslant 0.06 L_f$, $\zeta_p$, are plotted in
figure~\ref{fig_interm}(\textit{a}) for the longitudinal increments
and in figure~\ref{fig_interm}(\textit{b}) for the transverse
increments.
%
The exponent are very far from the Kolmogorov scaling $\zeta_p = p/3$.
They increase as $p$ for $p\ll1$, saturate to a value close to 1 for
$p>2$ and tend to decrease for $p>3$.
%
A similar shape of the $\zeta_p$ function has been predicted for
Burger turbulence \cite[]{BouchaudMezardParisi1995}.
%
The shape of $\zeta_p$ at very small $p$ is determined by the
scaling of the smallest velocity increments and the $p^1$-variation
shows that these smallest increments scales like $\delta u \sim r^p$.
%
The plateau at $p > 2$ is a consequence of the dominance by shocks of
the largest increments.
%
Note that these results are obtained for a relatively small forcing
Froude number $F_f \simeq 0.03$ corresponding to $c=40$.  The function
$\zeta_p$ has approximately the same extreme shape for a larger Froude
number $F_f \simeq 0.01$, corresponding to $c=10$.  Note also that the
decrease of $\zeta_p$ for $p>3$ is anomalous, which could be due to
the relatively narrow width of the range over which $\zeta_p$ is
computed.

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
}
\caption{
Ratio of the structure functions of the velocity increments 
$R_p(r) \equiv \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$
for $p = 2,$ 3 and 4.
The dotted straight lines indicate the values computed by the shock model:
$R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
%
The wave speed and the resolution are $c = 10$ and $n = 7680$.  }
\label{fig_ratio}
\end{figure}

The functions $R_p = \mean{|\delta u_L|^p}/\mean{|\delta u_T|^p}$ are
plotted in figure~\ref{fig_ratio} for $p =2$ to 4.  The predictions of
the shock model, $R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$, are also
plotted in dotted lines for comparison.  We see that the numerical
results are reasonably close to these predictions.  However, the
agreement is less good for smaller Froude number (not shown).  The
structure functions are fully determined by shocks only for Froude
numbers that are not too small, which is consistent with the snapshots
in figure~\ref{fig_phys} showing that the fields between the shocks
are more irregular for the smallest Froude number.

\begin{figure}
\centerline{
\includegraphics[width=\halfwidth]{../Figs/fig_flatness}
}
\caption{ Flatness of the longitudinal and transverse increments for
$c = 10$ and $n = 7680$. The straight continuous lines indicate the
$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
The inset shows the ratio $F_T/F_L$ and the corresponding value
computed by the shock model, $F_T/F_L = 1.5$.  }
\label{fig_flatness}
\end{figure}
%
Figure~\ref{fig_flatness} shows the flatness of the longitudinal and
transverse increments, computed from a numerical simulation for $c =
10$ and $n = 7680$.
%
For a Gaussian probability distribution the flatness factor is equal
to 3 whereas the shock model predict flatness factors scaling like
$r^{-1}$.
%
We see that here the flatness factors are much larger than 3, of the
order of $10^3$.
%
Remarkably, they scale approximately as $r^{-1}$ as predicted by the
shock model and the ratio $F_T/F_L$ is very close to the predicted
value 1.5.

% Figure~\ref{fig_flatness}(\textit{b}) shows the same quantities
% computed from atmospheric data measured by commercial aircraft.
% %
% The flatness curves have been taken from \cite{Lindborg1999}.
% Surprisingly, the atmospheric results are quite similar to the
% numerical ones. The flatness factors are very large and strongly
% decrease at scales smaller than 100 km.  Interestingly, the ratio
% $F_T/F_L$ is also very close to the value 1.5 predicted by the shock
% model.
% %
% We stress that even though these similarities are striking, the
% underlying dynamics are very different.
% %
% While there is no energy in the quasi-geostrophic modes in the
% numerical simulations, the atmospheric flows are usually close to be
% quasi-geostrophic at horizontal scales larger than 500 km and the
% vertical vorticity is in average of the same order of magnitude than
% the horizontal divergence at the mesoscales, i.e. at horizontal scales
% between 10 and 500 km \cite[]{Lindborg2007jas}.
% %
% Therefore, it is not surprising to also see differences between the
% atmospheric and the numerical results. The flatness factors in
% figure~\ref{fig_flatness}(\textit{b}) vary approximately as $r^{-3/2}$
% (dashed line), which is significantly faster than for the numerical
% simulations of the shallow-water model. Moreover, the second-order
% structure functions in the atmosphere scale as $r^{2/3}$
% \cite[]{Lindborg1999, ChoLindborg2001,
% FrehlichSharman2010}. Considering the scaling for the flatness
% factors, this implies that the variation with scale of the
% fourth-order structure functions is actually very weak, which is
% not in agreement with the prediction of the shock model.
% %
% Nevertheless, we do not know other explanations of such very large
% flatness factors with a ratio $F_T/F_L=1.5$ observed in the atmosphere.
% %
% Thus, we think that these results raise interesting questions
% regarding the interpretation of structure functions measured in the
% atmosphere.  How important are the discontinuities on horizontal
% cross-sections in these cases?
% %
% It is well known that the fronts separating cold and warm regions 
% explain many meteorological phenomena.
% %
% The curves in figure~\ref{fig_flatness} seem to indicate that 
% they could also have strong effects on the statistics of the atmosphere
% over a quite large range of scales.

### 2016-12-17 old/section_basic_theory.tex
First commit

\subsection{Physical system and governing equations}

We consider a thin layer of fluid over a flat bottom and with a free
surface.
%
Under the assumption that the characteristic horizontal scale of the
flow $L$ is much larger than the mean layer thickness $H_0$, it can be
shown that the pressure is only a function of the local layer
thickness $H(x, y)$, i.e.\ that the flow is hydrostatic.
%
Further assuming that the horizontal flow is vertically invariant, it
can be shown that the shallow-water system is governed by the
Saint-Venant equations \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray}
(\p_t + \uu\cdot \bnabla ) \uu   
&=& - c^2 \bnabla h - f \eez \wedge \uu + \nu \bnabla^2 \uu,   \label{eq_uu}\\
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = H/H_0$ the normalized layer thickness, %
$\bnabla$ the horizontal gradient, %
$\nu$ the kinetic viscosity, %
$f$ the Coriolis parameter %
and %
$c = \sqrt{gH_0}$, with $g$ the gravitational acceleration.
%
In the following, the Coriolis parameter is assumed to be spatially
homogeneous.

\subsection{Eigenmodes of the linearized equations}

\label{subsection_eigen}

Neglecting the non-linear and the dissipative terms, the governing
equations can be rewritten as
\begin{equation}
\p_t q = 0, \mbox{\hspace{1cm}} 
\p_t d = a \mbox{\hspace{6mm} and \hspace{6mm}} 
\p_t a = - c^2\varkappa^2 d, 
\end{equation}
where $q = \zeta - f\eta$ is the linear Charney potential vorticity, %
$d = \bnabla \cdot \uu$ the horizontal divergence, %
$a = -c^2\bnabla^2 \eta + f\zeta$ an ageostrophic variable and %
$\varkappa^2 = {k_d}^2 - \bnabla^2$ the Helmholtz operator, %
with $k_d = f/c$ the deformation wave number. %
Here, $\eta = h-1$ is the normalized surface displacement and %
$\zeta = \eez \cdot (\bnabla \wedge \uu)$ is the vertical component of
the vorticity.
%
The dispersion relation is $\omega^2 = {\omega_l}^2$, where
\begin{equation}
 \omega_l(\kk) \equiv c  \sqrt{ {k_d}^2 + |\kk|^2 } = \sqrt{ f^2 + c^2|\kk|^2 },
\end{equation}
which implies that in the non-rotating case the waves are
non-dispersive.
%
The eigenfunctions of the linear operator are the prograde and
retrograde linear waves with positive and negative frequencies,
respectivelly.
%
Denoting the prograde quantities by the index $+$, the retrograde
quantities by the index $-$ and the temporal and spatial Fourier
transform by a tilde, we have by definition %
$a = a_+ + a_-$, $d = d_+ + d_-$, %
$\widetilde{\p_t a_\pm} = \mp i \omega_l \tilde a_\pm$ and %
$\widetilde{\p_t d_\pm} = \mp i \omega_l \tilde d_\pm$.
%
The linearized governing equations for the waves can be rewritten as %
$i \tilde a_\pm = \pm \omega_l \tilde d_\pm$, which gives %
$ \tilde a_\pm = \tilde a /2 \pm \omega_l \tilde d /(2i) .$

\subsection{Conserved quantities}

The non-dissipative one-layer shallow-water equations conserve a local
quantity along the trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta_a/h$, where $\zeta_a = \zeta +
f$ is the absolute vorticity.
%
Note that since the lagrangian derivative of the Ertel potential
vorticity is $\D_t \ErtelPV = 0$, the space-averaged Ertel potential
vorticity is not conserved $\p_t \meanx{\ErtelPV} = \meanx{d \ErtelPV}
\neq 0 $, where the brackets $\meanx{}$ denote the space average.
%
In the case of two-dimensional turbulence, it can be shown that the
energy can not cascade towards small scales due to the 
constraints that the enstrophy $\meanx{ \zeta^2/2 }$ is conserved and
that the spectra of energy and enstrophy are proportional
\cite[]{Kraichnan1967}.
%
This result was further extended by \cite{Charney1971} to the case of
quasi-geostrophic turbulence using the analogy between the
enstrophy and the Charney linear potential enstrophy $\meanx{ q^2/2
}$, where $q$ is the linear potential vorticity equal in the shallow
water case to $q = \zeta - f \eta$.
%
Note, however, that the analogy does not hold for the nonlinear Ertel
potential vorticity $\ErtelPV$ and that the local conservation of
$\ErtelPV$ is a much weaker constraint for the dynamics of the flows.

The non-dissipative one-layer shallow-water equations also conserve
some space-averaged quantities.
%
For example, since
\begin{equation}
(\D_t+d) \zeta_a = 0 \Rightarrow \p_t \meanx{\zeta_a} = 0 ,
\end{equation}
the space-averaged absolute vorticity $\meanx{\zeta_a }$ is conserved.
Since the governing equation for the thickness $h$ and the mass flux
$\JJ = h \uu$ are
\begin{eqnarray}
(\D_t+d) h 
&=& 0, \label{eq_h_2}\\
(\D_t+d) \JJ 
&=& - \bnabla E_P - f \eez \wedge \JJ, \label{eq_JJ}
\end{eqnarray}
where $E_P = c^2 h^2/2$ is the total potential energy, the
space-averaged thickness $\meanx{ h }$ is conserved and the kinetic
momentum $\meanx{ \JJ }$ is conserved in the absolute not-rotating
reference frame.
%
Note that in contrast to the case of the Navier-Stokes equations, 
the dissipative shallow-water equations do not conserve $\meanx{ \JJ }$,
even with a Newtonian viscous operator.

The non-dissipative one-layer shallow-water equations also conserve
the space-averaged total energy, the local energy being the sum of the
local potential energy (PE), $E_P = c^2 h^2/2$, and the local kinetic
energy (KE), $E_K = \JJ\cdot\uu/2$.  Using (\ref{eq_uu}),
(\ref{eq_h_2}) and (\ref{eq_JJ}), it is straightforward to show that
\begin{eqnarray}
(\D_t + d) E_K
&=&  
- \uu \cdot \bnabla E_P, \\
(\D_t + d) E_P
&=&  
- E_P \bnabla \cdot \uu.
\end{eqnarray}
%
The space-averaged conversion from potential energy to kinetic energy
is equal to $C = -\meanx{ \uu \cdot \bnabla E_P } = \meanx{ E_P
\bnabla \cdot \uu }$.
%
The total potential energy can be split in three parts
\begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2.
\end{equation}
The first term corresponds the potential energy of the state with null
surface displacement.  The second term is a contribution to the
potential energy which is zero in average.  We call the third term
$E_A = c^2\eta^2/2$ the available potential energy (APE).  Its
space-average is indeed equal to the space-averaged APE.

### 2016-12-17 old/section_methods.tex
First commit

\subsection{Numerics}

From a numerical point of view, it is convenient to solve for the
eigenmodes of the linear operator $\hat q$ and $\hat a_\pm = \hat a
/2 \pm \omega_l \hat d /(2i)$.
%
We thus consider the following modified governing equations
\begin{eqnarray}
\bigl( \p_t  + \fdiss(\kk) \bigl) \hat q  
&=& \hat N_q  ,\label{eqqnum} \\
\bigl( \p_t  + \fdiss(\kk) \pm  i \omega_l \bigl)  \hat a_\pm  
&=& \hat N_{\pm} + \hat f_{\pm}, \label{eqapmnum}
\end{eqnarray}
where $\hat f_{\pm}$ are forcing terms and %
$\hat N_q$ and %
$\hat N_\pm = \hat N_a /2 \pm \omega_l \hat N_d/(2i)$ %
are non-linear terms computed from %
$\hat \NN_\uu = - \zeta \eez \wedge \uu - \bnabla |\uu|^2/2$ and %
$\hat N_\eta = - \bnabla \cdot (\eta \uu)$.
%
We have removed the Newtonian viscous operator in (\ref{eq_uu}) and
added more general dissipative operators in (\ref{eq_uu}) and
(\ref{eq_h}).  There is no strong physical motivations for this
modification but, as discussed by \cite{FargeSadourny1989}, molecular
dissipation of the form $\nu \bnabla^2 \uu$ is not necessarily a
relevant model of the actual small-scale dissipation for shallow-water
flows, which should rather be described as a transition from
two-dimensional to three-dimensional motions before reaching the
scales where dissipation actually occurs.

Equations (\ref{eqqnum}-\ref{eqapmnum}) are simulated by means of a
pseudo-spectral method with periodic boundary conditions.
%
Time advancement is carried out by a classical fourth-order
Runge-Kutta scheme for the nonlinear term and an exact integration for
the linear and dissipative terms.  This explicit integration is
especially interesting at very high resolution and very large $c$ when
the shortest waves are very fast with frequency of the order of
$\omega \simeq c \max(k)$.
%
We use an adaptable time step method which maximizes the time step
over a standard Courant-Friedrichs-Lewy condition
\cite[]{Lundbladh1999, AugierChomazBillant2012}.
%
Most of the aliasing is removed by truncating 8/9 of the modes along
each direction \cite[for a detail discussion on the issues of the
non-conservation of the non-quadratic energy and the aliasing errors
in the truncated one-layer shallow water model,
see][]{FargeSadourny1989}.

\subsection{Forced dissipative statistically stationary simulations}

We have carried out a number of simulations 
with large-scale forcing and small-scale dissipation
for different resolutions and different values of the wave speed.
%
The resolution is characterized by the number of nodes in the each
direction, $n$, and has been varied from 240 to 7680.
%
The wave speed $c$ has been varied over two orders of magnitude from
10 to 1000.
%
Table~\ref{tab} presents the parameters for a set of representative
simulations.

\begin{table}
  \begin{center}
% \def~{\hphantom{0}}
\begin{tabular}{cc@{\hskip 8mm}c@{\hskip 8mm}cccc@{\hskip 8mm}cc}
$n$ & $c$ & $\nu_8$ & $\eps$ & $\displaystyle\frac{\kmax}{\kdiss}$ & $\displaystyle\frac{\kdiss}{k_f}$ & $F_f$ & $\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ \\[3mm]
~960 &   10 & 1.5e-10 & 1.03 & 2.46 &  29 &  0.111 & 0.25 & 0.96 \\
1920 &   10 & 9.6e-13 & 1.00 & 2.46 &  58 &  0.110 & 0.37 & 0.92 \\
3840 &   10 & 6.0e-15 & 1.01 & 2.46 & 116 &  0.110 & 0.39 & 1.01 \\
7680 &   10 & 3.7e-17 & 1.03 & 2.46 & 231 &  0.111 & 0.32 & 0.95 \\[1mm]
~960 &   20 & 1.5e-10 & 0.98 & 2.47 &  29 &  0.055 & 0.65 & 0.51 \\
1920 &   20 & 9.6e-13 & 0.84 & 2.48 &  57 &  0.052 & 0.66 & 0.81 \\
3840 &   20 & 6.0e-15 & 0.99 & 2.46 & 115 &  0.055 & 0.56 & 0.68 \\[1mm]
~960 &   40 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.027 & 0.81 & 0.24 \\
1920 &   40 & 9.6e-13 & 1.01 & 2.46 &  58 &  0.028 & 0.78 & 0.28 \\
3840 &   40 & 6.0e-15 & 0.98 & 2.47 & 115 &  0.027 & 0.77 & 0.29 \\
7680 &   40 & 3.7e-17 & 0.94 & 2.47 & 230 &  0.027 & 0.76 & 0.32 \\[1mm]
~960 &  100 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.011 & 0.89 & 0.09 \\
1920 &  100 & 9.6e-13 & 0.98 & 2.47 &  58 &  0.011 & 0.90 & 0.11 \\
3840 &  100 & 6.0e-15 & 0.97 & 2.47 & 115 &  0.011 & 0.87 & 0.13 \\[1mm]
~960 &  200 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.005 & 0.95 & 0.05 \\
1920 &  200 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.005 & 0.94 & 0.06 \\
3840 &  200 & 6.0e-15 & 0.90 & 2.47 & 115 &  0.005 & 0.94 & 0.06 \\[1mm]
~960 &  400 & 1.5e-10 & 0.97 & 2.47 &  29 &  0.003 & 0.97 & 0.03 \\
1920 &  400 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.003 & 0.96 & 0.03 \\[1mm]
~960 & 1000 & 1.5e-10 & 1.16 & 2.45 &  29 &  0.001 & 0.98 & 0.01 \\
1920 & 1000 & 9.6e-13 & 0.91 & 2.47 &  57 &  0.001 & 0.98 & 0.01 \\
\end{tabular}
\caption{Overview of parameters for a set of representative simulations. 
The number of nodes in the each direction is denoted by $n$. 
The size of the numerical domain is equal to $L_h = 50$.
Only the wave numbers $5\delta k\leqslant|\kk|\leqslant8\delta k$ are forced
and the forcing wave number is defined as 
$k_f \equiv 6 \delta k$ 
corresponding to a characteristic forcing scale of approximately 
$L_f \equiv \pi/k_f = 3.57$.
%
$F_f = \eps^{1/3}/({k_f}^{1/3}c)$ is the forcing Froude number and
$\max |\uu|/c$ is the spatial and temporal maximum of a local Froude
number.  }
\label{tab}
\end{center}
\end{table}

The ageostrophic variable $a$ is forced in a shell in spectral space
corresponding to relatively small wave numbers $5\delta k\leqslant
|\kk| \leqslant 8\delta k$, where $\delta k = 2\pi/L_h$.
%
\Add{In the following, we use $L_h = 50$ in order to obtain a
characteristic forcing wave number of order unity, $k_f \equiv 6
\delta k \simeq 0.75$. The corresponding forcing scale is $L_f \equiv
\pi/k_f \simeq 4.2$.}
%
Since only the ageostrophic variable is forced ($\hat f_d = 0$),%
(i) only the thickness fluctuation $\eta$ is forced in the
non-rotating case and %
(ii) the force terms in (\ref{eqapmnum}) are simply equal to $\hat
f_\pm = \hat f_a/2$.
%
In order to compute the force $\hat f_a$, we start from a
pre-normalized force $\hat f_{0}$ obtained from a normal random
process decorrelated in time.
%
The force is then normalized such that the quadratic part of the total
energy $\langle|\uu|^2 + c^2 \eta^2\rangle/2$ is injected at a
constant rate.
%
The spectral injection rate of the quadratic energy averaged over one
time step is (see appendix~\ref{app_comp})
\begin{equation}
P_q(\kk, t) 
= 
\Re\{ \hat \uu(\kk)^* \cdot \hat \ff(\kk) 
+
c^2 \hat \eta(\kk)^* \hat f_\eta(\kk) \}
+ 
(|\hat\ff|^2 + c^2 |\hat f_\eta|^2) \delta t /2,
\end{equation}
where $\Re$ denotes the real part.
%
Writing $\hat f_a = \alpha \hat f_{0}$, it is straightforward to solve
a second-order equation for the coefficient $\alpha$ in order to fix
the injection rate $\Add{P_0 \equiv} \sum_\kk P_q(\kk, t)$ to unity.

The energy is dissipated at the smallest resolved scales by a
hyper-viscous operator, corresponding to a dissipative frequency equal
to $\fdiss(\kk) = \nu_n |\kk|^n$, with $n = 8$.  The value of the
hyperviscosity $\nu_8$ is chosen such as the hyper-Kolmogorov wave
number
\begin{equation}
k_{Kn} = \left( \frac{{\nu_n}^3}{\eps} \right)^\frac{1}{3n-2},
\end{equation}
is well resolved, $\kdiss =k_{K8} \simeq \kmax/ 2.5$, where $\kmax =
(8/9)\pi n/L_h$ is the maximum resolved wave number.

We have observed that when only the waves are forced, the vorticity
does not increase and that when the vorticity is small enough, it does
not significantly influence the waves.  Therefore, we have chosen not
to simulate a negligible vorticity field and to only solve equations
(\ref{eqapmnum}) with $\zeta = 0$.

\begin{figure}
\centerline{\includegraphics[width=13cm]{../Figs/fig_Emean_time}}
\caption{Space averaged energy 
$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ versus time 
for different wave speeds $c$ and resolutions $n$.
%
The energy and the time are normalized by 
$E_f\equiv (P_0/k_f)^{2/3}$ and $T_f\equiv (P_0 {k_f}^2)^{-1/3}$,
with $P_0 = 1 \simeq \eps$.
%
The colors corresponds to different wave speeds as indicated in the figure
$c= 10$, 20, 40, 70, 100, 200, 400, 700 and 1000.
%
The different resolutions are represented by different types of lines:
\Add{thin continuous lines, $n = 240$;
thick dashed lines, $n = 480$;
thin dotted lines, $n = 960$;
thick continuous lines, $n = 1920$;
thin dashed lines, $n = 3840$;
thick dotted lines, $n = 5760$ 
and
thin dotted dashed lines, $n = 7680$.}
}
\label{fig_Evstime}
\end{figure}

The time evolution of the instantaneous total energy is shown in
figure~\ref{fig_Evstime} for different wave speeds $c$.
%
The resolution \Add{and the dissipation wave number are} progressively
increased: %
$n = 240$ ($0\leqslant t/T_f \leqslant 100$), %
$n = 480$ ($100\leqslant t/T_f \leqslant 125$), %
$n = 960$ ($125\leqslant t/T_f \leqslant 140$), %
$n = 1920$, %
$n = 3840$, %
$n = 5760$ and %
$n = 7680$\Add{, where $T_f\equiv
(P_0 {k_f}^2)^{-1/3}$ is the characteristic forcing time}.
%
Each time the resolution is increased, the energy first sharply
increases and then fluctuates.  For most of the simulations, it is
clear that a statistically stationary regime is reached.
%
However, 
%
\Remove{in the relatively short simulations at the highest
resolution for the largest wave speeds ($n = 1920$, $c = 700$ and
1000),}
%
\Add{for some relatively short simulations with very large wave speed
and/or very large resolution,}
%
there are large fluctuations and it is not absolutely certain whether
a statistically stationary regime is reached.
%
\Add{This is in particular the case for the simulations for $c = 700$, $n
= 1920$ (thick red continuous line), $c = 200$, $n = 3840$ (thin
magenta dashed line) and $c=40$, $n = 7680$ (thin blue dotted dashed
line).}
%
\Add{Note that these simulations are already quite numerically
costly. For example, the simulation for $c=1000$ and $n = 1920$
during slightly less than $20T_f$ corresponds to approximately
$8\times 10^5$ time steps.}

Since the energy is injected at large scales and dissipated only at
the smallest resolved scales, the existence of a statistically
stationary regime implies a downscale flux of energy, which is equal
to the large-scale energy injection rate.
%
For the same energy injection rate and resolution, the mean energy
increases with the wave speed, implying that when $c$ increases the
mean energy has to be larger to lead to the same downscale energy
flux.
%
The results presented in the following are from the statistically
stationary regime.  Apart from the snapshots, all shown quantities are
averaged over a period corresponding to this regime.

Table~\ref{tab} presents numerical and physical quantities for a set
of representative simulations.
%
We characterize the simulations by the forcing Froude number
\begin{equation}
F_f \Add{\equiv} \frac{\eps^{1/3}}{{k_f}^{1/3}c}.
\end{equation}
\Add{Since the characteristic forcing wave number and the dissipation
rate are approximately equal to $k_f \equiv 6 \delta k \simeq 0.75$
and $\eps \simeq P_0 = 1$, the forcing Froude number is approximately
inversely proportional to the wave speed: $F_f \simeq 1.1/c$. This
allows us to simply use the wave speed to denote the simulations.}
% where $k_f \equiv 6 \delta k = 0.75$ is a wave number characterizing
% the forcing.
%
The ratio $\kdiss/k_f$ gives an order of magnitude of the width of the
inertial range.  It is a physical quantity related to the numerical
resolution on which the flow can depend.
%
Table~\ref{tab} also displays the minimum thickness $\min(h)$
characterizing the importance of the non-quadraticity of the energy,
and $\max(|\uu|/c)$, which can be interpreted as the maximum of a
local Froude number.

### 2016-12-17 old/Python/baseSW1lw.py

@@ -1,0 +1,133 @@
+
+
+import numpy as np
+import commands
+import glob
+from solveq2d import solveq2d
+
+
+Lh = 50.
+deltak = 2*np.pi/Lh
+kf = 6*deltak
+Lf = 2*np.pi/kf/2
+
+
+P0 = 1.
+
+Tf = (P0*kf**2)**(-1./3)
+Ef = (P0/kf)**(2./3)
+
+
+out = commands.getstatusoutput('hostname')
+computer = out[1]
+
+
+if computer == 'pierre-KTH':
+    path_base_dir_results = '/storage1/Results_SW1lw'
+elif computer == 'pierre-voyage':
+    path_base_dir_results = '/home/pierre/Dropbox/Results_SW1lw'
+elif computer == 'pelvoux':
+    path_base_dir_results = '/scratch/augier/Results_SW1lw'
+else:
+    raise ValueError('Unknown computer...')
+
+
+
+def tminmaxstatio_from_sim(sim, VERBOSE=True):
+    """Return tmin, tmax and tstatio."""
+    tmin = sim.output.spatial_means.time_first_saved()
+    tmax = sim.output.spatial_means.time_last_saved()
+    Deltat = tmax - tmin
+    if Deltat > 29:
+        tstatio = tmin+18
+    elif Deltat > 10:
+        tstatio = tmin+5
+    else:
+        tstatio = tmax-2.5
+
+    # special cases:
+    if sim.param.dir_save_run.endswith('3840_c=20_f=0_2013-10-04_12-17-26'):
+        tstatio = tmin+18
+        # tstatio = tmin
+    elif sim.param.dir_save_run.endswith(
+        '1920_c=20_f=0_2013-10-03_14-13-34'):
+        tstatio = tmin
+
+    elif sim.param.dir_save_run.endswith(
+        '1920_c=1000_f=0_2013-10-15_15-40-29'):
+        tstatio = tmin
+
+    elif sim.param.dir_save_run.endswith(
+        '1920_c=700_f=0_2013-10-15_15-33-51'):
+        tstatio = tmin
+
+    elif sim.param.dir_save_run.endswith(
+        '1920_c=400_f=0_2013-10-17_08-58-25'):
+        tstatio = tmin
+
+
+
+
+    if VERBOSE:
+        print('tmin = {0:.2f}, tmax = {1:.2f}, tstatio = {2:.2f}'.format(
+                tmin,tmax,tstatio)
+              )
+
[…]

### 2016-12-17 old/Python/compute_f_rotation_runs.py

@@ -1,0 +1,25 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from __future__ import print_function
+
+import numpy as np
+
+import baseSW1lw
+
+
+Bu = np.array([0.5, 1., 2., 4.])
+print('Bu =', Bu)
+
+c = 20.
+
+kf = baseSW1lw.Kf
+
+
+f = c*kf/np.sqrt(Bu)
+
+print('f =', f)
+
+
+kd = f/c
+print('kd/kf =', kd/kf)

### 2016-12-17 old/Python/fig_2Dfields.py

@@ -1,0 +1,258 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from __future__ import print_function
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+
+SAVE_FIG = 0
+nh = 960*2
+c = 20
+# c = 200
+
+if SAVE_FIG:
+    nh = 960*2
+
+
+
+fontsize = 21
+create_fig = CreateFigArticles(
+    short_name_article='SW1l',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+dirs = set_of_dir.dirs_from_values(solver='SW1lwaves',
+                                   FORCING=True,
+                                   c2=c**2)
+
+path = set_of_dir.paths[0]
+
+sim = solveq2d.load_state_phys_file(t_approx=1000, name_dir=path)
+
+nx = sim.param.nx
+c2 = sim.param.c2
+c = np.sqrt(c2)
+f = sim.param.f
+name_solver = sim.output.name_solver
+
+Lf = baseSW1lw.Lf
+
+eta = sim.state.state_phys['eta']
+
+ux = sim.state.state_phys['ux']
+uy = sim.state.state_phys['uy']
+
+
+x_seq = sim.oper.x_seq
+y_seq = sim.oper.y_seq
+[XX_seq, YY_seq] = np.meshgrid(x_seq, y_seq)
+
+
+Lmax = 3.001*Lf
+nxLmax = np.sum(x_seq<=Lmax)
+nyLmax = np.sum(y_seq<=Lmax)
+
+x_seq = x_seq[x_seq<=Lmax]
+y_seq = y_seq[x_seq<=Lmax]
+
+
+
+cond = np.logical_and(XX_seq<Lmax, YY_seq<Lmax)
+XX_seq = XX_seq[cond].reshape([nyLmax, nxLmax])
+YY_seq = YY_seq[cond].reshape([nyLmax, nxLmax])
+eta = eta[cond].reshape([nyLmax, nxLmax])
+ux = ux[cond].reshape([nyLmax, nxLmax])
[…]

### 2016-12-17 old/Python/fig_Emean_c.py

@@ -1,0 +1,221 @@
+#!/usr/bin/env python
+#coding=utf8
+
+
+from createfigs import CreateFigs
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import scipy.optimize as optimize
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+
+
+
+SAVE_FIG = 1
+name_file = 'fig_Emean_c'
+fontsize=21
+
+create_fig = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+
+Lf = baseSW1lw.Lf
+kf = baseSW1lw.kf
+
+
+
+def load_from_c(set_of_dir, c):
+
+    set_of_dir_c = set_of_dir.filter(c=c, f=0)
+    path = set_of_dir_c.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    (dico_time_means, dico_results
+     ) = sim.output.spatial_means.compute_time_means(tstatio)
+    c2 = sim.param['c2']
+    c = np.sqrt(c2)
+    EK = dico_time_means['EK']
+    Fr = np.sqrt(2*EK/c2)
+    EA = dico_time_means['EA']
+    EKr = dico_time_means['EKr']
+    EKd = EK - EKr
+    E = EK + EA
+    epsK = dico_time_means['epsK']
+    epsA = dico_time_means['epsA']
+    eps = epsK + epsA
+    epsK_tot = dico_time_means['epsK_tot']
+    epsA_tot = dico_time_means['epsA_tot']
+    print 'c = {0:8.1f}, Fr = {1:8.3f}, eps = {2:8.2f}'.format(
+        c, Fr, eps)
+    return locals()
+
+
+
+
+
+
+
+# fig2, ax2 = create_fig.figure_axe(name_file=name_file+'_ratio')
+fig, ax1 = create_fig.figure_axe(name_file=name_file,
+                                 fig_width_mm=200, fig_height_mm=155,
+                                 # size_axe=[0.12, 0.126, 0.83, 0.822]
[…]

### 2016-12-17 old/Python/fig_Emean_f.py

@@ -1,0 +1,181 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from create_figs_articles import CreateFigArticles
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import scipy.optimize as optimize
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+
+
+
+SAVE_FIG = 0
+name_file = 'fig_Emean_f'
+fontsize=21
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+Lf = baseSW1lw.Lf
+kf = baseSW1lw.kf
+
+
+
+def load_from_f(set_of_dir, f):
+
+    set_of_dir_f = set_of_dir.filter(f=f)
+    path = set_of_dir_f.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    (dico_time_means, dico_results
+     ) = sim.output.spatial_means.compute_time_means(tstatio)
+    c2 = sim.param['c2']
+    c = np.sqrt(c2)
+    f = sim.param['f']
+    kd = f/c
+    EK = dico_time_means['EK']
+    Fr = np.sqrt(2*EK/c2)
+    EA = dico_time_means['EA']
+    EKr = dico_time_means['EKr']
+    EKd = EK - EKr
+    E = EK + EA
+    epsK = dico_time_means['epsK']
+    epsA = dico_time_means['epsA']
+    eps = epsK + epsA
+    epsK_tot = dico_time_means['epsK_tot']
+    epsA_tot = dico_time_means['epsA_tot']
+    print 'c = {0:8.1f}, Fr = {1:8.3f}, eps = {2:8.2f}'.format(
+        c, Fr, eps)
+    return locals()
+
+
+
+
+
+fig, ax1 = create_fig.figure_axe(name_file=name_file,
+                                 fig_width_mm=200, fig_height_mm=155,
+                                 size_axe=[0.132, 0.125, 0.85, 0.845]
+                                 )
+
+# fig, ax1 = create_fig.figure_axe(name_file=name_file,
[…]

### 2016-12-17 old/Python/fig_Emean_f_c.py

@@ -1,0 +1,241 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from create_figs_articles import CreateFigArticles
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+import scipy.optimize as optimize
+
+from solveq2d import solveq2d
+
+
+
+
+num_fig = 1000
+SAVE_FIG = 1
+name_file = 'fig_time_mean_forcingw_f_c.eps'
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=19
+    )
+
+
+
+
+def load_from_namedir(set_of_dir, name_dir_results, tstatio):
+    path_dir_results = set_of_dir.path_dirs[name_dir_results]
+    sim = solveq2d.create_sim_plot_from_dir(path_dir_results)
+    (dico_time_means, dico_results
+     ) = sim.output.spatial_means.compute_time_means(tstatio)
+    c2 = sim.param['c2']
+    EK = dico_time_means['EK']
+    Fr = np.sqrt(2*EK/c2)
+    EA = dico_time_means['EA']
+    EKr = dico_time_means['EKr']
+    EKd = EK - EKr
+    E = EK + EA
+    epsK = dico_time_means['epsK']
+    epsA = dico_time_means['epsA']
+    eps = epsK + epsA
+    epsK_tot = dico_time_means['epsK_tot']
+    epsA_tot = dico_time_means['epsA_tot']
+    c = np.sqrt(set_of_dir.dico_c2[name_dir_results])
+    print 'c = {0:8.1f}, Fr = {1:8.3f}, eps = {2:8.2f}'.format(
+        c, Fr, eps)
+    return locals()
+
+
+
+
+
+fig, ax1 = create_fig.figure_axe(name_file=name_file)
+# ax1.set_xscale('log')
+# ax1.set_yscale('log')
+
+ax1.set_xlabel(r'$c$')
+ax1.set_ylabel(r'$E$')
+
+
+
+
+
+def plot_one_dir_base(dir_base, tstatio=40):
+
+    set_of_dir_results = solveq2d.SetOfDirResults(dir_base=dir_base)
+    dirs = set_of_dir_results.dirs_from_values(solver='SW1lwaves',
[…]

### 2016-12-17 old/Python/fig_Emean_resol.py

@@ -1,0 +1,192 @@
+#!/usr/bin/env python
+#coding=utf8
+
+
+from createfigs import CreateFigs
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import scipy.optimize as optimize
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+
+
+
+SAVE_FIG = 1
+name_file = 'fig_Emean_resol'
+fontsize=21
+
+create_fig = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+Lf = baseSW1lw.Lf
+kf = baseSW1lw.kf
+
+
+
+
+def load_from_nh(set_of_dir, nh):
+
+    set_of_dir_nh = set_of_dir.filter(nh=nh, f=0)
+    path = set_of_dir_nh.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    (dico_time_means, dico_results
+     ) = sim.output.spatial_means.compute_time_means(tstatio)
+    c2 = sim.param['c2']
+    c = np.sqrt(c2)
+    EK = dico_time_means['EK']
+    Fr = np.sqrt(2*EK/c2)
+    EA = dico_time_means['EA']
+    EKr = dico_time_means['EKr']
+    EKd = EK - EKr
+    E = EK + EA
+    epsK = dico_time_means['epsK']
+    epsA = dico_time_means['epsA']
+    eps = epsK + epsA
+    epsK_tot = dico_time_means['epsK_tot']
+    epsA_tot = dico_time_means['epsA_tot']
+
+    Enorm = np.sqrt(eps*Lf*c)
+
+    print 'c = {0:8.1f}, Fr = {1:8.3f}, eps = {2:8.2f}'.format(
+        c, Fr, eps)
+    return locals()
+
+
+
+
+
+fig, ax1 = create_fig.figure_axe(name_file=name_file,
+                                 fig_width_mm=200, fig_height_mm=155,
+                                 size_axe=[0.134, 0.126, 0.834, 0.822]
+                                 )
+
+# ax1.set_xscale('log')
[…]

### 2016-12-17 old/Python/fig_Emean_time.py

@@ -1,0 +1,189 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from createfigs import CreateFigs
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import scipy.optimize as optimize
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from baseSW1lw import Tf, Ef
+
+
+SAVE_FIG = 1
+name_file = 'fig_Emean_time'
+
+fontsize = 15
+
+
+create_figs = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+
+
+
+def load_from_path(path):
+    sim = solveq2d.create_sim_plot_from_dir(path)
+    dico = sim.output.spatial_means.load()
+    c = np.sqrt(sim.param.c2)
+    return dico, c
+
+
+
+colors = {10 : 'k', 
+          20:'r', 
+          40:'b',
+          70:'y',
+          100:'g', 
+          200:'m', 
+          400:'c',
+          700:'r',
+          1000:'k'
+    }
+
+size_axe = [0.08, 0.13, 0.21, 0.84]
+fig, ax1 = create_figs.figure_axe(name_file=name_file,
+                                 fig_width_mm=220, fig_height_mm=120,
+                                 size_axe=size_axe, 
+                                 )
+ax1.set_xlabel(r'$t/T_f$')
+ax1.set_ylabel(r'$E/E_f$')
+
+size_axe = [0.35, 0.13, 0.62, 0.84]
+
+
+ax2 = fig.add_axes(size_axe)
+ax2.set_xlabel(r'$t/T_f$')
+
+
+dir_base  = baseSW1lw.path_base_dir_results
+
+tn = Tf
+En = Ef
+
+def plot_one_resol(resol, style_lines='-', linewidth=1):
+    str_resol = repr(resol)
+    str_to_find_path = (
+        dir_base+'/Pure_standing_waves_'+
+        str_resol+'*'
+        )
+
+    # print str_to_find_path
+    paths_dir = glob.glob(str_to_find_path)
+    # print paths_dir
+    path_base = paths_dir[0]
+
+
+    set_of_dir = solveq2d.SetOfDirResults(path_base)
+
[…]

### 2016-12-17 old/Python/fig_Emean_time_f.py

@@ -1,0 +1,130 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from create_figs_articles import CreateFigArticles
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import scipy.optimize as optimize
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+
+
+
+SAVE_FIG = 0
+name_file = 'fig_Emean_time_f'
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=19
+    )
+
+
+
+
+def load_from_namedir(set_of_dir, name_dir_results):
+    path_dir_results = set_of_dir.path_dirs[name_dir_results]
+    sim = solveq2d.create_sim_plot_from_dir(path_dir_results)
+    dico = sim.output.spatial_means.load()
+    c = np.sqrt(sim.param.c2)
+    return dico, c
+
+
+
+colors = {10 : 'k', 
+          20:'r', 
+          40:'b',
+          70:'y',
+          100:'g', 
+          200:'m', 
+          400:'c',
+          700:'r',
+          1000:'k'
+    }
+
+size_axe = [0.13, 0.12, 0.845, 0.85]
+fig, ax1 = create_fig.figure_axe(name_file=name_file,
+                                 fig_width_mm=200, fig_height_mm=130,
+                                 size_axe=size_axe, 
+                                 )
+ax1.set_xlabel(r'$t$')
+ax1.set_ylabel(r'$E$')
+
+
+
+dir_base  = baseSW1lw.path_base_dir_results
+
+def plot_one_resol(resol, style_lines='-', linewidth=1):
+    str_resol = repr(resol)
+    str_to_find_path = (
+        dir_base+'/Pure_standing_waves_'+
+        str_resol+'*'
+        )
+
+    # print str_to_find_path
+    paths_dir = glob.glob(str_to_find_path)
+    # print paths_dir
+    path_base = paths_dir[0]
+
+
+    set_of_dir_results = solveq2d.SetOfDirResults(dir_base=path_base)
+    paths = set_of_dir_results.dirs_from_values(solver='SW1lwaves',
+                                                FORCING=True, 
+                                                c2=20**2)
+
[…]

### 2016-12-17 old/Python/fig_Kolmo.py

@@ -1,0 +1,194 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from __future__ import print_function
+
+import h5py
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+num_fig = 1000
+SAVE_FIG = 1
+
+c = 20
+nh = 240*2**3
+nh = 240*2**4
+
+name_file = (
+'fig_Kolmo_c={0}_N={1}'.format(c, nh)
+)
+
+def cumsum_inv(a):
+    return a[::-1].cumsum()[::-1]
+
+
+fontsize = 19
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+# tstatio = tmin + 3.5
+
+# if resol == 1920:
+#     tstatio = tmin
+# elif resol == 3840:
+#     pass
+
+
+c = np.sqrt(sim.param['c2'])
+
+dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+epsK = dico1['epsK']
+epsA = dico1['epsA']
+epsKsuppl = dico1['epsKsuppl']
+eps = epsK + epsA
+eps_small_scales = eps-epsKsuppl
+
+"""
+Interestingly, there is a "large-scale" dissipation ~1%
+due to the fact that the kinetic energy is not quadratic.
+"""
+
+print('eps = {0:.2f}, eps_small_scales = {1:.2f}'.format(eps, eps_small_scales))
+
+# epsn = eps_small_scales
+epsn = eps
+
+
+
[…]

### 2016-12-17 old/Python/fig_base_nothing.py

@@ -1,0 +1,148 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+num_fig = 1000
+SAVE_FIG = 0
+
+c = 40
+resol = 240*2**5
+
+name_file = (
+'fig_nothin_c={0}_nh={1}'.format(c, resol)
+
+)
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=19
+    )
+
+dir_base  = create_fig.path_base_dir+'/Results_SW1lw'
+
+
+
+str_resol = repr(resol)
+str_to_find_path = (
+    dir_base+'/Pure_standing_waves_'+
+    str_resol+'*/SE2D*c='+repr(c))+'_*'
+print str_to_find_path
+
+paths_dir = glob.glob(str_to_find_path)
+
+print paths_dir
+
+
+sim = solveq2d.create_sim_plot_from_dir(paths_dir[0])
+
+tmin = sim.output.spatial_means.first_saved_time()
+tstatio = tmin + 4.
+
+
+
+
+dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+
+kh = dico_results['kh']
+
+EK = (dico_results['spectrum1Dkx_EK'] + 
+      dico_results['spectrum1Dkx_EK'])/2
+EA = (dico_results['spectrum1Dkx_EA'] + 
+      dico_results['spectrum1Dkx_EA'])/2
+EKr = (dico_results['spectrum1Dkx_EKr'] + 
+       dico_results['spectrum1Dkx_EKr'])/2
+
+E_tot = EK + EA
+EKd = EK - EKr
+
+
+
+dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+epsK = dico1['epsK']
+epsA = dico1['epsA']
+eps = epsK + epsA
+# EK =  dico1['EK']
+U = np.sqrt(2*EK)
+c = np.sqrt(sim.param['c2'])
+
+
+
+
+
+
[…]

### 2016-12-17 old/Python/fig_flatness_atm.py

@@ -1,0 +1,115 @@
+
+
+
+from __future__ import print_function
+
+import os
+import sys
+import glob
+import numpy as np
+
+import matplotlib.pylab as plt
+
+
+import baseSW1lw
+
+# small trick in order to import the module lindborg1999.py
+path_here = os.getcwd()
+path_mod_lindborg1999 = os.path.split(path_here)[0]+'/Flatness_atm'
+sys.path.append(path_mod_lindborg1999)
+from lindborg1999 import r, FL, FT
+
+flatnessT = FT
+flatnessL = FL
+
+from create_figs_articles import CreateFigArticles
+SAVE_FIG = 1
+
+
+
+
+
+
+fontsize = 21
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+
+
+fig, ax1 = create_fig.figure_axe(
+    name_file='fig_flatness_atm',
+    fig_width_mm=200, fig_height_mm=155,
+    size_axe=[0.13, 0.127, 0.84, 0.835]
+    )
+
+ax1.set_xscale('log')
+ax1.set_yscale('log')
+
+ax1.set_xlabel('$r$ (km)')
+ax1.set_ylabel('$F_T$, $F_L$')
+
+l_FT = ax1.plot(r, flatnessT, 'k', linewidth=2)
+l_FL = ax1.plot(r, flatnessL, 'y', linewidth=2)
+
+
+plt.rc('legend', numpoints=1)
+leg1 = plt.figlegend(
+    [l_FT[0], l_FL[0]], 
+    ['$F_T$', '$F_L$'], 
+    loc=(0.2, 0.2), 
+    labelspacing = 0.18
+    )
+
+cond = np.logical_and(r > 3 , r < 2e2)
+ax1.plot(r[cond], 6e2*r[cond]**(-1), 
+                 'k', linewidth=1)
+ax1.text(1e1, 1.8e1,'$r^{-1}$',fontsize=fontsize)
+
+cond = np.logical_and(r > 3 , r < 1e2)
+ax1.plot(r[cond], 4e4*r[cond]**(-3./2), 
+                 'k--', linewidth=1)
[…]

### 2016-12-17 old/Python/fig_interm.py

@@ -1,0 +1,308 @@
+
+
+import matplotlib.pylab as plt
+import glob
+import numpy as np
+
+import baseSW1lw
+from baseSW1lw import Lf
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+name_file = 'fig_interm'
+
+SAVE_FIG = 1
+
+
+
+
+fontsize = 21
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+
+c = 10 
+c = 40
+nh = 240*2**5
+
+# c = 200
+# nh = 240*2**4
+
+key_var = 'uy' # for transverse since r = delta x
+# key_var = 'ux' # for longitudinal since r = delta x
+
+
+
+
+
+
+
+
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+
+
+
+
+(pdf_timemean, values_inc_timemean, nb_rx_to_plot
+ ) = sim.output.increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var=key_var)
+
+
+deltax = sim.param.Lx/sim.param.nx
+rxs = np.array(sim.output.increments.rxs, dtype=np.float64)*deltax
+
+if nh == 7680:
+    rmin = 8*deltax
+    rmax = 40*deltax
+
+elif nh == 3840:
+    rmin = 6*deltax
+    rmax = 20*deltax
+
+
+print('rmin = {0} ; rmax = {1}'.format(rmin, rmax))
+
+print('rmin/Lf = {0} ; rmax/Lf = {1}'.format(rmin/Lf, rmax/Lf))
+
+# if 4096
+# rmin = 8e-2
+# rmin = 8*deltax
+# rmax = 5e-1
+# rmax = 50*deltax
+
+# if 2048
+# rmin = 1.5e-1
+# rmin = 5*deltax
+# rmax = 20*deltax
+# rmax = 3e-1
+
[…]

### 2016-12-17 old/Python/fig_ratio_strfct.py

@@ -1,0 +1,425 @@
+
+from __future__ import print_function
+
+import h5py
+
+import matplotlib.pylab as plt
+import glob
+import numpy as np
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from createfigs import CreateFigs
+
+
+SAVE_FIG = 1
+
+
+fontsize = 21
+
+create_figs = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+dir_base  = create_figs.path_base_dir+'/Results_SW1lw'
+
+c = 10
+nh = 240*2**5
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+print(paths)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+
+increments = sim.output.increments
+
+
+pdf_ux, values_inc_ux, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='ux')
+
+pdf_uy, values_inc_uy, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='uy')
+
+pdf_eta, values_inc_eta, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='eta')
+
+
+S2_uL = increments.strfunc_from_pdf(pdf_ux, abs(values_inc_ux), 2)
+S3_uL = increments.strfunc_from_pdf(pdf_ux, abs(values_inc_ux), 3)
+S4_uL = increments.strfunc_from_pdf(pdf_ux, abs(values_inc_ux), 4)
+S5_uL = increments.strfunc_from_pdf(pdf_ux, abs(values_inc_ux), 5)
+
[…]

### 2016-12-17 old/Python/fig_spatiotempspectra.py

@@ -1,0 +1,151 @@
+#!/usr/bin/env python
+#coding=utf8
+
+from __future__ import print_function
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from createfigs import CreateFigs
+
+num_fig = 1000
+SAVE_FIG = 1
+
+c = 20
+resol = 240*2**4
+
+name_file = (
+'fig_spatiotempspectra_c={0}_Nh={1}'.format(c, resol)
+)
+
+fontsize=21
+create_fig = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+dir_base  = baseSW1lw.path_base_dir_results
+
+
+
+str_resol = repr(resol)
+str_to_find_path = (
+    dir_base+'/Pure_standing_waves_'+
+    str_resol+'*/SE2D*c='+repr(c))+'_*'
+print(str_to_find_path)
+
+paths = glob.glob(str_to_find_path)
+
+print(paths)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+
+
+
+
+
+
+
+
+
+dico_spectra, dico_results = sim.output.time_sigK.compute_spectra()
+
+omega = dico_spectra['omega']
+time_spectra_q = dico_spectra['time_spectra_q']
+time_spectra_a = dico_spectra['time_spectra_a']
+time_spectra_d = dico_spectra['time_spectra_d']
+omega_shell = dico_results['omega_shell']
+kh_shell = dico_results['kh_shell']
+
+
+
+deltak = baseSW1lw.deltak
+
+print('deltak/k = ', deltak/kh_shell)
+
+
+print('k/deltak = ', kh_shell/deltak)
+
+
+
+
+
+
+c = np.sqrt(sim.param['c2'])
+
+# dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+# epsK = dico1['epsK']
+# epsA = dico1['epsA']
[…]

### 2016-12-17 old/Python/fig_spect_energy_budg.py

@@ -1,0 +1,222 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import h5py
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+num_fig = 1000
+SAVE_FIG = 1
+
+c = 100
+nh = 240*2**3
+nh = 240*2**4
+
+name_file = (
+'fig_spect_energy_budg_c={0}_N={1}'.format(c, nh)
+)
+
+def cumsum_inv(a):
+    return a[::-1].cumsum()[::-1]
+
+
+fontsize = 19
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+c = np.sqrt(sim.param['c2'])
+
+dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+epsK = dico1['epsK']
+epsA = dico1['epsA']
+epsKsuppl = dico1['epsKsuppl']
+eps = epsK + epsA
+eps_small_scales = eps-epsKsuppl
+
+# epsn = eps_small_scales
+epsn = eps
+
+"""
+Interestingly, there is a "large-scale" dissipation ~1%
+due to the fact that the kinetic energy is not quadratic.
+Therefore, the flux decreases slightly at large scale (~1%).
+"""
+
+
+path_file = sim.output.spect_energy_budg.path_file
+
+f = h5py.File(path_file,'r')
+
+dset_times = f['times']
+times = dset_times[...]
+nt = len(times)
+
+dset_khE = f['khE']
+kh = dset_khE[...]
+
[…]

### 2016-12-17 old/Python/fig_spectra_c.py

@@ -1,0 +1,316 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+num_fig = 1000
+SAVE_FIG = 1
+
+nh = 240*2**3
+# nh = 240*2**4
+
+name_file = 'fig_spectra_c_Nx={0}'.format(nh)
+
+fontsize = 21
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+kf = baseSW1lw.kf
+
+paths = baseSW1lw.paths_from_nh(nh)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+set_of_dir = set_of_dir.filter(solver='SW1lwaves',
+                               FORCING=True, 
+                               f=0)
+
+
+def sprectra_from_c(c):
+
+    set_of_dir_c = set_of_dir.filter(c=c)
+    path = set_of_dir_c.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+    kh = dico_results['kh']
+
+    spectEK = (dico_results['spectrum1Dkx_EK'] + 
+          dico_results['spectrum1Dkx_EK'])/2
+    spectEA = (dico_results['spectrum1Dkx_EA'] + 
+          dico_results['spectrum1Dkx_EA'])/2
+    spectEKr = (dico_results['spectrum1Dkx_EKr'] + 
+           dico_results['spectrum1Dkx_EKr'])/2
+
+    spectEKd = spectEK - spectEKr
+    spectE = spectEK + spectEA
+    dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+    epsK = dico1['epsK']
+    epsA = dico1['epsA']
+    eps = epsK + epsA
[…]

### 2016-12-17 old/Python/fig_spectra_c=40_nh=7680.py

@@ -1,0 +1,156 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+SAVE_FIG = 1
+
+c = 40
+nh = 240*2**5
+
+name_file = (
+'fig_spectra_c={0}_nh={1}'.format(c, nh)
+)
+
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=19
+    )
+
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c, f=0)
+
+
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+path = set_of_dir.path_larger_t_start()
+
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+
+
+
+
+dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+
+kh = dico_results['kh']
+
+EK = (dico_results['spectrum1Dkx_EK'] + 
+      dico_results['spectrum1Dkx_EK'])/2
+EA = (dico_results['spectrum1Dkx_EA'] + 
+      dico_results['spectrum1Dkx_EA'])/2
+EKr = (dico_results['spectrum1Dkx_EKr'] + 
+       dico_results['spectrum1Dkx_EKr'])/2
+
+E_tot = EK + EA
+EKd = EK - EKr
+
+
+
+c = np.sqrt(sim.param['c2'])
+
+dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+epsK = dico1['epsK']
+epsA = dico1['epsA']
+epsKsuppl = dico1['epsKsuppl']
+eps = epsK + epsA
+eps_small_scales = eps-epsKsuppl
+
+# epsn = eps_small_scales
+epsn = eps
+
+
+
+fig, ax1 = create_fig.figure_axe(name_file=name_file,
[…]

### 2016-12-17 old/Python/fig_spectra_f.py

@@ -1,0 +1,319 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from createfigs import CreateFigs
+
+
+num_fig = 1000
+SAVE_FIG = 1
+
+nh = 240*2**3
+c = 20
+
+name_file = 'fig_spectra_f_Nx={0}'.format(nh)
+
+fontsize = 21
+create_figs = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+kf = baseSW1lw.kf
+
+paths = baseSW1lw.paths_from_nh_c_f(nh, c)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+set_of_dir = set_of_dir.filter(solver='SW1lwaves',
+                               FORCING=True,
+                               c2=c**2)
+
+
+def sprectra_from_f(f):
+
+    set_of_dir_c = set_of_dir.filter(f=f)
+    path = set_of_dir_c.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+    kh = dico_results['kh']
+
+    spectEK = (dico_results['spectrum1Dkx_EK'] + 
+          dico_results['spectrum1Dkx_EK'])/2
+    spectEA = (dico_results['spectrum1Dkx_EA'] + 
+          dico_results['spectrum1Dkx_EA'])/2
+    spectEKr = (dico_results['spectrum1Dkx_EKr'] + 
+           dico_results['spectrum1Dkx_EKr'])/2
+
+    spectEK[spectEK<1e-16] = 0.
+    spectEA[spectEA<1e-16] = 0.
+    spectEKr[spectEKr<1e-16] = 0.
+
+
+    spectEKd = spectEK - spectEKr
+    spectE = spectEK + spectEA
+    dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
[…]

### 2016-12-17 old/Python/fig_spectra_resol.py

@@ -1,0 +1,188 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+SAVE_FIG = 0
+c = 10
+# c = 40
+
+
+name_file = 'fig_spectra_resol_c={0}'.format(c)
+
+fontsize = 21
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+kf = baseSW1lw.kf
+
+
+paths_c = baseSW1lw.paths_from_c(c)
+
+set_of_dir = solveq2d.SetOfDirResults(paths_c)
+
+set_of_dir = set_of_dir.filter(solver='SW1lwaves',
+                               FORCING=True,
+                               f=0)
+
+
+
+
+
+def spectra_from_namedir(nh):
+
+    set_of_dir_nh = set_of_dir.filter(nh=nh)
+
+    path = set_of_dir_nh.path_larger_t_start()
+    sim = solveq2d.create_sim_plot_from_dir(path)
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+    kh = dico_results['kh']
+
+    spectEK = (dico_results['spectrum1Dkx_EK'] + 
+          dico_results['spectrum1Dkx_EK'])/2
+    spectEA = (dico_results['spectrum1Dkx_EA'] + 
+          dico_results['spectrum1Dkx_EA'])/2
+    spectEKr = (dico_results['spectrum1Dkx_EKr'] + 
+           dico_results['spectrum1Dkx_EKr'])/2
+
+    spectEKd = spectEK - spectEKr
+    spectE = spectEK + spectEA
+    dico1, dico2 = sim.output.spatial_means.compute_time_means(tstatio=tstatio)
+    epsK = dico1['epsK']
+    epsA = dico1['epsA']
+    eps = epsK + epsA
+    EK =  dico1['EK']
+    U = np.sqrt(2*EK)
[…]

### 2016-12-17 old/Python/fig_spectra_visco.py

@@ -1,0 +1,318 @@
+#!/usr/bin/env python
+#coding=utf8
+
+import numpy as np
+import matplotlib.pyplot as plt
+import glob
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from createfigs import CreateFigs
+
+
+num_fig = 1000
+SAVE_FIG = 1
+
+nh = 240*2**3*3
+name_file = 'fig_spectra_visco_Nx={0}'.format(nh)
+
+fontsize = 21
+create_figs = CreateFigs(
+    path_relative='../Figs',
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+kf = baseSW1lw.kf
+
+
+paths = baseSW1lw.paths_from_nh(nh)
+
+set_of_dir = solveq2d.SetOfDirResults(paths)
+set_of_dir = set_of_dir.filter(solver='SW1lwaves',
+                               FORCING=True, 
+                               f=0, c=20)
+
+# nh = 240*2**2
+# paths = baseSW1lw.paths_from_nh(nh)
+
+# set_of_dir2 = solveq2d.SetOfDirResults(paths)
+# set_of_dir2 = set_of_dir2.filter(solver='SW1lwaves',
+#                                  FORCING=True, 
+#                                  f=0, c=20)
+
+
+
+
+
+def sprectra_from_path(path):
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+
+    tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+    dico_results = sim.output.spectra.load1D_mean(tmin=tstatio)
+    kh = dico_results['kh']
+
+    spectEK = (dico_results['spectrum1Dkx_EK'] + 
+               dico_results['spectrum1Dkx_EK'])/2
+    spectEA = (dico_results['spectrum1Dkx_EA'] + 
+               dico_results['spectrum1Dkx_EA'])/2
+    spectEKr = (dico_results['spectrum1Dkx_EKr'] + 
+                dico_results['spectrum1Dkx_EKr'])/2
+
+    spectEKd = spectEK - spectEKr
+    spectE = spectEK + spectEA
[…]

### 2016-12-17 old/Python/fig_strfct.py

@@ -1,0 +1,340 @@
+
+from __future__ import print_function
+
+import h5py
+
+import matplotlib.pylab as plt
+import glob
+import numpy as np
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+from create_figs_articles import CreateFigArticles
+
+
+SAVE_FIG = 0
+
+
+
+
+
+fontsize = 19
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+dir_base  = create_fig.path_base_dir+'/Results_SW1lw'
+
+c = 40
+resol = 240*2**5
+
+key_var = 'uy' # for transverse since r = delta x
+# key_var = 'ux' # for longitudinal since r = delta x
+
+
+str_resol = repr(resol)
+str_to_find_path = (
+    dir_base+'/Pure_standing_waves_'+
+    str_resol+'*/SE2D*c='+repr(c))+'_*'
+# print str_to_find_path
+
+paths = glob.glob(str_to_find_path)
+print(paths)
+
+set_of_dir = solveq2d.SetOfDirResults(path_dirs_results=paths)
+path = set_of_dir.path_larger_t_start()
+
+sim = solveq2d.create_sim_plot_from_dir(path)
+
+tmin, tmax, tstatio = baseSW1lw.tminmaxstatio_from_sim(sim, VERBOSE=True)
+
+
+increments = sim.output.increments
+
+
+pdf_ux, values_inc_ux, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='ux')
+
+pdf_uy, values_inc_uy, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='uy')
+
+pdf_eta, values_inc_eta, nb_rx_to_plot = increments.load_pdf_from_file(
+    tmin=tmin, tmax=tmax, key_var='eta')
+
+
[…]

### 2016-12-17 old/Python/scaling_epsilon_c.py

@@ -1,0 +1,55 @@
+
+from __future__ import print_function
+
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+from create_figs_articles import CreateFigArticles
+SAVE_FIG = 0
+
+
+
+c = np.array([10, 20, 40, 70, 100, 200])
+eps = np.array([1, 0.94, 0.93, 0.89, 0.76, 0.8])
+# eps = np.array([1, 0.94, 0.93, 0.89, 0.85, 0.8])
+
+c = np.array([10, 20, 20, 40, 70, 100, 200, 400, 700, 1000])
+eps = np.array([1, 0.99, 0.97, 0.93, 0.9, 0.89, 0.88, 0.85, 0.79, 0.79])
+
+
+
+
+
+
+fontsize=20
+create_fig = CreateFigArticles(
+    short_name_article='SW1l', 
+    SAVE_FIG=SAVE_FIG, 
+    FOR_BEAMER=False, 
+    fontsize=fontsize
+    )
+
+
+fig, ax1 = create_fig.figure_axe(name_file='fig_eps_c')
+ax1.set_xlabel(r'$c$')
+ax1.set_ylabel(r'$\varepsilon$')
+
+coef = 0.0
+
+ax1.plot(c, eps*c**coef, 'k', linewidth=2)
+
+
+# ax1.set_xscale('log')
+# ax1.set_yscale('log')
+
+# ax1.set_xlim([kmin, kmax])
+# ax1.set_ylim([8e-3, 3e0])
+
+
+# create_fig.save_fig()
+
+
+create_fig.show()
+

### 2016-12-17 old/Python/table.py

@@ -1,0 +1,239 @@
+
+
+from __future__ import print_function
+
+import os
+import glob
+import numpy as np
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+nb_mm_between_c = 1
+
+dir_base  = baseSW1lw.path_base_dir_results
+paths_from_nh_c_f = baseSW1lw.paths_from_nh_c_f
+
+kf = baseSW1lw.kf
+Lf = baseSW1lw.Lf
+print('kf = {0:.2f};    Lf =  {1:.2f}'.format(kf, Lf))
+
+path_here = os.getcwd()
+path_file = 'table_try'
+ii=0
+while os.path.exists(
+    path_here+'/Table_files/'+path_file+'{0}.txt'.format(ii)):
+    ii+=1
+path_file = path_here+'/Table_files/'+path_file+'{0}.txt'.format(ii)
+ftable = open(path_file, 'w')
+
+ftable.write(
+r'$n$ & $c$ & '
+r'$\nu_8$ & '
+r'$\eps$ & '
+r'$\displaystyle\frac{\kmax}{k_d}$ & '
+r'$\displaystyle\frac{k_d}{k_f}$ & '
+r'$F_f$ & '
+r'$\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ '
+r'\\[3mm]'
+)
+
+
+def minhmaxu_from_sim(sim):
+    """Return minh and maxu."""
+    dico = sim.output.prob_dens_func.load()
+    bin_edges_eta = dico['bin_edges_eta']
+    bin_edges_u = dico['bin_edges_u']
+    return 1. + bin_edges_eta.min(), bin_edges_u.max()
+
+
+
+
+def print1sim(paths):
+    """Print informations on one simulation."""
+
+    print('\n\n')
+
+    if len(paths) == 1:
+        path = paths[0]
+    else:
+        set_of_dir = solveq2d.SetOfDirResults(paths)
+        path = set_of_dir.path_larger_t_start()
+
+    sim = solveq2d.create_sim_plot_from_dir(path)
+    param = sim.param
+    nx = param['nx']
+    c = np.sqrt(sim.param['c2'])
+    nu8 = param['nu_8']
+    f = sim.param['f']
+
[…]

### 2016-12-17 old/Python/table_rot.py

@@ -1,0 +1,146 @@
+
+
+from __future__ import print_function
+
+import os
+import glob
+import numpy as np
+
+import baseSW1lw
+from solveq2d import solveq2d
+
+nb_mm_between_c = 1
+
+dir_base  = baseSW1lw.path_base_dir_results
+paths_from_nh_c_f = baseSW1lw.paths_from_nh_c_f
+
+kf = baseSW1lw.kf
+Lf = baseSW1lw.Lf
+print('kf = {0:.2f};    Lf =  {1:.2f}'.format(kf, Lf))
+
+path_here = os.getcwd()
+path_file = 'table_try'
+ii=0
+while os.path.exists(
+    path_here+'/Table_files/'+path_file+'{0}.txt'.format(ii)):
+    ii+=1
+path_file = path_here+'/Table_files/'+path_file+'{0}.txt'.format(ii)
+ftable = open(path_file, 'w')
+
+
+ftable.write(
+r'$n$ & $c$ & '
+r'$\nu_8$ & '
+r'$f$ & $Ro$ & $Bu$ & '
+r'$\eps$ & '
+r'$\displaystyle\frac{\kmax}{k_d}$ & '
+r'$\displaystyle\frac{k_d}{k_f}$ & '
+r'$F_f$ & '
+r'$\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ '
+r'\\[3mm]'
+)
+
+
+
+# ftable.write(
+# r'$n$ & $c$ & '
+# r'$f$ & $Ro$ & $Bu$ & '
+# r'$\eps$ & $F_f$ & '
+# r'$\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ & '
+# r'$\displaystyle\frac{\kmax}{k_d}$ \\[3mm]'
+# )
+
+
+def minhmaxu_from_sim(sim):
+    """Return minh and maxu."""
+    dico = sim.output.prob_dens_func.load()
+    bin_edges_eta = dico['bin_edges_eta']
+    bin_edges_u = dico['bin_edges_u']
+    return 1. + bin_edges_eta.min(), bin_edges_u.max()
+
+
+
+
+def print1sim(set_of_dir, f):
+    """Print informations on one simulation."""
+
+    print('\n\n')
+
+    set_of_dir = set_of_dir.filter(f=f)
+    path = set_of_dir.path_larger_t_start()
+
[…]

### 2016-12-17 Latex/section_rotation.tex
Article compiled with a Makefile (without figure).

In order to study the effects of system rotation, we have carried
out four supplementary simulations for $c = 20$, $n = 1920$ and
constant and non-zero Coriolis parameter $f$.  The values of $f$ have
been chosen such that to yield relatively small Rossby numbers
\begin{equation}
Ro_f = \frac{\eps^{1/3} {k_f}^{2/3}}{f} \lesssim 0.1,
\end{equation}
and to span a range of Burger number,
\begin{equation}
Bu = \left(\frac{k_f}{k_d}\right)^2 = \left(\frac{Ro_f}{F_f}\right)^2,
\end{equation}
going from 0.5 to 4.  For these moderate values of global rotation, a
statistically stationary regime is also reached.  Table~\ref{tab_rot}
displays the parameters for these simulations.
\begin{table}
\begin{center}
\begin{tabular}{cc@{\hskip 8mm}c@{\hskip 8mm}ccc@{\hskip 8mm}cccc@{\hskip 8mm}cc}
$n$ & $c$ & $\nu_8$ & $f$ & $Ro$ & $Bu$ & $\eps$ & $\displaystyle\frac{\kmax}{\kdiss}$ & $\displaystyle\frac{\kdiss}{k_f}$ & $F_f$ & $\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ \\[3mm]
1920 &   20 & 9.6e-13 &  0   &  $\infty$ & $\infty$ & 0.99 & 2.46 &  58 &  0.055 & 0.59 & 0.56 \\
1920 &   20 & 9.6e-13 &  7.5 &   0.11 &      4 & 0.96 & 2.47 &  58 &  0.054 & 0.67 & 0.52 \\
1920 &   20 & 9.6e-13 & 10.7 &  0.076 &      2 & 0.93 & 2.47 &  58 &  0.054 & 0.70 & 0.62 \\
1920 &   20 & 9.6e-13 & 15.1 &  0.052 &      1 & 0.85 & 2.48 &  57 &  0.052 & 0.70 & 0.65 \\
1920 &   20 & 9.6e-13 & 21.3 &  0.037 &    0.5 & 0.84 & 2.48 &  57 &  0.052 & 0.66 & 0.81 \\
\end{tabular}
\caption{Overview of parameters for the simulations used to study the effect of rotation. 
}
\label{tab_rot}
\end{center}
\end{table}

\begin{figure}
% \centerline{
% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_f}
% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_f_Nx=1920}
% }
\caption{Effect of the rotation: (\textit{a}) mean energy versus
$k_d/k_f$ and (\textit{b}) energy spectra for $c = 20$ and $n =
1920$.}
\label{fig_effectBu}
\end{figure}

Figure~\ref{fig_effectBu}(\textit{a}) shows the mean energy as a
function of the Burger number.  We see that for $Bu = 2$ and 4, the
mean energy is very close to the value obtained for the non-rotating
case.
%
However, when $k_f<k_d$, i.e. for $Bu<1$, the mean energy increases.
%
Figure~\ref{fig_effectBu}(\textit{b}) presents the spectra for the
same simulations.  The spectra for $Bu = 2$ and 4 are very close to
the spectra for $f= 0$, which confirms that a weak rotation does not
deeply modify the non-rotating results.
%
We have also verified that for the moderate rotation rates
corresponding to $Bu>1$, the other results presented in
section~\ref{section_wave_cascade_f=0} on the non-rotating wave
cascade are only weakly modified.  In particular, the results for $Bu
= \infty$ and $Bu = 4$ are very similar.

### 2016-12-17 Latex/section_wave_cascade_f=0.tex
Article compiled with a Makefile (without figure).

@@
 \begin{figure}
-\centerline{
-\includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
+% \centerline{
+% \includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
 \caption{Spectral energy fluxes averaged over a long simulation for $c
@@
 \begin{figure}
-\centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
+% \centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
 \caption{
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
+% \centerline{
+% \includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
 \caption{Spatio-temporal spectra of KE (dark lines) and APE (light
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
-\includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
+% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
+% }
 \caption{Time- and space-averaged energy 
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
-\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
-}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
-\includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
+% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
+% }
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
+% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
+% }
 \caption{
@@
 \begin{figure}
-\centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
+% \centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
 \caption{Compensated spectra
@@
 \setlength{\halfwidth}{69mm}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
-\hspace{-4mm}
-\includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
-}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
-\hspace{-4mm}
-\includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c20}
+% \hspace{-4mm}
+% \includegraphics[width=\halfwidth]{../Figs/fig_2Dh_c200}
+% }
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c20}
+% \hspace{-4mm}
+% \includegraphics[width=\halfwidth]{../Figs/fig_2Duy_c200}
+% }
 \caption{
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_ux}
-\includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_uy}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_ux}
+% \includegraphics[width=\halfwidth]{../Figs/fig_interm_strfct_uy}
+% }
 \caption{
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_interm_ux}
-\includegraphics[width=\halfwidth]{../Figs/fig_interm_uy}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_interm_ux}
+% \includegraphics[width=\halfwidth]{../Figs/fig_interm_uy}
+% }
 \caption{
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
+% }
 \caption{
@@
 \begin{figure}
-\centerline{
-\includegraphics[width=\halfwidth]{../Figs/fig_flatness}
-}
+% \centerline{
+% \includegraphics[width=\halfwidth]{../Figs/fig_flatness}
+% }
 \caption{ Flatness of the longitudinal and transverse increments for

### 2016-12-17 Old/appendix_dissip_forcing.tex
Article compiled with a Makefile (without figure).

In this appendix, we give the expressions of the kinetic energy
dissipation and forcing rates, which are unusual for the one-layer
shallow-water model since the kinetic energy has not a quadratic
expression.

We consider viscous operators such as $\p_t \uu |_{\mbox{\tiny diss}}
=- \nu_n i^{-n} \bnabla^n \uu $ and $\p_t \eta |_{\mbox{\tiny diss}}
=- \nu_n i^{-n} \bnabla^n \eta $, with n even.  The values $n=-4$, 0,
2 and 8 correspond to hypo-viscosity, linear damping, newtonian
viscosity and hyper-viscosity, respectively.  In this study, we have
only used the value $n=8$.
%
Note that the dissipation operator is applied on $\eta$ and not on
$h$.  Using $\p_t \JJ |_{\mbox{\tiny diss}} = h \p_t \uu
|_{\mbox{\tiny diss}} + \uu \p_t h |_{\mbox{\tiny diss}} = - \nu_n
i^{-n} (h \bnabla^n \uu + \uu \bnabla^n \eta )$, the KE dissipation
rate can be computed as
\begin{eqnarray}
\p_t \meanx{E_K} |_{\mbox{\tiny diss}} 
&=& 
\mean{
\p_t \uu |_{\mbox{\tiny diss}} \cdot \JJ
+ \uu \cdot \p_t \JJ |_{\mbox{\tiny diss}}
} /2, \\
&=& 
- \nu_n i^{-n}
\mean{
\JJ \cdot \bnabla^n \uu + |\uu|^2 \bnabla^n \eta /2
} \\
% &=& 
% - \sum_\kk \hat f_{dn} \left[ \scalarprod{\JJ}{\uu}
% + \scalarprod{|\uu|^2/2}{\eta}
% \right]\\
&=& 
- \sum_\kk 2 f_{dn}  E_K(\kk)
- \sum_\kk  f_{dn} \scalarprod{|\uu|^2/2}{\eta},
\end{eqnarray}
where $ f_{dn} (\kk) = \nu_n |\kk|^n$ is the dissipative frequency.
The first term of the rhs is the usual term but there is also an
additional term that is not negatively defined.

The spectral injection rate of quadratic kinetic energy averaged over
one time step is
\begin{equation}
P_{K}(\kk, t) 
= \frac{1}{\delta t} \int_t^{t+\delta t} dt'
\scalarprod{\uu(t')}{\ff}
= 
\scalarprod{\uu}{\ff}
+ 
|\ff|^2 \delta t /2,
\end{equation}
where we have used the fact that the forcing $\ff$ is constant over
the time step.
%
In order to calculate the total KE injection rate, we have to take
into account the non-quadratic term in the expression of the kinetic
energy.
%
The forcing terms are $\p_t \uu |_f = \ff$, $\p_t h |_f = f_h$ and $
\p_t \JJ |_f = \ff_\JJ = h \ff + \uu f_h$ so that the instantaneous
injection rate can be written as
\begin{equation}
 P_{K\mbox{\tiny inst}}(\kk, t) 
= \p_t  E_K(\kk, t)|_f 
= \scalarprod{\JJ}{\ff}/2 + \scalarprod{\uu}{\ff_\JJ}/2.
\end{equation}
Averaging over one time step, we obtain
\begin{eqnarray}
 P_{K}(\kk, t) 
&=& \frac{1}{\delta t} \int_t^q{t+\delta t} 
dt'  P_{K\mbox{\tiny inst}}(\kk, t') 
\\
&=& \frac{1}{\delta t} \int_t^{t+\delta t} dt'
\left[
\scalarprod{\JJ(t')}{\ff}/2
+ \scalarprod{\uu(t')}{h(t') \ff + \uu(t') f_h}/2 
\right].
\end{eqnarray}
Using the estimates $\uu(t') = \uu(t)+ \ff (t'-t)$, $h(t') = h(t)+ f_h
(t'-t)$ and $\JJ(t') = \JJ(t)+ \ff f_h (t'-t)^2$, the KE injection
rate averaged over one time step can be computed at the leading order
as
\begin{eqnarray}
 P_{K}(\kk, t) \simeq 
& & \scalarprod{\JJ}{\ff}/2 + \scalarprod{\uu}{\ff_\JJ}/2 \nonumber\\
&+& \left[  
\scalarprod{\ff}{\ff_\JJ}/2  
+ \scalarprod{\uu}{f_h\ff} 
\right] \delta t /2.
\end{eqnarray}

### 2017-01-02 Python/make_fig_3.py
Add exit_if_figure_exists function on top of all python scripts; make pyfig

@@ -1,10 +1,11 @@
+#!/usr/bin/env python
 import pylab as pl
 import fluidsim as fls
 import os
 import h5py
 
 from base import _k_f, _eps, set_figsize
-from paths import paths_sim, path_pyfig
+from paths import paths_sim, path_pyfig, exit_if_figure_exists
 
 
 path_fig = path_pyfig + 'fig_3.png'
@@ -72,6 +73,7 @@ def fig3_struct(path, fig, ax1, tmin=0, tmax=1000):
 
 
 if __name__ == '__main__':
+    exit_if_figure_exists(__file__)
     set_figsize(10, 6)
     fig, ax = pl.subplots()
     fig3_struct(paths_sim['noise_c20nh3840Buinf'], fig, ax, tmin=15, tmax=75)

### 2017-01-03 Python/base.py
Rename and improve figures

@@ -4,15 +4,22 @@ import h5py
 from fluiddyn.util.paramcontainer import ParamContainer
 
 
-def set_font(size=14):
+def get_font(size=16):
     _font = {'family': 'serif',
              'weight': 'normal',
              'size': size,
              }
+    return _font
+
+
+def matplotlib_rc(mathjax=True, fontsize=16, interactive=False):
+    pl.rc('text', usetex=mathjax)
+    _font = get_font(fontsize)
     pl.rc('font', **_font)
-
-
-_font = set_font()
+    if interactive:
+        pl.ion()
+    else:
+        pl.ioff()
 
 
 def set_figsize(*size):

### 2017-01-03 Python/make_fig_Emean_time.py

@@ -2,14 +2,13 @@
 import pylab as pl
 import fluidsim as fls
 import os
+from itertools import product
 
-from base import _k_f, _eps, _font, set_figsize
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
+from base import _k_f, _eps, set_figsize, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
-
-
-def fig1_energy(paths, fig=None, ax=None, t_start=10., legend=None):
+def fig1_energy(paths, fig=None, ax=None, t_start=10., legend=None, linestyle=None):
     if fig is None or ax is None:
         ax = pl
 
@@ -30,36 +29,46 @@ def fig1_energy(paths, fig=None, ax=None, t_start=10., legend=None):
         E = E / E_f
         t = t / T_f
         label = legend[i]
-        ax.plot(t, E, linewidth=2, label=label)
+        ax.plot(t, E, linestyle, linewidth=2, label=label)
         print('{}\teps={}\tk_f={}\tE_f={}\tT_f={}'.format(
             label, P0, k_f, E_f, T_f))
 
-    try:
-        ax.xlabel('$t/T_f$', fontdict=_font)
-        ax.ylabel('$E/E_f$', fontdict=_font)
-    except:
-        ax.set_xlabel('$t/T_f$', fontdict=_font)
-        ax.set_ylabel('$E/E_f$', fontdict=_font)
+    ax.set_xlabel('$t/T_f$')
+    ax.set_ylabel('$E/E_f$')
 
     ax.legend()
 
 
 def get_legend_and_paths(c_list, nh_list):
     keys = ['c{}nh{}'.format(_c, _nh) for _c in c_list for _nh in nh_list]
-    return keys, [paths_sim['noise_' + k + 'Buinf'] for k in keys]
+    legend = ['c={}, n={}'.format(_c, _nh) for _c in c_list for _nh in nh_list]
+    return legend, [paths_sim['noise_' + k + 'Buinf'] for k in keys]
 
 
 if __name__ == '__main__':
+    matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
-    set_figsize(16, 16)
-    fig = pl.figure()
-    ax = []
+    set_figsize(16, 6)
     c = [20, 100, 400]
     nh = [960, 1920, 3840, 7680]
 
+    '''
+    fig = pl.figure()
+    ax = []
     for i in range(4):
[…]

### 2017-01-03 Python/make_fig_Kolmo_c=20_N=3840.py

@@ -4,10 +4,8 @@ import fluidsim as fls
 import os
 import h5py
 
-from base import _k_f, _eps, set_figsize
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
-
-
+from base import _k_f, _eps, set_figsize, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
 def fig3_struct(path, fig, ax1, tmin=0, tmax=1000):
@@ -45,33 +43,50 @@ def fig3_struct(path, fig, ax1, tmin=0, tmax=1000):
     ax1.set_xscale('log')
     ax1.set_yscale('linear')
 
-    ax1.set_xlabel('$r/L_f$')
-    ax1.set_ylabel('$S(r) / (4\epsilon r)$')
-
-    ax1.axhline(1., color='k', ls=':')
-
     # ax1.plot(rxs / Lf,
     #          (S_uL2JL+S_uT2JL+S_c2h2uL)/S_Kolmo_theo,
     #          'y', linewidth=1, label='sum check')
-    ax1.plot(rxs / Lf, S_Kolmo / S_Kolmo_theo, 'k', linewidth=2, label='S')
+    def _label(x, y):
+        pre = ''
+        if y == 'uu':
+            y = r'\mathbf{u}'
+            y2 = r'|\delta {}|^2'.format(y)
+        else:
+            if y == 'h':
+                pre = 'c ^ 2'
+            y2 = r'(\delta {})^2'.format(y)
+
+        return '$ \langle {} \delta {} {} \\rangle $'.format(pre, x, y2)
+
+    ax1.set_xlabel('$r/L_f$')
+    label1 = _label('J_L', 'uu')
+    label2 = _label('u_L', 'h')
+    label3 = label1[:-10] + ' + ' + label2[10:]
+    ax1.set_ylabel(label3.rstrip(' $') + ' / (4\epsilon_q r)$')
+
+    ax1.plot(rxs / Lf, S_Kolmo / S_Kolmo_theo, 'k', linewidth=4,
+             label=label3)
     ax1.plot(rxs / Lf, (S_uL2JL + S_uT2JL) / S_Kolmo_theo, 'r', linewidth=2,
-             label='$Su^2_LJ+Su^2_TJ$')
-    ax1.plot(rxs / Lf, S_c2h2uL / S_Kolmo_theo,
[…]

### 2017-01-03 Python/make_fig_flatness.py

@@ -2,10 +2,8 @@
 import pylab as pl
 import fluidsim as fls
 
-from base import _k_f, set_figsize, _rxs_str_func
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
-
-
+from base import _k_f, set_figsize, _rxs_str_func, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
 def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
@@ -38,7 +36,11 @@ def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
 
     ax.set_xlim([2e-3, 10])
     ax.set_ylim([2, 500])
-    ax.plot(rxs[cond] / L_f, 1 / rxs[cond], 'k', label='$r^{-1}$')
+    ax.plot(rxs[cond] / L_f, 1 / rxs[cond], 'k')
+    x_text = rxs[cond].mean() / L_f
+    y_text = 1. / rxs[cond].mean() * 1.05
+    ax.text(x_text, y_text, '$r^{-1}$')
+
     ax_inset = fig.add_axes([0.5, 0.5, 0.3, 0.3])
     ax_inset.set_xlabel('$r_x/L_f$')
     ax_inset.set_ylabel('$F_T / F_L$')
@@ -50,8 +52,9 @@ def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
 
 
 if __name__ == '__main__':
+    matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
     set_figsize(10, 6)
     fig, ax = pl.subplots()
-    fig12_flatness(paths_sim['noise_c20nh7680Buinf'], fig, ax)
+    fig12_flatness(paths_sim['noise_c20nh7680Buinf'], fig, ax, tmin=20)
     pl.savefig(path_fig)

### 2017-01-03 Python/make_fig_ratio_strfct.py

@@ -2,10 +2,8 @@
 import pylab as pl
 import fluidsim as fls
 
-from base import _k_f, set_figsize, _rxs_str_func
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
-
-
+from base import _k_f, set_figsize, _rxs_str_func, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
 def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000, delta_t=0.5):
@@ -40,13 +38,15 @@ def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000, de
                  linewidth=2, label='$R_{:.0f}$'.format(o))
         ax1.plot(rxs / L_f, ones * shock_model[int(o)], color2)
 
+    ax1.set_ylim([0., 10.])
     ax1.legend()
 
 
 if __name__ == '__main__':
+    matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
     set_figsize(10, 6)
     fig, ax = pl.subplots()
     fig11_ratio_struct(
-        paths_sim['noise_c20nh7680Buinf'], fig, ax, pl.arange(2, 6), tmin=10)
+        paths_sim['noise_c20nh7680Buinf'], fig, ax, pl.arange(2, 7), tmin=10)
     pl.savefig(path_fig)

### 2017-01-03 Python/make_fig_spect_energy_budg_c=100_N=3840.py

@@ -5,10 +5,8 @@ import os
 import h5py
 from fluidsim.base.output.spect_energy_budget import cumsum_inv
 
-from base import _index_where, _k_f, _eps, set_figsize
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
-
-
+from base import _index_where, _k_f, _eps, set_figsize, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
 def fig2_seb(path, fig=None, ax=None, t_start=10):
@@ -50,6 +48,7 @@ def fig2_seb(path, fig=None, ax=None, t_start=10):
 
 
 if __name__ == '__main__':
+    matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
     set_figsize(10, 6)
     fig, ax = pl.subplots()

### 2017-01-03 Python/make_fig_spectra_c=100_nh=7680.py

@@ -3,10 +3,8 @@ import pylab as pl
 import fluidsim as fls
 import h5py
 
-from base import _k_f, _eps, set_figsize
-from paths import paths_sim, path_pyfig, exit_if_figure_exists
-
-
+from base import _k_f, _eps, set_figsize, matplotlib_rc
+from paths import paths_sim, exit_if_figure_exists
 
 
 def _mean_spectra(sim, tmin=0, tmax=1000):
@@ -25,8 +23,8 @@ def _mean_spectra(sim, tmin=0, tmax=1000):
     imin_plot = pl.argmin(abs(times - tmin))
     imax_plot = pl.argmin(abs(times - tmax))
 
-    tmin_plot = times[imin_plot]
-    tmax_plot = times[imax_plot]
+    # tmin_plot = times[imin_plot]
+    # tmax_plot = times[imax_plot]
     machine_zero = 1e-15
     EK = dset_spectrumEK[imin_plot:imax_plot + 1].mean(0)
     EA = dset_spectrumEA[imin_plot:imax_plot + 1].mean(0)
@@ -66,6 +64,7 @@ def fig7_spectra(path, fig, ax, t_start):
 
 
 if __name__ == '__main__':
+    matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
     set_figsize(10, 6)
     fig, ax = pl.subplots()

### 2017-01-03 Python/paths.py

@@ -73,7 +73,7 @@ if not os.path.exists(path_pyfig):
 
 def exit_if_figure_exists(scriptname, extension='.png'):
     scriptname = os.path.basename(scriptname)
-    figname = os.path.splitext(scriptname)[0].strip('make_') + extension
+    figname = os.path.splitext(scriptname)[0].lstrip('make_') + extension
     figpath = os.path.join(path_pyfig, figname)
     if os.path.exists(figpath):
         print('Figure {} already made. {} exiting...'.format(figname, scriptname))

### 2018-05-17 Python/base.py
Uncommited changes from before

@@ -2,9 +2,13 @@ from __future__ import print_function, division
 import pylab as pl
 import h5py
 from fluiddyn.util.paramcontainer import ParamContainer
+from fluiddyn.output import rcparams
 
 
-def get_font(size=16):
+DPI = 300
+
+
+def get_font(size=7):
     _font = {'family': 'serif',
              'weight': 'normal',
              'size': size,
@@ -12,14 +16,24 @@ def get_font(size=16):
     return _font
 
 
-def matplotlib_rc(mathjax=True, fontsize=16, interactive=False):
-    pl.rc('text', usetex=mathjax)
-    _font = get_font(fontsize)
-    pl.rc('font', **_font)
+def matplotlib_rc(
+        fontsize=7, dpi=DPI, tex=True, interactive=False, pad=2):
+
+    # pl.rc('text', usetex=tex)
+    # _font = get_font(fontsize)
+    # pl.rc('font', **_font)
+
+    rcparams.set_rcparams(fontsize)
+    pl.rc('figure', dpi=dpi)
+    pl.rc('xtick', direction='in')
+    pl.rc('ytick', direction='in')
+
     if interactive:
         pl.ion()
     else:
         pl.ioff()
+
+    # pl.tight_layout(pad=pad)
 
 
 def set_figsize(*size):
@@ -59,6 +73,20 @@ def _eps(sim, t_start):
     return eps[ind:].mean()
 
 
+def _t_stationary(sim, eps_percent=15):
+    dico = sim.output.spatial_means.load()
+    time = dico['t']
+    epsilon = dico['epsK_tot'] + dico['epsA_tot']
+    eps_end = epsilon[-1]
+
+    for t, eps in zip(time[::-1], epsilon[::-1]):
+        percent = abs(eps - eps_end) / eps_end * 100
+        if percent > eps_percent:
+            break
+
+    return t
+
+
 So_var_dict = {}
 
 
@@ -79,18 +107,18 @@ def _rxs_str_func(sim, order, tmin, tmax, delta_t, key_var):
     oper = f['/info_simul/params/oper']
     nx = oper.attrs['nx']
     Lx = oper.attrs['Lx']
-    deltax = Lx/nx
+    deltax = Lx / nx
 
-    rxs = np.array(rxs, dtype=np.float64)*deltax
+    rxs = np.array(rxs, dtype=np.float64) * deltax
 
[…]

### 2018-05-17 Python/make_fig_Emean_time.py

@@ -1,22 +1,79 @@
 #!/usr/bin/env python
 import pylab as pl
-import fluidsim as fls
+from mpl_toolkits.mplot3d import Axes3D
 import os
-from itertools import product
+import itertools
+from collections import OrderedDict
+import fluidsim as fls
+from fluiddyn.io import stdout_redirected
 
 from base import _k_f, _eps, set_figsize, matplotlib_rc
-from paths import paths_sim, exit_if_figure_exists
+from paths import keyparams_from_path, paths_sim, exit_if_figure_exists
 
 
-def fig1_energy(paths, fig=None, ax=None, t_start=10., legend=None, linestyle=None):
-    if fig is None or ax is None:
-        ax = pl
+fontsize = 7
+THREE_D = False
+
+
+def fig1_plot_all(paths):
+    c_nh = OrderedDict.fromkeys([10, 20, 40, 100, 400, 700])
+    c_nh = {c: [] for c in c_nh.keys()}
+    for path in paths.values():
+        init_field, c, nh, Bu, efr = keyparams_from_path(path)
+        if init_field == 'noise' and Bu == 'inf':
+            c_nh[int(c)].append(int(nh))
+            c_nh[int(c)].sort(reverse=True)
+
+    c_nh_skip = [(400, 7680)]
+
+    if THREE_D:
+        fig = pl.figure()
+        try:
+            ax = pl.gca(projection='3d')
+        except:
+            ax = Axes3D(fig)
+
+        styles = itertools.cycle(['c', 'm', 'r', 'g'])
+    else:
+        fig, ax = pl.subplots()
+
+    styles = itertools.product('cmkrgb', ('-', '--', '-.', ':'))
+    for c, nh_list in sorted(c_nh.items(), key=lambda t: t[0], reverse=True):
+        if THREE_D:
+            legend, paths = get_legend_and_paths([c], nh_list)
+            fig1_energy(paths, fig, ax, legend=legend, t_start=30.,
+                        linestyle=styles)
+        else:
+            count_nh = range(4)
+
+            def count_matches_nh(it):
+                print(len(count_nh))
+                count_nh.pop()
+                return len(count_nh) > len(nh_list)
+
+            for nh, style in itertools.izip(nh_list, itertools.dropwhile(count_matches_nh, styles)):
[…]

### 2018-05-17 Python/make_fig_flatness.py

@@ -6,10 +6,29 @@ from base import _k_f, set_figsize, _rxs_str_func, matplotlib_rc
 from paths import paths_sim, exit_if_figure_exists
 
 
+fontsize = 7
+fontsize_inset = fontsize - 2
+
+
+def _ax_inset(fig, xlabel, left, bottom=0.6, width=0.35 / 2, height=0.45 / 2):
+    ax_inset = fig.add_axes([left, bottom, width, height])
+    ax_inset.set_xlabel(xlabel, size=fontsize_inset)
+    ax_inset.set_ylabel('$F_T / F_L$', size=fontsize_inset)
+    ax_inset.set_ylim([0, 1.6])
+    ax_inset.set_yticks(pl.arange(0, 2., 0.5))
+    ax_inset.axhline(1.5, linewidth=0.5, color='k', linestyle=':')
+
+    # Set the tick labels font
+    for ticklabel in (ax_inset.get_xticklabels() + ax_inset.get_yticklabels()):
+        ticklabel.set_fontsize(fontsize_inset)
+
+    return ax_inset
+
+
 def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
     sim = fls.load_sim_for_plot(path)
     order = [2, 4]
-    key_var = ['ux', 'uy']
+    key_var = ['uy', 'ux']
     rxs, So_var_dict, deltax = _rxs_str_func(
         sim, order, tmin, tmax, delta_t, key_var)
 
@@ -32,29 +51,39 @@ def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
         So_2 = So_var_dict['{0}_{1:.0f}'.format(key, 2)]
         F[key] = So_4 / So_2 ** 2
         ax.plot(rxs / L_f, F[key], color1,
-                linewidth=2, label=_label[key])
+                linewidth=1, label=_label[key])
 
     ax.set_xlim([2e-3, 10])
     ax.set_ylim([2, 500])
-    ax.plot(rxs[cond] / L_f, 1 / rxs[cond], 'k')
+    ax.plot(rxs[cond] / L_f, 1 / rxs[cond], 'k', linewidth=0.5)
     x_text = rxs[cond].mean() / L_f
     y_text = 1. / rxs[cond].mean() * 1.05
[…]

### 2018-05-17 Python/paths.py

@@ -1,17 +1,22 @@
 import os
 import sys
-import subprocess
-from glob import glob
 import re
+from glob import glob
+from socket import gethostname
 from collections import OrderedDict
+import pandas as pd
+
 from fluiddyn.util.paramcontainer import ParamContainer
+import fluidsim as fls
+
+from base import *
 
 
 def get_pathbase():
-    hostname = subprocess.check_output('hostname')
+    hostname = gethostname()
     hostname = hostname.lower()
     if hostname.startswith('pelvoux'):
-        pathbase = '/scratch/avmo/data/'
+        pathbase = '/media/avmo/lacie/13KTH'
     elif any(map(hostname.startswith, ['legilnx', 'nrj1sv', 'meige'])):
         pathbase = '$HOME/useful/project/13KTH/DataSW1L_Ashwin/'
     elif hostname.startswith('kthxps'):
@@ -26,6 +31,43 @@ def get_pathbase():
     return pathbase
 
 
+def keyparams_from_path(p):
+    c = re.search('(?<=c=)[0-9]*', p, re.X).group(0)
+    nh = re.search('(?<=_)[0-9]*(?=x)', p).group(0)
+    try:
+        Bu = re.search('(?<=Bu=)[0-9]*(\.[0-9])', p, re.X).group(0)
+    except AttributeError:
+        Bu = 'inf'
+
+    params_xml_path = os.path.join(p, 'params_simul.xml')
+    params = ParamContainer(path_file=params_xml_path)
+    init_field = params.init_fields.type
+    if init_field == 'noise':
+        return init_field, c, nh, Bu, None
+    else:
+        return init_field, c, nh, Bu, params.preprocess.init_field_const
+
+    
+pd_columns = [
+    r'$n$', r'$c$', r'$\nu_8$', r'$f$', r'$\epsilon$', r'$\frac{k_d}{k_f}$', 
+    r'$F_f$', r'$Ro_f$', r'$Bu$','$\min h$', r'$\frac{\max |\bf u|}{c}$', 
+    '$t_{stat}$', 'short name'
+]
+
+
+def pandas_from_path(p, key):
+    init_field, c, nh, Bu, init_field_const = keyparams_from_path(p)
+    params_xml_path = os.path.join(p, 'params_simul.xml')
+    params = ParamContainer(path_file=params_xml_path)
+    sim = fls.load_sim_for_plot(p, merge_missing_params=True)
+    return pd.Series(
[…]

### 2018-05-22 Python/base.py
Finalize tables

@@ -1,5 +1,8 @@
 from __future__ import print_function, division
 import pylab as pl
+from scipy.optimize import curve_fit
+from scipy import stats
+
 import h5py
 from fluiddyn.util.paramcontainer import ParamContainer
 from fluiddyn.output import rcparams
@@ -61,12 +64,15 @@ def _k_f(params=None, params_xml_path=None):
     return 2 * pl.pi / Lh * ((params.forcing.nkmax_forcing +
                               params.forcing.nkmin_forcing) // 2)
 
-
 def _k_max(params):
     delta_x = _delta_x(params)
     k_max = pl.pi / delta_x * params.oper.coef_dealiasing
     return k_max
 
+def _k_diss(params):
+    k_max = _k_max(params)
+    C = params.preprocess.viscosity_const
+    return k_max / C / pl.pi  # FIXME: Not sure why the pi is needed
 
 def _eps(sim=None, t_start=0, path=None):
     if sim is None and path is not None:
@@ -80,6 +86,7 @@ def _eps(sim=None, t_start=0, path=None):
 
 
 def _t_stationary(sim=None, eps_percent=15, path=None):
+    # Old function! Use epststmax instead
     if sim is None and path is not None:
         dico = SpatialMeansSW1L._load(path)
     else:
@@ -96,30 +103,38 @@ def _t_stationary(sim=None, eps_percent=15, path=None):
     return t
 
 
-def epsfit(path):
-    from scipy.optimize import curve_fit
-    dico = SpatialMeansSW1L._load(path)
-
-    t = dico['t']
-    epsilon = dico['epsK_tot'] + dico['epsA_tot']
-
 def epststmax(path=None, eps_percent=15):
     dico = SpatialMeansSW1L._load(path)
+    time = dico['t']
+    eps = dico['epsK_tot'] + dico['epsA_tot']
+    """
+    if 'noise' in path:
+        def f(x, amptan, ttan):
+            return amptan * pl.tanh(2 * (x / ttan)**4)
 
-    time = t = dico['t']
+        popt, pcov = curve_fit(f, time, eps)
+        eps_stat = popt[0]
+        time_stat = popt[1]
 
-    epsilon = dico['epsK_tot'] + dico['epsA_tot']
-    eps_end = epsilon[-1]
+        return eps_stat, time_stat, time[-1]
+    else:
+    """
+    def f(x, amptan, ttan, amplog, sigma):
[…]

### 2018-05-22 Python/paths.py

@@ -13,7 +13,7 @@ from fluiddyn.io.redirect_stdout import stdout_redirected
 
 import fluidsim as fls
 
-from base import _eps, _t_stationary, _k_d, _k_f, epststmax
+from base import _eps, _t_stationary, _k_d, _k_f, _k_diss, epststmax
 
 
 def get_pathbase():
@@ -24,7 +24,9 @@ def get_pathbase():
     elif any(map(hostname.startswith, ['legilnx', 'nrj1sv', 'meige'])):
         pathbase = '$HOME/useful/project/13KTH/DataSW1L_Ashwin/'
     elif hostname.startswith('kthxps'):
-        pathbase = '/scratch/avmo/13KTH/'
+        pathbase = '/run/media/avmo/lacie/13KTH/'
+        if not os.path.exists(pathbase):
+            pathbase = '/scratch/avmo/13KTH/'
     else:
         raise ValueError('Unknown hostname')
 
@@ -51,10 +53,12 @@ def keyparams_from_path(p):
     else:
         return init_field, c, nh, Bu, params.preprocess.init_field_const
 
-    
+EFR = r'$\frac{<\bf \Omega_0 >}{{(P k_f^2)}^{2/3}}$'
 pd_columns = [
-    r'$n$', r'$c$', r'$\nu_8$', r'$f$', r'$\epsilon$', r'$\frac{k_d}{k_f}$', 
-    r'$F_f$', r'$Ro_f$', r'$Bu$','$\min h$', r'$\frac{\max |\bf u|}{c}$', 
+    r'$n$', r'$c$', r'$\nu_8$', r'$f$', r'$\epsilon$', r'$\frac{k_{diss}}{k_f}$', 
+    r'$F_f$', r'$Ro_f$', r'$Bu$',
+    # '$\min h$', r'$\frac{\max |\bf u|}{c}$',
+    EFR,
     '$t_{stat}$', r'$t_{\max}$', 'short name'
 ]
 
@@ -67,14 +71,15 @@ def pandas_from_path(p, key, as_df=False):
     
     c = int(c)
     kf = _k_f(params)
-    kd_kf = _k_d(params) / kf
+    kd_kf = _k_diss(params) / kf
     # ts = _t_stationary(path=p)
     # eps = _eps(t_start=ts, path=p)
     eps, ts, tmax = epststmax(p)
+    efr = params.preprocess.init_field_const
     print([type(o) for o in (eps, kf, c)])
     Fr = (eps / kf) ** (1./3) / c
[…]

### 2018-05-22 Python/make_fig_Emean_time.py
Start working on figures

@@ -73,7 +73,7 @@ def fig1_energy(paths, fig=None, ax=None, t_start=0., legend=None, linestyle=Non
 
     for i, path in enumerate(paths):
         with stdout_redirected():
-            sim = fls.load_sim_for_plot(path)
+            sim = fls.load_sim_for_plot(path, merge_missing_params=True)
 
         P0 = _eps(sim, t_start)
         k_f = _k_f(sim.params)  # path + '/params_simul.xml')

### 2018-05-22 Python/make_fig_Kolmo_c=20_N=3840.py

@@ -9,7 +9,7 @@ from paths import paths_sim, exit_if_figure_exists
 
 
 def fig3_struct(path, fig, ax1, tmin=0, tmax=1000):
-    sim = fls.load_sim_for_plot(path)
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     path_file = os.path.join(path, 'increments.h5')
     f = h5py.File(path_file, 'r')
     dset_times = f['times']

### 2018-05-22 Python/make_fig_flatness.py

@@ -26,7 +26,7 @@ def _ax_inset(fig, xlabel, left, bottom=0.6, width=0.35 / 2, height=0.45 / 2):
 
 
 def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5):
-    sim = fls.load_sim_for_plot(path)
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     order = [2, 4]
     key_var = ['uy', 'ux']
     rxs, So_var_dict, deltax = _rxs_str_func(

### 2018-05-22 Python/make_fig_ratio_strfct.py

@@ -7,7 +7,7 @@ from paths import paths_sim, exit_if_figure_exists
 
 
 def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000, delta_t=0.5):
-    sim = fls.load_sim_for_plot(path)
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
 
     key_var = ['ux', 'uy']
     rxs, So_var_dict, deltax = _rxs_str_func(

### 2018-05-22 Python/make_fig_spect_energy_budg_c=100_N=3840.py

@@ -10,7 +10,7 @@ from paths import paths_sim, exit_if_figure_exists
 
 
 def fig2_seb(path, fig=None, ax=None, t_start=10):
-    sim = fls.load_sim_for_plot(path)
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
 
     path_file = os.path.join(path, 'spect_energy_budg.h5')
     f = h5py.File(path_file, 'r')
@@ -25,11 +25,11 @@ def fig2_seb(path, fig=None, ax=None, t_start=10):
     transferEAd = f['transfer2D_EAd'][imin_plot:].mean(0) / eps
     # transferEPd = f['transfer2D_EPd'][imin_plot:].mean(0) / eps
 
-    PiEKr = cumsum_inv(transferEKr) * sim.oper.deltakh
-    PiEKd = cumsum_inv(transferEKd) * sim.oper.deltakh
-    PiEAr = cumsum_inv(transferEAr) * sim.oper.deltakh
-    PiEAd = cumsum_inv(transferEAd) * sim.oper.deltakh
-    # PiEPd = cumsum_inv(transferEPd) * sim.oper.deltakh
+    PiEKr = cumsum_inv(transferEKr) * sim.oper.deltak
+    PiEKd = cumsum_inv(transferEKd) * sim.oper.deltak
+    PiEAr = cumsum_inv(transferEAr) * sim.oper.deltak
+    PiEAd = cumsum_inv(transferEAd) * sim.oper.deltak
+    # PiEPd = cumsum_inv(transferEPd) * sim.oper.deltak
 
     print(eps)
     ax.axhline(1., color='k', ls=':')

### 2018-05-22 Python/make_fig_spectra_c=100_nh=7680.py

@@ -36,7 +36,7 @@ def _mean_spectra(sim, tmin=0, tmax=1000):
 
 
 def fig7_spectra(path, fig, ax, t_start):
-    sim = fls.load_sim_for_plot(path)
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     kh, E_tot, EK, EA = _mean_spectra(sim, t_start)
     eps = _eps(sim, t_start)
     k_f = _k_f(sim.params)

### 2018-05-29 Python/base.py
Fix t_stat calculation using Kneedle algo

@@ -1,6 +1,9 @@
 from __future__ import print_function, division
+from warnings import warn
 import pylab as pl
+import numpy as np
 from scipy.optimize import curve_fit
+from scipy.signal import medfilt
 from scipy import stats
 
 import h5py
@@ -12,7 +15,7 @@ from fluidsim.solvers.sw1l.output.spatial_means import SpatialMeansSW1L
 DPI = 300
 
 
-def get_font(size=7):
+def get_font(size=10):
     _font = {'family': 'serif',
              'weight': 'normal',
              'size': size,
@@ -43,9 +46,28 @@ def matplotlib_rc(
 def set_figsize(*size):
     pl.rcParams['figure.figsize'] = tuple(size)
 
+def load_params(path):
+    if not path.endswith('.xml'):
+            path = os.path.join(path, 'params_simul.xml')
+    return ParamContainer(path_file=params_xml_path)
 
-def _index_where(arr, value):
-    return pl.argmin(abs(arr - value))
+def _index_where(arr, value, reverse=False):
+    if not reverse:
+        idx = pl.argmin(abs(arr - value))
+    else:
+        revidx = pl.argmin(abs(arr[::-1] - value))
+        idx = len(arr) - (revidx + 1)
+    return idx
+
+def _index_flat(y, x=None):
+    dx = x[1]-x[0]
+    dy = np.gradient(y, dx)
+    ddy = np.gradient(dy, dx)
+    curv = np.abs(ddy / (dy + 1) ** 1.5)
+    # value = max(1e-5, 0.01 * curv.max())
+    value = curv.std() * 0.01
+    return _index_where(curv, value, True)
+    # return np.argmin(abs(curv))
 
 
 def _delta_x(params):
@@ -56,9 +78,7 @@ def _delta_x(params):
 def _k_d(params):
     return params.f / params.c2 ** 0.5
 
-def _k_f(params=None, params_xml_path=None):
-    if params is None:
-        params = ParamContainer(path_file=params_xml_path)
+def _k_f(params=None):
 
     Lh = min(params.oper.Lx, params.oper.Ly)
     return 2 * pl.pi / Lh * ((params.forcing.nkmax_forcing +
@@ -103,41 +123,123 @@ def _t_stationary(sim=None, eps_percent=15, path=None):
     return t
 
 
-def epststmax(path=None, eps_percent=15):
+def epststmax(path):
     dico = SpatialMeansSW1L._load(path)
     time = dico['t']
[…]

### 2018-05-29 Python/make_fig_spect_energy_budg_c=100_N=3840.py

@@ -5,19 +5,22 @@ import os
 import h5py
 from fluidsim.base.output.spect_energy_budget import cumsum_inv
 
-from base import _index_where, _k_f, _eps, set_figsize, matplotlib_rc
+from base import _index_where, _k_f, _eps, set_figsize, matplotlib_rc, epststmax
 from paths import paths_sim, exit_if_figure_exists
 
 
-def fig2_seb(path, fig=None, ax=None, t_start=10):
+def fig2_seb(path, fig=None, ax=None, t_start=None):
     sim = fls.load_sim_for_plot(path, merge_missing_params=True)
 
     path_file = os.path.join(path, 'spect_energy_budg.h5')
     f = h5py.File(path_file, 'r')
-    imin_plot = _index_where(f['times'][...], t_start)
 
     k_f = _k_f(sim.params)
-    eps = _eps(sim, t_start)
+    # eps = _eps(sim, t_start)
+    eps, ts, tmax = epststmax(path)
+    if t_start is None:
+        t_start = ts
+    imin_plot = _index_where(f['times'][...], t_start)
     khE = (f['khE'][...] + 0.1) / k_f
     transferEKr = f['transfer2D_EKr'][imin_plot:].mean(0) / eps
     transferEKd = f['transfer2D_EKd'][imin_plot:].mean(0) / eps
@@ -50,7 +53,7 @@ def fig2_seb(path, fig=None, ax=None, t_start=10):
 if __name__ == '__main__':
     matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
-    set_figsize(10, 6)
+    set_figsize(5, 3)
     fig, ax = pl.subplots()
-    fig2_seb(paths_sim['noise_c100nh3840Buinf'], fig, ax, t_start=20)
+    fig2_seb(paths_sim['noise_c100nh3840Buinf'], fig, ax)  # , t_start=20)
     pl.savefig(path_fig)

### 2018-05-29 Python/paths.py

@@ -76,7 +76,6 @@ def pandas_from_path(p, key, as_df=False):
     # eps = _eps(t_start=ts, path=p)
     eps, ts, tmax = epststmax(p)
     efr = params.preprocess.init_field_const
-    print([type(o) for o in (eps, kf, c)])
     Fr = (eps / kf) ** (1./3) / c
     try:
         Ro = (eps * kf**2) ** (1./3) / params.f
@@ -138,7 +137,7 @@ def exit_if_figure_exists(scriptname, extension='.png'):
     figname = os.path.splitext(scriptname)[0].lstrip('make_') + extension
     figpath = os.path.join(path_pyfig, figname)
 
-    if len(sys.argv) > 1 and 'remake'.startswith(sys.argv[1]):
+    if len(sys.argv) > 1 and 'remake'.startswith(sys.argv[1]) and os.path.exists(figpath):
         os.remove(figpath)
 
     if os.path.exists(figpath):

### 2018-05-29 Python/make_fig_phys_fields_wave.py
Fig phys fields wave

@@ -1,0 +1,76 @@
+#!/usr/bin/env python
+import os
+import h5py
+import numpy as np
+import matplotlib.pyplot as plt
+import fluidsim as fls
+from base import _k_f, set_figsize, matplotlib_rc, set_figsize, _index_where
+from paths import paths_sim, exit_if_figure_exists
+
+
+def fig_phys_subplot(sim, fig, ax, key_field, x_slice=None, y_slice=None, cmap='inferno'):
+    kf = _k_f(sim.params)
+    Lf = np.pi / kf
+    X = sim.oper.x_seq / Lf
+    Y = sim.oper.y_seq / Lf
+
+    def slice_where(R, r1, r2):
+        i1 = _index_where(R, r1)
+        i2 = _index_where(R, r2)
+        return slice(i1, i2)
+
+    if x_slice is not None:
+        x_slice = slice_where(X, *x_slice)
+        X = X[x_slice]
+
+    if y_slice is not None:
+        y_slice = slice_where(Y, *y_slice)
+        Y = Y[y_slice]
+
+    try:
+        field = sim.state.get_var(key_field)
+    except ValueError:
+        field = sim.oper.ifft(sim.state.get_var(key_field + '_fft'))
+    
+    field = field[y_slice, x_slice]
+
+    cmap = plt.get_cmap(cmap)
+    ax.set_xlabel('$x/L_f$')
+    ax.set_ylabel('$y/L_f$')
+    ax.set_rasterization_zorder(1)
+    vmin = vmax = None
+    norm = None
+    contours = ax.pcolormesh(
+        X, Y, field, norm=norm, vmin=vmin, vmax=vmax, cmap=cmap, zorder=0)
+
+    cbar = fig.colorbar(contours, ax=ax)
+    cbar.solids.set_rasterized(True)
+    
+if __name__ == '__main__':
+    matplotlib_rc()
+    path_fig = exit_if_figure_exists(__file__)  # , extension='.eps'
+    set_figsize(6.65, 6)
+    fig, axes = plt.subplots(2, 2)
+    short_names = [
+        'noise_c20nh1920Buinf',
+        'noise_c400nh1920Buinf'
+    ]
+    sim0 = fls.load_state_phys_file(paths_sim[short_names[0]], merge_missing_params=True)
+    sim1 = sim0
[…]

### 2018-05-29 Python/base.py
Most figures

@@ -123,11 +123,11 @@ def _t_stationary(sim=None, eps_percent=15, path=None):
     return t
 
 
-def epststmax(path):
+def epsetstmax(path):
     dico = SpatialMeansSW1L._load(path)
     time = dico['t']
     eps = dico['epsK_tot'] + dico['epsA_tot']
-    
+    E = dico['EK'] + dico['EA']
     
     # if 'noise' in path:
     if eps.max() > 2 * eps[-1]:
@@ -160,13 +160,15 @@ def epststmax(path):
     eps_stat = float(eps_fit[-1])
     try:
         # idx = _index_flat(eps_fit, time)
-        time_stat = locate_knee(time, eps_fit, eps_stat)
+        idx = locate_knee(time, eps_fit, eps_stat)
+        time_stat = time[idx]
     except ValueError:
         raise ValueError("While calculating curvature in {}".format(path))
         # warn("While calculating curvature in {}".format(path))
         # time_stat = popt[1] + 6 * popt[3]
 
-    return eps_stat, time_stat, time[-1]
+    E_stat = E[idx:].mean()
+    return eps_stat, E_stat, time_stat, time[-1]
 
 def locate_knee(time, eps_fit, eps_stat):
     from kneed import KneeLocator
@@ -188,8 +190,7 @@ def locate_knee(time, eps_fit, eps_stat):
         # non-stationary case
         idx = -1
 
-    time_stat = time[idx]
-    return time_stat
+    return idx
 
 So_var_dict = {}
 

### 2018-05-29 Python/base_fig_energy.py

@@ -1,0 +1,84 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+from scipy.optimize import curve_fit
+from base import set_figsize, matplotlib_rc
+
+
+L_f = 50. / 6  # hardcoded Lh / nk_f
+
+
+def filter_df_by(df, keys, val):
+    groups = df.groupby(keys)
+    return groups.filter(
+        lambda x:all(x[keys[0]] == val),
+        dropna=True
+    )
+
+
+def model_func(c_eps, Cn):
+    return Cn * (L_f * c_eps) ** 0.5
+
+
+def get_cn(c_eps, E):
+    c_eps = c_eps.values
+    E = E.values
+    popt, pcov = curve_fit(model_func, c_eps, E)
+    return popt[0]
+
+
+def plot_energy(
+    df_main, fig=None, ax=None,
+    N=[960, 1920, 3840, 7680],
+    C=[10, 20, 40, 100, 400, 700],
+):
+    if fig is None and ax is None:
+        matplotlib_rc()
+        set_figsize(6.5, 3)
+        fig, ax = plt.subplots(1, 2)
+
+    df_n = {}
+    for n in N:
+        df_n[n] = filter_df_by(df_main, ['$n$'], n)
+
+    E_eps = r'$E/\sqrt{\epsilon}$'
+    for n, df in df_n.items():
+        df = df.assign(**{
+            E_eps: df['$E$'] / df['$\epsilon$'] ** 0.5})
+
+        c_eps = df['$c$'] * df['$\epsilon$']
+        Cn = get_cn(c_eps, df['$E$'])
+
+        E_eps_fit = model_func(c_eps.values, Cn) /  df['$\epsilon$'].values ** 0.5
+        # ax[0].plot(
+        ax[0].loglog(
+                df['$c$'].values, E_eps_fit, 'k:', linewidth=1)
+        df.plot(
+            '$c$', E_eps, ax=ax[0], style='x-',
+            label='$n={}, C_n={:.2f}$'.format(n, Cn),                       
+            logx=True, logy=True,
+        )
+    ax[0].set_ylabel(E_eps)
+    # ax[0].set_xticks(C)
+
+
+    df_c = {}
+    for c in C:
+        df_c[c] = filter_df_by(df_main, ['$c$'], c)
+
+    E_eps = r'$E/\sqrt{\epsilon L_f c}$'
+    for c, df in df_c.items():
[…]

### 2018-05-29 Python/make_fig_spect_energy_budg_c=100_N=3840.py

@@ -5,7 +5,7 @@ import os
 import h5py
 from fluidsim.base.output.spect_energy_budget import cumsum_inv
 
-from base import _index_where, _k_f, _eps, set_figsize, matplotlib_rc, epststmax
+from base import _index_where, _k_f, _eps, set_figsize, matplotlib_rc, epsetstmax
 from paths import paths_sim, exit_if_figure_exists
 
 
@@ -17,7 +17,7 @@ def fig2_seb(path, fig=None, ax=None, t_start=None):
 
     k_f = _k_f(sim.params)
     # eps = _eps(sim, t_start)
-    eps, ts, tmax = epststmax(path)
+    eps, E, ts, tmax = epsetstmax(path)
     if t_start is None:
         t_start = ts
     imin_plot = _index_where(f['times'][...], t_start)

### 2018-05-29 Python/make_fig_spectra_c=100_nh=7680.py

@@ -3,7 +3,7 @@ import pylab as pl
 import fluidsim as fls
 import h5py
 
-from base import _k_f, _eps, set_figsize, matplotlib_rc
+from base import _k_f, _eps, set_figsize, matplotlib_rc, _index_where
 from paths import paths_sim, exit_if_figure_exists
 
 
@@ -46,9 +46,17 @@ def fig7_spectra(path, fig, ax, t_start):
             eps ** (5. / 9) *
             k_f ** (4. / 9))
 
-    ax.plot(kh / k_f, E_tot / norm, 'k', linewidth=4, label='E')
-    ax.plot(kh / k_f, EK / norm, 'r', linewidth=2, label='$E_K$')
-    ax.plot(kh / k_f, EA / norm, 'b', linewidth=2, label='$E_A$')
+    kh_f = kh / k_f
+    ax.plot(kh_f, E_tot / norm, 'k', linewidth=4, label='E')
+    ax.plot(kh_f, EK / norm, 'r', linewidth=2, label='$E_K$')
+    ax.plot(kh_f, EA / norm, 'b', linewidth=2, label='$E_A$')
+    
+    s1 = slice(_index_where(kh_f, 2), _index_where(kh_f, 100))
+    s2 = slice(_index_where(kh_f, 30), _index_where(kh_f, 200))
+    ax.plot((kh_f)[s1], 0.7 * (kh_f ** -2 / norm)[s1], 'k-', linewidth=1)
+    ax.text(10, 0.055, '$k^{-2}$')
+    ax.plot((kh_f)[s2], (kh_f ** -1.5 / norm)[s2], 'k-', linewidth=1)
+    ax.text(70, 1.5, '$k^{-3/2}$')
     ax.set_xscale('log')
     ax.set_yscale('log')
 
@@ -59,14 +67,18 @@ def fig7_spectra(path, fig, ax, t_start):
     ax.set_ylim([lin_inf, lin_sup])
 
     ax.set_xlabel('$k/k_f$')
-    ax.set_ylabel(r'$E(k)/(k^{-2}c^{1/3}\epsilon^{5/9}k^{4/9}_f$')
+    ax.set_ylabel(r'$E(k)/\left(k^{-2}c^{1/3}\epsilon^{5/9}k^{4/9}_f\right)$')
     ax.legend()
+    fig.tight_layout()
 
 
 if __name__ == '__main__':
     matplotlib_rc()
     path_fig = exit_if_figure_exists(__file__)
[…]

### 2018-05-29 Python/paths.py

@@ -13,7 +13,7 @@ from fluiddyn.io.redirect_stdout import stdout_redirected
 
 import fluidsim as fls
 
-from base import _eps, _t_stationary, _k_d, _k_f, _k_diss, epststmax
+from base import _eps, _t_stationary, _k_d, _k_f, _k_diss, epsetstmax
 
 
 def get_pathbase():
@@ -58,7 +58,7 @@ pd_columns = [
     r'$n$', r'$c$', r'$\nu_8$', r'$f$', r'$\epsilon$', r'$\frac{k_{diss}}{k_f}$', 
     r'$F_f$', r'$Ro_f$', r'$Bu$',
     # '$\min h$', r'$\frac{\max |\bf u|}{c}$',
-    EFR,
+    EFR, r'$E$',
     '$t_{stat}$', r'$t_{\max}$', 'short name'
 ]
 
@@ -74,7 +74,7 @@ def pandas_from_path(p, key, as_df=False):
     kd_kf = _k_diss(params) / kf
     # ts = _t_stationary(path=p)
     # eps = _eps(t_start=ts, path=p)
-    eps, ts, tmax = epststmax(p)
+    eps, E, ts, tmax = epsetstmax(p)
     efr = params.preprocess.init_field_const
     Fr = (eps / kf) ** (1./3) / c
     try:
@@ -88,7 +88,7 @@ def pandas_from_path(p, key, as_df=False):
     data = [nh, c, params.nu_8, params.f, eps, kd_kf,
          Fr, Ro, Bu,
          # minh, maxuc,
-         efr,
+         efr, E,
          ts, tmax, key
         ]
     if as_df:

### 2018-09-20 Python/base.py
Ratio struct functions

@@ -11,7 +11,7 @@ from fluiddyn.util.paramcontainer import ParamContainer
 from fluiddyn.output import rcparams
 from fluidsim.solvers.sw1l.output.spatial_means import SpatialMeansSW1L
 
-from _try_dask_strfunc import strfunc_from_pdf5
+from _try_dask_strfunc import strfunc_from_pdf3 as strfunc_from_pdf
 
 
 DPI = 300
@@ -245,7 +245,7 @@ def epststmax_stepinfo(path):
     return eps_stat, time_stat, time[-1]
 
 def _rxs_str_func(
-    sim, order, tmin, tmax, delta_t, key_var, cache=True
+    sim, order, tmin, tmax, delta_t, key_var, cache=True, force_absolute=False
 ):
     np = pl
     self = sim.output.increments
@@ -302,8 +302,9 @@ imin = {3:8d} ; imax = {4:8d} ; delta_i = {5:8d}'''.format(
             pdf_var, values_inc_var, nb_rx_to_plot = self.load_pdf_from_file(
                 tmin=tmin, tmax=tmax, key_var=key)
 
-            absolute = (o % 2 == 0) # Use absolute values if order is even
-            So_var_dict[key_order] = strfunc_from_pdf5(
+            absolute = True if force_absolute else (o % 2 == 0) # Use absolute values if order is even
+
+            So_var_dict[key_order] = strfunc_from_pdf(
                 rxs,
                 pdf_var, values_inc_var, o, absolute=absolute)
 

### 2018-09-20 Python/make_fig_ratio_strfct.py

@@ -11,13 +11,12 @@ def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000, de
 
     key_var = ['ux', 'uy']
     rxs, So_var_dict, deltax = _rxs_str_func(
-        sim, order, tmin, tmax, delta_t, key_var)
+        sim, order, tmin, tmax, delta_t, key_var, force_absolute=True)
 
     ax1.set_xlabel('$r_x/L_f$')
     ax1.set_ylabel('$R_p(r)$')
 
     # ax1.set_title('Ratio of longitundinal and transverse struct. functions')
-    ax1.hold(True)
     ax1.set_xscale('log')
     ones = pl.ones(rxs.shape)
     shock_model = {0: 1.,
@@ -38,15 +37,17 @@ def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000, de
                  linewidth=2, label='$R_{:.0f}$'.format(o))
         ax1.plot(rxs / L_f, ones * shock_model[int(o)], color2)
 
-    ax1.set_ylim([0., 10.])
+    ax1.set_xlim([0.002, 2.])
+    ax1.set_ylim([0., 11])
     ax1.legend()
 
 
 if __name__ == '__main__':
-    matplotlib_rc()
-    path_fig = exit_if_figure_exists(__file__)
+    matplotlib_rc(10)
+    path_fig = exit_if_figure_exists(__file__, '.pdf')
     set_figsize(10, 6)
     fig, ax = pl.subplots()
     fig11_ratio_struct(
         paths_sim['noise_c20nh7680Buinf'], fig, ax, pl.arange(2, 7), tmin=10)
+    fig.tight_layout()
     pl.savefig(path_fig)

### 2018-09-20 Latex/section_wave_cascade_f=0.tex
Start to include figures in the pdf file.
Rename and improve figures
Change width in Latex to equivalent in inches
Start making notebooks
Include figures in the article + add todo to README.rst

@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
+\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spect_energy_budg_c=100_N=3840}}
 \caption{Spectral energy fluxes averaged over a long simulation for $c
@@
 \begin{figure}
-% \centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
+\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_Kolmo_c=20_N=3840}}
 \caption{
@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
+\centerline{
+\includegraphics[width=3.15in]{../Old/Figs/fig_spatiotempspectra_c20_Nh3840}}
 \caption{Spatio-temporal spectra of KE (dark lines) and APE (light
@@
 \begin{figure}
-% \centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_spectra_c=100_nh=7680}}
 \caption{Compensated spectra
@@
 \begin{figure}
-\setlength{\halfwidth}{69mm}
+% \setlength{\halfwidth}{2.72in}
+\centerline{\includegraphics[width=5.20in]{../Pyfig/fig_phys_fields_wave}}
 % \centerline{
@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
-% }
+\centerline{\includegraphics[width=\halfwidth]{../Pyfig/fig_ratio_strfct}}
 \caption{
@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_flatness}
-% }
+\centerline{\includegraphics[width=5.12in]{../Pyfig/fig_flatness}}
 \caption{ Flatness of the longitudinal and transverse increments for

### 2018-09-20 Python/make_fig_Kolmo.py
Improve combined flux struct func figsize

@@ -86,9 +86,9 @@ def fig3_struct(path, fig, ax1, tmin=0, tmax=1000):
 
     ax1.axhline(1., color='k', ls=':')
     # ax1.plot(rxs, pl.ones(rxs.shape), 'k:', linewidth=1)
-    ax1.set_xlim([None, 1.5])
-    ax1.set_ylim([-0.05, 1.1])
-    ax1.legend() #loc=1)
+    ax1.set_xlim([None, 2])
+    ax1.set_ylim([-0.1, 1.1])
+    ax1.legend(loc=8)
 
 
 if __name__ == '__main__':

### 2018-09-20 Python/make_fig_flux_struct_combined.py

@@ -11,10 +11,9 @@ from make_fig_Kolmo import fig3_struct
 
 
 if __name__ == '__main__':
-    matplotlib_rc(fontsize=12)
+    matplotlib_rc(fontsize=9)
     path_fig = exit_if_figure_exists(__file__, '.pdf')
-    set_figsize(16, 6)
-    fig, ax = pl.subplots(1, 2)
+    fig, ax = pl.subplots(1, 2, figsize=(7, 3))
     run = 'noise_c20nh3840Buinf'
     fig2_seb(paths_sim[run], fig, ax[0], t_start=20)
     fig3_struct(paths_sim[run], fig, ax[1], tmin=20, tmax=75)

### 2018-09-20 Python/make_fig_spect_energy_budg.py

@@ -48,7 +48,7 @@ def fig2_seb(path, fig=None, ax=None, t_start=None):
     ax.plot(khE, PiEK, 'r', linewidth=2, label=r'$\Pi_K$')
     ax.plot(khE, PiEA, 'b', linewidth=2, label=r'$\Pi_A$')
 
-    ax.set_ylim([-0.05, 1.1])
+    ax.set_ylim([-0.1, 1.1])
     ax.legend()
 
 

### 2018-09-20 Latex/section_wave_cascade_f=0.tex
Include combined figure in latex

@@
 \begin{figure}
-\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spect_energy_budg_c=100_N=3840}}
-\caption{Spectral energy fluxes averaged over a long simulation for $c
+\centerline{\includegraphics[width=\linewidth]{../Pyfig/fig_flux_struct_combined}}
+\caption{(Left) Spectral energy fluxes averaged over a long simulation for $c
 = 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
-and plotted versus $k/k_f$.  }
+and plotted versus $k/k_f$.
+(Right)
+Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo})
+averaged over a long simulation for $c = 20$ and $n = 3840$.
+%
+The structure functions are normalized by $4 \eps_q r$.
+%
+Black thick line, $\mean{ \delta J_L|\delta \uu|^2 }
++ c^2\mean{\delta u_L(\delta h)^2}$;
+light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
+dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
+%
+The dotted straight line shows $4 \eps_q r$,
+where $\eps_q$ is the quadratic energy dissipation rate.
+}
 \label{fig_seb}
@@
 
-\begin{figure}
-\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_Kolmo_c=20_N=3840}}
-\caption{
-Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo})
-averaged over a long simulation for $c = 20$ and $n = 3840$.
-%
-The structure functions are normalized by $4 \eps r$.
-%
-Black thick line, $\mean{ \delta J_L|\delta \uu|^2 }
-+ c^2\mean{\delta u_L(\delta h)^2}$;
-light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
-dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
-%
-The dotted straight line shows $4 \eps_q r$,
-where $\eps_q$ is the quadratic energy dissipation rate.
-}
-\label{fig_Kolmo}
-\end{figure}
-
-Figure~\ref{fig_Kolmo} shows the quantity $\mean{\delta J_L|\delta
+Figure~\ref{fig_seb} also shows the quantity $\mean{\delta J_L|\delta
 \uu|^2 } + c^2\mean{\delta u_L(\delta h)^2 }$ (black thick line)

### 2018-09-24 Python/paths.py
Cache dataframes

@@ -146,3 +146,7 @@ def exit_if_figure_exists(scriptname, extension='.png', override_exit=False):
     else:
         print('Making Figure {}.. '.format(figname))
         return figpath
+
+
+def load_df(name="df_w"):
+    return pd.read_csv(f"dataframes/{name}.csv", index_col=0)

### 2018-10-16 Latex/ArticleNew.tex
First revision by Erik

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997 Cambridge University Press

\NeedsTeXFormat{LaTeX2e}

\documentclass{jfm}
%\documentclass[referee]{jfm} %for double spaced output for submission

\usepackage{graphicx}
\usepackage{natbib}

\usepackage{color}
\usepackage{soul}
\usepackage{booktabs}
\pdfoptionpdfminorversion 4

% \pdfcompresslevel0

% See if the author has AMS Euler fonts installed: If they have, attempt2
% to use the 'upmath' package to provide upright math.
\ifCUPmtlplainloaded \else
  \checkfont{eurm10}
  \iffontfound
    \IfFileExists{upmath.sty}
      {\typeout{^^JFound AMS Euler Roman fonts on the system,
                   using the 'upmath' package.^^J}%
       \usepackage{upmath}}
      {\typeout{^^JFound AMS Euler Roman fonts on the system, but you
                   dont seem to have the}%
       \typeout{'upmath' package installed. JFM.cls can take advantage
                 of these fonts,^^Jif you use 'upmath' package.^^J}%
       \providecommand\upi{\pi}%
      }
  \else
    \providecommand\upi{\pi}%
  \fi
\fi

% See if the author has AMS symbol fonts installed: If they have, attempt
% to use the 'amssymb' package to provide the AMS symbol characters.

\ifCUPmtlplainloaded \else
  \checkfont{msam10}
  \iffontfound
    \IfFileExists{amssymb.sty}
      {\typeout{^^JFound AMS Symbol fonts on the system, using the
                'amssymb' package.^^J}%
       \usepackage{amssymb}%
       \let\le=\leqslant  \let\leq=\leqslant
       \let\ge=\geqslant  \let\geq=\geqslant
      }{}
  \fi
\fi

% See if the author has the AMS 'amsbsy' package installed: If they have,
% use it to provide better bold math support (with \boldsymbol).

\ifCUPmtlplainloaded \else
  \IfFileExists{amsbsy.sty}
    {\typeout{^^JFound the 'amsbsy' package on the system, using it.^^J}%
     \usepackage{amsbsy}}
    {\providecommand\boldsymbol[1]{\mbox{\boldmath $##1$}}}
\fi

%%% Example macros (some are not used in this sample file) %%%

% For units of measure
\newcommand\dynpercm{\nobreak\mbox{$\;$dyn\,cm$^{-1}$}}
\newcommand\cmpermin{\nobreak\mbox{$\;$cm\,min$^{-1}$}}

% Various bold symbols
\providecommand\bnabla{\boldsymbol{\nabla}}
\providecommand\bcdot{\boldsymbol{\cdot}}
\newcommand\biS{\boldsymbol{S}}
\newcommand\etb{\boldsymbol{\eta}}

% For multiletter symbols
\newcommand\Real{\mbox{Re}} % cf plain TeX's \Re and Reynolds number
\newcommand\Imag{\mbox{Im}} % cf plain TeX's \Im
\newcommand\Rey{\mbox{\textit{Re}}}  % Reynolds number
\newcommand\Pran{\mbox{\textit{Pr}}} % Prandtl number, cf TeX's \Pr product
\newcommand\Pen{\mbox{\textit{Pe}}}  % Peclet number
\newcommand\Ai{\mbox{Ai}}            % Airy function
\newcommand\Bi{\mbox{Bi}}            % Airy function

% For sans serif characters:
% The following macros are setup in JFM.cls for sans-serif fonts in text
% and math.  If you use these macros in your article, the required fonts
% will be substitued when you article is typeset by the typesetter.
%
% \textsfi, \mathsfi   : sans-serif slanted
% \textsfb, \mathsfb   : sans-serif bold
% \textsfbi, \mathsfbi : sans-serif bold slanted (doesnt exist in CM fonts)
%
% For san-serif roman use \textsf and \mathsf as normal.
%
\newcommand\ssC{\mathsf{C}}    % for sans serif C
\newcommand\sfsP{\mathsfi{P}}  % for sans serif sloping P
\newcommand\slsQ{\mathsfbi{Q}} % for sans serif bold-sloping Q

% Hat position
\newcommand\hatp{\skew3\hat{p}}      % p with hat
\newcommand\hatR{\skew3\hat{R}}      % R with hat
\newcommand\hatRR{\skew3\hat{\hatR}} % R with 2 hats
\newcommand\doubletildesigma{\skew2\tilde{\skew2\tilde{\Sigma}}}
%       italic Sigma with double tilde

% array strut to make delimiters come out right size both ends
\newsavebox{\astrutbox}
\sbox{\astrutbox}{\rule[-5pt]{0pt}{20pt}}
\newcommand{\astrut}{\usebox{\astrutbox}}

\newcommand\GaPQ{\ensuremath{G_a(P,Q)}}
\newcommand\GsPQ{\ensuremath{G_s(P,Q)}}
\newcommand\p{\ensuremath{\partial}}
\newcommand\tti{\ensuremath{\rightarrow\infty}}
\newcommand\kgd{\ensuremath{k\gamma d}}
\newcommand\shalf{\ensuremath{{\scriptstyle\frac{1}{2}}}}
\newcommand\sh{\ensuremath{^{\shalf}}}
\newcommand\smh{\ensuremath{^{-\shalf}}}
\newcommand\squart{\ensuremath{{\textstyle\frac{1}{4}}}}
\newcommand\thalf{\ensuremath{{\textstyle\frac{1}{2}}}}
\newcommand\Gat{\ensuremath{\widetilde{G_a}}}
\newcommand\ttz{\ensuremath{\rightarrow 0}}
\newcommand\ndq{\ensuremath{\frac{\mbox{$\partial$}}{\mbox{$\partial$} n_q}}}
\newcommand\sumjm{\ensuremath{\sum_{j=1}^{M}}}
\newcommand\pvi{\ensuremath{\int_0^{\infty}%
  \mskip \ifCUPmtlplainloaded -30mu\else -33mu\fi -\quad}}

\newcommand\etal{\mbox{\textit{et al.}}}
\newcommand\etc{etc.\ }
\newcommand\eg{e.g.\ }

\newcommand{\uu}{\textbf{u}}
\newcommand{\xx}{\textbf{x}}
\newcommand{\kk}{\textbf{k}}
\newcommand{\JJ}{\textbf{J}}
\newcommand{\rr}{\textbf{r}}
\newcommand{\ff}{\textbf{f}}
\newcommand{\FF}{\textbf{F}}
\newcommand{\baa}{\textbf{a}}
\newcommand{\bb}{\textbf{b}}
\newcommand{\NN}{\textbf{N}}

\newcommand{\eps}{\varepsilon}

\newcommand{\ErtelPV}{\mathcal{Q}}

\newcommand{\fdiss}{f_{\mbox{\scriptsize diss}}}

\newcommand{\D}{\mbox{D}}

\newcommand{\eez}{\boldsymbol{e_z}}
\newcommand{\scalarprod}[2]{\big( #1 \, , \ #2 \big)_{\kk}}

\newcommand{\mean}[1]{\langle #1 \rangle}

\newcommand{\meane}[1]{\langle #1 \rangle}
% \newcommand{\meane}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}e}}}

\newcommand{\meanx}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}\mbox{\scriptsize$\xx$}}}}

\newcommand{\meant}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}\theta}}}

\newcommand{\means}[1]{{\langle #1 \rangle_{\hspace{-0.4mm}s}}}

\newcommand{\shocks}{ {\mbox{\tiny shocks}} }

\newcommand{\kmax}{k_{\mbox{\scriptsize max}}}
\newcommand{\kdiss}{k_{\mbox{\scriptsize diss}}}

\newcommand{\mA}{\mathcal{A}}

\newlength{\halfwidth}
\setlength{\halfwidth}{2.6in}

\newcommand{\PA}[1]{{\color{green}#1}}

\newcommand{\Add}[1]{{\color{blue}#1}}
% \newcommand{\Add}[1]{#1}
\newcommand{\Remove}[1]{{\color{red}\st{#1}}}
% \newcommand{\Remove}[1]{}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\title[Shallow water wave turbulence]%
{ Shallow water wave turbulence}

\author[P. Augier, A.V. Mohanan and E. Lindborg]%
{Pierre Augier$^{1}$,   A. V. Mohanan$^{2}$ 
and Erik Lindborg$^2$ \ns }

\affiliation{$^2$ KTH Mechanics,
SE-100 44 Stockholm, Sweden\\[\affilskip]
$^1$ LEGI, BP53,
38041 Grenoble Cedex, France}

\pubyear{2013}
\volume{???}
\pagerange{???--???}
% Do not enter received and revised dates. These will be entered by
% the editorial office.
\date{?; revised ?; accepted ?. - To be entered by editorial office}
%\setcounter{page}{1}
\begin{document}

\maketitle

% \baselineskip 8mm
\begin{abstract}
The dynamics of irrotational shallow water wave turbulence forced in large scales
and dissipated  at small scales is investigated.
First, we derive the shallow water analogue of the `four-fifths law' of three-dimensional turbulence for a third order structure function involving velocity and displacement increments.
Using this relation and assuming that the flow is dominated by shocks we develop a simple model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ \eps $ is the mean dissipation rate and $ d $ the mean distance between the shocks, and that the
$ p $:th order displacement and velocity structure functions scale as
$ (\eps d)^{p/3} r/d $, where $ r $ is the separation. 
Then we carry out a series of forced simulations with resolutions up to $7680^2$, varying the Froude number,  $F_{f} = \eps^{1/3}  / ck_f^{1/3} $, where $ k_f $  is the forcing wave number and $c$ is the wave speed.
In all simulations a stationary state is reached  in which there is a constant spectral energy flux and equipartition between kinetic and potential energy in the constant flux range. The third order structure function relation is satisfied with a high degree of accuracy. 
Mean energy is found to scale as $ E \sim \sqrt{\epsilon c/k_f} $,  and is also dependent on resolution, indicating that shallow water wave turbulence does not fit into the paradigm of a Richardson-Kolmogorov cascade.  
In all simulations shocks develop, displayed as long thin bands of negative divergence in flow visualizations. The mean distance between the shocks is found to scale  as $ d \sim F_f^{1/2}/k_f $. Structure functions of second and higher order are found to scale in good agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow 0 $, shocks will become denser and weaker and finally disappear for a finite Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small, shocks will prevail if the Reynolds number is sufficiently large.

\end{abstract}

% \begin{keywords}
% \end{keywords}

\section{Introduction}

The shallow water (SW) equations  have been widely used to study basic
mechanisms occurring in geophysical flows \cite[see for
example][]{VallisLIVRE2006}.
%
The equations are based on the hydrostatic approximation which is
extremely well satisfied for a very wide range of scales in the oceans
and in the atmosphere.  They also rely on a stronger hypothesis
regarding the density stratification.  The fluid is assumed to be
structured in a limited number of thin homogeneous layers, which leads
to equations involving only two-dimensional operators. The two-layer
SW equations capture the baroclinic instability which is of
primary importance for the dynamics of the oceans and of the
atmosphere \cite[]{VallisLIVRE2006, Wirth2013}.
%
The single layer SW equations are very similar to
the two-dimensional compressible Navier-Stokes equations.  The
equations do not capture baroclinic instability but they constitute 
one of the simplest hydrodynamic models with coexisting eigenmodes of
the linearized operator with zero linear frequency and with finite
non-zero linear frequency, $\omega  \pm\sqrt{f^2 + c^2
k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
= |\kk|$ the wave number.
%

For geophysical applications, it is convenient to consider the limit
for which the linear wave frequency  is much larger than the
characteristic nonlinear frequency $ U k$, where $U$ is a
characteristic velocity.  In this limit, one can obtain a quasi-geostrophic
single layer SW model, i.e. derive self-consistent evolution
equations for a zero frequency variable, the Charney potential
vorticity, which is totally decoupled from the fast waves.
%
For finite rotation and wave speed, there are slow balanced motions,
which are associated with relatively weak non-zero linear frequency
modes and there is only a weak
interaction between waves and the balanced motions.
%
Due to their relative simplicity, the SW equations have
been used to study issues like the projection on the balanced manifold
\cite[]{Lorenz1980, MohebalhojehDritschel2000} and the production of
waves by balanced flows \cite[]{FargeSadourny1989,
LahayeZeitlin2012,Vanneste2013}. 
In this study, we consider the
same equations in order to address a related but different issue.

Balanced flows have a dynamics which is very similar to
two-dimensional turbulence, with an upscale energy cascade. %
Small scale energy dissipation vanishes in the limit of zero
viscosity.
%
In contrast to this, statistical mechanics indicates that wave energy
should be transferred towards small scales \cite[]{Warn1986}.
Numerical simulations have shown that long waves lose their energy by
transferring it to shorter waves \cite[]{Sadourny1975,
FargeSadourny1989, YuanHamilton1994}.  The mechanism of a wave cascade
has been proposed to explain the attraction towards the balanced flows
\cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
statistically stationary shallow-water flows can be obtained forcing
quasi-geostrophic modes at large scales and with dissipation only at
small scales.
%
They propose that the $k^{-5/3}$ spectra that are observed at the
atmospheric meso-scales  \cite[]{NastromGage1985,LiLindborg2018}
and reproduced by some atmospheric models based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008} could be reproduced by the one-layer
shallow-water model by a downscale energy cascade of waves.

However, few studies have investigated the dynamics of the downscale
energy cascade of waves in SW models.
%
Most numerical studies have investigated decaying flows and have not
focused on the cascade \cite[]{FargeSadourny1989,
LarichevMcWilliams1991, SpallMcWilliams1992,
PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
%
Moreover, there are strong discrepancies between different numerical
results and between these results and available theoretical results.
%
\cite{FargeSadourny1989} reported spectra scaling as $k^{-4}$
whereas those shown by \cite{LahayeZeitlin2012} scale as $k^{-6}$.

Some predictions are based on the weak wave turbulence formalism
\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}.  In the case of
inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the
exact solutions of the kinetic equation corresponding to a constant
downscale energy flux is associated with a spectrum scaling as $E(k)
\sim  k^{-8/3}$, while \cite{ZakharovSagdeev1970} 
used weak turbulence formalism to derive a spectrum of the form $ E(k) \sim  k^{-3/2} $ for acoustic turbulence. This prediction is of particular interest, since the aqoustic equations and the SW equations are identical when a first order expansion is made in
density or displacement pertubations. It may be questioned, however,  that weak turbulence formalism is applicable to acoustic and SW wave turbulence, no matter how weak the nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970} and 
\cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in the same direction have
the same velocity and interact strongly, which leads to the
formation of shocks.  In this case, the weak wave turbulence
formalism is unable to give valuable results.  Such sharp and long
structures have been observed in many simulations
\cite[]{FargeSadourny1989, PolvaniMcWilliamsSpallFord1994,
LahayeZeitlin2012} but their effects are not well understood.
%
As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by shocks will scale as $ k^{-2} $, a 
 prediction which has been confirmed by a great number of simulations of Burgers equation \cite[for a review, see ] []{Frisch2001}.
 The shocks also lead to very strong intermittency, as demonstrated by
\cite{BouchaudMezardParisi1995} and \cite{WeinanKhaninMazelSinai1997}
for Burgers turbulence.
%
\cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks 
and reported spectra scaling as $ k^{-2} $.
\cite{YuanHamilton1994} carried out
forced dissipative simulations of the SW equations showing similar spectra. 
However, the resolution in both these studies was quite coarse, ($386^2$
and $101^2$ grid points, respectively) so that the scaling range was very
narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
type of strongly anisotropic forcing with waves in only one
direction while \cite{YuanHamilton1994} forced in geostrophic modes
which severely complicates the interpretation.

The dynamics of waves in complex SW flows is not well
understood.  Even wave dynamics in absence of a balanced flow is not well
understood. A statistically stationary wave cascade has never been
simulated at high resolutions.
%
Is it possible to obtain a statistically stationary state in the very
fast wave regime, and how does the mean energy in this hypothetical
regime depends on the forcing and the wave speed?  
% What is the slope of 
How do energy spectra scale with the 
input parameters? From a theoretical point of view, the most interesting issue is, perhaps,  the nature of the dynamics in the limit of weak nonlinearities. Will shocks prevail in this limit?
%
Such questions are still open and straightforward simulations may
provide the answers.
In this paper, we investigate the dynamics of single layer SW wave turbulence 
forced  at large scales by means of 
simulations with up the  $7680^2$ grid points.
%
Before presenting the results of the simulations we develop some theory.
%

\section{Theory}
\label{section_basic_theory}
\input{section_basic_theory}

\label{section_advanced_theory}
\input{section_advanced_theory}

\section{Simulations}
\label{section_methods}
\input{section_methods}

%\label{section_wave_cascade_f=0}
%\input{section_wave_cascade_f=0}

%\section{Effects of global rotation}
%\label{section_rotation}
%\input{section_rotation}

\section{Conclusions}

We have carried out a theoretical and numerical investigation of SW wave turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the `four-fifths' law of Kolmogorov turbulence. Using this relation and straightforward statistical and geometrical arguments we developed a simple shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ d $ is the mean distance between the shocks, and that the $ p $:th order structure function above a certain minimum will scale as $ (\epsilon d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative simulations, varying the Froude number and the resolution. In all simulations, a statistically stationary state were reached and in all simulations we observed shocks. The flow variables in each Fourier mode was found to evolve as a linear wave, with equipartition between APE and KE over a period. The third order structure function relation was fulfilled with a high degree of accuracy. From the simulations we made two interesting observations that fall outside the predictive range of the model. The first observation  was  that mean energy in the stationary state approximately scales as (\ref{MeanEnergy}), suggesting that the normalised dissipation (\ref{Dissipation}) will go to zero both in the limit of small viscosity and large  wave speed. This is different from three dimensional Kolmogorov turbulence as well as strongly stratified turbulence, where, in both cases, dissipation is finite in the limit of small viscosity, and in the latter case also is independent of the degree of stratification. This observation suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade. The second observation we made was that the mean distance between the shocks scales as $ c^{-1/2} $, if the other parameters are held constant. As we increased $ c $, the shocks were thus becoming denser. Using this observation we tested the shock model by plotting the normalised and compensated structure functions of different orders. Generally we found that there was a quite good agreement between the simulation results and the model predictions, becoming better with decreasing  wave speed and increasing resolution.

Combining the model and the observations we can get a quite good picture of the dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow  0 $.  
The picture may become more vivid if we say `wave breaking' were we previously have talked about shock formation, and also say
`wave lengths' were we previously have talked about length scales. We identify the longest wave length, $ \lambda_l $,  with the forcing scale $  L_f $ and the breaking wave length, $ \lambda_b $, with the mean distance, $ d $, between the shocks. There are two dynamically different  regimes to consider, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $. We first consider the latter, whose width scales  $ \lambda_{l} /\lambda_b \sim F_f^{-1/2} $. Identifying the amplitude of the breaking waves with the shock amplitude, $ (\eps d)^{1/3} $, we find that the ratio between the amplitude of the longest waves and the breaking waves scales as $ E^{1/2}/(\eps d)^{1/3} \sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute  $ n $ with a Reynolds number to some power.  Thus, for small $ F_f $ and large Reynolds number the longest waves are not directly influenced by wave breaking. The Reynolds number dependence of the amplitude ratio makes it unlikely that a general similarity theory can be easily formulated for this range. Therefore, predictions from weak turbulence theory \cite[for example][]{ZakharovSagdeev1970}
are not likely to hold for this range, although it is not directly influenced by wave breaking. The exact values of the power law exponents in the argument, are, of course, not important. As for the short wave regime, the width scales as $  \lambda_b /\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number. As $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that breaking will disappear. On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large. Apparently, a necessary condition for wave breaking is that
\begin{equation} \label{NC}
\frac{\lambda_b}{\delta x} \sim \frac{\lambda_l F_f^{1/2}}{\delta x} \gg 1 \, .
\end{equation}
It may be interesting to note that the single point limit of the flatness factors shown if figure (\ref{fig_flatness}) scales as the ratio $ \lambda_b/\delta x $ and that this limit is equal to the flatness factor of velocity derivatives. So the condition (\ref{NC}) means that the flatness factor of velocity derivatives must be much larger than unity. Assuming that this is not only a necessary but also sufficient condition, we would able to formulate under what condition wave breaking will take place in terms of a Froude number and a Reynolds number if we knew how the shock width $ \delta x $ scales with these parameters.
In setting up the simulations we assumed that it is sufficient to resolve the Kolmogorov scale, $ \eta = (\nu^{3} / \epsilon)^{1/4} $, or the corresponding scale, $ \eta_8 = (\nu_8^{3}/\epsilon) ^{1/22} $, when hyperviscosity is used. The results from the simulations seem to support this assumption, suggesting that $ \delta x $ can be identified as the Kolmogorov scale.  Assuming that this is correct and defining the Reynolds number as $ Re \equiv \lambda_l^{4/3}\epsilon ^{1/3} /\nu $, we can write the condition for wave breaking as
\begin{equation} \label{Condition} 
Re^{3/4} Fr^{1/2} \gg 1 \, .
\end{equation} 
However, a little bit of reflection may lead us to doubt that the shock width is equal to the Kolmogorov scale. The reason for this is that dissipation only occurs at the shocks.
Using Navier-Stokes viscosity and assuming that the shock width is the characteristic dissipation length scale, the mean energy dissipation rate can be estimated as
\begin{equation}
\eps \sim \nu \frac{\mid \Delta u \mid ^2}{\delta x ^2} \frac{L_s \delta x}{\cal{A}} \sim \nu \frac{ \;\;\;  (\epsilon \lambda_b)^{2/3} }{\delta x \lambda_b} \, ,
\end{equation} 
where we have used the estimate (\ref{Strength}) for the shock amplitude. Consequently we obtain
\begin{equation} \label{ShockWidth}
\delta x \sim \frac{\eta^{4/3}}{\lambda_b^{1/3}} \sim \frac{\eta^{4/3}}{\lambda_l^{1/3}} F_f^{-1/6} \, ,
\end{equation} 
where we have used the observed scaling law (\ref{MeanDistance}) for $ \lambda_b = d $. An analogous result is obtained if we instead use hyperviscosity.  The estimate (\ref{ShockWidth}) suggests that $ \delta x $ should become somewhat larger  with increasing $ c $, but very slowly, $ \delta x \sim c^{1/6} $.  It is difficult to judge from the simulations  if this is actually the case. In figure (\ref{fig_spectra_c40}) we see that the maximum of the bottleneck in the high wave number end of the spectra appears at a somewhat smaller wave number in the run with largest $ c $ as compared to the two other runs. We leave it as an open question whether this is a signature of a slowly increasing shock width with increasing $ c $. It is interesting to note that if (\ref{ShockWidth}) is used as the estimate of $ \delta x $ in (\ref{NC}) instead of the Kolmogorov scale, we actually obtain the same condition (\ref{Condition}).

The question that originally motivated this study was if SW wave turbulence can be used as a model for energy dissipation in the the atmosphere and the oceans. Undoubtedly, the answer to this question is negative and the reason for this is not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum which is not consistent with the observed $ k^{-5/3} $-spectrum. The main reason is that 
SW wave turbulence is  a far too inefficient agent of dissipation. Since the Reynolds number of geophysical flows is extremely large and the stratification is strong, the  relation (\ref{Dissipation}) implies that dissipation would be absent in the interior of the atmosphere and the oceans with SW turbulence as the responsible agent. This not what we observe.

Although the answer to the question that originally motivated this study is negative, it may lead us or some other investigators to pursue another interesting research direction. As pointed out in the introduction, the acoustic equations are to the lowest order expansion in density pertubations identical to the SW equations. This study may therefore give important clues to the long standing problem of acoustic turbulence, in two and three dimensions. A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), apart from the constant. In three dimensions we find
\begin{equation}
\meane{ |\delta \uu|^2 \delta J_L } 
+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \varepsilon r. \label{eq_Kolmo3}
\end{equation}
 In the case of acoustic turbulence $ \delta h $ should  be interpreted as a density increment rather than a displacement increment.  If shocks in  three dimensions are assumed to form as  smooth surfaces rather than smooth lines, then the mean distance, $ d $, between the shocks will appear in the model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total  shock area and $ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as $ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will form in a similar way as in two dimensions. If they do, the most interesting questions are if the mean energy and the mean distance between the shocks scale in a similar way in three dimensions as in two dimensions. Simulations or experiments of acoustic turbulence may provide answers to these questions -- answers that will lead to further clues to a theoretical understanding of acoustic turbulence. 
 We hope that the present study will stimulate research in this direction.

%\appendix

%\section{Kinetic energy dissipation and forcing rates}
%\label{app_comp}
%\input{appendix_dissip_forcing}

\bibliographystyle{jfm}
\bibliography{biblio}

\end{document}

### 2018-10-16 Latex/appendixR.tex
First revision by Erik

In this appendix,  we show that \begin{equation}  \lim_{r \rightarrow 0}  R_p (r) =  2p -1, \end{equation}
for an irrotational and isotropic velocity field, 
where  $ R_p (r ) $ is the ratio between the longitudinal and transverse structure functions of order $ p $, defined in (\ref{Ratio}).
We start by considering $ p = 2 $.   If $ u $ and $ v $ are the velocity component in the $ x $- and $ y $-directions, respectively, it is clear that
\begin{equation}
 \lim_{r \rightarrow 0}  R_2 (r) = \frac{\left \langle \frac{\partial u}{\partial x}  \frac{\partial u}{\partial x}  \right \rangle} {\left \langle \frac{\partial v}{\partial x}  \frac{\partial v}{\partial x}  \right \rangle} .
\end{equation} 
Since the velocity field is irrotational we can write it as $ {\bf u} = \bnabla \phi $, where $ \phi $ is the velocity potential. By statistical homogeneity we find
\begin{equation} \label{Tensor}
\left \langle \frac{\partial u_i}{\partial x_j}  \frac{\partial u_k}{\partial x_l}  \right \rangle = \left \langle  \frac{\partial ^2 \phi}{\partial x_i \partial x_j}  \frac{\partial ^2 \phi}{\partial x_k\partial x_l} \right  \rangle = 
\left \langle \phi \frac{\partial^4 \phi}{\partial x_i \partial x_j \partial x_k \partial x_l }\right \rangle 
\end{equation} 
The fourth order tensor on the left hand side of (\ref{Tensor}) is

### 2018-10-16 Latex/section_advanced_theory.tex
First revision by Erik

@@
-\subsection{Analysis of the wave energy cascade}
-
-\subsubsection{Formulation of the spectral energy budget for
-non-quadratic energy}
-
-In order to analyze the flux of energy, we derive the spectral energy
+In order to analyze the spectral flux of energy, we derive the spectral energy
 budget, i.e.\ the governing equations for spectral KE and APE
-functions.
-%
-This is not as straightforward as in incompressible turbulence since
-the expression of the kinetic energy $E_K = \JJ\cdot\uu/2$ is not
-quadratic.
-%
-In order to define the spectral KE function, we use the relation
+functions. This is not as straightforward as in incompressible turbulence since
+the expression of the kinetic energy  is not
+quadratic. To define the spectral KE function, we use the relation
 \begin{equation}
-\meanx{ E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
+\mean { E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
 \end{equation}
@@
 \end{equation}
-where $\Re$ denotes the real part, $\kk$ is the wave number and the
+and $\Re$ denotes the real part, $\kk$ is the wave number and the
 hat denotes the Fourier transform.
@@
 \begin{equation}
-E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2, 
+E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2.
 \end{equation}
-such as $\meanx{ E_K } = \sum_\kk E_K(\kk)$.
-%
-Similarly, the PE can be written as the sum over all wave numbers of
-the spectral PE function $E_P(\kk) = c^2 |\hat h|^2/2 = c^2
-\scalarprod{h}{h}/2$, where, by definition,
+Similarly, the APE can be written as the sum over all wave numbers of
+the spectral APE function 
 \begin{equation}
-\scalarprod{a}{b} \equiv \Re\{ \hat a(\kk)^* \hat b(\kk) \}.
+E_A(\kk) =  c^2 \scalarprod{\eta}{\eta}/2 \, .
 \end{equation}
-
-The equation for the spectral KE and PE functions can be written as
+The inviscid equation for the spectral KE and APE functions can be written as
 \begin{eqnarray}
-\p_t E_K(\kk) &=& T_K(\kk) + C_K(\kk),\\
-\p_t E_P(\kk) &=& T_P(\kk) - C_P(\kk),
+\p_t E_K(\kk) &=& T_K(\kk) - C (\kk),\\
+\p_t E_A(\kk) &=& T_A(\kk) + C (\kk),
 \end{eqnarray}
@@
 \begin{equation}
-C_K(\kk) 
-= -\scalarprod{\uu}{\bnabla E_P}/2 - c^2 \scalarprod{\JJ}{\bnabla h}/2,
+T_K(\kk) 
+= -\scalarprod{\bnabla \cdot \uu}{E_K} 
+-\scalarprod{\uu }{\bnabla E_K } \, ,
 \end{equation}
 \begin{equation}
-C_P(\kk) = c^2 \scalarprod{h}{hd} /2,
+T_A(\kk) = -c^2 \scalarprod{\bnabla \eta }{\JJ}- c^2\scalarprod{\eta}{\bnabla \cdot \JJ}  \, ,
 \end{equation}
+are the spectral transfer functions of KE and APE, respectively, and
 \begin{equation}
-T_P(\kk) = -c^2 \scalarprod{h}{\uu \cdot \bnabla h + hd/2}
+C (\kk) 
+= \scalarprod{\uu}{\bnabla E_P}
 \end{equation}
-and
-\begin{equation}
-T_K(\kk) 
-= -\scalarprod{\uu}{\uu \cdot \bnabla \JJ}/2
--\scalarprod{\JJ}{\uu \cdot \bnabla \uu}/2
--\scalarprod{\uu}{d\JJ}/2.
-\end{equation}
-The mean conversion from potential energy to kinetic energy can be
-computed from the two conversion spectral functions as $C = \sum_\kk
-C_K(\kk) = \sum_\kk C_P(\kk)$.
+is the spectral KE-APE conversion function.
+The spectral energy flux functions of KE and APE are defined as
+\begin{eqnarray}
+\Pi_K (k) = \sum_{| {\bf k}^{\prime} | > k} T_K ( {\bf k}^\prime ) \, , \;\;\;  \Pi_A (k) = \sum_{| {\bf k}^{\prime} | > k} T_A ( {\bf k}^\prime ) 
+\end{eqnarray}
 
-\subsubsection{Exact Kolmogorov law for irrotational flows}
+We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third order velocity structure function of incompressible isotropic turbulence.
+In the case of irrotational shallow water wave turbulence the analogous law contains a third order structure function involving both velocity and displacement increments.
+In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational.
+To derive the law it is convenient to start from the following equations
+\begin{eqnarray} \label{IRR}
+\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
+\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
+\p_t h   &=& -\bnabla \cdot \JJ \, ,
+\end{eqnarray}
+where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}).
+We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
+Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $.
+Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find
 
-As in incompressible homogeneous isotropic turbulence, an exact
-Kolmogorov law for irrotational flows can be derived.
-%
-It is convenient to start from the following form of the governing
-equations
-\begin{eqnarray}
-\p_t \uu &=& -\bnabla \cdot (|\uu|^2/2) - c^2 \bnabla h  
-- \zeta_a \eez \wedge \uu, \\
-\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
-\p_t h   &=& -\bnabla \cdot \JJ.
-\end{eqnarray}
-Assuming that the flow is irrotational and that there is no global
-rotation ($\zeta_a=0$), it can be shown that
 \begin{equation}
@@
 \end{eqnarray}
-We then assume homogeneity and take the ensemble average denoted by
-$\meane{}$.  The separation vector is noted $\rr = \xx' - \xx$.  For
+We then assume homogeneity and take the average denoted by
+$\meane{}$.   For
 every function $g(\xx, \xx')$, we have $\p_i' \meane{g} =
--\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We obtain
+-\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We thus obtain
 \begin{eqnarray}
@@
 %
-Using again homogeneity, we get
+Using homogeneity again, we get
 \begin{equation}
@@
 \end{equation}
-Using isotropy and integrating yield an exact Kolmogorov law for
-one-layer shallow water irrotational turbulence
+For separations that are considerably larger than dissipative scales of motion and considerably smaller than forcing scales a standard argument \cite[see for example][]{Frisch} gives that the left hand side is approximately equal to $ -8 \eps $, where $ \eps $ is the mean dissipation rate.
+It is interesting to note that a factor of $ 8 $ appears in the case when the velocity field is irrotational while a corresponding factor of $ 4 $ appears in the case when the velocity field is non-divergent.
+Using isotropy and integrating yield the Kolmogorov law for
+irrotational shallow water wave  turbulence
 \begin{equation}
@@
 \end{equation}
-where $\eps$ is the energy dissipation rate and $J_L \equiv
+where $J_L \equiv
 \JJ\cdot\rr / |\rr|$ and $u_L \equiv \uu\cdot\rr / |\rr|$ are
@@
 
-\subsection{Simple model for structure functions determined by a
-random set of shocks}
-\label{subsection_shock_model}
-
-\cite{BouchaudMezardParisi1995} and \cite{Kuznetsov2004} showed that
-the presence of discontinuities can strongly influence the statistics
-and in particular lead to very strong intermittency.
-%
-We now present an extremely simple model based on the assumption that
-shocks totally dominate the flow.  The structure functions are
-calculated by averaging increments over the total surface of the
-domain $\mA$.  Considering that the increments are produced only by
-discontinuity lines, we get
+We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
+The model is similar to the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation, although we derive it by using quite different arguments. 
+We consider a domain with total area  $ {\mA} $ occupied by shocks which we 
+consider as smooth lines. We denote the total length of all shocks by $ L_s $.  The mean distance between the shocks within the domain can be estimated as
+\begin{equation}
+d \simeq \frac{\mA} {L_s} .
+\end{equation} 
+A structure function of a flow variable is defined as the area average of increments  between two points separated by a distance $ r $.
+Assuming that the contribution from increments where the two points are not separated by a shock is negligible for higher order structure functions we obtain
 \begin{eqnarray}
 \meane{|\delta h|^p} 
-&=& \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p \nonumber\\
-&\simeq& \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
+=  \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p 
+ \simeq  \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
 \end{eqnarray}
@@
 vector $\rr$ %
-and $\Delta h (s)$ is the step in $h$ at a shock.
+and $\Delta h (s)$ is the shock displacement amplitude.
 %
 Assuming isotropy, the integral can be split and we get
-\begin{equation}
+\begin{equation} \label{StepH}
 \meane{|\delta h|^p} 
 \simeq 
-r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h (s)|^p}
-=
-r \frac{L_s}{\mA} \frac{2}{\pi} \means{|\Delta h (s)|^p},
+r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h |^p}
+\simeq  \frac{2}{\pi} \means{|\Delta h |^p} \frac{r}{d} ,
 \end{equation}
-where $\meant{}$ denotes the mean over $\theta$, %
-$L_s$ is the total length of the shocks in the domain %
-and $\means{}$ denotes the mean over all shocks.
+where $\meant{}$ is the mean over $\theta$
+and $\means{}$ is the mean over all shocks.
 
@@
 perpendicular to the shocks, which implies that the longitudinal and
-transverse increments are related by $\delta u_L = \delta u
+transverse increments can be written as  $\delta u_L = \delta u
 \sin\theta$, $\delta u_T = \delta u \cos\theta$.
@@
 Applying the same averaging method, we obtain
-\begin{equation}
+\begin{equation} \label{StepL}
 \meane{|\delta u_L|^p} 
 \simeq 
-r \frac{L_s}{\mA} 
 \meant{|\sin\theta|^{1+p}}
-\means{|\Delta u (s)|^p}
+\means{|\Delta u |^p} \frac{r}{d}
 \end{equation}
 and
-\begin{equation}
+\begin{equation} \label{StepT} 
 \meane{|\delta u_T|^p} 
 \simeq 
-r \frac{L_s}{\mA} 
 \meant{|\sin\theta||\cos\theta|^{p}}
-\means{|\Delta u (s)|^p},
+\means{|\Delta u |^p} \frac{r}{d},
 \end{equation}
-where $\Delta u (s)$ is the velocity step at a shock.
+where $\Delta u $ is the shock velocity amplitude.
 %
 These assumptions completely determine the ratio between the
-longitudinal and transverse structure functions, which can be
-analytically computed as
-\begin{eqnarray}
+longitudinal and transverse structure functions, which can be computed as
+\begin{eqnarray} \label{Ratio}
 R_p(r) \equiv \frac{\meane{|\delta u_L|^p}}{\meane{|\delta u_T|^p}} = 
@@
 giving the numerical values $R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
-
-Interestingly, for an isotropic and purely divergent flow ($\zeta =
-0$), the longitudinal and transverse second order structure functions
+Interestingly, for an isotropic and irrotational velocity field, the longitudinal and transverse second order structure functions
 are exactly related by $\meane{(\delta u_L)^2} = \p_r( r\meane{(\delta
-u_T)^2} )$ \cite[]{Lindborg2007jas}.
-%
-If we further assume than both second order structure functions follow
+u_T)^2} )$ \cite[]{Lindborg2007jas}. If we further assume than both second order structure functions follow
 the same scaling law $\meane{ (\delta u_L)^2} \propto \meane{ (\delta
 u_T)^2} \propto r^\alpha$, then we have $\meane{ (\delta u_L)^2} =
-(1+\alpha) \meane{ (\delta u_T)^2} $, which gives $ R_2 = 2
-\Leftrightarrow \alpha = 1$.
+(1+\alpha) \meane{ (\delta u_T)^2} $, which gives $ R_2 = 2 $ for 
+$  \alpha = 1$.  In the limit $ r \rightarrow 0 $ we have $ \alpha = 2 $ and $ R_2 = 3 $.
+%
 
-The shock model also provides predictions of the flatness factors of
-the velocity increments
-\begin{eqnarray}
+In order for (\ref{StepH}-\ref{StepT}) to match with the third order structure function relation (\ref{eq_Kolmo})  the shock amplitudes should scale as
+\begin{equation} \label{Strength}
+ | \Delta u | \sim | c \Delta h | \sim (\varepsilon d)^{1/3} \, ,
+\end{equation} 
+and the structure functions of order $ p $ will consequently scale as
+\begin{equation} \label{StrucFunc}
+\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (\varepsilon  d)^{p/3} \,  \frac{r}{d} \, .
+\end{equation} 
+Assuming that (\ref{StrucFunc}) is valid for second order moments and that the non-quadratic contribution to the KE spectrum is negligible the corresponding scaling law for the energy spectra reads
+\begin{equation} \label{Spectra}
+E_K(k)  \sim  E_A(k) \sim \varepsilon ^{2/3} d^{-1/3} k^{-2} \, .
+\end{equation} 
+The  model  provides the following predictions for the flatness factors of velocity increments
+\begin{eqnarray} \label{FL}
 F_L &=&  \frac{\meane{|\delta u_L|^4}}{\meane{|\delta u_L|^2}^2}
-= r^{-1} \frac{\means{|\Delta u|^4}}{\means{|\Delta u|^2}^2} 
-\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2},\\
+\propto 
+\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2} \frac{d}{r}   = \frac{9\pi}{15}  \frac{d}{r} \\ \label{FT}
 F_T &=&  \frac{\meane{|\delta u_T|^4}}{\meane{|\delta u_T|^2}^2} 
-= r^{-1} \frac{\means{|\Delta u|^4}}{\means{|\Delta u|^2}^2} 
-\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2},
+\propto
+\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2} =  \frac{9\pi}{10}  \frac{d}{r} 
 \end{eqnarray}
-and on the ratio of the two flatness factors, which is simply equal to
-$F_T/F_L = 1.5$ according to the model.
+The ratio between the two flatness factors is equal  to
+$F_T/F_L = 3/2$ according to the model.
+
+Being such a simple model it must have  limitations.
+First, it is obvious that  the model can  only be valid for separations  that fulfill the condition $ \delta x \ll r \ll d $,  where $ \delta x $ is the shock width.
+Second, the model cannot be valid for low order moments or structure functions.
+The minimum order for which the model may be valid is not easily determined.
+According to  \cite{BouchaudMezardParisi1995} structure functions of shock dominated turbulence of all orders $ p  \ge 1 $ scale linearly in $ r $.
+It is quite easily argued, however, that the shocks can not determine the scaling of the structure functions of order $ p=1 $.
+To see this, consider the first order moment of the absolute value of $ \delta u_L $. 
+The longitudinal velocity increment is always negative over a shock, that is to say that the difference of the projection of the velocity on the direction over which the shock is crossed is always negative.
+In a domain with periodic boundary conditions the mean value of $ \delta u_L $   is zero.
+The negative values of $ \delta u_L $ for separations where a shock is crossed must therefore be compensated by positive values for separations where no shock is crossed.
+There is no reason to believe that these values are all positive,  but they are only positive on average.
+Thus,
+$ \means{ |\delta u_L | } < \langle | \delta u_L | \rangle _{ns} $, where the left hand side is the mean value over all separations where a shock is crossed and the right hand side is the mean value over separations where no shock is crossed.
+Therefore, the model is not valid for first order moments.
+It may be conjectured that it is valid for
+second and higher order structure functions.

### 2018-10-16 Latex/section_basic_theory.tex
First revision by Erik

In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
surface can be written as  \cite[see for example][]{VallisLIVRE2006}
\begin{eqnarray} \label{UEq}
\p_t \uu + \uu\cdot \bnabla  \uu   
&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
\end{eqnarray}
where $\uu$ is the horizontal velocity, %
$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite. This can only be accomplished by permitting the term to be nonlinear in the flow variables. There are different forms of nonlinear terms that fulfill both conditions and it may be disputed which is the best one. However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfill any of these two conditions in a strict sense. Therefore, we will not discuss this matter further. The inviscid SW equations conserve a local
quantity along trajectories of the fluid particles, the Ertel
potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity. In this paper this conservation law will be of no relevance since we only consider
irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential. In a domain with no net fluxes through the boundaries the inviscid equations conserve total energy $ E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy. The latter can be split into three terms as \begin{equation}
E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2, 
\end{equation}
where the first term corresponds the potential energy of the state with no
surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}. As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
 The velocity potential and the displacement of the linearized inviscid SW equations both satisfy the wave equation,
\begin{equation}
\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
\end{equation}
with equipartition between KE and APE over a wave period in each Fourier mode.

### 2018-10-16 Latex/section_methods.tex
Article compiled with a Makefile (without figure).
Start to include figures in the pdf file.
Rename and improve figures
Change width in Latex to equivalent in inches
First revision by Erik

--- 2016-12-17 old/section_methods.tex
@@
-\subsection{Numerics}
-
-From a numerical point of view, it is convenient to solve for the
-eigenmodes of the linear operator $\hat q$ and $\hat a_\pm = \hat a
-/2 \pm \omega_l \hat d /(2i)$.
-%
-We thus consider the following modified governing equations
-\begin{eqnarray}
-\bigl( \p_t  + \fdiss(\kk) \bigl) \hat q  
-&=& \hat N_q  ,\label{eqqnum} \\
-\bigl( \p_t  + \fdiss(\kk) \pm  i \omega_l \bigl)  \hat a_\pm  
-&=& \hat N_{\pm} + \hat f_{\pm}, \label{eqapmnum}
-\end{eqnarray}
-where $\hat f_{\pm}$ are forcing terms and %
-$\hat N_q$ and %
-$\hat N_\pm = \hat N_a /2 \pm \omega_l \hat N_d/(2i)$ %
-are non-linear terms computed from %
-$\hat \NN_\uu = - \zeta \eez \wedge \uu - \bnabla |\uu|^2/2$ and %
-$\hat N_\eta = - \bnabla \cdot (\eta \uu)$.
-%
-We have removed the Newtonian viscous operator in (\ref{eq_uu}) and
-added more general dissipative operators in (\ref{eq_uu}) and
-(\ref{eq_h}).  There is no strong physical motivations for this
-modification but, as discussed by \cite{FargeSadourny1989}, molecular
-dissipation of the form $\nu \bnabla^2 \uu$ is not necessarily a
-relevant model of the actual small-scale dissipation for shallow-water
+We have carried out a series of twenty forced-dissipative simulations of the SW equations in a quadratic domain with periodic boundary conditions using a standard pseudo spectral code.
+The simulations were started from zero initial conditions and were run till a statistically stationary state was reached.
+The equations
+were reformulated in terms of  the three eigenmodes of the linearized equations in Fourier space. One of these eigenmodes is zero for an irrotational flow.  
+We first carried out a few test simulations in which all three eigenmodes were allowed to evolve in time.
+However, when only the two wave modes are forced vorticity remains very small throughout the simulations and does not affect the wave dynamics.
+Therefore, we chose to solve the equations only for the two wave modes.
+As discussed in the previous section,  a linear viscous term in (\ref{eq_uu})
+will not conserve momentum exactly and does not give a strictly positive definite expression for energy dissipation.
+We have relaxed the requirements of exact momentum conservation and positive definite energy dissipation.
+Instead of  using the nonlinear form of the viscous term in (\ref{eq_uu}) we have used a higher order linear operator  $ \nu_8 \nabla^{8} $ both in (\ref{eq_uu}) and
+(\ref{eq_h}), where $ \nu_8 $ is a `hyperdiffusion' or a `hyperviscosity'. There is no strong physical motivation for this
+modification but, as discussed by \cite{FargeSadourny1989}, a molecular viscous operator 
+ of the form $\nu \nabla^2 $ is not necessarily a
+relevant model of the actual small-scale dissipation for SW
 flows, which should rather be described as a transition from
@@
 scales where dissipation actually occurs.
-
-Equations (\ref{eqqnum}-\ref{eqapmnum}) are simulated by means of a
-pseudo-spectral method with periodic boundary conditions.
 %
@@
 the linear and dissipative terms.  This explicit integration is
-especially interesting at very high resolution and very large $c$ when
-the shortest waves are very fast with frequency of the order of
-$\omega \simeq c \max(k)$.
-%
+especially useful at very high resolution and very large $c$ when
+the shortest waves are very fast. 
 We use an adaptable time step method which maximizes the time step
@@
 in the truncated one-layer shallow water model,
-see][]{FargeSadourny1989}.
-
-\subsection{Forced dissipative statistically stationary simulations}
-
-We have carried out a number of simulations 
-with large-scale forcing and small-scale dissipation
-for different resolutions and different values of the wave speed.
+see][]{FargeSadourny1989}. The resolution is characterized by the number of nodes, $n$, in the each
+direction and has been varied from 960 to 7680.
 %
-The resolution is characterized by the number of nodes in the each
-direction, $n$, and has been varied from 240 to 7680.
-%
-The wave speed $c$ has been varied over two orders of magnitude from
-10 to 1000.
-%
-Table~\ref{tab} presents the parameters for a set of representative
-simulations.
+The wave speed $c$ has been varied over almost two orders of magnitude from
+10 to 700. The wave modes are forced in a shell in spectral space 
+corresponding to relatively small wave numbers, 
+$ 5 \delta k <  |\kk| <  8 \delta k$,  
+where  $ \delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic domain. 
+The forcing is white noice in time and designed so that the energy injection rate is normalized to unity at each time step.
+The energy is dissipated at the smallest resolved scales by hyperviscosity.
+The value of the
+hyperviscosity, $\nu_8$, is chosen in such a way that the  maximum wave number is larger than the dissipation wave number
+\begin{equation} 
+k_{d} = \left( \frac{{\nu_8}^3}{\eps} \right)^{-\frac{1}{22}},
+\end{equation}
+ where $ \eps $ is the mean energy dissipation rate. We found that  $
+ k_{d} \simeq \kmax/ 2.5$, where $\kmax =
+(8/9)\pi n/L $ is the maximum wave number, is  sufficient in order for dissipation spectra to be resolved.
+Since the energy injection rate is normalized to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state.
+The strength of the stratification is characterized by a Froude number, defined as
+\begin{equation} \label{Fr}
+F_f = \frac{\varepsilon^{1/3}}{c k_f^{1/3}} \, ,
+\end{equation} 
+a parameter that can be determined from the start of each simulations. 
+The  simulation parameters are listed in table 1.
 
@@
 \begin{center}
-% \def~{\hphantom{0}}
-\begin{tabular}{cc@{\hskip 8mm}c@{\hskip 8mm}cccc@{\hskip 8mm}cc}
-$n$ & $c$ & $\nu_8$ & $\eps$ & $\displaystyle\frac{\kmax}{\kdiss}$ & $\displaystyle\frac{\kdiss}{k_f}$ & $F_f$ & $\min h$ & $\displaystyle\frac{\max |\uu|}{c}$ \\[3mm]
-~960 &   10 & 1.5e-10 & 1.03 & 2.46 &  29 &  0.111 & 0.25 & 0.96 \\
-1920 &   10 & 9.6e-13 & 1.00 & 2.46 &  58 &  0.110 & 0.37 & 0.92 \\
-3840 &   10 & 6.0e-15 & 1.01 & 2.46 & 116 &  0.110 & 0.39 & 1.01 \\
-7680 &   10 & 3.7e-17 & 1.03 & 2.46 & 231 &  0.111 & 0.32 & 0.95 \\[1mm]
-~960 &   20 & 1.5e-10 & 0.98 & 2.47 &  29 &  0.055 & 0.65 & 0.51 \\
-1920 &   20 & 9.6e-13 & 0.84 & 2.48 &  57 &  0.052 & 0.66 & 0.81 \\
-3840 &   20 & 6.0e-15 & 0.99 & 2.46 & 115 &  0.055 & 0.56 & 0.68 \\[1mm]
-~960 &   40 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.027 & 0.81 & 0.24 \\
-1920 &   40 & 9.6e-13 & 1.01 & 2.46 &  58 &  0.028 & 0.78 & 0.28 \\
-3840 &   40 & 6.0e-15 & 0.98 & 2.47 & 115 &  0.027 & 0.77 & 0.29 \\
-7680 &   40 & 3.7e-17 & 0.94 & 2.47 & 230 &  0.027 & 0.76 & 0.32 \\[1mm]
-~960 &  100 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.011 & 0.89 & 0.09 \\
-1920 &  100 & 9.6e-13 & 0.98 & 2.47 &  58 &  0.011 & 0.90 & 0.11 \\
-3840 &  100 & 6.0e-15 & 0.97 & 2.47 & 115 &  0.011 & 0.87 & 0.13 \\[1mm]
-~960 &  200 & 1.5e-10 & 0.99 & 2.46 &  29 &  0.005 & 0.95 & 0.05 \\
-1920 &  200 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.005 & 0.94 & 0.06 \\
-3840 &  200 & 6.0e-15 & 0.90 & 2.47 & 115 &  0.005 & 0.94 & 0.06 \\[1mm]
-~960 &  400 & 1.5e-10 & 0.97 & 2.47 &  29 &  0.003 & 0.97 & 0.03 \\
-1920 &  400 & 9.6e-13 & 0.99 & 2.46 &  58 &  0.003 & 0.96 & 0.03 \\[1mm]
-~960 & 1000 & 1.5e-10 & 1.16 & 2.45 &  29 &  0.001 & 0.98 & 0.01 \\
-1920 & 1000 & 9.6e-13 & 0.91 & 2.47 &  57 &  0.001 & 0.98 & 0.01 \\
+
+\label{Table1}
+\begin{tabular}{lrrrrrrrr}
+
+\toprule
+{} &   $n$ &  $c$ &  $\nu_8$ &  $\eps$ &  $ k_{d}  / {k_f} $ &   $F_f$ &    $t_{\max}$ \\
+\midrule
+W1  &   960 &   10 & 1.56e-10 &        1.04 &                    28.8 &   0.111 &                49.9 \\
+W2  &  1920 &   10 & 9.68e-13 &        1.06 &                    57.7 &   0.112 &               49.8 \\
+W3  &  3840 &   10 &    6e-15 &         1.10&                     115 &   0.113 &               49.9 \\
+W4  &  7680 &   10 & 3.72e-17 &        1.18 &                     231 &   0.116 &               49.9 \\
+W5  &   960 &   20 & 1.56e-10 &           1.00 &                    28.8 &   0.055 &              49.9 \\
+W6  &  1920 &   20 & 9.69e-13 &        1.02 &                    57.7 &  0.0553 &                120 \\
+W7  &  3840 &   20 & 6.01e-15 &        1.08 &                     115 &  0.0563 &                120 \\
+W8  &  7680 &   20 & 3.72e-17 &        1.21 &                     231 &  0.0585 &                 120 \\
+W9  &   960 &   40 & 1.56e-10 &          1.00 &                    28.8 &  0.0274 &                49.8 \\
+W10 &  1920 &   40 & 9.68e-13 &       1.00 &                    57.7 &  0.0274 &               49.8 \\
+W11 &  3840 &   40 &    6e-15 &        1.06 &                     115 &   0.028 &               49.8 \\
+W12 &   960 &  100 & 1.56e-10 &       1.00 &                    28.8 &   0.011 &                49.8 \\
+W13 &  1920 &  100 & 9.69e-13 &        1.01 &                    57.7 &   0.011 &                 120 \\
+W14 &  3840 &  100 & 6.01e-15 &        1.06 &                     115 &  0.0112 &                 120 \\
+W15 &  7680 &  100 & 3.72e-17 &        1.22 &                     231 &  0.0117 &                95.8 \\
+W16 &   960 &  400 & 1.56e-10 &        1.14 &                    28.8 & 0.00287 &                 120 \\
+W17 &  1920 &  400 & 9.69e-13 &        1.15 &                    57.7 & 0.00288 &                 120 \\
+W18 &  3840 &  400 & 6.01e-15 &        1.12 &                     115 & 0.00286 &                119 \\
+W19 &   960 &  700 & 1.56e-10 &        1.27 &                    28.8 &  0.0017 &                49.8 \\
+W20 &  1920 &  700 & 9.68e-13 &        1.05 &                    57.7 &  0.0016 &                49.8 \\
+\bottomrule
+
 \end{tabular}
-\caption{Overview of parameters for a set of representative simulations. 
-The number of nodes in the each direction is denoted by $n$. 
-The size of the numerical domain is equal to $L_h = 50$.
-Only the wave numbers $5\delta k\leqslant|\kk|\leqslant8\delta k$ are forced
-and the forcing wave number is defined as 
-$k_f \equiv 6 \delta k$ 
-corresponding to a characteristic forcing scale of approximately 
-$L_f \equiv \pi/k_f = 3.57$.
-%
-$F_f = \eps^{1/3}/({k_f}^{1/3}c)$ is the forcing Froude number and
-$\max |\uu|/c$ is the spatial and temporal maximum of a local Froude
-number.  }
-\label{tab}
+\caption{Parameters for all simulations.
+$ n $: number of nodes in each direction, $ c $: wave speed, $ \nu_8 $: hyperviscosity, $ \eps $: time averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio between dissipation wave number and forcing wave number, $ F_f  $: Froude number, $ t_{max} $:   end time of simulation.}
 \end{center}
@@
 
-The ageostrophic variable $a$ is forced in a shell in spectral space
-corresponding to relatively small wave numbers $5\delta k\leqslant
-|\kk| \leqslant 8\delta k$, where $\delta k = 2\pi/L_h$.
-%
-\Add{In the following, we use $L_h = 50$ in order to obtain a
-characteristic forcing wave number of order unity, $k_f \equiv 6
-\delta k \simeq 0.75$. The corresponding forcing scale is $L_f \equiv
-\pi/k_f \simeq 4.2$.}
-%
-Since only the ageostrophic variable is forced ($\hat f_d = 0$),%
-(i) only the thickness fluctuation $\eta$ is forced in the
-non-rotating case and %
-(ii) the force terms in (\ref{eqapmnum}) are simply equal to $\hat
-f_\pm = \hat f_a/2$.
-%
-In order to compute the force $\hat f_a$, we start from a
-pre-normalized force $\hat f_{0}$ obtained from a normal random
-process decorrelated in time.
-%
-The force is then normalized such that the quadratic part of the total
-energy $\langle|\uu|^2 + c^2 \eta^2\rangle/2$ is injected at a
-constant rate.
-%
-The spectral injection rate of the quadratic energy averaged over one
-time step is (see appendix~\ref{app_comp})
-\begin{equation}
-P_q(\kk, t) 
-= 
-\Re\{ \hat \uu(\kk)^* \cdot \hat \ff(\kk) 
-+
-c^2 \hat \eta(\kk)^* \hat f_\eta(\kk) \}
-+ 
-(|\hat\ff|^2 + c^2 |\hat f_\eta|^2) \delta t /2,
-\end{equation}
-where $\Re$ denotes the real part.
-%
-Writing $\hat f_a = \alpha \hat f_{0}$, it is straightforward to solve
-a second-order equation for the coefficient $\alpha$ in order to fix
-the injection rate $\Add{P_0 \equiv} \sum_\kk P_q(\kk, t)$ to unity.
-
-The energy is dissipated at the smallest resolved scales by a
-hyper-viscous operator, corresponding to a dissipative frequency equal
-to $\fdiss(\kk) = \nu_n |\kk|^n$, with $n = 8$.  The value of the
-hyperviscosity $\nu_8$ is chosen such as the hyper-Kolmogorov wave
-number
-\begin{equation}
-k_{Kn} = \left( \frac{{\nu_n}^3}{\eps} \right)^\frac{1}{3n-2},
-\end{equation}
-is well resolved, $\kdiss =k_{K8} \simeq \kmax/ 2.5$, where $\kmax =
-(8/9)\pi n/L_h$ is the maximum resolved wave number.
-
-We have observed that when only the waves are forced, the vorticity
-does not increase and that when the vorticity is small enough, it does
-not significantly influence the waves.  Therefore, we have chosen not
-to simulate a negligible vorticity field and to only solve equations
-(\ref{eqapmnum}) with $\zeta = 0$.
-
 \begin{figure}
-\centerline{\includegraphics[width=13cm]{../Figs/fig_Emean_time}}
-\caption{Space averaged energy 
-$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ versus time 
-for different wave speeds $c$ and resolutions $n$.
-%
-The energy and the time are normalized by 
-$E_f\equiv (P_0/k_f)^{2/3}$ and $T_f\equiv (P_0 {k_f}^2)^{-1/3}$,
-with $P_0 = 1 \simeq \eps$.
-%
-The colors corresponds to different wave speeds as indicated in the figure
-$c= 10$, 20, 40, 70, 100, 200, 400, 700 and 1000.
-%
-The different resolutions are represented by different types of lines:
-\Add{thin continuous lines, $n = 240$;
-thick dashed lines, $n = 480$;
-thin dotted lines, $n = 960$;
-thick continuous lines, $n = 1920$;
-thin dashed lines, $n = 3840$;
-thick dotted lines, $n = 5760$ 
-and
-thin dotted dashed lines, $n = 7680$.}
-}
+\centerline{\includegraphics[width=5.12in]{../Pyfig/fig_Emean_time}}
+\caption{Space averaged energy, 
+$E = E_K + E_A $, versus time 
+for all simulations. }
 \label{fig_Evstime}
@@
 
-The time evolution of the instantaneous total energy is shown in
-figure~\ref{fig_Evstime} for different wave speeds $c$.
-%
-The resolution \Add{and the dissipation wave number are} progressively
-increased: %
-$n = 240$ ($0\leqslant t/T_f \leqslant 100$), %
-$n = 480$ ($100\leqslant t/T_f \leqslant 125$), %
-$n = 960$ ($125\leqslant t/T_f \leqslant 140$), %
-$n = 1920$, %
-$n = 3840$, %
-$n = 5760$ and %
-$n = 7680$\Add{, where $T_f\equiv
-(P_0 {k_f}^2)^{-1/3}$ is the characteristic forcing time}.
-%
-Each time the resolution is increased, the energy first sharply
-increases and then fluctuates.  For most of the simulations, it is
-clear that a statistically stationary regime is reached.
-%
-However, 
-%
-\Remove{in the relatively short simulations at the highest
-resolution for the largest wave speeds ($n = 1920$, $c = 700$ and
-1000),}
-%
-\Add{for some relatively short simulations with very large wave speed
-and/or very large resolution,}
-%
-there are large fluctuations and it is not absolutely certain whether
-a statistically stationary regime is reached.
-%
-\Add{This is in particular the case for the simulations for $c = 700$, $n
-= 1920$ (thick red continuous line), $c = 200$, $n = 3840$ (thin
-magenta dashed line) and $c=40$, $n = 7680$ (thin blue dotted dashed
-line).}
-%
-\Add{Note that these simulations are already quite numerically
-costly. For example, the simulation for $c=1000$ and $n = 1920$
-during slightly less than $20T_f$ corresponds to approximately
-$8\times 10^5$ time steps.}
+\begin{figure}
+\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_energy_w}}
+\caption{Left: Mean energy in the stationary state versus $ c $ for different resolutions.
+The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2} $.
+Right: Normalized mean energy in the stationary state versus resolution $ n $ for different $ c $.}
+\label{MeanE}
+\end{figure}
 
-Since the energy is injected at large scales and dissipated only at
-the smallest resolved scales, the existence of a statistically
-stationary regime implies a downscale flux of energy, which is equal
-to the large-scale energy injection rate.
-%
-For the same energy injection rate and resolution, the mean energy
-increases with the wave speed, implying that when $c$ increases the
-mean energy has to be larger to lead to the same downscale energy
-flux.
-%
-The results presented in the following are from the statistically
-stationary regime.  Apart from the snapshots, all shown quantities are
-averaged over a period corresponding to this regime.
+The time evolution of  
+mean energy is shown in
+figure~\ref{fig_Evstime} for all twenty simulations.
+After an initial period of growth, mean energy is leveling out at different values for different runs.
+This is not the same picture as we see in simulations of three-dimensional incompressible turbulence or stratified turbulence, where all curves would have leveled out more or less at the same value.
+We find that mean energy in the stationary state is a function of both $ c $ (or the Froude number) and resolution $ n $ and that the functional dependence  can be approximately written as
+\begin{equation} \label{MeanEnergy}
+E \propto \sqrt{L_f c \eps} \, n^{\alpha}  \, ,
+\end{equation} 
+where $ L_f = \pi/k_f $ is the forcing scale.
+In figure \ref{MeanE} to the left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $ n $.
+For each resolution the  points are approaching a power law $ C_n c^{1/2} $  with increasing values of $ C_n $ for increasing $ n $.
+In the same figure to the right we see
+$ E/\sqrt{L_f c \eps} $ for different values of $ c $.
+For each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is becoming slightly larger with increasing $ c $, approaching almost the same value $ \alpha \approx 0.33 $ for the three highest values of $ c $.
+The relation (\ref{MeanEnergy}) can be reformulated as
+\begin{equation} \label{Dissipation}
+\frac{\eps} {(E^{3/2} / L_f)} \propto \frac{E^{1/2}}{c} n^{-2\alpha}
+\end{equation} 
+Since the simulations are well resolved the dependence on resolution should not be interpreted as consequence of the numerics but rather as a Reynolds number effect, although it is not hundred percent clear how a Reynolds number should be defined in our case.
+We may note, however, that $ n $ is  proportional $ k_{d} / k_f $ and  the corresponding ratio in Kolmogorov turbulence scales as $ Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $ \nu $ is the kinematic viscosity.
+If we simply define a Reynolds number as
+\begin{equation}
+Re = \left ( \frac{k_d} {k_f} \right )^{4/3} \, ,
+\end{equation} 
+we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8 \alpha/3} $.
+The normalised energy dissipation on the left hand side of  (\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
+This is very different from three-dimensional turbulence
+where there is a local Richardson-Kolmogorov cascade, in which energy is successively transfered from large to small scales of motion.
+That the cascade is local means that eddies of a particular scale are not directly influenced by eddies of widely different scales.
+As a consequence, the normalized dissipation is of the order of unity independent of Reynolds number \cite[]{Pope, TennekesLumley}.
+A review of the experimental evidence and theoretical implications of this fundamental law of Kolmogorov turbulence is given by \cite{Vassilicos2015}.
+Our result (\ref{Dissipation})  suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade.
+Moreover, it is not only in the limit of large Reynolds number the normalized dissipation will go to zero but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
+This is  different from three-dimensional stratified turbulence where the ratio on the left hand side of (\ref{Dissipation}) is of the order of unity in the limit of strong stratification  \cite[]{Lindborg2006, Brethouwer2007}.
 
-Table~\ref{tab} presents numerical and physical quantities for a set
-of representative simulations.
-%
-We characterize the simulations by the forcing Froude number
-\begin{equation}
-F_f \Add{\equiv} \frac{\eps^{1/3}}{{k_f}^{1/3}c}.
+ The `four-fifths law' for the third order structure function of Kolmogorov turbulence is often derived using the assumption of a local cascade \cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the limit of large Reynolds number \cite[]{Frisch}.
+As we just discussed, these assumptions seem to be violated in the case of SW wave turbulence.
+Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave turbulence is satisfied with a high degree of accuracy in our simulations.
+In figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and the third order structure function to the right.
+There is a broad constant flux range  with equipartition between KE and APE flux and an almost equally broad range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two third order structure functions associated with KE and APE.
+The assumptions of a local cascade and finite dissipation do not seem to be necessary in order for the third order structure function law  (\ref{eq_Kolmo}) to be valid.
+
+\begin{figure}
+\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_flux_struct_combined}}
+\caption{Left: Time averaged normalised spectral energy fluxes versus $ k/k_f $. Right: Time averaged normalised third order structure functions versus $ r/L_f $. From run W7. }
+\label{Flux}
+\end{figure}
+
+\begin{figure}
+ \centerline{
+ \includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
+\caption{Frequency spectra of KE  and APE for different $ k = \mid {\bf k} \mid $, from run W7. The spectra are plotted  as functions of $\omega/\omega_l$, where
+$\omega_l = c k$.  From top to bottom: $ k /\delta k
+= 12$, 27, 62, 143, 327, and 746.  }
+\label{fig_spatiotemp_spectra}
+\end{figure}
+\begin{figure}
+ \centerline{
+ \includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
+\caption{Left: divergence $ \bnabla \cdot {\bf u} $. Right: velocity component in the $ y $-direction: $ u_y $. Top: run W6. Bottom: run W17.  }
+\label{Physical}
+\end{figure}
+\begin{figure}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_shock_sep.pdf}}
+\caption{Mean distance between the shocks as function of Froude number.  }
+\label{fig_distance}
+\end{figure}
+
+The equipartition of KE and APE spectral fluxes suggests that the flow to leading order may be described as a collection of linear gravity waves with equipartition of KE and APE in each mode.
+To investigate this further we have collected time series of the flow variables from Fourier modes whose magnitude fall within certain shells,  $ \mid {\bf k} \mid \in [ k -\delta k/2, \; k+ \delta k/2] $,  and computed temporal power law spectra from these time series and averaged over all wave numbers in each shell.
+In other words we have computed KE and APE frequency spectra corresponding to different magnitudes of modes.
+Figure~\ref{fig_spatiotemp_spectra} presents such
+spectra plotted as a functions of the normalized frequency
+$\omega/\omega_l$, where $ \omega_l = kc $ is the linear wave frequency, 
+The spectra are strongly dominated by  peaks at $\omega =
+\omega_l$. As can be seen, there is equipartition between KE and APE in each shell.  
+Although the widening of the peaks around the linear frequency most likely is an effects of nonlinearities, 
+we can quite safely conclude that the time evolution of the flow variables in each Fourier mode to leading order can be described as a linear wave.
+
+Visualizations of the flow field give a completely different picture from what may be expected from a collection of linear gravity waves.
+They are totally dominated by the appearance of shock waves.
+In figure (\ref{Physical}) we see the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity component in the $ y $-direction, $ u_y $, to the right.
+The two figures at the top are from run W6 while the two figures at the bottom are from run W17.
+The difference between the two runs is that $ c $ is larger by a factor of $ 20 $ in W17 as compared to W6.
+To the left we see the shocks displayed as elongated bands of negative divergence.
+That the divergence is negative at the shocks can be understood from the fact that the velocity component perpendicular to the shock always has a negative jump in the direction of shock propagation.
+Apparently, the mean distance between the shocks is considerably smaller in run W17 with the larger value of $ c $ compared to run $ W6 $  with the smaller value of $ c $.
+The shocks are also visible in the figures to right where $ u_y $ is displayed.
+It may be interesting to note that the shocks along the $ x $-axis appear as extra sharp in this plot, since there is a strong jump  of $ u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly visible, since there is no jump of $ u_{y} $ over these.
+In the two figures to the right we see a variation of the flow field over the length scale $ L_f $ which is not seen in the two figures to the left.
+This variation is evidently a footprint of the random forcing.
+Although the forcing length scale $ L_f $ is the same in the two simulations the mean distance, $ d $,  between the shocks is much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit surprising.
+We have calculated $ d $ by counting the number of negative spikes of the divergence along ten lines parallel to the $ x $-axis and ten lines parallel to the $ y $-axis and then divided  total length of all the lines by the number of spikes.
+Generally, we found that $ d \sim c^{-1/2} $, or
+\begin{equation} \label{MeanDistance}
+d \propto L_f F_f ^{1/2} \, ,
 \end{equation} 
-\Add{Since the characteristic forcing wave number and the dissipation
-rate are approximately equal to $k_f \equiv 6 \delta k \simeq 0.75$
-and $\eps \simeq P_0 = 1$, the forcing Froude number is approximately
-inversely proportional to the wave speed: $F_f \simeq 1.1/c$. This
-allows us to simply use the wave speed to denote the simulations.}
-% where $k_f \equiv 6 \delta k = 0.75$ is a wave number characterizing
-% the forcing.
-%
-The ratio $\kdiss/k_f$ gives an order of magnitude of the width of the
-inertial range.  It is a physical quantity related to the numerical
-resolution on which the flow can depend.
-%
-Table~\ref{tab} also displays the minimum thickness $\min(h)$
-characterizing the importance of the non-quadraticity of the energy,
-and $\max(|\uu|/c)$, which can be interpreted as the maximum of a
-local Froude number.
+independent of resolution $ n $.
+In figure (\ref{fig_distance}) we have plotted $ d/L_f $ versus Froude number for all twenty runs.
+As can be seen the points follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight systematic deviation at the highest $ F_f $, which may be due to the fact that $ d $ is rather close to the length of the side of the box for the largest $ F_f $.
+
+\begin{figure}
+ \centerline{
+ \includegraphics[width=5.0in]{../Pyfig/fig_struct_order_246}}
+\caption{From top to bottom: second, fourth and sixth order compensated and normalised longitudinal structure functions.
+Left: runs with $ n=3840 $: W3, W7, W11 and W18.
+Right: runs with $ n = 7860 $: W4, W8 and W15.
+}
+\label{fig_StrucFunc}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_ratio_strfct}}
+\caption{
+Ratio of the structure functions 
+$R_p(r) = \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$ from run W4, 
+for $ p = 2, \, 3, \, 4, \, 5, \, 6. $
+The dotted straight lines indicate the values predicted by (\ref{Ratio}):
+$R_2 = 2$, $R_3 = 3\pi/4$,  $R_4 = 8/3$, $ R_5 = 15 \pi /16 $ and $ R_6 = 16/5 $.}
+\label{fig_ratio}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=12cm]{../Pyfig/fig_flatness}}
+\caption{ Flatness of the longitudinal and transverse increments for
+$c = 10$ and $n = 7680$. The straight continuous lines indicate the
+$r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
+The inset shows the ratio $F_T/F_L$ and the corresponding value computed by the shock model, $F_T/F_L = 1.5$.  }
+\label{fig_flatness}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=11cm]{../Pyfig/fig_spectra}}
+\caption{Compensated and normalised energy spectra
+from runs with $ n = 7680 $: W4, W8 and W15.}
+\label{fig_spectra_c40}
+\end{figure}
+
+We will now present the results for the structure functions. Substituting (\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure functions are expected to scale as
+\begin{equation} \label{StrucFunc2}
+\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (L_f F_f^{1/2})^{p/3-1}  \eps^{p/3}  r  \, .
+\end{equation}
+for separation distances that fulfill the condition $ \delta x \ll r \ll d $, where $ \delta x $ is the shock width.
+The scaling (\ref{StrucFunc2}) is expected to become better and better fulfilled with decreasing $ c $ (or increasing $ F_f $), for two reasons.
+First, according to (\ref{MeanDistance}) $ d $ is increasing with $ F_f $, and the scaling range is therefore becoming wider for decreasing $ c $, if  $ \delta x $ or the resolution  $ n $ is kept constant.
+Second, according to (\ref{Strength}) the amplitude of the shocks scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming increasingly strong for large $ d $ (small $ c $).
+Thus, the assumption that the structure functions are totally dominated by increments where a shock is crossed will be better fulfilled for small $ c $.
+This effect is expected to be particularly important for lower order structure functions.
+The scaling (\ref{StrucFunc2}) is also expected top become better and better fulfilled with increased resolution $ n $, since $ \delta x $ is decreasing with increasing $ n $.
+
+ As expected, we have found that 
+the displacement structure functions scale exactly in the same way as the velocity structure functions, why we only plot velocity structure functions.
+In figure (\ref{fig_StrucFunc}) we see the compensated and normalised second, fourth and sixth order longitudinal structure functions from the five simulations with $ n = 3840 $ to the left and the three simulations with $ n = 7860 $ to the right.
+At small separation, $ r < \delta x $, the structure functions have the dependence $ \sim r^{p} $, which is characteristic of a smooth velocity field, indicating that the shocks are reasonably well resolved.
+There is a small bump around the shock width,
+$ r \approx \delta x $, and at $ r > \delta x $, there is a range where the compensated structure functions are flat, or almost flat.
+As expected, this range is becoming broader for smaller  $ c $ (or larger $ F_f $).
+The range is also broader in the higher resolution runs to the right as compared to the lower resolution simulations to the left.
+There is clearly a better collapse of the curves for the sixth order structure functions compared to the second order structure functions.
+This is not surprising, since the shock contribution to the structure functions should become increasingly dominant with increasing order.
+Plots of the transverse structure functions are very similar to the plots of the longitudinal structure functions, with the difference that the transverse structure functions are somewhat smoother at $ r \approx \delta x $.
+In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta u_L \mid ^{p} \rangle /  \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p= 2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the values predicted by (\ref{Ratio}).
+As can be seen, there is a quite good agreement with the predicted values in a limited range of separations, $ r > \delta x $.
+Somewhat unexpectedly, the range in which there is a good agreement becomes more narrow with increasing $ p $, an observation that we cannot explain.
+It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small $ r $, which is the theoretical single point limit for an irrotational isotropic field.
+In figure (\ref{fig_flatness}) we se the flatness factor, $ F_T $,  of the transverse structure functions at the top and the ratio, $ F_T/F_L $,  at the bottom.
+The figures to the left show the results from the five simulations with  $ n = 3840 $ and the figures to the right show the results from the three simulations with $ n = 7860 $.
+The flatness factor  shows increasingly large values for decreasing $ r $ with a dependence that is rather close to but somewhat steeper than $ r^{-1} $.
+At small $ r $ the curves  are leveling out at very large values.
+For $ n = 7869 $ and $ c = 10 $ we see that $ F_{T} \approx 400 $ at small $ r $.
+The degree to which the flatness factor is increasing with decreasing scale is by some authors defined  as the most appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
+If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
+In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a limited range of separations, $ r > \delta x $, which is becoming somewhat broader as $ c $ is increasing and  is also somewhat broader in the higher resolution runs shown to the right as compared to the lower resolution runs shown to the left.
+This is in accordance with the shock model predictions (\ref{FL}) and (\ref{FT}).
+
+Finally, we present  energy spectra.
+As expected, we found that APE and KE spectra were almost indistinguishable from each other, why we only plot the total spectra.
+In figure (\ref{fig_spectra_c40}) we see the compensated and normalised energy spectra from the three highest resolution runs.
+The compensated spectra are almost flat in a broad range.
+In the high wave number end the compensated spectra show a `bottleneck', which we interpret as a signature of the shocks, and at the very highest wave numbers the magnitude of the spectra is strongly decreasing, indicating that the shocks are reasonably well resolved.
+The $ k^{-2} $-dependence and the associated scaling predicted by (\ref{Spectra}) are very well satisfied in a limited range of high wave numbers close to the bottleneck.
+At smaller wave number the spectra are becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with largest $ c $ does not collapse perfectly onto the other two spectra.

### 2018-10-16 Latex/section_wave_cascade_f=0.tex
First revision by Erik

--- 2016-12-17 Latex/section_wave_cascade_f=0.tex
@@
-\subsection{Downscale energy cascade of waves}
-\label{subsection_cascade}
-
 \begin{figure}
-% \centerline{
-% \includegraphics[width=8cm]{../Figs/fig_spect_energy_budg_c=100_N=3840}}
-\caption{Spectral energy fluxes averaged over a long simulation for $c
-= 100$ and $n = 3840$.  The fluxes are nondimensionalized by $\eps$
-and plotted versus $k/k_f$.  }
-\label{fig_seb}
-\end{figure}
-
-The spectral energy fluxes of total energy, KE and APE are plotted in
-figure~\ref{fig_seb} as functions of $k/k_f$.
-%
-The fluxes are approximately zero at the wave numbers smaller than the
-forced wave numbers.  They increase sharply at the forced wave numbers
-to values close to $\eps$ for the total energy flux and to $0.5\eps$
-for the KE and APE fluxes.  The fluxes then decrease to zero over the
-dissipation range.
-%
-The energy is transferred from the forced wave numbers to the
-dissipation wave numbers with a constant flux equal to the mean
-forcing and dissipation rates.
-%
-There is an inertial range where the flux is constant and
-equipartitioned between equal KE and APE fluxes.
-%
-However, at wave numbers $k \simeq 2 k_f$, the flux is not exactly
-equal to $\eps$.  This is very likely related to the energy injection
-at wave numbers for which the force is zero, which is due to the
-non-quadraticity of the kinetic energy (see appendix~\ref{app_comp}).
-%
-Nevertheless this effect is non-negligible only for wave number of the
-order of $k\simeq 2 k_f$, i.e.\ at the first harmonics of the forced
-wave numbers, such that there is a clear and wide inertial range
-between $k\gtrsim 3 k_f$ to the dissipation range starting at wave
-number of the order of $k \sim 70 k_f$.
-
-\begin{figure}
-% \centerline{\includegraphics[width=8cm]{../Figs/fig_Kolmo_c=20_N=3840}}
-\caption{
-Third order structure functions involved in the exact Kolmogorov law (\ref{eq_Kolmo}) 
-averaged over a long simulation for $c = 20$ and $n = 3840$.
-%
-The structure functions are normalized by $4 \eps r$.
-%
-Black thick line, $\mean{ \delta J_L|\delta \uu|^2 } 
-+ c^2\mean{\delta u_L(\delta h)^2}$;
-light thin line, $c^2\mean{\delta u_L (\delta h)^2}$;
-dark thin line, $\mean{\delta J_L |\delta \uu|^2}$.
-%
-The dotted straight line shows $4 \eps_q r$, 
-where $\eps_q$ is the quadratic energy dissipation rate.
-}
-\label{fig_Kolmo}
-\end{figure}
-
-Figure~\ref{fig_Kolmo} shows the quantity $\mean{\delta J_L|\delta
-\uu|^2 } + c^2\mean{\delta u_L(\delta h)^2 }$ (black thick line)
-normalized by $4 \eps r$ for $c = 20$ and $n = 1920$.
-%
-In this section, the brackets $\mean{}$ denote the average over space
-and time.
-%
-The dotted straight line shows the quantity $4 \eps_q r$, where
-$\eps_q$ is the quadratic energy dissipation rate (see
-appendix~\ref{app_comp}) which takes place at small scales.
-%
-We see that the Kolmogorov law (\ref{eq_Kolmo}) is well satisfied
-between \Add{$r \simeq 0.02L_f$ and $r \simeq 0.1 L_f$}.  The dark and
-light thin continuous lines correspond to the quantities $\mean{\delta
-J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta h)^2}$,
-respectively.
-%
-These two quantities are nearly equal over the inertial and
-dissipation ranges, which is consistent with a wave cascade when
-$f=0$.
-%
-The agreement with the Kolmogorov law and the equality between
-$\mean{\delta J_L|\delta \uu|^2 }$ and $c^2\mean{\delta u_L(\delta
-h)^2}$ are the equivalents in the separation space of the plateau in
-the total energy flux and the equality between $\Pi_K$ and $\Pi_A$,
-respectively.
-
-\begin{figure}
-% \centerline{
-% \includegraphics[width=8cm]{../Figs/fig_spatiotempspectra_c=20_Nh=3840}}
-\caption{Spatio-temporal spectra of KE (dark lines) and APE (light
-lines) for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
-$\omega_l = c k$.  From the larger to the smaller spectra, $k/\delta k
+ \centerline{
+ \includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
+\caption{Spatio-temporal spectra of KE  and APE for $c = 20$ and $n = 3840$ versus $\omega/\omega_l$, where
+$\omega_l = c k$.  From top to bottom: $k/\delta k
 = 12$, 27, 62, 143, 327, and 746.  }
@@
 inside each shell.
+
+\begin{figure}
+ \centerline{
+ \includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
+\caption{ }
+\label{Physical}
+\end{figure}
 %
@@
 number is the linear frequency.  However, the widening of the peaks
-can be explained only by nonlinear effects.  \Add{The equipartition
+can be explained only by nonlinear effects.  The equipartition
 between kinetic and potential energies is expected since the flow only
@@
 \subsection{Time- and space-averaged energy as a function of $c$}
-
-\begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_c}
-% \includegraphics[width=\halfwidth]{../Figs/fig_Emean_resol}
-% }
-\caption{Time- and space-averaged energy 
-$\langle h|\uu|^2 + c^2 h^2 \rangle/2$ 
-of the statistically stationary flows.
-%
-In (\textit{a}), the energy is divided by 
-$\sqrt{\eps}$ and plotted versus $c$ for 3 resolutions:
-$n = 960$, dotted lines; 
-$n = 1920$, continuous lines and 
-$n = 3840$, dashed lines. 
-The cyan curves show the law $C_n \sqrt{\eps L_f c}$, 
-with $C_n$ a fit coefficient.
-%
-In (\textit{b}), the energy is divided by 
-$\sqrt{\eps L_f c}$ and plotted versus $n$
-for six values of $c$ as indicated in the legend.
-}
-\label{fig_Evsc}
-\end{figure}
 
@@
 
-\subsection{Energy spectra}
-
 We now turn to the study of the energy spectra.  A dimensional
@@
 where $\alpha$ and $\beta$ are two free parameters.
-
-\begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k32}
-% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k32}
-% }
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=1920_k2}
-% \includegraphics[width=\halfwidth]{../Figs/fig_spectra_c_Nx=3840_k2}
-% }
-\caption{
-Compensated energy spectra versus $k/k_f$ for different wave speeds $c$.
-%
-The spectra are compensated by $k^{-3/2}\sqrt{\varepsilon c} $ 
-in (\textit{a,b})
-and by $k^{-2}c^{1/3} \eps^{5/9} k_f^{4/9} $ 
-in (\textit{c,d}).
-%
-The resolution is 
-$n = 1920$ in (\textit{a,c}) and 
-$n = 3840$ in (\textit{b,d}).
-%
-In (\textit{a,c}), the wave speed goes from 10 to 1000
-and 
-in (\textit{b,d}) from 10 to 200 
-(for the precise values, see figure~\ref{fig_Evstime}).
-}
-\label{fig_spectra_c}
-\end{figure}
 
@@
 c^{1/3} \eps^{5/9} k_f^{4/9}$.
-
-\begin{figure}
-% \centerline{\includegraphics[width=8cm]{../Figs/fig_spectra_c=40_nh=7680}}
-\caption{Compensated spectra
-of total energy (thick black line)
-kinetic energy (thin dark line) and
-available potential energy (thin light line)
-for $c = 40$ and $n = 7680$.}
-\label{fig_spectra_c40}
-\end{figure}
 
@@
 \begin{figure}
-\setlength{\halfwidth}{69mm}
+\setlength{\halfwidth}{2.72in}
 % \centerline{
@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_ratio_strfct}
-% }
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_ratio_strfct}}
 \caption{
@@
 \begin{figure}
-% \centerline{
-% \includegraphics[width=\halfwidth]{../Figs/fig_flatness}
-% }
+\centerline{\includegraphics[width=12cm]{../Pyfig/fig_flatness}}
 \caption{ Flatness of the longitudinal and transverse increments for
@@
 $r^{-1}$-scaling and the straight dashed line the $r^{-3/2}$-scaling.
-The inset shows the ratio $F_T/F_L$ and the corresponding value
-computed by the shock model, $F_T/F_L = 1.5$.  }
+The inset shows the ratio $F_T/F_L$ and the corresponding value computed by the shock model, $F_T/F_L = 1.5$.  }
 \label{fig_flatness}
+\end{figure}'
+
+\begin{figure}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_spectra}}
+\caption{Compensated spectra
+of total energy (thick black line)
+kinetic energy (thin dark line) and
+available potential energy (thin light line)
+for $c = 40$ and $n = 7680$.}
+\label{fig_spectra_c40}
 \end{figure}

### 2018-10-16 Latex/ArticleNew.tex
Second revision by Erik

@@
 In all simulations, a statistically stationary state were reached and in all simulations we observed shocks.
-The flow variables in each Fourier mode was found to evolve as a linear wave, with equipartition between APE and KE over a period.
+The flow variables in each Fourier mode were found to evolve in accordance with linear wave dynamics, with equipartition between APE and KE over a period.
 The third order structure function relation was fulfilled with a high degree of accuracy.
@@
 We identify the longest wave length, $ \lambda_l $,  with the forcing scale $  L_f $ and the breaking wave length, $ \lambda_b $, with the mean distance, $ d $, between the shocks.
-There are two dynamically different  regimes to consider, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $.
+There are two dynamically different  regimes, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $.
 We first consider the latter, whose width scales  $ \lambda_{l} /\lambda_b \sim F_f^{-1/2} $.
@@
 are not likely to hold for this range, although it is not directly influenced by wave breaking.
-The exact values of the power law exponents in the argument, are, of course, not important.
+The exact values of the power law exponents in the argument leading to this conclusion are, of course, not important.
 As for the short wave regime, the width scales as $  \lambda_b /\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number.
 As $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that breaking will disappear.
-On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large.
-Apparently, a necessary condition for wave breaking is that
-\begin{equation} \label{NC}
-\frac{\lambda_b}{\delta x} \sim \frac{\lambda_l F_f^{1/2}}{\delta x} \gg 1 \, .
-\end{equation}
-It may be interesting to note that the single point limit of the flatness factors shown if figure (\ref{fig_flatness}) scales as the ratio $ \lambda_b/\delta x $ and that this limit is equal to the flatness factor of velocity derivatives.
-So the condition (\ref{NC}) means that the flatness factor of velocity derivatives must be much larger than unity.
-Assuming that this is not only a necessary but also sufficient condition, we would able to formulate under what condition wave breaking will take place in terms of a Froude number and a Reynolds number if we knew how the shock width $ \delta x $ scales with these parameters.
-In setting up the simulations we assumed that it is sufficient to resolve the Kolmogorov scale, $ \eta = (\nu^{3} / \epsilon)^{1/4} $, or the corresponding scale, $ \eta_8 = (\nu_8^{3}/\epsilon) ^{1/22} $, when hyperviscosity is used.
-The results from the simulations seem to support this assumption, suggesting that $ \delta x $ can be identified as the Kolmogorov scale.
-Assuming that this is correct and defining the Reynolds number as $ Re \equiv \lambda_l^{4/3}\epsilon ^{1/3} /\nu $, we can write the condition for wave breaking as
-\begin{equation} \label{Condition} 
-Re^{3/4} Fr^{1/2} \gg 1 \, .
-\end{equation} 
-However, a little bit of reflection may lead us to doubt that the shock width is equal to the Kolmogorov scale. The reason for this is that dissipation only occurs at the shocks.
-Using Navier-Stokes viscosity and assuming that the shock width is the characteristic dissipation length scale, the mean energy dissipation rate can be estimated as
-\begin{equation}
-\eps \sim \nu \frac{\mid \Delta u \mid ^2}{\delta x ^2} \frac{L_s \delta x}{\cal{A}} \sim \nu \frac{ \;\;\;  (\epsilon \lambda_b)^{2/3} }{\delta x \lambda_b} \, ,
-\end{equation} 
-where we have used the estimate (\ref{Strength}) for the shock amplitude. Consequently we obtain
-\begin{equation} \label{ShockWidth}
-\delta x \sim \frac{\eta^{4/3}}{\lambda_b^{1/3}} \sim \frac{\eta^{4/3}}{\lambda_l^{1/3}} F_f^{-1/6} \, ,
-\end{equation} 
-where we have used the observed scaling law (\ref{MeanDistance}) for $ \lambda_b = d $.
-An analogous result is obtained if we instead use hyperviscosity.
-The estimate (\ref{ShockWidth}) suggests that $ \delta x $ should become somewhat larger  with increasing $ c $, but very slowly, $ \delta x \sim c^{1/6} $.
-It is difficult to judge from the simulations  if this is actually the case.
-In figure (\ref{fig_spectra_c40}) we see that the maximum of the bottleneck in the high wave number end of the spectra appears at a somewhat smaller wave number in the run with largest $ c $ as compared to the two other runs.
-We leave it as an open question whether this is a signature of a slowly increasing shock width with increasing $ c $.
-It is interesting to note that if (\ref{ShockWidth}) is used as the estimate of $ \delta x $ in (\ref{NC}) instead of the Kolmogorov scale, we actually obtain the same condition (\ref{Condition}).
+On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large, since the shock width $ \delta x $ is decreasing indefinitely with increasing Reynolds number.
 
@@
 This study may therefore give important clues to the long standing problem of acoustic turbulence, in two and three dimensions.
-A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), apart from the constant.
+A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), with the only difference that the constant $ 4 $ on the right hand side should be replaced by $ 8/3 $.
 In three dimensions we find
@@
 \end{equation}
- In the case of acoustic turbulence $ \delta h $ should  be interpreted as a density increment rather than a displacement increment.
+ In the case of acoustic turbulence $ \delta h $ should  be interpreted as a normalised density increment rather than a displacement increment.
 If shocks in  three dimensions are assumed to form as  smooth surfaces rather than smooth lines, then the mean distance, $ d $, between the shocks will appear in the model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total  shock area and $ \cal{V} $ is the volume of the domain.

### 2018-10-16 Python/make_fig_diss_spectra.py
WIP dissipation spectra

@@ -1,0 +1,92 @@
+#!/usr/bin/env python
+from fractions import Fraction
+import numpy as np
+import matplotlib.pyplot as plt
+import seaborn as sns
+import fluidsim as fls
+import h5py
+
+from base import (
+    _k_max, _k_diss, _eps, set_figsize, matplotlib_rc, _index_where, linestyles, rev_legend)
+from paths import paths_sim, exit_if_figure_exists, load_df
+from make_fig_spectra import _mean_spectra
+
+#color_list = \
+#    iter(['r', 'b', 'g', 'c', 'm', 'y', 'k'])
+    # iter(plt.cm.jet(pl.linspace(0,1,3)))
+# style = linestyles()
+
+
+def _label():
+    numerator = r'\nu_8 k^{8} k_d E(k)'
+    return f"${numerator}$"
+
+
+def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb):
+    sim = fls.load_sim_for_plot(path, merge_missing_params=True)
+    kh, E_tot, EK, EA = _mean_spectra(sim, t_start)
+    eps = _eps(sim, t_start)
+    k_d = _k_diss(sim.params)
+
+
+    o = 2
+    norm = (k_d * sim.params.nu_8 * kh**8)
+    color_list = sns.color_palette()
+
+    kh_f = kh / k_d
+    ax.plot(
+        kh_f, E_tot * norm,
+        c=color_list[run_nb],
+        linewidth=1, 
+        label=f'$c = {c}, n= {sim.params.oper.nx}$')
+    
+    ax.vlines(kh_f[np.where(
+        (E_tot * norm) == (E_tot * norm).max())
+    ], 0, 1.2, colors=color_list[run_nb], linewidth=0.5)
+
+#     if run_nb == 0:
+#         s1 = slice(_index_where(kh_f, 3), _index_where(kh_f, 80))
+#         s2 = slice(_index_where(kh_f, 30), _index_where(kh_f, 200))
+#         ax.plot((kh_f)[s1], 0.7 * (kh_f ** -2 / norm)[s1], 'k-', linewidth=1)
+#         ax.text(10, 0.2, '$k^{-2}$')
+    ax.set_ylim(0, 1.2)
+    ax.set_xlim(0.6, 2.)
+
+    ax.set_xlabel('$k/k_d$')
+    ax.set_ylabel(_label())
+    # ax.legend()
+    # rev_legend(ax, loc=1, fontsize=8)
+
+
[…]

### 2018-10-17 Python/make_fig_diss_spectra.py
Dissipation spectra for c=20 on left and n=1920 on right groups

@@ -2,6 +2,7 @@
 from fractions import Fraction
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.ticker import AutoMinorLocator
 import seaborn as sns
 import fluidsim as fls
 import h5py
@@ -18,7 +19,7 @@ from make_fig_spectra import _mean_spectra
 
 
 def _label():
-    numerator = r'\nu_8 k^{8} k_d E(k)'
+    numerator = r'2 \nu_8 k^{8} k_d E(k) / \epsilon'
     return f"${numerator}$"
 
 
@@ -34,23 +35,27 @@ def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb):
     color_list = sns.color_palette()
 
     kh_f = kh / k_d
+    integral = np.trapz(2 * E_tot*norm, kh_f, dx=kh_f[1] - kh_f[0])
+
     ax.plot(
-        kh_f, E_tot * norm,
+        kh_f, 2 * E_tot * norm / eps, # (2 * integral),
         c=color_list[run_nb],
         linewidth=1, 
-        label=f'$c = {c}, n= {sim.params.oper.nx}$')
+        # label=f'$c = {c}, n= {sim.params.oper.nx}$'
+        label=f'int={integral}'
+    )
+    
     
     ax.vlines(kh_f[np.where(
         (E_tot * norm) == (E_tot * norm).max())
-    ], 0, 1.2, colors=color_list[run_nb], linewidth=0.5)
+    ], 0, 2.2, colors=color_list[run_nb], linewidth=0.5)
 
-#     if run_nb == 0:
-#         s1 = slice(_index_where(kh_f, 3), _index_where(kh_f, 80))
-#         s2 = slice(_index_where(kh_f, 30), _index_where(kh_f, 200))
-#         ax.plot((kh_f)[s1], 0.7 * (kh_f ** -2 / norm)[s1], 'k-', linewidth=1)
-#         ax.text(10, 0.2, '$k^{-2}$')
-    ax.set_ylim(0, 1.2)
-    ax.set_xlim(0.6, 2.)
+    # more minor ticks
+    minor_locator = AutoMinorLocator(5)
+    ax.xaxis.set_minor_locator(minor_locator)
+
+    ax.set_ylim(0, 2.2)
+    ax.set_xlim(0.6, 2.5) #2
 
     ax.set_xlabel('$k/k_d$')
     ax.set_ylabel(_label())
[…]

### 2018-10-17 Python/make_fig_diss_spectra.py
Exact ratios of k where dissipation peaks

@@ -37,18 +37,20 @@ def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb):
     kh_f = kh / k_d
     integral = np.trapz(2 * E_tot*norm, kh_f, dx=kh_f[1] - kh_f[0])
 
+    kdiss_max = kh_f[np.where(
+        (E_tot * norm) == (E_tot * norm).max())
+    ]
     ax.plot(
         kh_f, 2 * E_tot * norm / eps, # (2 * integral),
         c=color_list[run_nb],
         linewidth=1, 
         # label=f'$c = {c}, n= {sim.params.oper.nx}$'
-        label=f'int={integral}'
+        label=f'{kdiss_max}'
+        # label=f'int={integral}'
     )
     
     
-    ax.vlines(kh_f[np.where(
-        (E_tot * norm) == (E_tot * norm).max())
-    ], 0, 2.2, colors=color_list[run_nb], linewidth=0.5)
+    ax.vlines(kdiss_max, 0, 2.2, colors=color_list[run_nb], linewidth=0.5)
 
     # more minor ticks
     minor_locator = AutoMinorLocator(5)

### 2018-10-17 Latex/ArticleNew.tex
line length

@@
 % \baselineskip 8mm
+
 \begin{abstract}
-The dynamics of irrotational shallow water wave turbulence forced in large scales
-and dissipated  at small scales is investigated.
-First, we derive the shallow water analogue of the `four-fifths law' of three-dimensional turbulence for a third order structure function involving velocity and displacement increments.
-Using this relation and assuming that the flow is dominated by shocks we develop a simple model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ \eps $ is the mean dissipation rate and $ d $ the mean distance between the shocks, and that the
-$ p $:th order displacement and velocity structure functions scale as
-$ (\eps d)^{p/3} r/d $, where $ r $ is the separation. 
-Then we carry out a series of forced simulations with resolutions up to $7680^2$, varying the Froude number,  $F_{f} = \eps^{1/3}  / ck_f^{1/3} $, where $ k_f $  is the forcing wave number and $c$ is the wave speed.
-In all simulations a stationary state is reached  in which there is a constant spectral energy flux and equipartition between kinetic and potential energy in the constant flux range.
-The third order structure function relation is satisfied with a high degree of accuracy.
-Mean energy is found to scale as $ E \sim \sqrt{\epsilon c/k_f} $,  and is also dependent on resolution, indicating that shallow water wave turbulence does not fit into the paradigm of a Richardson-Kolmogorov cascade.
-In all simulations shocks develop, displayed as long thin bands of negative divergence in flow visualizations.
-The mean distance between the shocks is found to scale  as $ d \sim F_f^{1/2}/k_f $.
-Structure functions of second and higher order are found to scale in good agreement with the model.
-We conclude that in the weak limit, $ F_f \rightarrow 0 $, shocks will become denser and weaker and finally disappear for a finite Reynolds number.
-On the other hand, for a given $ F_{f} $, no matter how small, shocks will prevail if the Reynolds number is sufficiently large.
+
+The dynamics of irrotational shallow water wave turbulence forced in large
+scales and dissipated at small scales is investigated. First, we derive the
+shallow water analogue of the `four-fifths law' of three-dimensional turbulence
+for a third order structure function involving velocity and displacement
+increments. Using this relation and assuming that the flow is dominated by
+shocks we develop a simple model predicting that the shock amplitude scales as
+$ (\epsilon d)^{1/3} $, where $ \eps $ is the mean dissipation rate and $ d $
+the mean distance between the shocks, and that the $ p $:th order displacement
+and velocity structure functions scale as $ (\eps d)^{p/3} r/d $, where $ r $
+is the separation. Then we carry out a series of forced simulations with
+resolutions up to $7680^2$, varying the Froude number, $F_{f} = \eps^{1/3} /
+ck_f^{1/3} $, where $ k_f $ is the forcing wave number and $c$ is the wave
+speed. In all simulations a stationary state is reached in which there is a
+constant spectral energy flux and equipartition between kinetic and potential
+energy in the constant flux range. The third order structure function relation
+is satisfied with a high degree of accuracy. Mean energy is found to scale as $
+E \sim \sqrt{\epsilon c/k_f} $, and is also dependent on resolution, indicating
+that shallow water wave turbulence does not fit into the paradigm of a
+Richardson-Kolmogorov cascade. In all simulations shocks develop, displayed as
+long thin bands of negative divergence in flow visualizations. The mean
+distance between the shocks is found to scale as $ d \sim F_f^{1/2}/k_f $.
+Structure functions of second and higher order are found to scale in good
+agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow
+0 $, shocks will become denser and weaker and finally disappear for a finite
+Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small,
+shocks will prevail if the Reynolds number is sufficiently large.
 
@@
 \cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
-inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the
-exact solutions of the kinetic equation corresponding to a constant
-downscale energy flux is associated with a spectrum scaling as $E(k)
-\sim  k^{-8/3}$, while \cite{ZakharovSagdeev1970} 
-used weak turbulence formalism to derive a spectrum of the form $ E(k) \sim  k^{-3/2} $ for acoustic turbulence.
-This prediction is of particular interest, since the aqoustic equations and the SW equations are identical when a first order expansion is made in
-density or displacement pertubations.
-It may be questioned, however,  that weak turbulence formalism is applicable to acoustic and SW wave turbulence, no matter how weak the nonlinearities are supposed to be.
-As pointed out by \cite{KadomtsevPet1970} and
-\cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in the same direction have
-the same velocity and interact strongly, which leads to the
-formation of shocks.  In this case, the weak wave turbulence
-formalism is unable to give valuable results.  Such sharp and long
-structures have been observed in many simulations
-\cite[]{FargeSadourny1989, PolvaniMcWilliamsSpallFord1994,
-LahayeZeitlin2012} but their effects are not well understood.
+inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
+solutions of the kinetic equation corresponding to a constant downscale energy
+flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
+\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
+of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
+of particular interest, since the aqoustic equations and the SW equations are
+identical when a first order expansion is made in density or displacement
+pertubations. It may be questioned, however, that weak turbulence formalism is
+applicable to acoustic and SW wave turbulence, no matter how weak the
+nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
+and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
+the same direction have the same velocity and interact strongly, which leads to
+the formation of shocks. In this case, the weak wave turbulence formalism is
+unable to give valuable results. Such sharp and long structures have been
+observed in many simulations \cite[]{FargeSadourny1989,
+PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
+well understood.
 %
-As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by shocks will scale as $ k^{-2} $, a 
- prediction which has been confirmed by a great number of simulations of Burgers equation \cite[for a review, see ] []{Frisch2001}.
- The shocks also lead to very strong intermittency, as demonstrated by
-\cite{BouchaudMezardParisi1995} and \cite{WeinanKhaninMazelSinai1997}
-for Burgers turbulence.
+As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
+shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
+great number of simulations of Burgers equation \cite[for a review, see ]
+[]{Frisch2001}. The shocks also lead to very strong intermittency, as
+demonstrated by \cite{BouchaudMezardParisi1995} and
+\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
 %
@@
 % What is the slope of
-How do energy spectra scale with the 
-input parameters? From a theoretical point of view, the most interesting issue is, perhaps,  the nature of the dynamics in the limit of weak nonlinearities. Will shocks prevail in this limit?
+How do energy spectra scale with the input parameters? From a theoretical point
+of view, the most interesting issue is, perhaps, the nature of the dynamics in
+the limit of weak nonlinearities. Will shocks prevail in this limit?
 %
@@
 
-We have carried out a theoretical and numerical investigation of SW wave turbulence.
-First, we derived the SW analogue (\ref{eq_Kolmo}) of the the `four-fifths' law of Kolmogorov turbulence.
-Using this relation and straightforward statistical and geometrical arguments we developed a simple shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3} $, where $ d $ is the mean distance between the shocks, and that the $ p $:th order structure function above a certain minimum will scale as $ (\epsilon d)^{p/3} r/d $.
-Then, we carried out a series of twenty forced dissipative simulations, varying the Froude number and the resolution.
-In all simulations, a statistically stationary state were reached and in all simulations we observed shocks.
-The flow variables in each Fourier mode were found to evolve in accordance with linear wave dynamics, with equipartition between APE and KE over a period.
-The third order structure function relation was fulfilled with a high degree of accuracy.
-From the simulations we made two interesting observations that fall outside the predictive range of the model.
-The first observation  was  that mean energy in the stationary state approximately scales as (\ref{MeanEnergy}), suggesting that the normalised dissipation (\ref{Dissipation}) will go to zero both in the limit of small viscosity and large  wave speed.
-This is different from three dimensional Kolmogorov turbulence as well as strongly stratified turbulence, where, in both cases, dissipation is finite in the limit of small viscosity, and in the latter case also is independent of the degree of stratification.
-This observation suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade.
-The second observation we made was that the mean distance between the shocks scales as $ c^{-1/2} $, if the other parameters are held constant.
-As we increased $ c $, the shocks were thus becoming denser.
-Using this observation we tested the shock model by plotting the normalised and compensated structure functions of different orders.
-Generally we found that there was a quite good agreement between the simulation results and the model predictions, becoming better with decreasing  wave speed and increasing resolution.
+We have carried out a theoretical and numerical investigation of SW wave
+turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the
+`four-fifths' law of Kolmogorov turbulence. Using this relation and
+straightforward statistical and geometrical arguments we developed a simple
+shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3}
+$, where $ d $ is the mean distance between the shocks, and that the $ p $:th
+order structure function above a certain minimum will scale as $ (\epsilon
+d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative
+simulations, varying the Froude number and the resolution. In all simulations,
+a statistically stationary state were reached and in all simulations we
+observed shocks. The flow variables in each Fourier mode were found to evolve
+in accordance with linear wave dynamics, with equipartition between APE and KE
+over a period. The third order structure function relation was fulfilled with a
+high degree of accuracy. From the simulations we made two interesting
+observations that fall outside the predictive range of the model. The first
+observation was that mean energy in the stationary state approximately scales
+as (\ref{MeanEnergy}), suggesting that the normalised dissipation
+(\ref{Dissipation}) will go to zero both in the limit of small viscosity and
+large wave speed. This is different from three dimensional Kolmogorov
+turbulence as well as strongly stratified turbulence, where, in both cases,
+dissipation is finite in the limit of small viscosity, and in the latter case
+also is independent of the degree of stratification. This observation suggests
+that SW wave turbulence does not fit into the paradigm of a local
+Richardson-Kolmogorov cascade. The second observation we made was that the mean
+distance between the shocks scales as $ c^{-1/2} $, if the other parameters are
+held constant. As we increased $ c $, the shocks were thus becoming denser.
+Using this observation we tested the shock model by plotting the normalised and
+compensated structure functions of different orders. Generally we found that
+there was a quite good agreement between the simulation results and the model
+predictions, becoming better with decreasing wave speed and increasing
+resolution.
 
-Combining the model and the observations we can get a quite good picture of the dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow  0 $.  
-The picture may become more vivid if we say `wave breaking' were we previously have talked about shock formation, and also say
-`wave lengths' were we previously have talked about length scales.
-We identify the longest wave length, $ \lambda_l $,  with the forcing scale $  L_f $ and the breaking wave length, $ \lambda_b $, with the mean distance, $ d $, between the shocks.
-There are two dynamically different  regimes, the short wave  regime, $ [\delta x, \; \lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $.
-We first consider the latter, whose width scales  $ \lambda_{l} /\lambda_b \sim F_f^{-1/2} $.
-Identifying the amplitude of the breaking waves with the shock amplitude, $ (\eps d)^{1/3} $, we find that the ratio between the amplitude of the longest waves and the breaking waves scales as $ E^{1/2}/(\eps d)^{1/3} \sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute  $ n $ with a Reynolds number to some power.
-Thus, for small $ F_f $ and large Reynolds number the longest waves are not directly influenced by wave breaking.
-The Reynolds number dependence of the amplitude ratio makes it unlikely that a general similarity theory can be easily formulated for this range.
-Therefore, predictions from weak turbulence theory \cite[for example][]{ZakharovSagdeev1970}
-are not likely to hold for this range, although it is not directly influenced by wave breaking.
-The exact values of the power law exponents in the argument leading to this conclusion are, of course, not important.
-As for the short wave regime, the width scales as $  \lambda_b /\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number.
-As $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that breaking will disappear.
-On the other hand, it may be argued that wave breaking will take place for any small $ F_f $, provided that the Reynolds number is sufficiently large, since the shock width $ \delta x $ is decreasing indefinitely with increasing Reynolds number.
+Combining the model and the observations we can get a quite good picture of the
+dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow 0 $. The
+picture may become more vivid if we say `wave breaking' were we previously have
+talked about shock formation, and also say `wave lengths' were we previously
+have talked about length scales. We identify the longest wave length, $
+\lambda_l $, with the forcing scale $ L_f $ and the breaking wave length, $
+\lambda_b $, with the mean distance, $ d $, between the shocks. There are two
+dynamically different regimes, the short wave regime, $ [\delta x, \;
+\lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $. We first
+consider the latter, whose width scales $ \lambda_{l} /\lambda_b \sim
+F_f^{-1/2} $. Identifying the amplitude of the breaking waves with the shock
+amplitude, $ (\eps d)^{1/3} $, we find that the ratio between the amplitude of
+the longest waves and the breaking waves scales as $ E^{1/2}/(\eps d)^{1/3}
+\sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute $ n $ with a
+Reynolds number to some power. Thus, for small $ F_f $ and large Reynolds
+number the longest waves are not directly influenced by wave breaking. The
+Reynolds number dependence of the amplitude ratio makes it unlikely that a
+general similarity theory can be easily formulated for this range. Therefore,
+predictions from weak turbulence theory \cite[for
+example][]{ZakharovSagdeev1970} are not likely to hold for this range, although
+it is not directly influenced by wave breaking. The exact values of the power
+law exponents in the argument leading to this conclusion are, of course, not
+important. As for the short wave regime, the width scales as $ \lambda_b
+/\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number. As
+$ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that
+breaking will disappear. On the other hand, it may be argued that wave breaking
+will take place for any small $ F_f $, provided that the Reynolds number is
+sufficiently large, since the shock width $ \delta x $ is decreasing
+indefinitely with increasing Reynolds number.
 
-The question that originally motivated this study was if SW wave turbulence can be used as a model for energy dissipation in the the atmosphere and the oceans.
-Undoubtedly, the answer to this question is negative and the reason for this is not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum which is not consistent with the observed $ k^{-5/3} $-spectrum.
-The main reason is that
-SW wave turbulence is  a far too inefficient agent of dissipation.
-Since the Reynolds number of geophysical flows is extremely large and the stratification is strong, the  relation (\ref{Dissipation}) implies that dissipation would be absent in the interior of the atmosphere and the oceans with SW turbulence as the responsible agent.
-This not what we observe.
+The question that originally motivated this study was if SW wave turbulence can
+be used as a model for energy dissipation in the the atmosphere and the oceans.
+Undoubtedly, the answer to this question is negative and the reason for this is
+not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
+which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
+reason is that SW wave turbulence is a far too inefficient agent of
+dissipation. Since the Reynolds number of geophysical flows is extremely large
+and the stratification is strong, the relation (\ref{Dissipation}) implies that
+dissipation would be absent in the interior of the atmosphere and the oceans
+with SW turbulence as the responsible agent. This not what we observe.
 
-Although the answer to the question that originally motivated this study is negative, it may lead us or some other investigators to pursue another interesting research direction.
-As pointed out in the introduction, the acoustic equations are to the lowest order expansion in density pertubations identical to the SW equations.
-This study may therefore give important clues to the long standing problem of acoustic turbulence, in two and three dimensions.
-A similar shock model as we developed in two dimensions may easily be formulated in three dimensions, where the third order structure function law will be  similar to (\ref{eq_Kolmo}), with the only difference that the constant $ 4 $ on the right hand side should be replaced by $ 8/3 $.
-In three dimensions we find
+Although the answer to the question that originally motivated this study is
+negative, it may lead us or some other investigators to pursue another
+interesting research direction. As pointed out in the introduction, the
+acoustic equations are to the lowest order expansion in density pertubations
+identical to the SW equations. This study may therefore give important clues to
+the long standing problem of acoustic turbulence, in two and three dimensions.
+A similar shock model as we developed in two dimensions may easily be
+formulated in three dimensions, where the third order structure function law
+will be similar to (\ref{eq_Kolmo}), with the only difference that the constant
+$ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions
+we find
 \begin{equation}
@@
 \end{equation}
- In the case of acoustic turbulence $ \delta h $ should  be interpreted as a normalised density increment rather than a displacement increment.
-If shocks in  three dimensions are assumed to form as  smooth surfaces rather than smooth lines, then the mean distance, $ d $, between the shocks will appear in the model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total  shock area and $ \cal{V} $ is the volume of the domain.
-The shock amplitude will thus scale as $ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will form in a similar way as in two dimensions.
-If they do, the most interesting questions are if the mean energy and the mean distance between the shocks scale in a similar way in three dimensions as in two dimensions.
-Simulations or experiments of acoustic turbulence may provide answers to these questions -- answers that will lead to further clues to a theoretical understanding of acoustic turbulence.
- We hope that the present study will stimulate research in this direction.
+In the case of acoustic turbulence $ \delta h $ should be interpreted as a
+normalised density increment rather than a displacement increment. If shocks in
+three dimensions are assumed to form as smooth surfaces rather than smooth
+lines, then the mean distance, $ d $, between the shocks will appear in the
+model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total shock area and
+$ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as
+$ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon
+d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will
+form in a similar way as in two dimensions. If they do, the most interesting
+questions are if the mean energy and the mean distance between the shocks scale
+in a similar way in three dimensions as in two dimensions. Simulations or
+experiments of acoustic turbulence may provide answers to these questions --
+answers that will lead to further clues to a theoretical understanding of
+acoustic turbulence. We hope that the present study will stimulate research in
+this direction.
 

### 2018-10-17 Latex/section_advanced_theory.tex
line length

@@
 
-We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third order velocity structure function of incompressible isotropic turbulence.
-In the case of irrotational shallow water wave turbulence the analogous law contains a third order structure function involving both velocity and displacement increments.
-In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational.
-To derive the law it is convenient to start from the following equations
+We will now derive an analogue of the so called `four-fifths law'
+\cite[]{Kolmogorov1941} for the the third order velocity structure function of
+incompressible isotropic turbulence. In the case of irrotational shallow water
+wave turbulence the analogous law contains a third order structure function
+involving both velocity and displacement increments. In order for such a law to
+exist it is necessary that the velocity field is either non-divergent
+(incompressible) or irrotational. To derive the law it is convenient to start
+from the following equations
 \begin{eqnarray} \label{IRR}
@@
 \end{eqnarray}
-where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}).
-We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
-Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $.
-Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find
+where we have used the assumption that the velocity field is irrotational in
+(\ref{IRR}). We consider two points, positioned at $ \bf x $ and $ {\bf
+x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
+Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $
+as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $
+\partial^{\prime}_i $. Treating $ \bf x $ and $ {\bf x}^\prime $ as independent
+variables we find
 
@@
 \end{equation}
-For separations that are considerably larger than dissipative scales of motion and considerably smaller than forcing scales a standard argument \cite[see for example][]{Frisch} gives that the left hand side is approximately equal to $ -8 \eps $, where $ \eps $ is the mean dissipation rate.
-It is interesting to note that a factor of $ 8 $ appears in the case when the velocity field is irrotational while a corresponding factor of $ 4 $ appears in the case when the velocity field is non-divergent.
-Using isotropy and integrating yield the Kolmogorov law for
-irrotational shallow water wave  turbulence
+For separations that are considerably larger than dissipative scales of motion
+and considerably smaller than forcing scales a standard argument \cite[see for
+example][]{Frisch} gives that the left hand side is approximately equal to $ -8
+\eps $, where $ \eps $ is the mean dissipation rate. It is interesting to note
+that a factor of $ 8 $ appears in the case when the velocity field is
+irrotational while a corresponding factor of $ 4 $ appears in the case when the
+velocity field is non-divergent. Using isotropy and integrating yield the
+Kolmogorov law for irrotational shallow water wave turbulence
 \begin{equation}

### 2018-10-17 Latex/section_methods.tex
line length

@@
-We have carried out a series of twenty forced-dissipative simulations of the SW equations in a quadratic domain with periodic boundary conditions using a standard pseudo spectral code.
-The simulations were started from zero initial conditions and were run till a statistically stationary state was reached.
-The equations
-were reformulated in terms of  the three eigenmodes of the linearized equations in Fourier space. One of these eigenmodes is zero for an irrotational flow.  
-We first carried out a few test simulations in which all three eigenmodes were allowed to evolve in time.
-However, when only the two wave modes are forced vorticity remains very small throughout the simulations and does not affect the wave dynamics.
-Therefore, we chose to solve the equations only for the two wave modes.
-As discussed in the previous section,  a linear viscous term in (\ref{eq_uu})
-will not conserve momentum exactly and does not give a strictly positive definite expression for energy dissipation.
-We have relaxed the requirements of exact momentum conservation and positive definite energy dissipation.
-Instead of  using the nonlinear form of the viscous term in (\ref{eq_uu}) we have used a higher order linear operator  $ \nu_8 \nabla^{8} $ both in (\ref{eq_uu}) and
-(\ref{eq_h}), where $ \nu_8 $ is a `hyperdiffusion' or a `hyperviscosity'. There is no strong physical motivation for this
-modification but, as discussed by \cite{FargeSadourny1989}, a molecular viscous operator 
- of the form $\nu \nabla^2 $ is not necessarily a
-relevant model of the actual small-scale dissipation for SW
-flows, which should rather be described as a transition from
-two-dimensional to three-dimensional motions before reaching the
-scales where dissipation actually occurs.
+We have carried out a series of twenty forced-dissipative simulations of the SW
+equations in a quadratic domain with periodic boundary conditions using a
+standard pseudo spectral code. The simulations were started from zero initial
+conditions and were run till a statistically stationary state was reached. The
+equations were reformulated in terms of the three eigenmodes of the linearized
+equations in Fourier space. One of these eigenmodes is zero for an irrotational
+flow. We first carried out a few test simulations in which all three eigenmodes
+were allowed to evolve in time. However, when only the two wave modes are
+forced vorticity remains very small throughout the simulations and does not
+affect the wave dynamics. Therefore, we chose to solve the equations only for
+the two wave modes. As discussed in the previous section, a linear viscous term
+in (\ref{eq_uu}) will not conserve momentum exactly and does not give a
+strictly positive definite expression for energy dissipation. We have relaxed
+the requirements of exact momentum conservation and positive definite energy
+dissipation. Instead of using the nonlinear form of the viscous term in
+(\ref{eq_uu}) we have used a higher order linear operator $ \nu_8 \nabla^{8} $
+both in (\ref{eq_uu}) and (\ref{eq_h}), where $ \nu_8 $ is a `hyperdiffusion'
+or a `hyperviscosity'. There is no strong physical motivation for this
+modification but, as discussed by \cite{FargeSadourny1989}, a molecular viscous
+operator of the form $\nu \nabla^2 $ is not necessarily a relevant model of the
+actual small-scale dissipation for SW flows, which should rather be described
+as a transition from two-dimensional to three-dimensional motions before
+reaching the scales where dissipation actually occurs.
 %
-Time advancement is carried out by a classical fourth-order
-Runge-Kutta scheme for the nonlinear term and an exact integration for
-the linear and dissipative terms.  This explicit integration is
-especially useful at very high resolution and very large $c$ when
-the shortest waves are very fast. 
-We use an adaptable time step method which maximizes the time step
-over a standard Courant-Friedrichs-Lewy condition
-\cite[]{Lundbladh1999, AugierChomazBillant2012}.
+Time advancement is carried out by a classical fourth-order Runge-Kutta scheme
+for the nonlinear term and an exact integration for the linear and dissipative
+terms. This explicit integration is especially useful at very high resolution
+and very large $c$ when the shortest waves are very fast. We use an adaptable
+time step method which maximizes the time step over a standard
+Courant-Friedrichs-Lewy condition \cite[]{Lundbladh1999,
+AugierChomazBillant2012}.
 %
-Most of the aliasing is removed by truncating 8/9 of the modes along
-each direction \cite[for a detail discussion on the issues of the
-non-conservation of the non-quadratic energy and the aliasing errors
-in the truncated one-layer shallow water model,
-see][]{FargeSadourny1989}. The resolution is characterized by the number of nodes, $n$, in the each
-direction and has been varied from 960 to 7680.
+Most of the aliasing is removed by truncating 8/9 of the modes along each
+direction \cite[for a detail discussion on the issues of the non-conservation
+of the non-quadratic energy and the aliasing errors in the truncated one-layer
+shallow water model, see][]{FargeSadourny1989}. The resolution is characterized
+by the number of nodes, $n$, in the each direction and has been varied from 960
+to 7680.
 %
-The wave speed $c$ has been varied over almost two orders of magnitude from
-10 to 700. The wave modes are forced in a shell in spectral space 
-corresponding to relatively small wave numbers, 
-$ 5 \delta k <  |\kk| <  8 \delta k$,  
-where  $ \delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic domain. 
-The forcing is white noice in time and designed so that the energy injection rate is normalized to unity at each time step.
-The energy is dissipated at the smallest resolved scales by hyperviscosity.
-The value of the
-hyperviscosity, $\nu_8$, is chosen in such a way that the  maximum wave number is larger than the dissipation wave number
+The wave speed $c$ has been varied over almost two orders of magnitude from 10
+to 700. The wave modes are forced in a shell in spectral space corresponding to
+relatively small wave numbers, $ 5 \delta k < |\kk| < 8 \delta k$, where $
+\delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
+domain. The forcing is white noice in time and designed so that the energy
+injection rate is normalized to unity at each time step. The energy is
+dissipated at the smallest resolved scales by hyperviscosity. The value of the
+hyperviscosity, $\nu_8$, is chosen in such a way that the maximum wave number
+is larger than the dissipation wave number
 \begin{equation}
@@
 \end{equation}
- where $ \eps $ is the mean energy dissipation rate. We found that  $
- k_{d} \simeq \kmax/ 2.5$, where $\kmax =
-(8/9)\pi n/L $ is the maximum wave number, is  sufficient in order for dissipation spectra to be resolved.
-Since the energy injection rate is normalized to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state.
-The strength of the stratification is characterized by a Froude number, defined as
+where $ \eps $ is the mean energy dissipation rate. We found that $ k_{d}
+\simeq \kmax/ 2.5$, where $\kmax = (8/9)\pi n/L $ is the maximum wave number,
+is sufficient in order for dissipation spectra to be resolved. Since the energy
+injection rate is normalized to unity and all simulations reach a stationary
+state in which dissipation is equal to the injection rate, $ \nu_8 $ can be
+chosen already from the start so that this condition will be fulfilled in the
+stationary state. The strength of the stratification is characterized by a
+Froude number, defined as
 \begin{equation} \label{Fr}
@@
 \end{tabular}
-\caption{Parameters for all simulations.
-$ n $: number of nodes in each direction, $ c $: wave speed, $ \nu_8 $: hyperviscosity, $ \eps $: time averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio between dissipation wave number and forcing wave number, $ F_f  $: Froude number, $ t_{max} $:   end time of simulation.}
+\caption{Parameters for all simulations. $ n $: number of nodes in each
+direction, $ c $: wave speed, $ \nu_8 $: hyperviscosity, $ \eps $: time
+averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio
+between dissipation wave number and forcing wave number, $ F_f $: Froude
+number, $ t_{max} $: end time of simulation.}
 \end{center}
@@
 \centerline{\includegraphics[width=5.12in]{../Pyfig/fig_Emean_time}}
-\caption{Space averaged energy, 
-$E = E_K + E_A $, versus time 
-for all simulations. }
+\caption{Space averaged energy, $E = E_K + E_A $, versus time for all
+simulations. }
 \label{fig_Evstime}
@@
 \centerline{\includegraphics[width=5.8in]{../Pyfig/fig_energy_w}}
-\caption{Left: Mean energy in the stationary state versus $ c $ for different resolutions.
-The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2} $.
-Right: Normalized mean energy in the stationary state versus resolution $ n $ for different $ c $.}
+\caption{Left: Mean energy in the stationary state versus $ c $ for different
+resolutions. The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2}
+$. Right: Normalized mean energy in the stationary state versus resolution $ n
+$ for different $ c $.}
 \label{MeanE}
@@
 
-The time evolution of  
-mean energy is shown in
-figure~\ref{fig_Evstime} for all twenty simulations.
-After an initial period of growth, mean energy is leveling out at different values for different runs.
-This is not the same picture as we see in simulations of three-dimensional incompressible turbulence or stratified turbulence, where all curves would have leveled out more or less at the same value.
-We find that mean energy in the stationary state is a function of both $ c $ (or the Froude number) and resolution $ n $ and that the functional dependence  can be approximately written as
+The time evolution of mean energy is shown in figure~\ref{fig_Evstime} for all
+twenty simulations. After an initial period of growth, mean energy is leveling
+out at different values for different runs. This is not the same picture as we
+see in simulations of three-dimensional incompressible turbulence or stratified
+turbulence, where all curves would have leveled out more or less at the same
+value. We find that mean energy in the stationary state is a function of both $
+c $ (or the Froude number) and resolution $ n $ and that the functional
+dependence can be approximately written as
 \begin{equation} \label{MeanEnergy}
@@
 \end{equation}
-where $ L_f = \pi/k_f $ is the forcing scale.
-In figure \ref{MeanE} to the left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $ n $.
-For each resolution the  points are approaching a power law $ C_n c^{1/2} $  with increasing values of $ C_n $ for increasing $ n $.
-In the same figure to the right we see
-$ E/\sqrt{L_f c \eps} $ for different values of $ c $.
-For each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is becoming slightly larger with increasing $ c $, approaching almost the same value $ \alpha \approx 0.33 $ for the three highest values of $ c $.
-The relation (\ref{MeanEnergy}) can be reformulated as
+where $ L_f = \pi/k_f $ is the forcing scale. In figure \ref{MeanE} to the
+left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $
+n $. For each resolution the points are approaching a power law $ C_n c^{1/2} $
+with increasing values of $ C_n $ for increasing $ n $. In the same figure to
+the right we see $ E/\sqrt{L_f c \eps} $ for different values of $ c $. For
+each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
+becoming slightly larger with increasing $ c $, approaching almost the same
+value $ \alpha \approx 0.33 $ for the three highest values of $ c $. The
+relation (\ref{MeanEnergy}) can be reformulated as
 \begin{equation} \label{Dissipation}
@@
 \end{equation}
-Since the simulations are well resolved the dependence on resolution should not be interpreted as consequence of the numerics but rather as a Reynolds number effect, although it is not hundred percent clear how a Reynolds number should be defined in our case.
-We may note, however, that $ n $ is  proportional $ k_{d} / k_f $ and  the corresponding ratio in Kolmogorov turbulence scales as $ Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $ \nu $ is the kinematic viscosity.
-If we simply define a Reynolds number as
+Since the simulations are well resolved the dependence on resolution should not
+be interpreted as consequence of the numerics but rather as a Reynolds number
+effect, although it is not hundred percent clear how a Reynolds number should
+be defined in our case. We may note, however, that $ n $ is proportional $
+k_{d} / k_f $ and the corresponding ratio in Kolmogorov turbulence scales as $
+Re^{3/4} $ since the Kolmogorov scale is proportional to $ \nu^{3/4} $, where $
+\nu $ is the kinematic viscosity. If we simply define a Reynolds number as
 \begin{equation}
@@
 \end{equation}
-we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8 \alpha/3} $.
-The normalised energy dissipation on the left hand side of  (\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
-This is very different from three-dimensional turbulence
-where there is a local Richardson-Kolmogorov cascade, in which energy is successively transfered from large to small scales of motion.
-That the cascade is local means that eddies of a particular scale are not directly influenced by eddies of widely different scales.
-As a consequence, the normalized dissipation is of the order of unity independent of Reynolds number \cite[]{Pope, TennekesLumley}.
-A review of the experimental evidence and theoretical implications of this fundamental law of Kolmogorov turbulence is given by \cite{Vassilicos2015}.
-Our result (\ref{Dissipation})  suggests that SW wave turbulence does not fit into the paradigm of a local Richardson-Kolmogorov cascade.
-Moreover, it is not only in the limit of large Reynolds number the normalized dissipation will go to zero but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
-This is  different from three-dimensional stratified turbulence where the ratio on the left hand side of (\ref{Dissipation}) is of the order of unity in the limit of strong stratification  \cite[]{Lindborg2006, Brethouwer2007}.
+we can substitute $ n^{-2\alpha} $ in (\ref{Dissipation}) with $ Re^{-8
+\alpha/3} $. The normalised energy dissipation on the left hand side of
+(\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
+This is very different from three-dimensional turbulence where there is a local
+Richardson-Kolmogorov cascade, in which energy is successively transfered from
+large to small scales of motion. That the cascade is local means that eddies of
+a particular scale are not directly influenced by eddies of widely different
+scales. As a consequence, the normalized dissipation is of the order of unity
+independent of Reynolds number \cite[]{Pope, TennekesLumley}. A review of the
+experimental evidence and theoretical implications of this fundamental law of
+Kolmogorov turbulence is given by \cite{Vassilicos2015}. Our result
+(\ref{Dissipation}) suggests that SW wave turbulence does not fit into the
+paradigm of a local Richardson-Kolmogorov cascade. Moreover, it is not only in
+the limit of large Reynolds number the normalized dissipation will go to zero
+but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
+This is different from three-dimensional stratified turbulence where the ratio
+on the left hand side of (\ref{Dissipation}) is of the order of unity in the
+limit of strong stratification \cite[]{Lindborg2006, Brethouwer2007}.
 
- The `four-fifths law' for the third order structure function of Kolmogorov turbulence is often derived using the assumption of a local cascade \cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the limit of large Reynolds number \cite[]{Frisch}.
-As we just discussed, these assumptions seem to be violated in the case of SW wave turbulence.
-Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave turbulence is satisfied with a high degree of accuracy in our simulations.
-In figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and the third order structure function to the right.
-There is a broad constant flux range  with equipartition between KE and APE flux and an almost equally broad range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two third order structure functions associated with KE and APE.
-The assumptions of a local cascade and finite dissipation do not seem to be necessary in order for the third order structure function law  (\ref{eq_Kolmo}) to be valid.
+The `four-fifths law' for the third order structure function of Kolmogorov
+turbulence is often derived using the assumption of a local cascade
+\cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the
+limit of large Reynolds number \cite[]{Frisch}. As we just discussed, these
+assumptions seem to be violated in the case of SW wave turbulence.
+Nevertheless, the analogous law (\ref{eq_Kolmo}) that we derived for SW wave
+turbulence is satisfied with a high degree of accuracy in our simulations. In
+figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and
+the third order structure function to the right. There is a broad constant flux
+range with equipartition between KE and APE flux and an almost equally broad
+range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two
+third order structure functions associated with KE and APE. The assumptions of
+a local cascade and finite dissipation do not seem to be necessary in order for
+the third order structure function law (\ref{eq_Kolmo}) to be valid.
 
@@
 \centerline{\includegraphics[width=5.8in]{../Pyfig/fig_flux_struct_combined}}
-\caption{Left: Time averaged normalised spectral energy fluxes versus $ k/k_f $. Right: Time averaged normalised third order structure functions versus $ r/L_f $. From run W7. }
+\caption{Left: Time averaged normalised spectral energy fluxes versus $ k/k_f
+$. Right: Time averaged normalised third order structure functions versus $
+r/L_f $. From run W7. }
 \label{Flux}
@@
 \begin{figure}
- \centerline{
- \includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
-\caption{Frequency spectra of KE  and APE for different $ k = \mid {\bf k} \mid $, from run W7. The spectra are plotted  as functions of $\omega/\omega_l$, where
-$\omega_l = c k$.  From top to bottom: $ k /\delta k
-= 12$, 27, 62, 143, 327, and 746.  }
+\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
+\caption{Frequency spectra of KE and APE for different $ k = \mid {\bf k} \mid
+$, from run W7. The spectra are plotted as functions of $\omega/\omega_l$,
+where $\omega_l = c k$. From top to bottom: $ k /\delta k = 12$, 27, 62, 143,
+327, and 746. }
 \label{fig_spatiotemp_spectra}
 \end{figure}
+
 \begin{figure}
- \centerline{
- \includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
+\centerline{\includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
 \caption{Left: divergence $ \bnabla \cdot {\bf u} $. Right: velocity component in the $ y $-direction: $ u_y $. Top: run W6. Bottom: run W17.  }
@@
 \end{figure}
+
 \begin{figure}
@@
 
-The equipartition of KE and APE spectral fluxes suggests that the flow to leading order may be described as a collection of linear gravity waves with equipartition of KE and APE in each mode.
-To investigate this further we have collected time series of the flow variables from Fourier modes whose magnitude fall within certain shells,  $ \mid {\bf k} \mid \in [ k -\delta k/2, \; k+ \delta k/2] $,  and computed temporal power law spectra from these time series and averaged over all wave numbers in each shell.
-In other words we have computed KE and APE frequency spectra corresponding to different magnitudes of modes.
-Figure~\ref{fig_spatiotemp_spectra} presents such
-spectra plotted as a functions of the normalized frequency
-$\omega/\omega_l$, where $ \omega_l = kc $ is the linear wave frequency, 
-The spectra are strongly dominated by  peaks at $\omega =
-\omega_l$. As can be seen, there is equipartition between KE and APE in each shell.  
-Although the widening of the peaks around the linear frequency most likely is an effects of nonlinearities, 
-we can quite safely conclude that the time evolution of the flow variables in each Fourier mode to leading order can be described as a linear wave.
+The equipartition of KE and APE spectral fluxes suggests that the flow to
+leading order may be described as a collection of linear gravity waves with
+equipartition of KE and APE in each mode. To investigate this further we have
+collected time series of the flow variables from Fourier modes whose magnitude
+fall within certain shells, $ \mid {\bf k} \mid \in [ k -\delta k/2, \; k+
+\delta k/2] $, and computed temporal power law spectra from these time series
+and averaged over all wave numbers in each shell. In other words we have
+computed KE and APE frequency spectra corresponding to different magnitudes of
+modes. Figure~\ref{fig_spatiotemp_spectra} presents such spectra plotted as a
+functions of the normalized frequency $\omega/\omega_l$, where $ \omega_l = kc
+$ is the linear wave frequency, The spectra are strongly dominated by peaks at
+$\omega = \omega_l$. As can be seen, there is equipartition between KE and APE
+in each shell. Although the widening of the peaks around the linear frequency
+most likely is an effects of nonlinearities, we can quite safely conclude that
+the time evolution of the flow variables in each Fourier mode to leading order
+can be described as a linear wave.
 
-Visualizations of the flow field give a completely different picture from what may be expected from a collection of linear gravity waves.
-They are totally dominated by the appearance of shock waves.
-In figure (\ref{Physical}) we see the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity component in the $ y $-direction, $ u_y $, to the right.
-The two figures at the top are from run W6 while the two figures at the bottom are from run W17.
-The difference between the two runs is that $ c $ is larger by a factor of $ 20 $ in W17 as compared to W6.
-To the left we see the shocks displayed as elongated bands of negative divergence.
-That the divergence is negative at the shocks can be understood from the fact that the velocity component perpendicular to the shock always has a negative jump in the direction of shock propagation.
-Apparently, the mean distance between the shocks is considerably smaller in run W17 with the larger value of $ c $ compared to run $ W6 $  with the smaller value of $ c $.
-The shocks are also visible in the figures to right where $ u_y $ is displayed.
-It may be interesting to note that the shocks along the $ x $-axis appear as extra sharp in this plot, since there is a strong jump  of $ u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly visible, since there is no jump of $ u_{y} $ over these.
-In the two figures to the right we see a variation of the flow field over the length scale $ L_f $ which is not seen in the two figures to the left.
-This variation is evidently a footprint of the random forcing.
-Although the forcing length scale $ L_f $ is the same in the two simulations the mean distance, $ d $,  between the shocks is much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit surprising.
-We have calculated $ d $ by counting the number of negative spikes of the divergence along ten lines parallel to the $ x $-axis and ten lines parallel to the $ y $-axis and then divided  total length of all the lines by the number of spikes.
-Generally, we found that $ d \sim c^{-1/2} $, or
+Visualizations of the flow field give a completely different picture from what
+may be expected from a collection of linear gravity waves. They are totally
+dominated by the appearance of shock waves. In figure (\ref{Physical}) we see
+the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
+component in the $ y $-direction, $ u_y $, to the right. The two figures at the
+top are from run W6 while the two figures at the bottom are from run W17. The
+difference between the two runs is that $ c $ is larger by a factor of $ 20 $
+in W17 as compared to W6. To the left we see the shocks displayed as elongated
+bands of negative divergence. That the divergence is negative at the shocks can
+be understood from the fact that the velocity component perpendicular to the
+shock always has a negative jump in the direction of shock propagation.
+Apparently, the mean distance between the shocks is considerably smaller in run
+W17 with the larger value of $ c $ compared to run $ W6 $ with the smaller
+value of $ c $. The shocks are also visible in the figures to right where $ u_y
+$ is displayed. It may be interesting to note that the shocks along the $ x
+$-axis appear as extra sharp in this plot, since there is a strong jump of $
+u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly
+visible, since there is no jump of $ u_{y} $ over these. In the two figures to
+the right we see a variation of the flow field over the length scale $ L_f $
+which is not seen in the two figures to the left. This variation is evidently a
+footprint of the random forcing. Although the forcing length scale $ L_f $ is
+the same in the two simulations the mean distance, $ d $, between the shocks is
+much smaller in run $ W17 $ than in run $ W6 $, which may seem a little bit
+surprising. We have calculated $ d $ by counting the number of negative spikes
+of the divergence along ten lines parallel to the $ x $-axis and ten lines
+parallel to the $ y $-axis and then divided total length of all the lines by
+the number of spikes. Generally, we found that $ d \sim c^{-1/2} $, or
 \begin{equation} \label{MeanDistance}
@@
 \end{equation}
-independent of resolution $ n $.
-In figure (\ref{fig_distance}) we have plotted $ d/L_f $ versus Froude number for all twenty runs.
-As can be seen the points follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight systematic deviation at the highest $ F_f $, which may be due to the fact that $ d $ is rather close to the length of the side of the box for the largest $ F_f $.
+independent of resolution $ n $. In figure (\ref{fig_distance}) we have plotted
+$ d/L_f $ versus Froude number for all twenty runs. As can be seen the points
+follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight
+systematic deviation at the highest $ F_f $, which may be due to the fact that
+$ d $ is rather close to the length of the side of the box for the largest $
+F_f $.
 
@@
 \includegraphics[width=5.0in]{../Pyfig/fig_struct_order_246}}
-\caption{From top to bottom: second, fourth and sixth order compensated and normalised longitudinal structure functions.
-Left: runs with $ n=3840 $: W3, W7, W11 and W18.
-Right: runs with $ n = 7860 $: W4, W8 and W15.
-}
+\caption{From top to bottom: second, fourth and sixth order compensated and
+normalised longitudinal structure functions. Left: runs with $ n=3840 $: W3,
+W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15. }
 \label{fig_StrucFunc}
@@
 
-We will now present the results for the structure functions. Substituting (\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure functions are expected to scale as
+We will now present the results for the structure functions. Substituting
+(\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure
+functions are expected to scale as
 \begin{equation} \label{StrucFunc2}
@@
 \end{equation}
-for separation distances that fulfill the condition $ \delta x \ll r \ll d $, where $ \delta x $ is the shock width.
-The scaling (\ref{StrucFunc2}) is expected to become better and better fulfilled with decreasing $ c $ (or increasing $ F_f $), for two reasons.
-First, according to (\ref{MeanDistance}) $ d $ is increasing with $ F_f $, and the scaling range is therefore becoming wider for decreasing $ c $, if  $ \delta x $ or the resolution  $ n $ is kept constant.
-Second, according to (\ref{Strength}) the amplitude of the shocks scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming increasingly strong for large $ d $ (small $ c $).
-Thus, the assumption that the structure functions are totally dominated by increments where a shock is crossed will be better fulfilled for small $ c $.
-This effect is expected to be particularly important for lower order structure functions.
-The scaling (\ref{StrucFunc2}) is also expected top become better and better fulfilled with increased resolution $ n $, since $ \delta x $ is decreasing with increasing $ n $.
+for separation distances that fulfill the condition $ \delta x \ll r \ll d $,
+where $ \delta x $ is the shock width. The scaling (\ref{StrucFunc2}) is
+expected to become better and better fulfilled with decreasing $ c $ (or
+increasing $ F_f $), for two reasons. First, according to (\ref{MeanDistance})
+$ d $ is increasing with $ F_f $, and the scaling range is therefore becoming
+wider for decreasing $ c $, if $ \delta x $ or the resolution $ n $ is kept
+constant. Second, according to (\ref{Strength}) the amplitude of the shocks
+scales as $ (\eps d)^{1/3} $, which means that the shocks are becoming
+increasingly strong for large $ d $ (small $ c $). Thus, the assumption that
+the structure functions are totally dominated by increments where a shock is
+crossed will be better fulfilled for small $ c $. This effect is expected to be
+particularly important for lower order structure functions. The scaling
+(\ref{StrucFunc2}) is also expected top become better and better fulfilled with
+increased resolution $ n $, since $ \delta x $ is decreasing with increasing $
+n $.
 
- As expected, we have found that 
-the displacement structure functions scale exactly in the same way as the velocity structure functions, why we only plot velocity structure functions.
-In figure (\ref{fig_StrucFunc}) we see the compensated and normalised second, fourth and sixth order longitudinal structure functions from the five simulations with $ n = 3840 $ to the left and the three simulations with $ n = 7860 $ to the right.
-At small separation, $ r < \delta x $, the structure functions have the dependence $ \sim r^{p} $, which is characteristic of a smooth velocity field, indicating that the shocks are reasonably well resolved.
-There is a small bump around the shock width,
-$ r \approx \delta x $, and at $ r > \delta x $, there is a range where the compensated structure functions are flat, or almost flat.
-As expected, this range is becoming broader for smaller  $ c $ (or larger $ F_f $).
-The range is also broader in the higher resolution runs to the right as compared to the lower resolution simulations to the left.
-There is clearly a better collapse of the curves for the sixth order structure functions compared to the second order structure functions.
-This is not surprising, since the shock contribution to the structure functions should become increasingly dominant with increasing order.
-Plots of the transverse structure functions are very similar to the plots of the longitudinal structure functions, with the difference that the transverse structure functions are somewhat smoother at $ r \approx \delta x $.
-In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta u_L \mid ^{p} \rangle /  \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p= 2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the values predicted by (\ref{Ratio}).
-As can be seen, there is a quite good agreement with the predicted values in a limited range of separations, $ r > \delta x $.
-Somewhat unexpectedly, the range in which there is a good agreement becomes more narrow with increasing $ p $, an observation that we cannot explain.
-It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small $ r $, which is the theoretical single point limit for an irrotational isotropic field.
-In figure (\ref{fig_flatness}) we se the flatness factor, $ F_T $,  of the transverse structure functions at the top and the ratio, $ F_T/F_L $,  at the bottom.
-The figures to the left show the results from the five simulations with  $ n = 3840 $ and the figures to the right show the results from the three simulations with $ n = 7860 $.
-The flatness factor  shows increasingly large values for decreasing $ r $ with a dependence that is rather close to but somewhat steeper than $ r^{-1} $.
-At small $ r $ the curves  are leveling out at very large values.
-For $ n = 7869 $ and $ c = 10 $ we see that $ F_{T} \approx 400 $ at small $ r $.
-The degree to which the flatness factor is increasing with decreasing scale is by some authors defined  as the most appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
+As expected, we have found that the displacement structure functions scale
+exactly in the same way as the velocity structure functions, why we only plot
+velocity structure functions. In figure (\ref{fig_StrucFunc}) we see the
+compensated and normalised second, fourth and sixth order longitudinal
+structure functions from the five simulations with $ n = 3840 $ to the left and
+the three simulations with $ n = 7860 $ to the right. At small separation, $ r
+< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
+is characteristic of a smooth velocity field, indicating that the shocks are
+reasonably well resolved. There is a small bump around the shock width, $ r
+\approx \delta x $, and at $ r > \delta x $, there is a range where the
+compensated structure functions are flat, or almost flat. As expected, this
+range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
+also broader in the higher resolution runs to the right as compared to the
+lower resolution simulations to the left. There is clearly a better collapse of
+the curves for the sixth order structure functions compared to the second order
+structure functions. This is not surprising, since the shock contribution to
+the structure functions should become increasingly dominant with increasing
+order. Plots of the transverse structure functions are very similar to the
+plots of the longitudinal structure functions, with the difference that the
+transverse structure functions are somewhat smoother at $ r \approx \delta x $.
+In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta
+u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
+2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the
+values predicted by (\ref{Ratio}). As can be seen, there is a quite good
+agreement with the predicted values in a limited range of separations, $ r >
+\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
+becomes more narrow with increasing $ p $, an observation that we cannot
+explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
+$ r $, which is the theoretical single point limit for an irrotational
+isotropic field. In figure (\ref{fig_flatness}) we se the flatness factor, $
+F_T $, of the transverse structure functions at the top and the ratio, $
+F_T/F_L $, at the bottom. The figures to the left show the results from the
+five simulations with $ n = 3840 $ and the figures to the right show the
+results from the three simulations with $ n = 7860 $. The flatness factor shows
+increasingly large values for decreasing $ r $ with a dependence that is rather
+close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
+leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
+$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
+is increasing with decreasing scale is by some authors defined as the most
+appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
 If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
-In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a limited range of separations, $ r > \delta x $, which is becoming somewhat broader as $ c $ is increasing and  is also somewhat broader in the higher resolution runs shown to the right as compared to the lower resolution runs shown to the left.
-This is in accordance with the shock model predictions (\ref{FL}) and (\ref{FT}).
+In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
+limited range of separations, $ r > \delta x $, which is becoming somewhat
+broader as $ c $ is increasing and is also somewhat broader in the higher
+resolution runs shown to the right as compared to the lower resolution runs
+shown to the left. This is in accordance with the shock model predictions
+(\ref{FL}) and (\ref{FT}).
 
-Finally, we present  energy spectra.
-As expected, we found that APE and KE spectra were almost indistinguishable from each other, why we only plot the total spectra.
-In figure (\ref{fig_spectra_c40}) we see the compensated and normalised energy spectra from the three highest resolution runs.
-The compensated spectra are almost flat in a broad range.
-In the high wave number end the compensated spectra show a `bottleneck', which we interpret as a signature of the shocks, and at the very highest wave numbers the magnitude of the spectra is strongly decreasing, indicating that the shocks are reasonably well resolved.
-The $ k^{-2} $-dependence and the associated scaling predicted by (\ref{Spectra}) are very well satisfied in a limited range of high wave numbers close to the bottleneck.
-At smaller wave number the spectra are becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with largest $ c $ does not collapse perfectly onto the other two spectra.
+Finally, we present energy spectra. As expected, we found that APE and KE
+spectra were almost indistinguishable from each other, why we only plot the
+total spectra. In figure (\ref{fig_spectra_c40}) we see the compensated and
+normalised energy spectra from the three highest resolution runs. The
+compensated spectra are almost flat in a broad range. In the high wave number
+end the compensated spectra show a `bottleneck', which we interpret as a
+signature of the shocks, and at the very highest wave numbers the magnitude of
+the spectra is strongly decreasing, indicating that the shocks are reasonably
+well resolved. The $ k^{-2} $-dependence and the associated scaling predicted
+by (\ref{Spectra}) are very well satisfied in a limited range of high wave
+numbers close to the bottleneck. At smaller wave number the spectra are
+becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
+largest $ c $ does not collapse perfectly onto the other two spectra.

### 2018-10-17 Latex/section_methods.tex
mainly typos

@@
 We have carried out a series of twenty forced-dissipative simulations of the SW
-equations in a quadratic domain with periodic boundary conditions using a
-standard pseudo spectral code. The simulations were started from zero initial
+equations in a quadratic domain with periodic boundary conditions using the
+standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
+fluidsim}.
+%
+The simulations were started from zero initial
 conditions and were run till a statistically stationary state was reached. The
@@
 shallow water model, see][]{FargeSadourny1989}. The resolution is characterized
-by the number of nodes, $n$, in the each direction and has been varied from 960
+by the number of nodes, $n$, in each direction and has been varied from 960
 to 7680.
@@
 \delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
-domain. The forcing is white noice in time and designed so that the energy
+domain. The forcing is white noise in time and designed so that the energy
 injection rate is normalized to unity at each time step. The energy is
@@
 \end{equation}
-where $ L_f = \pi/k_f $ is the forcing scale. In figure \ref{MeanE} to the
+where $ L_f = \pi/k_f $ is the forcing scale. In figure~\ref{MeanE} to the
 left, we see $ E/\sqrt{\eps} $ as function of $ c $ for different resolutions $
@@
 turbulence is satisfied with a high degree of accuracy in our simulations. In
-figure \ref{Flux} we wee the spectral energy flux from run W7 to the left and
+figure~\ref{Flux} we see the spectral energy flux from run W7 to the left and
 the third order structure function to the right. There is a broad constant flux
@@
 may be expected from a collection of linear gravity waves. They are totally
-dominated by the appearance of shock waves. In figure (\ref{Physical}) we see
+dominated by the appearance of shock waves. In figure~\ref{Physical} we see
 the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
@@
 \end{equation}
-independent of resolution $ n $. In figure (\ref{fig_distance}) we have plotted
+independent of resolution $ n $. In figure~\ref{fig_distance} we have plotted
 $ d/L_f $ versus Froude number for all twenty runs. As can be seen the points
@@
 particularly important for lower order structure functions. The scaling
-(\ref{StrucFunc2}) is also expected top become better and better fulfilled with
+(\ref{StrucFunc2}) is also expected to become better and better fulfilled with
 increased resolution $ n $, since $ \delta x $ is decreasing with increasing $
@@
 exactly in the same way as the velocity structure functions, why we only plot
-velocity structure functions. In figure (\ref{fig_StrucFunc}) we see the
+velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
 compensated and normalised second, fourth and sixth order longitudinal
@@
 transverse structure functions are somewhat smoother at $ r \approx \delta x $.
-In figure (\ref{fig_ratio}) we see the ratio $ R_{p}(r) = \langle \mid \delta
+In figure~\ref{fig_ratio} we see the ratio $ R_{p}(r) = \langle \mid \delta
 u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
@@
 $ r $, which is the theoretical single point limit for an irrotational
-isotropic field. In figure (\ref{fig_flatness}) we se the flatness factor, $
+isotropic field. In figure~\ref{fig_flatness} we se the flatness factor, $
 F_T $, of the transverse structure functions at the top and the ratio, $
@@
 spectra were almost indistinguishable from each other, why we only plot the
-total spectra. In figure (\ref{fig_spectra_c40}) we see the compensated and
+total spectra. In figure~\ref{fig_spectra_c40} we see the compensated and
 normalised energy spectra from the three highest resolution runs. The

### 2018-10-23 Latex/article.tex
Article compiled with a Makefile (without figure).
Change width in Latex to equivalent in inches
Update Erik's files

@@
 \usepackage{soul}
-
+\usepackage{booktabs}
 \pdfoptionpdfminorversion 4
@@
 
-\newcommand{\eps}{\varepsilon}
-
 \newcommand{\ErtelPV}{\mathcal{Q}}
@@
 \newlength{\halfwidth}
-\setlength{\halfwidth}{66mm}
+\setlength{\halfwidth}{2.6in}
 
@@
 
-\title[Wave energy cascade in shallow-water flows]%
-{Wave energy cascade in forced-dissipative one-layer shallow-water flows}
+\title[Shallow water wave turbulence]%
+{ Shallow water wave turbulence}
 
-\author[P. Augier and E. Lindborg]%
-{Pierre Augier$^{1,2}$%
-  \thanks{Email address for correspondence: p.augier@damtp.cam.ac.uk},\ns
-and Erik Lindborg$^1$}
+\author[P. Augier, A.V. Mohanan and E. Lindborg]%
+{Pierre Augier$^{1}$,   A. V. Mohanan$^{2}$
+and Erik Lindborg$^2$ \ns }
 
-\affiliation{$^1$Linn\'e Flow Centre, KTH Mechanics,
+\affiliation{$^2$ KTH Mechanics,
 SE-100 44 Stockholm, Sweden\\[\affilskip]
-$^2$Department of Applied Mathematics and Theoretical Physics,
-University of Cambridge, Cambridge CB3 0WA, United Kingdom}
+$^1$ LEGI, BP53,
+38041 Grenoble Cedex, France}
 
@@
 % \baselineskip 8mm
+
 \begin{abstract}
-The dynamics of one-layer shallow-water flows forced in medium-scale
-wave modes and dissipation acting at small scales is investigated by
-means of theoretical analysis and numerical simulations with
-resolutions up to $7680^2$.
-%
-We first focus on the non-rotating case for which a statistically
-stationary regime is obtained for all resolutions and Froude numbers
-$F_f = \eps/(k_f c)$, where $\eps$ is the energy dissipation rate,
-$k_f$ the forcing wave number and $c$ the wave speed.
-%
-All the injected energy goes into a downscale energy
-cascade. Consequently, the spectral energy flux is constant and
-positive between the forcing wave number and the wave numbers where
-dissipation is active.  The spectral energy flux is exactly
-equipartioned between kinetic and potential energy.  An exact third
-order structure function law of Kolmogorov type is derived and
-numerically verified.  However, the downscale cascade is less
-efficient than in three-dimensional Navier-Stokes turbulence, since
-the mean energy of the statistically stationary flow scales as
-$\sqrt{\eps c /k_f}$ and varies with the dissipative scale.
-%
-Moreover, the spectra scale as $k^{-2}$ and the structure functions of
-order larger than two scale approximately as $r$.
-%
-%
-This intermittent scaling is explained by a simple model based on the
-assumption that the statistics is totally determined by shocks.
-%
-It is verified that the dynamics is not drastically modified by system
-rotation as long as the forcing wave number is larger than the
-deformation wave number $k_d = f/c$, where $f$ is the Coriolis
-parameter.
+
+The dynamics of irrotational shallow water wave turbulence forced in large
+scales and dissipated at small scales is investigated. First, we derive the
+shallow water analogue of the `four-fifths law' of Kolmogorov turbulence
+for a third order structure function involving velocity and displacement
+increments. Using this relation and assuming that the flow is dominated by
+shocks we develop a simple model predicting that the shock amplitude scales as
+$ (\epsilon d)^{1/3} $, where $ \epsilon $ is the mean dissipation rate and $ d $
+the mean distance between the shocks, and that the $ p $:th order displacement
+and velocity structure functions scale as $ (\epsilon d)^{p/3} r/d $, where $ r $
+is the separation. Then we carry out a series of forced simulations with
+resolutions up to $7680^2$, varying the Froude number, $F_{f} = \epsilon^{1/3} /
+ck_f^{1/3} $, where $ k_f $ is the forcing wave number and $c$ is the wave
+speed. In all simulations a stationary state is reached in which there is a
+constant spectral energy flux and equipartition between kinetic and potential
+energy in the constant flux range. The third order structure function relation
+is satisfied with a high degree of accuracy. Mean energy is found to scale as $
+E \sim \sqrt{\epsilon c/k_f} $, and is also dependent on resolution, indicating
+that shallow water wave turbulence does not fit into the paradigm of a
+Richardson-Kolmogorov cascade. In all simulations shocks develop, displayed as
+long thin bands of negative divergence in flow visualisations. The mean
+distance between the shocks is found to scale as $ d \sim F_f^{1/2}/k_f $.
+Structure functions of second and higher order are found to scale in good
+agreement with the model. We conclude that in the weak limit, $ F_f \rightarrow
+0 $, shocks will become denser and weaker and finally disappear for a finite
+Reynolds number. On the other hand, for a given $ F_{f} $, no matter how small,
+shocks will prevail if the Reynolds number is sufficiently large.
+
 \end{abstract}
@@
 
-The shallow-water models have been widely used to study basic
+The shallow water (SW) equations  have been widely used to study basic
 mechanisms occurring in geophysical flows \cite[see for
@@
 %
-These models are based on the hydrostatic approximation which is
+The equations are based on the hydrostatic approximation which is
 extremely well satisfied for a very wide range of scales in the oceans
-and in the atmosphere \Add{and on which are based the so-called
-primitive equations}.  They also rely on a stronger hypothesis
+and in the atmosphere.  They also rely on a stronger hypothesis
 regarding the density stratification.  The fluid is assumed to be
 structured in a limited number of thin homogeneous layers, which leads
-to equations involving only two-dimensional operators. \Add{However,
-as long as there is no overturning, the shallow-water model in the
-limit of a large number of layers and the primitive equations describe
-the same dynamics. In the opposite limit, two models are particularly
-important from the theoretical point of view.} The two-layer
-shallow-water model captures the baroclinic instability which is of
+to equations involving only two-dimensional operators. The two-layer
+SW equations capture the baroclinic instability which is of
 primary importance for the dynamics of the oceans and of the
@@
 %
-The equations of the one-layer shallow-water model are very similar to
+The single layer SW equations are very similar to
 the two-dimensional compressible Navier-Stokes equations.  The
-one-layer model does not capture the baroclinic instability but it is
+equations do not capture baroclinic instability but they constitute
 one of the simplest hydrodynamic models with coexisting eigenmodes of
 the linearized operator with zero linear frequency and with finite
-non-zero linear frequency, $\omega = \pm \omega_l = \pm\sqrt{f^2 + c^2
-k^2}$, where $f$ is the Coriolis parameter, $c$ the wave speed and $k
+non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
+k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
 = |\kk|$ the wave number.
@@
 
-For geophysical applications, it is convenient to consider the limits
-for which the linear frequency $\omega_{l}$ is much larger than the
-characteristic nonlinear frequency $\omega_{nl} = U k$, where $U$ is a
-characteristic velocity.  In the limit $f/\omega_{nl} \sim
-ck/\omega_{nl} \rightarrow \infty$, one can obtain a quasi-geostrophic
-one-layer shallow-water model, i.e. derive self-consistent evolution
-equations for the 0-linear-frequency variable, the Charney potential
-vorticity.  In this limit, the dynamics of the 0-linear-frequency
-variable is totally decorrelated from the fast waves.
+For geophysical applications, it is convenient to consider the limit
+for which the linear wave frequency  is much larger than the
+characteristic nonlinear frequency $ U k$, where $U$ is a
+characteristic velocity.  In this limit, one can obtain a quasi-geostrophic
+single layer SW model, i.e. derive self-consistent evolution
+equations for a zero frequency variable, the Charney potential
+vorticity, which is totally decoupled from the fast waves.
 %
@@
 which are associated with relatively weak non-zero linear frequency
-modes.
+modes and there is only a weak
+interaction between waves and the balanced motions.
 %
-When $\omega_{nl}(k) \ll \omega_{l}(k) $, there is only a weak
-interaction between waves and the balanced modes.
-%
-Due to its relative simplicity, the one-layer shallow-water model has
+Due to their relative simplicity, the SW equations have
 been used to study issues like the projection on the balanced manifold
@@
 waves by balanced flows \cite[]{FargeSadourny1989,
-LahayeZeitlin2012,Vanneste2013}. \Add{In this study, we consider the
-same model in order to address a related but different issue.}
+LahayeZeitlin2012,Vanneste2013}.
+In this study, we consider the
+same equations in order to address a related but different issue.
 
 Balanced flows have a dynamics which is very similar to
-two-dimensional turbulence.
-%
-In the quasi-geostrophic limit, the space-averaged energy and the
-space-averaged potential enstrophy are conserved, positive definite
-and proportional in Fourier space. This leads\Add{, as in
-two-dimensional turbulence,} to an upscale energy cascade and a
-downscale enstrophy cascade.
-%
-Thus, the small-scale dissipation vanishes in the limit of zero
+two-dimensional turbulence, with an upscale energy cascade. %
+Small scale energy dissipation vanishes in the limit of zero
 viscosity.
@@
 %
-\Add{They propose that the $k^{-5/3}$ spectra that are observed at the
-atmospheric meso-scales} \cite[]{NastromGage1985, FrehlichSharman2010}
-\Add{and reproduced by some atmospheric models based on the primitive
-equations} \cite[]{KoshykHamilton2001, Skamarock2004,
-Hamilton_etal2008} \Add{could be reproduced by the one-layer
-shallow-water model by a downscale energy cascade of waves.}
-
+They propose that the $k^{-5/3}$ spectra that are observed at the
+atmospheric meso-scales  \cite[]{NastromGage1985,LiLindborg2018}
+and reproduced by some atmospheric models based on the primitive
+equations \cite[]{KoshykHamilton2001, Skamarock2004,
+Hamilton_etal2008} could be reproduced by the one-layer
+shallow-water model by a downscale energy cascade of waves.
 However, few studies have investigated the dynamics of the downscale
-energy cascade of waves in shallow-water models.
-%
+energy cascade of waves in SW models.
 Most numerical studies have investigated decaying flows and have not
@@
 %
-\cite{FargeSadourny1989} reported spectra scaling like $k^{-4}$
-whereas those shown by \cite{LahayeZeitlin2012} scale like $k^{-6}$.
+\cite{FargeSadourny1989} reported spectra scaling as $k^{-4}$
+whereas those shown by \cite{LahayeZeitlin2012} scale as $k^{-6}$.
 
@@
 \cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
-inertial-gravity waves, \cite{FalkovichMedvedev1992} showed that the
-exact solutions of the kinetic equation corresponding to a constant
-downscale energy flux is associated with a spectrum scaling like $E(k)
-\sim P^{2/3} k^{-8/3}$.
+inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
+solutions of the kinetic equation corresponding to a constant downscale energy
+flux is associated with a spectrum scaling as $E(k) \sim k^{-8/3}$, while
+\cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
+of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
+of particular interest, since the acoustic equations and the SW equations are
+identical when a first order expansion is made in density or displacement
+perturbations. It may be questioned, however, that weak turbulence formalism is
+applicable to acoustic and SW wave turbulence, no matter how weak the
+nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
+and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
+the same direction have the same velocity and interact strongly, which leads to
+the formation of shocks. In this case, the weak wave turbulence formalism is
+unable to give valuable results. Such sharp and long structures have been
+observed in many simulations \cite[]{FargeSadourny1989,
+PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
+well understood.
 %
-However, as pointed out by \cite{FalkovichMeyer1996} when the
-dispersion is small enough, waves moving in the same direction have
-the same velocity and interact strongly, which can lead to the
-formation of shocks. \Add{In this case, the weak wave turbulence
-formalism is unable to give valuable results.}  Such sharp and long
-structures have been observed in many simulations
-\cite[]{FargeSadourny1989, PolvaniMcWilliamsSpallFord1994,
-LahayeZeitlin2012} but \Add{their effects} are not well understood.
-%
-\cite{Kuznetsov2004} predicted that a flow dominated by shocks should
-be associated with spectra scaling like $E(k) \sim k^{-2}$.
+As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
+shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
+great number of simulations of Burgers equation \cite[for a review, see ]
+[]{Frisch2001}. The shocks also lead to very strong intermittency, as
+demonstrated by \cite{BouchaudMezardParisi1995} and
+\cite{WeinanKhaninMazelSinai1997} for Burgers turbulence.
 %
 \cite{FalkovichMeyer1996} simulated acoustic turbulence dominated by shocks
-and reported spectra in agreement with this theoretical prediction.
-%
-The shocks also lead to very strong intermittency, as demonstrated by
-\cite{BouchaudMezardParisi1995} and \cite{WeinanKhaninMazelSinai1997}
-in the case of Burgers turbulence.
-%
+and reported spectra scaling as $ k^{-2} $.
+\cite{YuanHamilton1994} carried out
+forced dissipative simulations of the SW equations showing similar spectra.
+However, the resolution in both these studies was quite coarse, ($386^2$
+and $101^2$ grid points, respectively) so that the scaling range was very
+narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
+type of strongly anisotropic forcing with waves in only one
+direction while \cite{YuanHamilton1994} forced in geostrophic modes
+which severely complicates the interpretation.
 
-The dynamics of waves in complex shallow-water flows is not well
-understood.  \Add{Our long-term goal is to understand this dynamics
-which involves interactions between balance and unbalance parts of the
-flow. However, even the wave cascade without balance flow is not well
-understood.} A statistically stationary wave cascade has never been
-simulated at high resolution.
+The dynamics of waves in complex SW flows is not well
+understood.  Even wave dynamics in absence of a balanced flow is not well
+understood. A statistically stationary wave cascade has never been
+simulated at high resolutions.
 %
@@
 % What is the slope of
-\Add{How does} the energy spectra \Add{scale as a function of the
-input parameters}?
+How do energy spectra scale with the input parameters? From a theoretical point
+of view, the most interesting issue is, perhaps, the nature of the dynamics in
+the limit of weak nonlinearities. Will shocks prevail in this limit?
 %
-All these questions are open and straightforward simulations may
+Such questions are still open and straightforward simulations may
 provide the answers.
+In this paper, we investigate the dynamics of single layer SW wave turbulence
+forced  at large scales by means of
+simulations with up the  $7680^2$ grid points.
+%
+Before presenting the results of the simulations we develop some theory.
+%
 
-\cite{YuanHamilton1994} and \cite{FalkovichMeyer1996} carried out
-forced dissipated simulation of the one-layer shallow water model and
-acoustic turbulence, respectively.
+\section{Theory}
+
+In a non-rotating system of reference the SW equations for a thin layer of fluid over a flat bottom and with a free
+surface can be written as  \cite[see for example][]{VallisLIVRE2006}
+\begin{eqnarray} \label{UEq}
+\p_t \uu + \uu\cdot \bnabla  \uu   
+&=& - c^2 \bnabla h + \frac{\nu}{h}  \bnabla^2 \uu,   \label{eq_uu}\\ \label{HEq}
+\p_t   h    &=& - \bnabla \cdot (h \uu).  \label{eq_h}
+\end{eqnarray}
+where $\uu$ is the horizontal velocity, %
+$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
+$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed.
+The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $.
+As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite.
+This can only be accomplished by permitting the term to be nonlinear in the flow variables.
+There are different forms of nonlinear terms that fulfil both conditions and it may be disputed which is the best one.
+However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfil any of these two conditions in a strict sense and we will therefore not discuss this matter further.
+The inviscid SW equations conserve a local
+quantity along trajectories of the fluid particles, the Ertel
+potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity.
+This conservation law will be of no relevance in the present study in which we only consider
+irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential.
+In a domain with no net fluxes through the boundaries the inviscid equations conserve energy, $ E = E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy.
+The latter can be split into three terms as \begin{equation}
+E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2, 
+\end{equation}
+where the first term corresponds to the potential energy of a state with no
+surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
+$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}.
+As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
+ The velocity potential and the displacement of the linearised inviscid SW equations both satisfy the wave equation,
+\begin{equation}
+\frac{\partial ^2 \eta}{\partial t^2} = c^2 \nabla^2 \eta \, ,
+\end{equation}
+with equipartition between KE and APE over a wave period in each Fourier mode.
+
+In order to analyze the spectral flux of energy, we derive the spectral energy
+budget, i.e.\ the governing equations for spectral KE and APE
+functions. This is not as straightforward as in incompressible turbulence since
+the expression of the kinetic energy  is not
+quadratic. To define the spectral KE function, we use the relation
+\begin{equation}
+\mean { E_K } = \sum_\kk \scalarprod{\uu}{\JJ}/2,
+\end{equation}
+where
+\begin{equation}
+\scalarprod{\baa}{\bb} \equiv \Re\{ \hat \baa(\kk)^* \cdot \hat \bb(\kk) \},
+\end{equation}
+and $\Re$ denotes the real part, $\kk$ is the wave number and the
+hat denotes the Fourier transform.
 %
-However, the resolution in both studies was quite coarse \Add{($386^2$
-and $101^2$ grid points, respectively)} so that the inertial range was very
-narrow.  Moreover, \cite{FalkovichMeyer1996} used a very particular
-type of strongly anisotropic forcing \Add{with waves in only one
-direction} while \cite{YuanHamilton1994} forced in geostrophic modes
-which severely complicates the interpretation.
+The spectral KE function can therefore be defined as
+\begin{equation}
+E_K(\kk) \equiv \scalarprod{\uu}{\JJ}/2.
+\end{equation}
+Similarly, the APE can be written as the sum over all wave numbers of
+the spectral APE function 
+\begin{equation}
+E_A(\kk) =  c^2 \scalarprod{\eta}{\eta}/2 \, .
+\end{equation}
+The inviscid equation for the spectral KE and APE functions can be written as
+\begin{eqnarray}
+\p_t E_K(\kk) &=& T_K(\kk) - C (\kk),\\
+\p_t E_A(\kk) &=& T_A(\kk) + C (\kk),
+\end{eqnarray}
+where
+\begin{equation}
+T_K(\kk) 
+= -\scalarprod{\bnabla \cdot \uu}{E_K} 
+-\scalarprod{\uu }{\bnabla E_K } \, ,
+\end{equation}
+\begin{equation}
+T_A(\kk) = -c^2 \scalarprod{\bnabla \eta }{\JJ}- c^2\scalarprod{\eta}{\bnabla \cdot \JJ}  \, ,
+\end{equation}
+are the spectral transfer functions of KE and APE, respectively, and
+\begin{equation}
+C (\kk) 
+= \scalarprod{\uu}{\bnabla E_P}
+\end{equation}
+is the spectral KE-APE conversion function.
+The spectral energy flux functions of KE and APE are defined as
+\begin{eqnarray}
+\Pi_K (k) = \sum_{| {\bf k}^{\prime} | > k} T_K ( {\bf k}^\prime ) \, , \;\;\;  \Pi_A (k) = \sum_{| {\bf k}^{\prime} | > k} T_A ( {\bf k}^\prime ) 
+\end{eqnarray}
 
-In this paper, we investigate the dynamics of one-layer shallow-water
-flows forced in the wave modes by means of high resolution numerical
-simulations \Add{with up the  $7680^2$ grid points}.
+We will now derive an analogue of the so called `four-fifths  law' \cite[]{Kolmogorov1941} for the the third order velocity structure function of incompressible isotropic turbulence.
+In the case of irrotational SW wave turbulence the analogous law contains a third order structure function involving both velocity and displacement increments.
+In order for such a law to exist it is necessary that the velocity field is either non-divergent (incompressible) or irrotational.
+To derive the law it is convenient to start from the following equations
+\begin{eqnarray} \label{IRR}
+\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
+\p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
+\p_t h   &=& -\bnabla \cdot \JJ \, ,
+\end{eqnarray}
+where we have used the  assumption that the velocity field is irrotational in (\ref{IRR}).
+We consider two points, positioned at $ \bf x $ and $ {\bf x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
+Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $ as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $ \partial^{\prime}_i $.
+Treating $ \bf x $ and $ {\bf x}^\prime $ as independent variables we find
+
+\begin{equation}
+\p_t ( J_i' u_i ) = - \p_i( J_i'|\uu|^2/2) - \p_i'(u_j J_j' u_i')
+-\p_i (J_i' c^2 h)  - \p_i' (u_i E_p')
+\end{equation}
+and
+\begin{equation}
+\p_t ( h' h ) = - \p_i( h'J_i ) - \p_i'( hJ_i' ),
+\end{equation}
+which gives
+\begin{eqnarray}
+\p_t ( \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h )
+&=& - \p_i( J_i'|\uu|^2/2) - \p_i'( J_i|\uu'|^2/2) %\nonumber \\&& 
+- \p_i'(u_j J_j' u_i') - \p_i(u_j' J_j u_i) \nonumber\\
+&& -c^2\p_i (J_i'h) - c^2\p_i' (J_ih') %\nonumber\\&& 
+- \p_i' (u_i E_p') - \p_i (u_i' E_p) \nonumber\\
+&& -2c^2\p_i' (J_i'h) - 2c^2\p_i (J_ih').
+\end{eqnarray}
+We then assume homogeneity and take the average denoted by
+$\meane{}$.   For
+every function $g(\xx, \xx')$, we have $\p_i' \meane{g} =
+-\p_i\meane{g} = \bnabla_{\rr} \meane{g}|_i$. We thus obtain
+\begin{eqnarray}
+\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
+&=& + \bnabla_{\rr}\cdot\meane{ \JJ'|\uu|^2/2 - \JJ|\uu'|^2/2 } \nonumber\\
+&& - \bnabla_{\rr}\cdot\meane{ u_j J_j' \uu' - u_j' J_j \uu } \nonumber\\
+&& - \bnabla_{\rr}\cdot\meane{ \uu E_p'- \uu' E_p } \nonumber\\
+&& -c^2\bnabla_{\rr}\cdot\meane{ \JJ'h - \JJ h' }
+\end{eqnarray}
 %
-The model is described in section~\ref{section_basic_theory}.
+We then introduce the structure functions and the operator $\delta$
+returning the increment of a variable between two points separated by $\rr$, 
+for example $\delta h (\xx, \rr) = h(\xx+\rr)- h(\xx)$.
 %
-We then derive some new theoretical results for this model and for
-turbulence dominated by shocks
-(section~\ref{section_advanced_theory}).
+Using homogeneity again, we obtain
+\begin{equation}
+\meane{ (\delta h)^2 \delta\uu } = 
+-\meane{ h'^2 \uu } + \meane{ h^2 \uu' }
++2\meane{ hh' \uu } - 2\meane{ hh' \uu' }
+\end{equation}
+and 
+\begin{equation}
+\meane{ |\delta \uu|^2 \delta\JJ } = 
+\meane{  |\uu|^2 \JJ' } - \meane{ |\uu'|^2\JJ }
++\meane{ u_ju_j' \JJ' } - \meane{  u_ju_j' \JJ },
+\end{equation}
+which gives
+\begin{equation}
+2\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
+= \bnabla_{\rr} \cdot ( \meane{ |\delta \uu|^2 \delta\JJ } 
++ c^2\meane{ (\delta h)^2 \delta\uu } ).
+\end{equation}
+For separations that are considerably larger than dissipative scales of motion and considerably smaller than forcing scales a standard argument \cite[see for example][]{Frisch} gives that the left hand side is approximately equal to $ -8 \epsilon $, where $ \epsilon $ is the mean dissipation rate.
+It is interesting to note that a factor of $ 8 $ appears in the case when the velocity field is irrotational while a corresponding factor of $ 4 $ appears in the case when the velocity field is non-divergent.
+Assuming isotropy and integrating yield the Kolmogorov law for
+irrotational shallow water wave  turbulence
+\begin{equation}
+\meane{ |\delta \uu|^2 \delta J_L } 
++ c^2\meane{ (\delta h)^2 \delta u_L } = -4 \epsilon r, \label{eq_Kolmo}
+\end{equation}
+where $J_L \equiv
+\JJ\cdot\rr / |\rr|$ and $u_L \equiv \uu\cdot\rr / |\rr|$ are
+longitudinal increments.
+
+We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
+The model has some similarities with the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation.
+The main difference is the that the mean dissipation rate, $\epsilon $, enters into the estimate of the shock amplitude and the final expressions of the structure functions in our model, but is absent in the model of \cite{BouchaudMezardParisi1995}.
+We consider a domain with total area  $ {\mA} $ occupied by shocks which we 
+consider as smooth lines. We denote the total length of all shocks by $ L_s $.  The mean distance between the shocks within the domain can be estimated as
+\begin{equation}
+d \simeq \frac{\mA} {L_s} .
+\end{equation} 
+A structure function of a flow variable is defined as the area average of increments  between two points separated by a distance $ r $.
+Assuming that the contribution from increments where the two points are not separated by a shock is negligible for higher order structure functions we obtain
+\begin{eqnarray}
+\meane{|\delta h|^p} 
+=  \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p 
+ \simeq  \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
+\end{eqnarray}
+where $\theta$ is the angle between the shock line and the separation
+vector $\rr$ %
+and $\Delta h (s)$ is the shock displacement amplitude.
 %
-The numerical methods and the forcing are described in
-section~\ref{section_methods}.
+Assuming isotropy, the integral can be split and we get
+\begin{equation} \label{StepH}
+\meane{|\delta h|^p} 
+\simeq 
+r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h |^p}
+\simeq  \frac{2}{\pi} \means{|\Delta h |^p} \frac{r}{d} ,
+\end{equation}
+where $\meant{}$ is the mean over $\theta$
+and $\means{}$ is the mean over all shocks.
+
+For velocity increments, we can also use a characteristic of the
+velocity singularities.  The step in velocity is only in the component
+perpendicular to the shocks, which implies that the longitudinal and
+transverse increments can be written as  $\delta u_L = \delta u
+\sin\theta$, $\delta u_T = \delta u \cos\theta$.
 %
-The main numerical results corresponding to the simple case without
-global rotation are presented in
-section~\ref{section_wave_cascade_f=0}.
+Applying the same averaging method, we obtain
+\begin{equation} \label{StepL}
+\meane{|\delta u_L|^p} 
+\simeq 
+\meant{|\sin\theta|^{1+p}}
+\means{|\Delta u |^p} \frac{r}{d}
+\end{equation}
+and
+\begin{equation} \label{StepT} 
+\meane{|\delta u_T|^p} 
+\simeq 
+\meant{|\sin\theta||\cos\theta|^{p}}
+\means{|\Delta u |^p} \frac{r}{d},
+\end{equation}
+where $\Delta u $ is the shock velocity amplitude.
 %
-We investigate the sensibility of the non-rotating results to a
-moderate rotation (section~\ref{section_rotation}).
+These assumptions completely determine the ratio between the
+longitudinal and transverse structure functions, which can be computed as
+\begin{eqnarray} \label{Ratio}
+R_p(r) \equiv \frac{\meane{|\delta u_L|^p}}{\meane{|\delta u_T|^p}} = 
+\frac{\meant{|\sin\theta|^{1+p}}}{\meant{|\sin\theta||\cos\theta|^p}},
+\end{eqnarray}
+giving the numerical values $R_2 = 2$, $R_3 = 6\pi/8$ and $R_4 = 8/3$.
+Interestingly, for an isotropic and irrotational velocity field, the longitudinal and transverse second order structure functions
+are exactly related by $\meane{(\delta u_L)^2} = \p_r( r\meane{(\delta
+u_T)^2} )$ \cite[]{Lindborg2007jas}. If we further assume than both second order structure functions follow
+the same scaling law $\meane{ (\delta u_L)^2} \propto \meane{ (\delta
+u_T)^2} \propto r^\alpha$, then we have $\meane{ (\delta u_L)^2} =
+(1+\alpha) \meane{ (\delta u_T)^2} $, which gives $ R_2 = 2 $ for 
+$  \alpha = 1$.  In the limit $ r \rightarrow 0 $ we have $ \alpha = 2 $ and $ R_2 = 3 $.
+%
 
-\section{The one-layer shallow-water model}
-\label{section_basic_theory}
-% \input{section_basic_theory}
+In order for (\ref{StepH}-\ref{StepT}) to match with the third order structure function law (\ref{eq_Kolmo})  the shock amplitudes should scale as
+\begin{equation} \label{Strength}
+ | \Delta u | \sim | c \Delta h | \sim (\epsilon d)^{1/3} \, ,
+\end{equation} 
+and the structure functions of order $ p $ will consequently scale as
+\begin{equation} \label{StrucFunc}
+\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (\epsilon  d)^{p/3} \,  \frac{r}{d} \, .
+\end{equation} 
+Assuming that (\ref{StrucFunc}) is valid for second order moments and that the non-quadratic contribution to the KE spectrum is negligible the corresponding scaling law for the energy spectra reads
+\begin{equation} \label{Spectra}
+E_K(k)  \sim  E_A(k) \sim \epsilon ^{2/3} d^{-1/3} k^{-2} \, .
+\end{equation} 
+The  model  provides the following predictions for the flatness factors of velocity increments
+\begin{eqnarray} \label{FL}
+F_L &=&  \frac{\meane{|\delta u_L|^4}}{\meane{|\delta u_L|^2}^2}
+\propto 
+\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2} \frac{d}{r}   = \frac{9\pi}{15}  \frac{d}{r} \\ \label{FT}
+F_T &=&  \frac{\meane{|\delta u_T|^4}}{\meane{|\delta u_T|^2}^2} 
+\propto
+\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2} =  \frac{9\pi}{10}  \frac{d}{r} 
+\end{eqnarray}
+The ratio between the two flatness factors is equal  to
+$F_T/F_L = 3/2$ according to the model.
 
-\section{Theoretical analysis}
-\label{section_advanced_theory}
-% \input{section_advanced_theory}
+We now turn to the question of how the shock width, $ \delta x $, can be estimated.
+One suggestion would be that $ \delta x $  is equal to the Kolmogorov length scale, $ \nu^{3/4}/\epsilon^{1/4} $.
+However, exact solutions of Burgers equation \cite[see for example][]{Whitham}
+suggests that  $ \delta x \propto \nu $ rather than $ \delta x \propto \nu ^{3/4} $.
+The scaling of the energy spectra (\ref{Spectra}) also suggests that $ d $ should enter into the expression for $ \delta x$, apart from $ \nu $ and $ \epsilon $.
+Dimensional analysis thus gives
+\begin{equation} \label{Width}
+\delta x \sim \frac{\nu}{\; (d\epsilon)^{1/3}} \, ,
+\end{equation} 
+which is considerably smaller than the Kolmogorov length scale.
+This result can also be derived in the following way.
+Assuming that all dissipation takes place at the shocks, whose total area is equal to $ L_s \delta x $,  and remembering that $ \epsilon $ is defined as the mean over the domain area $ \cal  A$, we find
+\begin{equation} \label{Estimate}
+\epsilon \sim \nu \frac{ \mid \Delta u \mid ^{2} }{\delta x^2} \frac{L_s \delta x}{\cal{A}} \sim \nu \frac{\epsilon^{2/3}} {\delta x d^{1/3}} \, ,
+\end{equation} 
+again giving (\ref{Width}). 
+Applying the same averaging method we obtain the following estimates for skewness and flatness of the velocity derivative, $ \partial_x u $,
+\begin{eqnarray}
+S_{\partial_x u}  & \sim & \left ( \frac{d}{\delta x} \right )^{1/2} \sim \frac{d^{2/3} \epsilon ^{1/6}}{\nu^{1/2}} \, , \\
+\label{FD} F_{\partial_x u} & \sim &  \frac{d}{\delta x} \sim \frac{d^{4/3} \epsilon^{1/3}} {\nu} \, ,
+\end{eqnarray} 
+where the skewness is negative.
+For Kolmgogorov turbulence observations indicate that $ F_{\partial_x u} \propto \nu^{-1/6} $  \cite[]{VanAtta_Antonia1980}, a dependence which is well capture by the multifractal model of
+\cite{Meneveau_Streenivasan1991}.
+In SW wave turbulence there is a much stronger increase of  the flatness factor with decreasing  $ \nu $, which can be explained the fact that dissipation takes place only at the shocks.
 
-\section{Numerical methods}
-\label{section_methods}
-% \input{section_methods}
+Finally, we estimate the Mach number of the shocks, that is the ratio between the shock propagation velocity and $ c $.
+According to \cite{Baines1998} the Mach number of a SW shock can be calculated as
+\begin{equation}
+M = \sqrt{\frac{h_+}{h_-} \frac{h_+  + h_-}{2}} \, ,
+\end{equation} 
+where $ h_+ $ and $ h_- $ are the nondimensional layer thickness before and after the shock, respectively.
+Noting that $ h_+ - h_- =  \;  \mid \!\!
+\Delta h | $, expanding in small $ | \Delta h | $ and using (\ref{Strength}) the Mach number can be estimated as
+\begin{equation} \label{Mach}
+M \sim 1 + \frac{3}{4} \frac{\;\; (\epsilon d)^{1/3}}{c} \, ,
+\end{equation} 
+and is only slightly larger than unity for all relevant applications.
 
-\section{Wave cascade without global rotation}
-\label{section_wave_cascade_f=0}
-% \input{section_wave_cascade_f=0}
+The model we have developed is, indeed, very simple.
+As such, it must, of course, have limitations.
+First, it is obvious that  the linear scaling of the structure functions only can be valid for separations  that fulfil the condition $ \delta x \ll r \ll d $.
+Second, the model cannot be valid for low order moments or structure functions.
+The minimum order for which the model may be valid is not easily determined.
+According to  \cite{BouchaudMezardParisi1995} structure functions of shock dominated turbulence of all orders $ p  \ge 1 $ scale linearly in $ r $.
+It is quite easily argued, however, that the shocks can not determine the scaling of the structure functions of order $ p=1 $.
+To see this, consider the first order moment of the absolute value of $ \delta u_L $. 
+The longitudinal velocity increment is always negative over a shock, that is to say that the difference of the projection of the velocity on the direction over which the shock is crossed is always negative.
+In a domain with periodic boundary conditions the mean value of $ \delta u_L $   is zero.
+The negative values of $ \delta u_L $ for separations where a shock is crossed must therefore be compensated by positive values for separations where no shock is crossed.
+There is no reason to believe that these values are all positive,  but they are only positive on average.
+Thus,
+$ \means{ |\delta u_L | } < \langle | \delta u_L | \rangle _{ns} $, where the left hand side is the mean value over all separations where a shock is crossed and the right hand side is the mean value over separations where no shock is crossed.
+Therefore, the model is not valid for first order moments.
+It may be conjectured that it is valid for
+second and higher order structure functions.
 
-\section{Effects of global rotation}
-\label{section_rotation}
-% \input{section_rotation}
+\section{Simulations}
+
+We have carried out a series of twenty forced-dissipative simulations of the SW
+equations in a quadratic domain with periodic boundary conditions using the
+standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
+fluidsim}.
+%
+The simulations were started from zero initial
+conditions and were run till a statistically stationary state was reached. The
+equations were reformulated in terms of the three eigenmodes of the linearized
+equations in Fourier space. One of these eigenmodes is zero for an irrotational
+flow. We first carried out a few test simulations in which all three eigenmodes
+were allowed to evolve in time. However, when only the two wave modes are
+forced vorticity remains very small throughout the simulations and does not
+affect the wave dynamics. Therefore, we chose to solve the equations only for
+the two wave modes. As discussed in the previous section, a linear viscous term
+in (\ref{eq_uu}) will not conserve momentum exactly and does not give a
+strictly positive definite expression for energy dissipation. We have relaxed
+the requirements of exact momentum conservation and positive definite energy
+dissipation. Instead of using the nonlinear form of the viscous term in
+(\ref{eq_uu}) we have used a higher order linear operator $ \nu_8 \nabla^{8} $
+both in (\ref{eq_uu}) and (\ref{eq_h}), where $ \nu_8 $ is a `hyperdiffusion'
+or a `hyperviscosity'. There is no strong physical motivation for this
+modification but, as discussed by \cite{FargeSadourny1989}, a molecular viscous
+operator of the form $\nu \nabla^2 $ is not necessarily a relevant model of the
+actual small-scale dissipation for SW flows, which should rather be described
+as a transition from two-dimensional to three-dimensional motions before
+reaching the scales where dissipation actually occurs.
+%
+Time advancement is carried out by a classical fourth-order Runge-Kutta scheme
+for the nonlinear term and an exact integration for the linear and dissipative
+terms. This explicit integration is especially useful at very high resolution
+and very large $c$ when the shortest waves are very fast. We use an adaptable
+time step method which maximizes the time step over a standard
+Courant-Friedrichs-Lewy condition \cite[]{Lundbladh1999,
+AugierChomazBillant2012}.
+%
+Most of the aliasing is removed by truncating 8/9 of the modes along each
+direction \cite[for a detail discussion on the issues of the non-conservation
+of the non-quadratic energy and the aliasing errors in the truncated one-layer
+shallow water model, see][]{FargeSadourny1989}. The resolution is characterized
+by the number of nodes, $n$, in each direction and has been varied from 960
+to 7680.
+%
+The wave speed $c$ has been varied over almost two orders of magnitude from 10
+to 700. The wave modes are forced in a shell in spectral space corresponding to
+relatively small wave numbers, $ 5 \delta k < |\kk| < 8 \delta k$, where $
+\delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
+domain. 
+The forcing is white noise in time and designed so that the energy
+injection rate is normalised to unity at each time step. When the flow has reached a stationary state dissipation should therefore be equal to unity. 
+The strength of the stratification is characterized by a
+Froude number, defined as
+\begin{equation} \label{Fr}
+F_f = \frac{\epsilon^{1/3}}{c k_f^{1/3}} \, ,
+\end{equation}
+a parameter that can be determined from the start of each simulations.
+Energy is dissipated at the smallest resolved scales by hyperviscosity.
+An intricate question is how the value of $ \nu_{8} $ should be chosen so that the shocks are resolved.
+The standard resolution requirement in turbulence simulations of this type is that the hyperviscosity analogue to the Kolmogorov scale
+\begin{equation}  \label{KolmEight}
+\eta_{8} = \left( \frac{{\nu_8}^3}{\epsilon} \right)^{\frac{1}{22}},
+\end{equation}
+should be resolved.
+However, our estimate (\ref{Width}) of the shock width suggests that this may not be a sufficient condition, since $ d $ is likely to enter the expression for $ \delta x $ also in the case when we use hyperviscosity.
+A similar estimate as in (\ref{Estimate}) gives
+\begin{equation} \label{EtaEight}
+\delta x \sim \eta_{8} \left ( \frac{\eta_8}{d} \right)^{1/21} \, .
+\end{equation} 
+Thus, the shock width dependence on $ d $ can be expected to be extremely weak when hyperviscosity is used.
+Therefore we simply use the standard resolution requirement that (\ref{KolmEight}) should be resolved.
+We have found that setting
+$  k_{d} \simeq \kmax/ 2.5$, where $ k_{d} = 1/\eta_8 $ and $\kmax =
+(8/9)\pi n/L $ is the maximum wave number, is  sufficient to resolve the shocks.
+Since the energy injection rate is normalised to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state.
+ The  simulation parameters are listed in table 1.
+
+\begin{table}
+\begin{center}
+
+\label{Table1}
+\begin{tabular}{lrrrrrrrr}
+
+\toprule
+{} &   $n$ &  $c$ &  $\nu_8$ &  $\epsilon$ &  $ k_{d}  / {k_f} $ &   $F_f$ &    $t_{\max}$ \\
+\midrule
+W1  &   960 &   10 & 1.56e-10 &        1.04 &                    28.8 &   0.111 &                49.9 \\
+W2  &  1920 &   10 & 9.68e-13 &        1.06 &                    57.7 &   0.112 &               49.8 \\
+W3  &  3840 &   10 &    6e-15 &         1.10&                     115 &   0.113 &               49.9 \\
+W4  &  7680 &   10 & 3.72e-17 &        1.18 &                     231 &   0.116 &               49.9 \\
+W5  &   960 &   20 & 1.56e-10 &           1.00 &                    28.8 &   0.055 &              49.9 \\
+W6  &  1920 &   20 & 9.69e-13 &        1.02 &                    57.7 &  0.0553 &                120 \\
+W7  &  3840 &   20 & 6.01e-15 &        1.08 &                     115 &  0.0563 &                120 \\
+W8  &  7680 &   20 & 3.72e-17 &        1.21 &                     231 &  0.0585 &                 120 \\
+W9  &   960 &   40 & 1.56e-10 &          1.00 &                    28.8 &  0.0274 &                49.8 \\
+W10 &  1920 &   40 & 9.68e-13 &       1.00 &                    57.7 &  0.0274 &               49.8 \\
+W11 &  3840 &   40 &    6e-15 &        1.06 &                     115 &   0.028 &               49.8 \\
+W12 &   960 &  100 & 1.56e-10 &       1.00 &                    28.8 &   0.011 &                49.8 \\
+W13 &  1920 &  100 & 9.69e-13 &        1.01 &                    57.7 &   0.011 &                 120 \\
+W14 &  3840 &  100 & 6.01e-15 &        1.06 &                     115 &  0.0112 &                 120 \\
+W15 &  7680 &  100 & 3.72e-17 &        1.22 &                     231 &  0.0117 &                95.8 \\
+W16 &   960 &  400 & 1.56e-10 &        1.14 &                    28.8 & 0.00287 &                 120 \\
+W17 &  1920 &  400 & 9.69e-13 &        1.15 &                    57.7 & 0.00288 &                 120 \\
+W18 &  3840 &  400 & 6.01e-15 &        1.12 &                     115 & 0.00286 &                119 \\
+W19 &   960 &  700 & 1.56e-10 &        1.27 &                    28.8 &  0.0017 &                49.8 \\
+W20 &  1920 &  700 & 9.68e-13 &        1.05 &                    57.7 &  0.0016 &                49.8 \\
+\bottomrule
+
+\end{tabular}
+\caption{Parameters for all simulations. $ n $: number of nodes in each
+direction, $ c $: wave speed, $ \nu_8 $: hyperviscosity, $ \epsilon $: time
+averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio
+between dissipation wave number and forcing wave number, $ F_f $: Froude
+number, $ t_{max} $: end time of simulation.}
+\end{center}
+\end{table}
+
+\begin{figure}
+\centerline{\includegraphics[width=5.12in]{../Pyfig/fig_Emean_time}}
+\caption{Space averaged energy, $E = E_K + E_A $, versus time for all
+simulations. }
+\label{fig_Evstime}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_energy_w}}
+\caption{Left: Mean energy in the stationary state versus $ c $ for different
+resolutions. The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2}
+$. Right: Normalised mean energy in the stationary state versus resolution $ n
+$ for different $ c $.}
+\label{MeanE}
+\end{figure}
+
+The time evolution of mean energy is shown in figure~\ref{fig_Evstime} for all
+twenty simulations. After an initial period of growth, mean energy is leveling
+out at different values for different runs. This is not the same picture as we
+see in simulations of three-dimensional incompressible turbulence or stratified
+turbulence, where all curves would have leveled out more or less at the same
+value. We find that mean energy in the stationary state is a function of both $
+c $ (or the Froude number) and resolution $ n $ and that the functional
+dependence can be approximately written as
+\begin{equation} \label{MeanEnergy}
+E \sim \sqrt{L_f c \epsilon} \, n^{\alpha}  \, ,
+\end{equation}
+where $ L_f = \pi/k_f $ is the forcing scale. In figure~\ref{MeanE} to the
+left, we see $ E/\sqrt{\epsilon} $ as function of $ c $ for different resolutions $
+n $. For each resolution the points are approaching a power law $ C_n c^{1/2} $
+with increasing values of $ C_n $ for increasing $ n $. In the same figure to
+the right we see $ E/\sqrt{L_f c \epsilon} $ for different values of $ c $. For
+each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
+becoming slightly larger with increasing $ c $, approaching almost the same
+value $ \alpha \approx 0.33 $ for the three highest values of $ c $. The
+relation (\ref{MeanEnergy}) can be reformulated as
+\begin{equation} \label{Dissipation}
+\frac{\epsilon} {(E^{3/2} / L_f)} \sim \frac{E^{1/2}}{c} n^{-2\alpha} \, .
+\end{equation}
+Since the simulations are well resolved the dependence on resolution should not
+be interpreted as consequence of the numerics but rather as a Reynolds number
+effect, although it is not hundred percent clear how a Reynolds number should
+be defined in our case. We may note, however, that $ n \sim L_f/\delta x $ and in the case of Navier-Stokes viscosity
+ we should have $ \delta x \propto \nu $, according to (\ref{Width}). Therefore,  $ n $ may be substituted by a Reynolds number. The normalised energy dissipation on the left hand side of
+(\ref{Dissipation}) will thus go to zero in the limit of large Reynolds number.
+This is very different from three-dimensional turbulence where there is a local
+Richardson-Kolmogorov cascade, in which energy is successively transfered from
+large to small scales of motion. That the cascade is local means that eddies of
+a particular scale are not directly influenced by eddies of widely different
+scales. As a consequence, the normalised dissipation is of the order of unity
+independent of Reynolds number \cite[]{Pope, TennekesLumley}. A review of the
+experimental evidence and theoretical implications of this fundamental law of
+Kolmogorov turbulence is given by \cite{Vassilicos2015}. Our result
+(\ref{Dissipation}) suggests that SW wave turbulence does not fit into the
+paradigm of a local Richardson-Kolmogorov cascade. Moreover, it is not only in
+the limit of large Reynolds number the normalised dissipation will go to zero
+but also in the limit of strong stratification, $ E^{1/2}/c \rightarrow 0 $.
+This is different from three-dimensional stratified turbulence where the ratio
+on the left hand side of (\ref{Dissipation}) is of the order of unity in the
+limit of strong stratification \cite[]{Lindborg2006, Brethouwer2007}.
+
+The `four-fifths law' for the third order structure function of Kolmogorov
+turbulence is often derived using the assumption of a local cascade
+\cite[]{Vassilicos2015} or the assumption that dissipation stays finite in the
+limit of large Reynolds number \cite[]{Frisch}. As we just discussed, these
+assumptions seem to be violated in the case of SW wave turbulence.
+Nevertheless, the analogous law (\ref{eq_Kolmo}) is satisfied with a high degree of accuracy in our simulations. In
+figure~\ref{Flux} we see the spectral energy flux from run W7 to the left and
+the third order structure function to the right. There is a broad constant flux
+range with equipartition between KE and APE flux and an almost equally broad
+range where (\ref{eq_Kolmo}) is satisfied, with equipartition between the two
+third order structure functions associated with KE and APE. The assumptions of
+a local cascade and finite dissipation do not seem to be necessary in order for
+the third order structure function law (\ref{eq_Kolmo}) to be valid.
+
+\begin{figure}
+\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_flux_struct_combined}}
+\caption{Left: Time averaged normalised spectral energy fluxes versus $ k/k_f
+$. Right: Time averaged normalised third order structure functions versus $
+r/L_f $. From run W7. }
+\label{Flux}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=3.15in]{../Pyfig/fig_spatiotempspectra}}
+\caption{Frequency spectra of KE and APE for different $ k = \mid {\bf k} \mid
+$, from run W7. The spectra are plotted as functions of $\omega/\omega_l$,
+where $\omega_l = c k$. From top to bottom: $ k /\delta k = 12$, 27, 62, 143,
+327, and 746. }
+\label{fig_spatiotemp_spectra}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave}}
+\caption{Left: divergence $ \bnabla \cdot {\bf u} $. Right: velocity component in the $ y $-direction: $ u_y $. Top: run W6. Bottom: run W17.  }
+\label{Physical}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_shock_sep.pdf}}
+\caption{Mean distance between the shocks as function of Froude number.  }
+\label{fig_distance}
+\end{figure}
+
+The equipartition of KE and APE spectral fluxes suggests that the flow to
+leading order may be described as a collection of linear gravity waves with energy
+equipartition in each mode. To investigate this further we have
+collected time series of the flow variables from Fourier modes whose magnitude
+fall within certain shells, $ \mid {\bf k} \mid \in [ k -\delta k/2, \; k+
+\delta k/2] $, and computed temporal power law spectra from these time series
+and averaged over all wave numbers in each shell. In other words, we have
+computed KE and APE frequency spectra corresponding to different magnitudes of
+modes. Figure~\ref{fig_spatiotemp_spectra} presents such spectra plotted as 
+functions of the normalised frequency $\omega/\omega_l$, where $ \omega_l = kc
+$ is the linear wave frequency. The spectra are strongly dominated by peaks at
+$\omega = \omega_l$. As can be seen, there is equipartition between KE and APE
+in each shell. Although the widening of the peaks around the linear frequency
+most likely is an effect of nonlinearities, we can quite safely conclude that
+the time evolution of the flow variables in each Fourier mode to leading order
+can be described as a linear wave.
+
+Visualisations of the flow field give a completely different picture from what
+may be expected from a collection of linear gravity waves. They are totally
+dominated by the appearance of shock waves. In figure~\ref{Physical} we see
+the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
+component in the $ y $-direction, $ u_y $, to the right. The two figures at the
+top are from run W6 while the two figures at the bottom are from run W17. The
+difference between the two runs is that $ c $ is larger by a factor of $ 20 $
+in W17 as compared to W6. To the left we see the shocks displayed as elongated
+bands of negative divergence. That the divergence is negative at the shocks can
+be understood from the fact that the velocity component perpendicular to the
+shock always has a negative jump in the direction of shock propagation.
+Apparently, the mean distance between the shocks is considerably smaller in run
+W17 with the larger value of $ c $ compared to run $ W6 $ with the smaller
+value of $ c $. 
+The shocks are also visible in the figures to right where $ u_y
+$ is displayed. It may be interesting to note that the shocks along the $ x
+$-axis appear as extra sharp in this plot, since there is a strong jump of $
+u_{y} $ over these shocks, while the shocks along the $ y $-axis are hardly
+visible, since there is no jump of $ u_{y} $ over these. In the two figures to
+the right we see a variation of the flow field over the length scale $ L_f $
+which is not seen in the two figures to the left. This variation is evidently a
+footprint of the random forcing. Although the forcing length scale $ L_f $ is
+the same in the two simulations the mean distance, $ d $, between the shocks is
+much smaller in run $ W17 $ than in run $ W6 $, which may come as a surprise.
+Another interesting observation is that the shocks in run W17 (lower figures) appear to have smaller curvature on average than the shocks in run W6 (upper figures).
+In both runs, the shocks are weak in the sense that the Mach number is close to unity and the interaction between the shocks should therefore be weak \cite[see][]{ApazidisEliasson2018}.
+However, as measured by the Mach number  (\ref{Mach}), the shocks are much weaker in run W17, where $ c $ is larger by a factor of 20 as compared to run W6 and $ d $ also is smaller.
+The shock interaction should therefore be weaker in run W17.
+The observation that the curvature of the shocks is smaller in run W17 than in run W6 may be explained by this fact.
+We have calculated  the mean distance, $ d $, between the shocks by counting the number of negative spikes
+of the divergence along ten lines parallel to the $ x $-axis and ten lines
+parallel to the $ y $-axis and then divided total length of all the lines by
+the number of spikes. Generally, we found that $ d \propto c^{-1/2} $, or
+\begin{equation} \label{MeanDistance}
+d \sim L_f F_f ^{1/2} \, ,
+\end{equation}
+independent of resolution $ n $. In figure~\ref{fig_distance} we have plotted
+$ d/L_f $ versus Froude number for all twenty runs. As can be seen, the points
+follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight
+systematic deviation at the highest $ F_f $, which may be due to the fact that
+$ d $ is rather close to the length of the side of the box for the largest $
+F_f $.
+
+\begin{figure}
+\centerline{
+\includegraphics[width=5.0in]{../Pyfig/fig_struct_order_246}}
+\caption{From top to bottom: second, fourth and sixth order compensated and
+normalised longitudinal structure functions. Left: runs with $ n=3840 $: W3,
+W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15. }
+\label{fig_StrucFunc}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=11cm]{../Pyfig/fig_ratio_strfct}}
+\caption{
+Ratio of the structure functions
+$R_p(r) = \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$ from run W4,
+for $ p = 2, \, 3, \, 4, \, 5, \, 6. $
+The dotted straight lines indicate the values predicted by (\ref{Ratio}):
+$R_2 = 2$, $R_3 = 3\pi/4$,  $R_4 = 8/3$, $ R_5 = 15 \pi /16 $ and $ R_6 = 16/5 $.}
+\label{fig_ratio}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=12cm]{../Pyfig/fig_flatness}}
+\caption{ Top: Flatness factor of transverse velocity increments. Bottom: Ratio between transverse and longitudinal flatness factor. Left: runs with $ n=3840 $: W3,
+W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15.  The dotted straight lines indicate the value 1.5 predicted by the shock model.  }
+\label{fig_flatness}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=11cm]{../Pyfig/fig_spectra}}
+\caption{Time averaged compensated and normalised energy spectra
+from runs with $ n = 7680 $: W4, W8 and W15.}
+\label{fig_spectra_c40}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=13cm]{../Pyfig/fig_diss_spectra}}
+\caption{Time averaged normalised dissipation spectra.
+Left: Constant $ c = 20 $ and varying $ n $, runs  W5, W6, W7 and W8.
+Right: Constant $ n= 1920 $ and varying $ c $, runs W2, W6, W10, W13, W17 and W20.
+The vertical lines indicate the wave numbers of the maxima.}
+\label{fig_disspectra}
+\end{figure}
+
+We will now present the results for the structure functions. Substituting
+(\ref{MeanDistance}) into (\ref{StrucFunc}) we find that the structure
+functions are expected to scale as
+\begin{equation} \label{StrucFunc2}
+\meane{|\delta u |^p}  \sim \meane{(c|\delta h |)^p} \sim  (L_f F_f^{1/2})^{p/3-1}  \epsilon^{p/3}  r  \, .
+\end{equation}
+for separation distances that fulfil the condition $ \delta x \ll r \ll d $.
+The scaling (\ref{StrucFunc2}) is
+expected to become better and better fulfilled with decreasing $ c $ (or
+increasing $ F_f $). According to (\ref{MeanDistance})
+$ d $ is increasing with $ F_f $, and the scaling range is therefore becoming
+wider for decreasing $ c $, if $ \delta x $ or the resolution  is kept
+constant. The scaling
+(\ref{StrucFunc2}) is also expected to become better and better fulfilled with
+increased resolution $ n $, since $ \delta x $ is decreasing with increasing $
+n $.
+
+As expected, we have found that the displacement structure functions scale
+exactly in the same way as the velocity structure functions, why we only plot
+velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
+compensated and normalised second, fourth and sixth order longitudinal
+structure functions from the five simulations with $ n = 3840 $ to the left and
+the three simulations with $ n = 7860 $ to the right. At small separation, $ r
+< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
+is characteristic of a smooth velocity field, indicating that the shocks are
+reasonably well resolved. There is a small bump around the shock width, $ r
+\approx \delta x $, and at $ r > \delta x $, there is a range where the
+compensated structure functions are flat, or almost flat. As expected, this
+range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
+also broader in the higher resolution runs to the right as compared to the
+lower resolution simulations to the left. There is clearly a better collapse of
+the curves for the sixth order structure functions compared to the second order
+structure functions. This is not surprising, since the shock contribution to
+the structure functions should become increasingly dominant with increasing
+order. Plots of the transverse structure functions are very similar to the
+plots of the longitudinal structure functions, with the difference that the
+transverse structure functions are somewhat smoother at $ r \approx \delta x $.
+In figure~\ref{fig_ratio} we see the ratio $ R_{p}(r) = \langle \mid \delta
+u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
+2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the
+values predicted by (\ref{Ratio}). As can be seen, there is a quite good
+agreement with the predicted values in a limited range of separations, $ r >
+\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
+becomes more narrow with increasing $ p $, an observation that we cannot
+explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
+$ r $, which is the theoretical single point limit for an irrotational
+isotropic field. In figure~\ref{fig_flatness} we se the flatness factor, $
+F_T $, of the transverse structure functions at the top and the ratio, $
+F_T/F_L $, at the bottom. The figures to the left show the results from the
+five simulations with $ n = 3840 $ and the figures to the right show the
+results from the three simulations with $ n = 7860 $. The flatness factor shows
+increasingly large values for decreasing $ r $ with a dependence that is rather
+close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
+leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
+$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
+is increasing with decreasing scale is by some authors defined as the most
+appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
+If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
+In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
+limited range of separations, $ r > \delta x $, which is becoming somewhat
+broader as $ c $ is increasing and is also somewhat broader in the higher
+resolution runs shown to the right as compared to the lower resolution runs
+shown to the left. This is in accordance with the shock model predictions
+(\ref{FL}) and (\ref{FT}).
+
+Finally, we present energy and dissipation spectra. As expected, we found that APE and KE
+spectra were almost identical, why we only plot the
+total spectra. In figure~\ref{fig_spectra_c40} we see  compensated and
+normalised energy spectra from the three highest resolution runs. The
+compensated spectra are almost flat in a broad range. In the high wave number
+end the compensated spectra show a `bottleneck', which we interpret as a
+signature of the shocks. The $ k^{-2} $-dependence and the associated scaling predicted
+by (\ref{Spectra}) are very well satisfied in a limited range of high wave
+numbers close to the bottleneck. At smaller wave numbers the spectra are
+becoming somewhat steeper than $ k^{-2} $ and the spectrum from the run with
+largest $ c $ does not collapse perfectly onto the other two spectra.  In figure \ref{fig_disspectra}
+ we see normalised dissipation spectra for fixed $ c= 20 $ and different $ n $ to the left, and fixed $ n = 1920 $
+and different $ c $ to the right.
+First we note that the spectra go to zero quite nicely for large $ k $, indicating that the shock width $ \delta x $ is well resolved.
+Second, we note that there is a slight shift of the maximum in both figures, even though we have normalised the wave number by $ k_d = 1/\eta_8 $.
+These shifts may be explained by the estimate (\ref{EtaEight}) predicting that $ \delta x $ should vary slightly with $ d $.
+If the maximum of the dissipation spectra is associated with $ \delta x $, there should be a shift of the maximum  to the right with increasing $ n $ and to the left with increasing $ c $, since $ d \propto c^{-1/2} $.
+ The ratio between the maximum and the minimum $ n $ in the left figure is equal to 8 and  according to (\ref{EtaEight}) the corresponding ratio between the wave numbers at which the maxima are observed should be $ 8^{1/21} \approx 1.1 $, which is exactly the value we observe.
+The ratio between the maximum and minimum $ c $ in the right figure is equal to $ 70 $.
+Assuming that $ d \propto c^{-1/2} $ the ratio between the wave numbers at which the maxima are observed should be $ 70^{1/42} \approx 1.1 $, while the observed ratio is equal to $ 1.16 $.
 
@@
 
-We have numerically investigated one-layer shallow-water flows forced
-with medium-scale waves and dissipated at small scales.
-%
-First, we have focused on the non-rotating case and varied the
-resolution and the wave speed over a wide range.
-%
-The spectral energy budget for the full non-quadratic energy has been
-derived and has allowed us to show that the KE and the APE fluxes are
-constant and equal over a wide range of wave numbers.
-%
-The KE and APE spatio-temporal spectra present equal and very strong
-peaks at the linear wave frequency.
-%
-These two results show that there is a downscale energy cascade of
-non-dispersive waves, explaining the generation of statistically
-stationary flows.
-%
-We have derived an exact Kolmogorov law for the one-layer
-shallow-water flow based on the assumption that there is a constant
-energy flux due to a purely divergent flow and verified that the
-numerical results are in agreement with this theoretical law.
+We have carried out a theoretical and numerical investigation of SW wave
+turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the
+`four-fifths' law of Kolmogorov turbulence. Using this relation and
+straightforward statistical and geometrical arguments we developed a simple
+shock model predicting that the shock amplitude scales as $ (\epsilon d)^{1/3}
+$, where $ d $ is the mean distance between the shocks, and that the $ p $:th
+order structure function above a certain minimum will scale as $ (\epsilon
+d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative
+simulations, varying the Froude number and the resolution. In all simulations,
+a statistically stationary state was reached and in all simulations we
+observed shocks. The flow variables in each Fourier mode were found to evolve
+in accordance with linear wave dynamics, with equipartition between APE and KE
+over a period. The third order structure function relation was fulfilled with a
+high degree of accuracy. From the simulations we made two interesting
+observations that fall outside the predictive scope of the model. The first
+observation was that mean energy in the stationary state approximately scales
+as (\ref{MeanEnergy}), suggesting that the normalised dissipation
+(\ref{Dissipation}) will go to zero both in the limit of small viscosity and
+large wave speed. This is different from three-dimensional Kolmogorov
+turbulence as well as strongly stratified turbulence, where, in both cases,
+dissipation is finite in the limit of small viscosity, and in the latter case
+also is independent of the degree of stratification. This observation suggests
+that SW wave turbulence does not fit into the paradigm of a local
+Richardson-Kolmogorov cascade. The second observation we made was that the mean
+distance between the shocks scales as $ c^{-1/2} $, if the other parameters are
+held constant. As we increased $ c $, the shocks were thus becoming denser.
+Using this observation we tested the shock model by plotting the normalised and
+compensated structure functions of different orders. Generally we found that
+there was a quite good agreement between the simulation results and the model
+predictions, becoming better with decreasing wave speed and increasing
+resolution.
 
-The time- and spaced-averaged energy scales like $E = C_n \sqrt{\eps
-L_f c}$ and increases with the resolution at least up to $n = 5760$.
-The spectra scale like the Zakharov-Sagdeev spectrum $k^{-3/2}
-\sqrt{\eps c}$ at relatively small wave numbers $k \lesssim 2 k_f$ and
-like $k^{-2} c^{1/3} \eps^{5/9} k_f^{4/9}$ over the inertial range.
-We stress that we lack any convincing theoretical explanations for
-these scaling laws and we hope our results will motivate theoretical
-investigations on these challenging issues.
+Combining the model and the observations we can get a quite good picture of the
+dynamics in the limit of weak nonlinearities, $ F_{f} \rightarrow 0 $. The
+picture may become more vivid if we say `wave breaking' were we previously have
+talked about shock formation, and also say `wave lengths' were we previously
+have talked about length scales. We identify the longest wave length, $
+\lambda_l $, with the forcing scale $ L_f $ and the breaking wave length, $
+\lambda_b $, with the mean distance, $ d $, between the shocks. There are two
+dynamically different regimes, the short wave regime, $ [\delta x, \;
+\lambda_b] $, and the long wave regime, $ [\lambda_b, \, \lambda_l] $. We first
+consider the latter, whose width scales $ \lambda_{l} /\lambda_b \sim
+F_f^{-1/2} $. Identifying the amplitude of the breaking waves with the shock
+amplitude, $ (\epsilon d)^{1/3} $, we find that the ratio between the amplitude of
+the longest waves and the breaking waves scales as $ E^{1/2}/(\epsilon d)^{1/3}
+\sim F_{f}^{-5/12} n^{\alpha/2} $, where we may substitute $ n $ with a
+Reynolds number. Thus, for small $ F_f $ and large Reynolds
+number the longest waves are not directly influenced by wave breaking. The
+Reynolds number dependence of the amplitude ratio makes it unlikely that a
+general similarity theory can be easily formulated for this range. Therefore,
+predictions from weak turbulence theory \cite[for
+example][]{ZakharovSagdeev1970} are not likely to hold for this range, although
+it is not directly influenced by wave breaking. The exact values of the power
+law exponents in the argument leading to this conclusion are, of course, not
+important. As for the short wave regime, the width scales as $ \lambda_b
+/\delta x \sim F_f^{1/2} $ for fixed $ \delta x $ or fixed Reynolds number. As
+$ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that
+breaking will disappear. Clearly, a necessary condition for wave breaking is 
+\begin{equation} \label{Condition} 
+\frac{\lambda_b}{\delta x} \gg 1 \, .
+\end{equation} 
+It is interesting to note that this condition means that the flatness factor of velocity derivatives (\ref{FD}) should be much larger than unity and that this flatness factor is equal to the longitudinal flatness factor (\ref{FL}) in the limit $ r \rightarrow 0 $.
+Substituting (\ref{Width}) into (\ref{Condition})  and assuming that (\ref{MeanDistance}) is valid also in the case when Navier-Stokes viscosity is used we can formulate
+the condition as
+\begin{equation} 
+Re F_f^{2/3} \gg 1 \, ,
+\end{equation} 
+where we have defined the Reynolds number as $ Re  \equiv \epsilon^{1/3} L_{f}^{4/3} / \nu $. It may be conjectured  that such a condition is sufficient for wave breaking. If this is true, 
+wave breaking will appear for any small $ F_f $ provided that the Reynolds number is sufficiently large.
 
-Nevertheless, the $k^{-2}$ scaling can be explained by the presence of
-discontinuities \cite[]{Kuznetsov2004}.  The snapshots indeed show
-very sharp hydraulic jumps, which are the equivalent of shocks in
-compressible flows.
-%
-Following \cite{BouchaudMezardParisi1995} and
-\cite{WeinanKhaninMazelSinai1997}, we have built a simple model based
-on the assumption that the structure functions are determined only by
-shocks.
-%
-Using only this hypothesis, we explain the extreme intermittent
-characteristics of the flows, i.e.\ the $r^1$-scaling of the structure
-functions of order larger than 2 and the $r^{-1}$-scaling of the
-flatness.
-%
-Adding a simple hypothesis on the structure of the velocity field
-across the shocks, namely $\delta u_L = \delta u \sin\theta$ and
-$\delta u_T = \delta u \cos\theta$, where $\theta$ is the angle
-between the shock line and the separation vector, we have predicted
-the values of ratios of structure functions $R_p(r) \equiv
-\mean{|\delta u_L|^p}/\mean{|\delta u_T|^p}$ and of the flatness
-factors $F_T/F_L = 1.5$.
-%
-% Very interestingly, the flatness factors computed from atmospheric
-% data \cite[]{Lindborg1999} are also very large with a slope close to
-% $-1$ and a ratio $F_T/F_L$ equal to $1.5 \pm 0.1$.
-%
-Finally, we have shown that as long as $k_f>k_d$, the dispersion added
-by the rotation does not prevent the production of the regime studied
-in the non-rotating case and only weakly modify the results on the
-wave cascade.
+The question that originally motivated this study was if SW wave turbulence can
+be used as a model for energy dissipation in the atmosphere and the oceans.
+Undoubtedly, the answer to this question is negative and the reason for this is
+not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
+which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
+reason is that SW wave turbulence is a far too inefficient agent of
+dissipation. Since the Reynolds number of geophysical flows is extremely large
+and the stratification is strong, the relation (\ref{Dissipation}) implies that
+dissipation would be absent in the interior of the atmosphere and the oceans
+with SW turbulence as the responsible agent. This not what we observe. In a companion paper \cite[]{LindborgMohanan}
+we develop a toy model of geophysical turbulence which is similar to the SW equations in the mathematical structure, but is absent of shocks. 
+In this model energy is dissipated through a local cascade involving both vortical and wave modes.
 
-% In order to draw conclusions on the interpretation of turbulent
-% measurements in geophysical flows, we first have to stress that the
-% one-layer shallow-water model can only give insights on some
-% mechanisms important for geophysical fluids but is not suitable for
-% simulate the oceans and atmosphere.
-% %
-% Most of the simulations of theses systems are performed solving the
-% so-called primitive equations, which are (or in the atmospheric case
-% are very similar to) the Navier-Stokes equations under the Boussinesq
-% and the hydrostatic approximations.
-% %
-% We focus on the non-rotating case since it is a reasonable
-% approximation for the medium scales for which an energy cascade seems
-% to strongly influence the dynamics of geophysical flows, namely the
-% mesoscales in the atmosphere and the sub-mesoscales in the oceans.
-% %
-% The dominant balance for the primitive equations in the strongly
-% stratified and high Reynolds number limits corresponds to flows
-% structured in thin layers \cite[]{BillantChomaz2001}.
-% %
-% This layering, which has been widely observed in nature, is of course
-% inconsistent with the one-layer shallow-water model.
-% %
-% Another aspect of the dominant balance in the strongly stratified and
-% high Reynolds number case is that the energetic waves are not fast
-% compared to the balanced flows ($\omega_l \sim \omega_{nl}$), which is
-% very different from the case of the studied one-layer shallow-water
-% flows.
-% %
-% Moreover, the strongly stratified and high Reynolds number dominant
-% balance would corresponds in terms of the shallow-water Froude number
-% to $Fr \sim 1$.  This limit can not be correctly simulated even with a
-% multi-layer shallow-water model since when $Fr \sim 1$ the thickness
-% of the layers tends to reach the value 0 for which the shallow-water
-% models cease to be well defined.
-% %
-% Therefore, the shallow-water models are not suitable for simulating
-% the geophysical medium scales where the cascade is important.
+Although the answer to the question that originally motivated this study is
+negative, it may lead us or some other investigators to pursue another
+interesting research direction. As pointed out in the introduction, the
+acoustic equations are to the lowest order expansion in density perturbations
+identical to the SW equations. This study may therefore give important clues to
+the long standing problem of acoustic turbulence, in two and three dimensions.
+A similar shock model as we developed in two dimensions may easily be
+formulated in three dimensions, where the third order structure function law
+will be similar to (\ref{eq_Kolmo}), with the only difference that the constant
+$ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions
+we find
+\begin{equation}
+\meane{ |\delta \uu|^2 \delta J_L }
++ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \epsilon r. \label{eq_Kolmo3}
+\end{equation}
+In the case of acoustic turbulence $ \delta h $ should be interpreted as a
+normalised density increment rather than a displacement increment. If shocks in
+three dimensions are assumed to form as smooth surfaces rather than smooth
+lines, then the mean distance between the shocks will appear in the
+model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total shock area and
+$ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as
+$ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon
+d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will
+form in a similar way as in two dimensions. Generally, shock waves have similar 
+stability properties in two and three dimensions \cite[]{ApazidisEliasson2018, LivertsApazidis2016} and 
+it can therefore be expected that the three-dimensional case should be similar to the two-dimensional case. 
+If it is, the most interesting
+questions are if the mean energy and the mean distance between the shocks scale
+in a similar way in three dimensions as in two dimensions. Simulations or
+experiments of acoustic turbulence may provide answers to these questions --
+answers that will lead to further clues to a theoretical understanding of
+acoustic turbulence. We hope that the present study will stimulate research in
+this direction.
 
-Our results on the dynamics of the wave energy cascade in the
-one-layer shallow-water model can yet give interesting informations on
-the interpretation of turbulent measurements in geophysical fluids.
-%
-Since we have shown in this case that many statistical results are
-dominated by the effects of the discontinuities due to shocks, we can
-conjecture that the discontinuities or front in the atmosphere can
-significantly influence the cascade processes and the statistical
-results.
-%
-It would be interesting in the future to quantity the effects of the
-processes of frontogenesis in terms of downscale energy cascade in
-geophysical flows.
+%\appendix
 
-\section*{Acknowledgements}
-
-The authors thank Gregory Falkovich and Sergey Nazarenko for valuable
-comments and suggestions regarding the interpretation of the
-simulations.
-
-\appendix
-
-\section{Kinetic energy dissipation and forcing rates}
-\label{app_comp}
-% \input{appendix_dissip_forcing}
+%\section{Kinetic energy dissipation and forcing rates}
+%\label{app_comp}
+%\input{appendix_dissip_forcing}
 

### 2018-10-23 Old_Latex/ArticleNew.tex
Update Erik's files

--- 2018-10-17 Latex/ArticleNew.tex
@@
 the linearized operator with zero linear frequency and with finite
-non-zero linear frequency, $\omega  \pm\sqrt{f^2 + c^2
+non-zero linear frequency, $\omega = \pm\sqrt{f^2 + c^2
 k^2}$, where $f$ is the Coriolis parameter, $c$ the gravity wave speed and $k
@@
 of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
-of particular interest, since the aqoustic equations and the SW equations are
+of particular interest, since the acoustic equations and the SW equations are
 identical when a first order expansion is made in density or displacement
-pertubations. It may be questioned, however, that weak turbulence formalism is
+perturbations. It may be questioned, however, that weak turbulence formalism is
 applicable to acoustic and SW wave turbulence, no matter how weak the
@@
 We have carried out a theoretical and numerical investigation of SW wave
-turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the the
+turbulence. First, we derived the SW analogue (\ref{eq_Kolmo}) of the
 `four-fifths' law of Kolmogorov turbulence. Using this relation and
@@
 observation was that mean energy in the stationary state approximately scales
-as (\ref{MeanEnergy}), suggesting that the normalised dissipation
+as (\ref{MeanEnergy}), suggesting that the normalized dissipation
 (\ref{Dissipation}) will go to zero both in the limit of small viscosity and
@@
 held constant. As we increased $ c $, the shocks were thus becoming denser.
-Using this observation we tested the shock model by plotting the normalised and
+Using this observation we tested the shock model by plotting the normalized and
 compensated structure functions of different orders. Generally we found that
@@
 The question that originally motivated this study was if SW wave turbulence can
-be used as a model for energy dissipation in the the atmosphere and the oceans.
+be used as a model for energy dissipation in the atmosphere and the oceans.
 Undoubtedly, the answer to this question is negative and the reason for this is
@@
 interesting research direction. As pointed out in the introduction, the
-acoustic equations are to the lowest order expansion in density pertubations
+acoustic equations are to the lowest order expansion in density perturbations
 identical to the SW equations. This study may therefore give important clues to
@@
 In the case of acoustic turbulence $ \delta h $ should be interpreted as a
-normalised density increment rather than a displacement increment. If shocks in
+normalized density increment rather than a displacement increment. If shocks in
 three dimensions are assumed to form as smooth surfaces rather than smooth

### 2018-10-23 Old_Latex/Estimates.tex
Update Erik's files

\documentclass[12pt]{article}
\usepackage{graphicx}

\topmargin 0in % 25mm-1in makes the body start 25mm below top of paper
\headheight 3ex 
\headsep 14mm

\advance \topmargin by -\headheight
\advance \topmargin by -\headsep

% height of thesis textarea (11pt font):
\topskip 5ex
\textheight 225mm

\oddsidemargin 	4mm     % 3cm - 1in - 1mm correction lwmech4
\evensidemargin \oddsidemargin
% width of thesis textarea (11pt font):
\textwidth 160mm
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\parskip 0ex
\parindent 1em

\setlength{\unitlength}{1truemm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\noindent {\bf \large Estimate of the characteristic shock width and lifetime in  terms of $ \nu, \; \epsilon, \; Re $ and $ Fr $.}
\vskip 5mm
\noindent Definitions
\begin{equation}
Re = \frac{\varepsilon^{1/3} L^{4/3}}{\nu} \, ,\;\;\;\;\; Fr = \frac{\varepsilon^{1/3} L^{1/3}}{c} 
\end{equation} 
The characteristic shock width, $ \delta x $, can be estimated by assuming that all dissipation takes place within the shocks and that the dissipation scale is equal to $ \delta x $. The mean dissipation over the domain area $ \cal{A} $
can thus be estimated as
\begin{equation}
\varepsilon \sim \nu  \frac{\Delta u^2} {\delta x^2} \frac{L_s \delta x} {\cal{A}}\sim \frac{\nu \varepsilon^{2/3} }{\delta x d^{1/3}} \, ,
\end{equation} 
With 
\begin{equation} \label{dScale}
d \sim Fr L   
\end{equation} 
we find that
\begin{equation}
\delta x \sim Re^{-1/4} Fr^{-1/3} \, \frac{\nu^{3/4}}{\varepsilon^{1/4}} \, ,
\end{equation}
where we recognise $ {\nu^{3/4}}/{\varepsilon^{1/4}} $ as the Kolmogorov length scale. The characteristic life time can be estimated as
\begin{equation}
\tau \sim  \frac{\Delta u^2}{\varepsilon} \frac{L_s \delta x}{A} \sim \frac{\delta x}{\; (\varepsilon d)^{1/3}} \sim Re^{-1/2} Fr^{-2/3} \left ( \frac {\nu}{\epsilon} \right )^{1/2} 
\end{equation} 
where we recognise  $ (  {\nu}/{\epsilon}  )^{1/2} $ as the Kolmogorov time scale. A necessary condition for the appearance of shocks is that $ \delta x \ll d $, leading to the condition
\begin{equation}
Re^{5/4} Fr^{4/3} \gg 1 \, .
\end{equation} 
It may be conjectured that this is not only a necessary condition but also a sufficient conditions for shocks to appear.

\end{document}

### 2018-10-23 Old_Latex/appendix_dissip_forcing.tex
Update Erik's files

--- 2016-12-17 Old/appendix_dissip_forcing.tex
@@
 expression.
+
+Since only the ageostrophic variable is forced ($\hat f_d = 0$),%
+(i) only the thickness fluctuation $\eta$ is forced in the
+non-rotating case and %
+(ii) the force terms in (\ref{eqapmnum}) are simply equal to $\hat
+f_\pm = \hat f_a/2$.
+%
+In order to compute the force $\hat f_a$, we start from a
+pre-normalized force $\hat f_{0}$ obtained from a normal random
+process decorrelated in time.
+%
+The force is then normalized such that the quadratic part of the total
+energy $\langle|\uu|^2 + c^2 \eta^2\rangle/2$ is injected at a
+constant rate.
+%
+The spectral injection rate of the quadratic energy averaged over one
+time step is (see appendix~\ref{app_comp})
+\begin{equation}
+P_q(\kk, t) 
+= 
+\Re\{ \hat \uu(\kk)^* \cdot \hat \ff(\kk) 
++
+c^2 \hat \eta(\kk)^* \hat f_\eta(\kk) \}
++ 
+(|\hat\ff|^2 + c^2 |\hat f_\eta|^2) \delta t /2,
+\end{equation}
+where $\Re$ denotes the real part.
+%
+Writing $\hat f_a = \alpha \hat f_{0}$, it is straightforward to solve
+a second-order equation for the coefficient $\alpha$ in order to fix
+the injection rate $\Add{P_0 \equiv} \sum_\kk P_q(\kk, t)$ to unity.
 

### 2018-10-23 Old_Latex/section_advanced_theory.tex
Update Erik's files

--- 2018-10-17 Latex/section_advanced_theory.tex
@@
 x}^\prime $, separated by the vector $ {\bf r} = {\bf x}^\prime - {\bf x} $.
-Using Cartesian tensor notation we denote derivates with respect to $ {\bf x} $
+Using Cartesian tensor notation we denote derivatives with respect to $ {\bf x} $
 as $ \partial_i $ and derivatives with respect to $ {\bf x}^\prime $ as $
@@
 
-We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
-The model is similar to the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation, although we derive it by using quite different arguments.
-We consider a domain with total area  $ {\mA} $ occupied by shocks which we
-consider as smooth lines. We denote the total length of all shocks by $ L_s $.  The mean distance between the shocks within the domain can be estimated as
+We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and
+statistical arguments to construct a model for velocity and displacement
+structure functions of any order above a certain minimum. The model is similar
+to the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation,
+although we derive it by using quite different arguments. We consider a domain
+with total area $ {\mA} $ occupied by shocks which we consider as smooth lines.
+We denote the total length of all shocks by $ L_s $. The mean distance between
+the shocks within the domain can be estimated as
 \begin{equation}
@@
 \end{equation}
-Assuming that (\ref{StrucFunc}) is valid for second order moments and that the non-quadratic contribution to the KE spectrum is negligible the corresponding scaling law for the energy spectra reads
+Assuming that (\ref{StrucFunc}) is valid for second order moments and that the
+non-quadratic contribution to the KE spectrum is negligible the corresponding
+scaling law for the energy spectra reads
 \begin{equation} \label{Spectra}
@@
 
-Being such a simple model it must have  limitations.
-First, it is obvious that  the model can  only be valid for separations  that fulfill the condition $ \delta x \ll r \ll d $,  where $ \delta x $ is the shock width.
-Second, the model cannot be valid for low order moments or structure functions.
-The minimum order for which the model may be valid is not easily determined.
-According to  \cite{BouchaudMezardParisi1995} structure functions of shock dominated turbulence of all orders $ p  \ge 1 $ scale linearly in $ r $.
-It is quite easily argued, however, that the shocks can not determine the scaling of the structure functions of order $ p=1 $.
-To see this, consider the first order moment of the absolute value of $ \delta u_L $.
-The longitudinal velocity increment is always negative over a shock, that is to say that the difference of the projection of the velocity on the direction over which the shock is crossed is always negative.
-In a domain with periodic boundary conditions the mean value of $ \delta u_L $   is zero.
-The negative values of $ \delta u_L $ for separations where a shock is crossed must therefore be compensated by positive values for separations where no shock is crossed.
-There is no reason to believe that these values are all positive,  but they are only positive on average.
-Thus,
-$ \means{ |\delta u_L | } < \langle | \delta u_L | \rangle _{ns} $, where the left hand side is the mean value over all separations where a shock is crossed and the right hand side is the mean value over separations where no shock is crossed.
-Therefore, the model is not valid for first order moments.
-It may be conjectured that it is valid for
-second and higher order structure functions.
+Being such a simple model it must have limitations. First, it is obvious that
+the model can only be valid for separations that fulfill the condition $ \delta
+x \ll r \ll d $, where $ \delta x $ is the shock width. Second, the model
+cannot be valid for low order moments or structure functions. The minimum order
+for which the model may be valid is not easily determined. According to
+\cite{BouchaudMezardParisi1995} structure functions of shock dominated
+turbulence of all orders $ p \ge 1 $ scale linearly in $ r $. It is quite
+easily argued, however, that the shocks can not determine the scaling of the
+structure functions of order $ p=1 $. To see this, consider the first order
+moment of the absolute value of $ \delta u_L $. The longitudinal velocity
+increment is always negative over a shock, that is to say that the difference
+of the projection of the velocity on the direction over which the shock is
+crossed is always negative. In a domain with periodic boundary conditions the
+mean value of $ \delta u_L $ is zero. The negative values of $ \delta u_L $ for
+separations where a shock is crossed must therefore be compensated by positive
+values for separations where no shock is crossed. There is no reason to believe
+that these values are all positive, but they are only positive on average.
+Thus, $ \means{ |\delta u_L | } < \langle | \delta u_L | \rangle _{ns} $, where
+the left hand side is the mean value over all separations where a shock is
+crossed and the right hand side is the mean value over separations where no
+shock is crossed. Therefore, the model is not valid for first order moments. It
+may be conjectured that it is valid for second and higher order structure
+functions.

### 2018-10-23 Old_Latex/section_basic_theory.tex
Update Erik's files

--- 2018-10-16 Latex/section_basic_theory.tex
@@
 \end{eqnarray}
-where $\uu$ is the horizontal velocity, %
-$h = 1 + \eta $ the non-dimensional thickness of the fluid layer,  $ \eta $ being the surface displacement, 
-$\nu$ the kinematic viscosity and $ c $ is the gravity wave speed.
-The SW equations conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $.
-As a matter of fact, we have constructed the viscous term in (\ref{UEq}) in such a way that momentum is conserved and energy dissipation is positive definite.
-This can only be accomplished by permitting the term to be nonlinear in the flow variables.
-There are different forms of nonlinear terms that fulfill both conditions and it may be disputed which is the best one.
-However, in the simulations we will use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfill any of these two conditions in a strict sense.
-Therefore, we will not discuss this matter further.
-The inviscid SW equations conserve a local
-quantity along trajectories of the fluid particles, the Ertel
-potential vorticity $\ErtelPV = \zeta /h$, where $\zeta  $ is the vorticity, which in a rotating system should be interpreted as absolute vorticity.
-In this paper this conservation law will be of no relevance since we only consider
-irrotational flows for which the velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the velocity potential.
-In a domain with no net fluxes through the boundaries the inviscid equations conserve total energy $ E_K + E_P $, where $ E_K =   {\bf J}  \cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential energy.
-The latter can be split into three terms as \begin{equation}
+where $\uu$ is the horizontal velocity, $h = 1 + \eta $ the non-dimensional
+thickness of the fluid layer, $ \eta $ being the surface displacement, $\nu$
+the kinematic viscosity and $ c $ is the gravity wave speed. The SW equations
+conserve mass, $ h $, and momentum $ {\bf J} = h{\bf u} $. As a matter of fact,
+we have constructed the viscous term in (\ref{UEq}) in such a way that momentum
+is conserved and energy dissipation is positive definite. This can only be
+accomplished by permitting the term to be nonlinear in the flow variables.
+There are different forms of nonlinear terms that fulfill both conditions and
+it may be disputed which is the best one. However, in the simulations we will
+use diffusion terms in both (\ref{UEq}) and (\ref{HEq}) that will not fulfill
+any of these two conditions in a strict sense. Therefore, we will not discuss
+this matter further. The inviscid SW equations conserve a local quantity along
+trajectories of the fluid particles, the Ertel potential vorticity $\ErtelPV =
+\zeta /h$, where $\zeta $ is the vorticity, which in a rotating system should
+be interpreted as absolute vorticity. In this paper this conservation law will
+be of no relevance since we only consider irrotational flows for which the
+velocity can be written as $ \uu = \bnabla \phi $ , where $ \phi $ is the
+velocity potential. In a domain with no net fluxes through the boundaries the
+inviscid equations conserve total energy $ E_K + E_P $, where $ E_K = {\bf J}
+\cdot {\uu} /2 $ is kinetic energy and $ E_P = c^{2} h^2/2 $ is potential
+energy. The latter can be split into three terms as
+\begin{equation}
 E_P = c^2/2 + c^2\eta+ c^2 \eta^2/2,
@@
 where the first term corresponds the potential energy of the state with no
-surface displacement.  The third term, which is quadratic in the surface displacement, may be named available potential energy (APE),
-$E_A = c^2\eta^2/2$, a concept introduced by  \cite{Lorenz1955}.
-As a consequence of mass and energy conservation the SW equations also conserve the sum of kinetic and available potential energy, $ E_K + E_A $.
- The velocity potential and the displacement of the linearized inviscid SW equations both satisfy the wave equation,
+surface displacement. The third term, which is quadratic in the surface
+displacement, may be named available potential energy (APE), $E_A =
+c^2\eta^2/2$, a concept introduced by \cite{Lorenz1955}. As a consequence of
+mass and energy conservation the SW equations also conserve the sum of kinetic
+and available potential energy, $ E_K + E_A $. The velocity potential and the
+displacement of the linearized inviscid SW equations both satisfy the wave
+equation,
 \begin{equation}

### 2018-10-26 Latex/article.tex
Submitted version which includes comments suggested by Ashwin

@@
 \author[P. Augier, A.V. Mohanan and E. Lindborg]%
-{Pierre Augier$^{1}$,   A. V. Mohanan$^{2}$
+{Pierre Augier$^{1}$, Ashwin Vishnu Mohanan$^{2}$
 and Erik Lindborg$^2$ \ns }
@@
 \cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
-statistically stationary shallow-water flows can be obtained forcing
+statistically stationary shallow-water flows can be obtained by forcing
 quasi-geostrophic modes at large scales and with dissipation only at
@@
 where the skewness is negative.
-For Kolmgogorov turbulence observations indicate that $ F_{\partial_x u} \propto \nu^{-1/6} $  \cite[]{VanAtta_Antonia1980}, a dependence which is well capture by the multifractal model of
+For Kolmogorov turbulence observations indicate that $ F_{\partial_x u} \propto \nu^{-1/6} $  \cite[]{VanAtta_Antonia1980}, a dependence which is well capture by the multifractal model of
 \cite{Meneveau_Streenivasan1991}.
@@
 \begin{equation} \label{MeanEnergy}
-E \sim \sqrt{L_f c \epsilon} \, n^{\alpha}  \, ,
+E \sim \sqrt{\epsilon L_f c} \, n^{\alpha}  \, ,
 \end{equation}
@@
 with increasing values of $ C_n $ for increasing $ n $. In the same figure to
-the right we see $ E/\sqrt{L_f c \epsilon} $ for different values of $ c $. For
+the right we see $ E/\sqrt{\epsilon L_f c} $ for different values of $ c $. For
 each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
@@
 We have calculated  the mean distance, $ d $, between the shocks by counting the number of negative spikes
-of the divergence along ten lines parallel to the $ x $-axis and ten lines
-parallel to the $ y $-axis and then divided total length of all the lines by
-the number of spikes. Generally, we found that $ d \propto c^{-1/2} $, or
+of the divergence along two hundred lines parallel to the $ x $-axis and
+equally many parallel to the $ y $-axis and then divided total length of all
+the lines by the number of spikes. Generally, we found that $ d \propto
+c^{-1/2} $, or
 \begin{equation} \label{MeanDistance}
@@
 normalised longitudinal structure functions. Left: runs with $ n=3840 $: W3,
-W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15. }
+W7, W11, W14 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15. }
 \label{fig_StrucFunc}
@@
 Ratio of the structure functions
-$R_p(r) = \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$ from run W4,
+$R_p(r) = \mean{|\delta u_L|^p} / \mean{|\delta u_T|^p}$ from run W8,
 for $ p = 2, \, 3, \, 4, \, 5, \, 6. $
@@
 \caption{ Top: Flatness factor of transverse velocity increments. Bottom: Ratio between transverse and longitudinal flatness factor. Left: runs with $ n=3840 $: W3,
-W7, W11 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15.  The dotted straight lines indicate the value 1.5 predicted by the shock model.  }
+W7, W11, W14 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15.  The dotted straight lines indicate the value 1.5 predicted by the shock model.  }
 \label{fig_flatness}
@@
 As expected, we have found that the displacement structure functions scale
-exactly in the same way as the velocity structure functions, why we only plot
+exactly in the same way as the velocity structure functions, and for this
+reason we only plot
 velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
@@
 u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
-2,3,4,5,6 $ from run W4, together with dotted straight lines, indicating the
+2,3,4,5,6 $ from run W8, together with dotted straight lines, indicating the
 values predicted by (\ref{Ratio}). As can be seen, there is a quite good

### 2018-10-26 Latex/article.tex
Edits which should have been included for sure, but did not make the cut

@@
 Finally, we present energy and dissipation spectra. As expected, we found that APE and KE
-spectra were almost identical, why we only plot the
+spectra were almost identical, and therefore we only plot the
 total spectra. In figure~\ref{fig_spectra_c40} we see  compensated and
@@
 dissipation would be absent in the interior of the atmosphere and the oceans
-with SW turbulence as the responsible agent. This not what we observe. In a companion paper \cite[]{LindborgMohanan}
+with SW turbulence as the responsible agent. This is not what we observe. In a companion paper \cite[]{LindborgMohanan}
 we develop a toy model of geophysical turbulence which is similar to the SW equations in the mathematical structure, but is absent of shocks. 
-In this model energy is dissipated through a local cascade involving both vortical and wave modes.
+In this model, energy is dissipated through a local cascade involving both vortical and wave modes.
 

### 2019-02-18 Python/base.py
Start plotting laplacian runs : laplacian_nupt1

@@ -1,8 +1,13 @@
 from __future__ import print_function, division
 from warnings import warn
 import itertools
+import os
+
 import pylab as pl
 import numpy as np
+import pandas as pd
+import xarray as xr
+
 import seaborn as sns
 from scipy.optimize import curve_fit
 from scipy.signal import medfilt
@@ -15,9 +20,27 @@ from fluidsim.solvers.sw1l.output.spatial_means import SpatialMeansSW1L
 
 #from _try_dask_strfunc import strfunc_from_pdf3 as strfunc_from_pdf
 from fluidsim.base.output.increments import strfunc_from_pdf
+import fluidsim as fls
 
 DPI = 300
 
+
+def load_spatial_means(path, sim=None):
+    if sim is None and path:
+        if os.path.isdir(path):
+            path_txt = os.path.join(path, "spatial_means.txt")
+            path_json = os.path.join(path, "spatial_means.json")
+        try:
+            try:
+                return SpatialMeansSW1L._load(path_txt)
+            except AttributeError:
+                from fluidsim.solvers.sw1l.output.spatial_means import _old_load_txt
+                return _old_load_txt(path_txt)
+        except FileNotFoundError:
+            df = pd.read_json(path_json, orient="records", lines=True)
+            return xr.Dataset.from_dataframe(df)
+    else:
+        dico = sim.output.spatial_means.load()
 
 def get_font(size=10):
     _font = {'family': 'serif',
@@ -100,10 +123,7 @@ def _k_diss(params):
     return k_max / C / pl.pi  # FIXME: Not sure why the pi is needed
 
 def _eps(sim=None, t_start=0, path=None):
-    if sim is None and path is not None:
-        dico = SpatialMeansSW1L._load(path)
-    else:
-        dico = sim.output.spatial_means.load()
+    dico = load_spatial_means(path, sim)
     t = dico['t']
     ind = _index_where(t, t_start)
     eps = dico['epsK_tot'] + dico['epsA_tot']
@@ -112,10 +132,7 @@ def _eps(sim=None, t_start=0, path=None):
 
 def _t_stationary(sim=None, eps_percent=15, path=None):
     # Old function! Use epststmax instead
-    if sim is None and path is not None:
-        dico = SpatialMeansSW1L._load(path)
-    else:
-        dico = sim.output.spatial_means.load()
[…]

### 2019-02-18 Python/make_fig_energy_lap.py

@@ -1,0 +1,13 @@
+import matplotlib.pyplot as plt
+from base import matplotlib_rc
+from paths import load_df, exit_if_figure_exists
+from base_fig_energy import plot_energy
+
+matplotlib_rc(fontsize=10)
+path_fig = exit_if_figure_exists(__file__, '.png')
+df_w = load_df("df_lap")
+fig, ax = plt.subplots(1, 2, figsize=(6.5,3))
+plot_energy(df_w, fig, ax, N=[960, 2880], C=[10])
+fig.tight_layout()
+fig.savefig(path_fig)
+fig.savefig(path_fig.replace(".png", ".pdf"))

### 2019-02-18 Python/make_fig_flatness_lap.py

@@ -1,0 +1,68 @@
+#!/usr/bin/env python
+import pylab as pl
+import seaborn as sns
+import numpy as np
+import fluidsim as fls
+
+from base import _k_f, set_figsize, _rxs_str_func, matplotlib_rc, set_share_axes
+from paths import paths_sim, paths_lap, exit_if_figure_exists, load_df
+from make_fig_flatness import *
+
+
+if __name__ == '__main__':
+    matplotlib_rc(fontsize=fontsize)
+    path_fig = exit_if_figure_exists(__file__)
+    set_figsize(5, 4)
+    fig, ax = pl.subplots(2, 2, sharey=False, sharex=False)
+
+    df_w = load_df("df_lap")
+    df_3840 = df_w[df_w["$n$"] == 3840]
+    df_7680 = df_w[df_w["$n$"] == 7680]
+    
+    ax_inset3 = None  # _ax_inset(fig, '$r/L_f$', 0.325, 0.362)
+    ax_inset7 = None  # _ax_inset(fig, '$r:/L_f$', 0.775, 0.362)
+
+    sns.set_palette("cubehelix", 5)
+    plot_df(df_3840, fig, ax[:,0], ax_inset3)
+    sns.set_palette("cubehelix", 3)
+    plot_df(df_7680, fig, ax[:,1], ax_inset7)
+
+    for ax1 in ax[1,:]:
+        ax1.set_yscale("linear")
+        ax1.hlines([1.5], 1e-3, 10, linestyles="dashed", linewidths=(0.5,))
+
+    for ax1 in ax.flat:
+        ax1.set_xlim([1e-3, 10])
+
+    for ax1 in ax[1,:].flat:
+        ax1.set_ylim([0.7, 1.6])
+
+    for ax1 in ax[0,:]:
+        ax1.set_ylim([2, 500])
+        ax1.set_xlabel(None)
+        ax1.xaxis.set_tick_params(which='both', labelleft=False, labelright=False)
+        ax1.xaxis.offsetText.set_visible(False)
+
+    for ax1 in ax[:,1]:
+        ax1.set_ylabel(None)
+        ax1.yaxis.set_tick_params(which='both', labelleft=False, labelright=False)
+        ax1.yaxis.offsetText.set_visible(False)
+
+    ax[0,0].set_ylabel('$F_T$')
+    ax[1,0].set_ylabel('$F_T/F_L$')
+    ax[0,0].annotate(
+        "increasing $c$",
+        (3e-2, 3e0),
[…]

### 2019-02-18 Python/paths.py

@@ -57,7 +57,7 @@ def keyparams_from_path(p):
 
 EFR = r'$\frac{<\bf \Omega_0 >}{{(P k_f^2)}^{2/3}}$'
 pd_columns = [
-    r'$n$', r'$c$', r'$\nu_8$', r'$f$', r'$\epsilon$', r'$\frac{k_{diss}}{k_f}$', 
+    r'$n$', r'$c$', r'$\nu_8$', r'$\nu_2$', r'$f$', r'$\epsilon$', r'$\frac{k_{diss}}{k_f}$', 
     r'$F_f$', r'$Ro_f$', r'$Bu$',
     # '$\min h$', r'$\frac{\max |\bf u|}{c}$',
     EFR, r'$E$',
@@ -87,7 +87,7 @@ def pandas_from_path(p, key, as_df=False):
     maxuc = 0
     # del sim
     gc.collect()
-    data = [nh, c, params.nu_8, params.f, eps, kd_kf,
+    data = [nh, c, params.nu_8, params.nu_2, params.f, eps, kd_kf,
          Fr, Ro, Bu,
          # minh, maxuc,
          efr, E,
@@ -131,6 +131,7 @@ def specific_paths_dict(patterns=('/noise/SW1L*NOISE2*', '/vortex_grid/SW1L*VG*'
 paths_sim = specific_paths_dict()
 paths_sim_old = specific_paths_dict(['/noise/SW1L*NOISE_*'])
 path_pyfig = os.path.join(os.path.dirname(__file__), '../Pyfig/')
+paths_lap = specific_paths_dict(['/laplacian_nupt1/*'])
 if not os.path.exists(path_pyfig):
     os.mkdir(path_pyfig)
 

### 2019-02-18 Python/peak_detection.py

@@ -63,10 +63,11 @@ def avg_shock_seperation_from_shortname(
     with stdout_redirected():
         sim = fls.load_state_phys_file(path, merge_missing_params=True)
     mean, std = avg_shock_seperation(sim)
+    
     if not os.path.exists(save_as):
         with open(save_as, "a") as f:
-            result = "# short_name,path,mean,std\n"
-            f.write(result)
+            heading = "# short_name,path,mean,std\n"
+            f.write(heading)
 
     with open(save_as, "a") as f:
         result = f"{short_name},{path},{mean},{std}\n"
@@ -74,7 +75,7 @@ def avg_shock_seperation_from_shortname(
     return mean, std
 
 
-def run(nh_min, nh_max=10_000, df=None, save_as="dataframes/shock_sep.csv", dict_paths=paths_sim):
+def run(nh_min, nh_max=10_000, df=None, save_as="dataframes/shock_sep.csv", dict_paths=paths_sim, overwrite=False):
     if df is None:
         df = load_df()
     df = df[(df["$n$"] > nh_min) & (df["$n$"] < nh_max)]
@@ -82,6 +83,9 @@ def run(nh_min, nh_max=10_000, df=None, save_as="dataframes/shock_sep.csv", dict
         short = df.iloc[i]["short name"]
         print(dict_paths[short])
 
+    if os.path.exists(save_as) and overwrite:
+        os.remove(save_as)
+        
     return (
         df["short name"]
         .apply(

### 2019-02-18 Python/table_utils.py

@@ -1,0 +1,54 @@
+from base import *
+from paths import *
+import scipy
+import pandas as pd
+from pandas import DataFrame
+
+
+def float_format(val, *args):
+    # if isinstance(val, int):
+    if val.is_integer():
+        return '{:d}'.format(int(val), *args)
+    else:
+        return '{:.3g}'.format(val, *args)
+
+pd.options.display.float_format = float_format
+
+def get_row(df, col_name, col_val):
+    return df[df[col_name] == col_val]
+
+
+def clean_up(df):
+    df = df[
+        df["$n$"]>=960
+    ]
+    df = df[df["$t_{stat}$"] < 0.8 * df["$t_{\max}$"]]
+    return df
+
+def sort_reindex(df, prefix=None):
+    df = df.sort_values(by=[r'$c$', r'$n$', r'$Bu$', EFR])
+    if prefix is not None:
+        df.index = ['{}{}'.format(prefix, i) for i in range(1,len(df) + 1)]
+    else:
+        df.index = range(1,len(df) + 1)
+    # df = df.reindex(range(1,len(df) + 1))
+    return df
+
+
+from IPython import display
+
+def to_latex(df, strip_cols, filename=None):
+    df = df.drop(strip_cols, axis=1)
+            
+    output = df.to_latex(escape=False)
+
+    if filename == '':
+        print(output)
+    elif filename == 'jupyter':
+        display.display_html(df)
+    else:
+        with open(filename, 'a') as f:
+            f.write(output)
+
+
+print('scipy ==', scipy.__version__, '; pandas ==', pd.__version__, '; numpy ==', np.__version__)  # important!

### 2019-03-26 Python/make_fig_phys_fields_wave.py
Fix color scale of fig_phys_fields_wave_lap, update table for laplacian runs to include Re, ReFf2/3

@@ -8,7 +8,8 @@ from base import _k_f, set_figsize, matplotlib_rc, set_figsize, _index_where
 from paths import paths_sim, exit_if_figure_exists
 
 
-def fig_phys_subplot(sim, fig, ax, key_field, x_slice=None, y_slice=None, cmap='inferno'):
+def fig_phys_subplot(sim, fig, ax, key_field, x_slice=None, y_slice=None, cmap='inferno',
+                     vmin=None, vmax=None):
     kf = _k_f(sim.params)
     Lf = np.pi / kf
     X = sim.oper.x_seq / Lf
@@ -38,7 +39,6 @@ def fig_phys_subplot(sim, fig, ax, key_field, x_slice=None, y_slice=None, cmap='
     ax.set_xlabel('$x/L_f$')
     ax.set_ylabel('$y/L_f$')
     ax.set_rasterization_zorder(1)
-    vmin = vmax = None
     norm = None
     contours = ax.pcolormesh(
         X, Y, field, norm=norm, vmin=vmin, vmax=vmax, cmap=cmap, zorder=0)

### 2019-03-26 Python/make_fig_phys_fields_wave_lap.py

@@ -23,7 +23,9 @@ if __name__ == '__main__':
     sim1 = fls.load_state_phys_file(paths_sim[short_names[1]], merge_missing_params=True)
     keys = ['div', 'uy', 'div', 'uy']
     for ax, sim, key_field in zip(axes.ravel(), [sim0, sim0, sim1, sim1], keys):
-        fig_phys_subplot(sim, fig, ax, key_field, x_slice=[0,3], y_slice=[0,3])
+        vmax = 10 if key_field == "div" else 3.5
+        vmin = -50 if key_field == "div" else -3.5
+        fig_phys_subplot(sim, fig, ax, key_field, x_slice=[0,3], y_slice=[0,3], vmax=vmax, vmin=vmin)
 
     label ={
         'h': 'h',

### 2019-03-26 Python/paths.py

@@ -39,6 +39,12 @@ def get_pathbase():
     return pathbase
 
 
+def params_from_path(p):
+    params_xml_path = os.path.join(p, 'params_simul.xml')
+    params = ParamContainer(path_file=params_xml_path)
+    return params
+
+
 def keyparams_from_path(p):
     c = re.search('(?<=c=)[0-9]*', p, re.X).group(0)
     nh = re.search('(?<=_)[0-9]*(?=x)', p).group(0)
@@ -47,8 +53,7 @@ def keyparams_from_path(p):
     except AttributeError:
         Bu = 'inf'
 
-    params_xml_path = os.path.join(p, 'params_simul.xml')
-    params = ParamContainer(path_file=params_xml_path)
+    params = params_from_path(p)
     init_field = params.init_fields.type
     if init_field == 'noise':
         return init_field, c, nh, Bu, None

### 2019-03-26 Python/make_fig_phys_fields_wave_lap.py
Plot div for WL1,4,12,13. Redefine F_f, Re, Ro_f based on L_f

@@ -9,23 +9,46 @@ from paths import paths_lap as paths_sim, exit_if_figure_exists
 from make_fig_phys_fields_wave import fig_phys_subplot
 
 
+def load_sim(short_name):
+    params, Simul = fls.load_for_restart(
+        paths_sim[short_name], merge_missing_params=True)
+    params.oper.type_fft = "default"  # Enforce
+    params.output.HAS_TO_SAVE = False
+    params.output.ONLINE_PLOT_OK = False
+    params.ONLY_COARSE_OPER = False
+    return Simul(params)
+
+# load_sim = lambda short_name: fls.load_state_phys_file(
+#     paths_sim.get(short_name), merge_missing_params=True)
+ 
 if __name__ == '__main__':
     matplotlib_rc(fontsize=10)
     path_fig = exit_if_figure_exists(__file__, extension='.pdf')
     set_figsize(6.65, 5.8)
     fig, axes = plt.subplots(2, 2)
+    
     short_names = [
-        'noise_c20nh2880Buinf',  # WL7
-        'noise_c200nh2880Buinf'  # WL13
+          'noise_c10nh960Buinf',   # WL1
+          'noise_c10nh3840Buinf',  # WL5
+          'noise_c200nh960Buinf',   # WL12
+          'noise_c200nh2880Buinf',  # WL13
     ]
-    sim0 = fls.load_state_phys_file(paths_sim[short_names[0]], merge_missing_params=True)
-    sim1 = sim0
-    sim1 = fls.load_state_phys_file(paths_sim[short_names[1]], merge_missing_params=True)
-    keys = ['div', 'uy', 'div', 'uy']
-    for ax, sim, key_field in zip(axes.ravel(), [sim0, sim0, sim1, sim1], keys):
+#         'noise_c20nh2880Buinf',  # WL7
+#         'noise_c200nh2880Buinf'  # WL13
+#     ]
+#     sim0 = load_sim(short_names[0])
+#     sim1 = sim0
+#     sim1 = load_sim(short_names[1])
+#     keys = ['div', 'uy', 'div', 'uy']
+#     for ax, sim, key_field in zip(axes.ravel(), [sim0, sim0, sim1, sim1], keys):
+    keys = ['div'] * 4
+    for ax, sim, key_field in zip(axes.ravel(), map(load_sim, short_names), keys):
         vmax = 10 if key_field == "div" else 3.5
[…]

### 2019-03-26 Python/paths.py

@@ -71,7 +71,7 @@ def shortname_from_path(path):
 EFR = r'$\frac{<\bf \Omega_0 >}{{(P k_f^2)}^{2/3}}$'
 pd_columns = [
     r'$n$', r'$c$', r'$\nu_8$', r'$\nu_2$', r'$f$', r'$\epsilon$', r'$\frac{k_{diss}}{k_f}$', 
-    r'$F_f$', r'$Ro_f$', r'$Bu$',
+    r'$F_f$', r'$Ro_f$', '$Re$', '$ReF_f^{2/3}$', r'$Bu$',
     # '$\min h$', r'$\frac{\max |\bf u|}{c}$',
     EFR, r'$E$',
     '$t_{stat}$', r'$t_{\max}$', 'short name'
@@ -86,14 +86,20 @@ def pandas_from_path(p, key, as_df=False):
     
     c = int(c)
     kf = _k_f(params)
+    Lf = np.pi / kf
     kd_kf = _k_diss(params) / kf
     # ts = _t_stationary(path=p)
     # eps = _eps(t_start=ts, path=p)
     eps, E, ts, tmax = epsetstmax(p)
     efr = params.preprocess.init_field_const
-    Fr = (eps / kf) ** (1./3) / c
+    if params.nu_2 > 0:
+        Re = eps * (1/3) * Lf ** (4/3) / params.nu_2
+    else:
+        Re = np.nan  # defined differently
+
+    Fr = (eps * Lf) ** (1./3) / c
     try:
-        Ro = (eps * kf**2) ** (1./3) / params.f
+        Ro = (eps / Lf**2) ** (1./3) / params.f
     except ZeroDivisionError:
         Ro = np.inf
     minh = 0
@@ -101,7 +107,7 @@ def pandas_from_path(p, key, as_df=False):
     # del sim
     gc.collect()
     data = [nh, c, params.nu_8, params.nu_2, params.f, eps, kd_kf,
-         Fr, Ro, Bu,
+         Fr, Ro, Re, Re * Fr**(2/3), Bu,
          # minh, maxuc,
          efr, E,
          ts, tmax, key

### 2019-03-26 Python/base.py
Update tables with redefined Fr

@@ -155,21 +155,26 @@ def epsetstmax(path):
         def f(x, amptan, ttan):
             return amptan * pl.tanh(2 * (x / ttan)**4)
 
-        guesses = [pl.median(eps), time[eps==eps.max()]]
+        guesses = np.array([pl.median(eps), time[eps==eps.max()][0]])
     else:
         # def f(x, amptan, ttan, amplog, sigma):
         def f(x, amptan, ttan, amplog, tlog, sigma):
             return (amptan * pl.tanh(2 * (x/ttan)**4) +
                     amplog * stats.lognorm.pdf(x, scale=pl.exp(tlog), s=sigma))
 
-        guesses = {
-            'amptan': pl.median(eps),
-            'ttan': time[eps==eps.max()],
-            'amplog': eps.max(),
-            'tlog': time[eps==eps.max()],
-            'sigma': eps.std()
-        }
-        guesses = pl.array(list(guesses.values()), dtype=float)
+        guesses = np.array((
+            # amptan'
+            pl.median(eps),
+            # ttan'
+            time[eps==eps.max()],
+            # amplog
+            eps.max(),
+            # tlog
+            time[eps==eps.max()],
+            # sigma
+            eps.std()
+        ), dtype=float)
+        # guesses = pl.array(list(guessesd.values()), dtype=float)
 
     try:
         popt, pcov = curve_fit(f, time, eps, guesses, maxfev=3000)

### 2019-03-27 Python/paths.py
Fix Re definition and F_f definition for flatness plot

@@ -93,7 +93,7 @@ def pandas_from_path(p, key, as_df=False):
     eps, E, ts, tmax = epsetstmax(p)
     efr = params.preprocess.init_field_const
     if params.nu_2 > 0:
-        Re = eps * (1/3) * Lf ** (4/3) / params.nu_2
+        Re = eps ** (1/3) * Lf ** (4/3) / params.nu_2
     else:
         Re = np.nan  # defined differently
 

### 2019-03-27 Python/paths.py
Shock detection for all remaining laplacian runs, note t23 errored, so it was copied from t24

@@ -29,6 +29,8 @@ def get_pathbase():
             pathbase = '/scratch/avmo/13KTH/'
     elif os.getenv("SNIC_RESOURCE") == 'beskow':
         pathbase = '$SNIC_NOBACKUP/data/'
+    elif os.getenv("SNIC_RESOURCE") == 'tetralith':
+        pathbase = "/proj/kthmech/users/$USER/data/"
     else:
         raise ValueError('Unknown hostname')
 
@@ -137,7 +139,7 @@ def specific_paths_dict(patterns=('/noise/SW1L*NOISE2*', '/vortex_grid/SW1L*VG*'
     pathbase = get_pathbase()
 
     for pattern in patterns:
-        paths_dict.update(make_paths_dict(pathbase + pattern))
+        paths_dict.update(make_paths_dict(os.path.join(pathbase, pattern)))
 
     return paths_dict
 
@@ -145,7 +147,7 @@ def specific_paths_dict(patterns=('/noise/SW1L*NOISE2*', '/vortex_grid/SW1L*VG*'
 paths_sim = specific_paths_dict()
 paths_sim_old = specific_paths_dict(['/noise/SW1L*NOISE_*'])
 path_pyfig = os.path.join(os.path.dirname(__file__), '../Pyfig/')
-paths_lap = specific_paths_dict(['/laplacian_nupt1/*'])
+paths_lap = specific_paths_dict(['laplacian_nupt1/*'])
 if not os.path.exists(path_pyfig):
     os.mkdir(path_pyfig)
 

### 2019-03-27 Python/peak_detection.py

@@ -68,6 +68,7 @@ def avg_shock_seperation_from_shortname(
     t_approx=None,
 ):
     path = dict_paths[short_name]
+    print("Processing:", path)
     with stdout_redirected():
         # Need to load so because type_fft maybe set to use an MPI class
         params, Simul = fls.load_for_restart(path, t_approx, merge_missing_params=True)

### 2019-03-27 Python/run_peak_detection_laplacian.py

@@ -1,11 +1,13 @@
+import numpy as np
 from peak_detection import run
 from paths import paths_lap, load_df
 
 
 df = load_df("df_lap")
-df = df[(df["$n$"] == 960) | (df["$n$"] == 2880)]
+df = df[np.logical_not((df["$n$"] == 960) | (df["$n$"] == 2880))]
 print(df)
-for t in range(24,25):
+for t in range(24,26):
+    print("Time:", t)
     run(
         nh_min=0,
         df=df,

### 2019-04-02 Python/run_peak_detection_laplacian.py
Compute shock sep for new laplacian runs

@@ -4,9 +4,15 @@ from paths import paths_lap, load_df
 
 
 df = load_df("df_lap")
-df = df[np.logical_not((df["$n$"] == 960) | (df["$n$"] == 2880))]
+df = df[
+    np.logical_and(
+        df["$c$"] > 10,
+        np.logical_not((df["$n$"] == 960) | (df["$n$"] == 2880))
+    )
+]
 print(df)
-for t in range(24,26):
+# FIXME: t=12,21
+for t in range(22,26):
     print("Time:", t)
     run(
         nh_min=0,

### 2019-04-03 Python/base.py
Updated figure and table with 2nd set of laplacian runs

@@ -25,6 +25,28 @@ import fluidsim as fls
 DPI = 300
 
 
+def load_sim(path, coarse=True):
+    path = str(path)
+    params, Simul = fls.load_for_restart(path, merge_missing_params=True)
+    params.oper.type_fft = "default"  # Enforce
+    params.output.HAS_TO_SAVE = False
+    params.output.ONLINE_PLOT_OK = False
+    
+    params.ONLY_COARSE_OPER = coarse 
+    if coarse:
+        params.path_run = path
+        params.init_fields.type = "constant"
+        params.init_fields.modif_after_init = False
+        params.NEW_DIR_RESULTS = False
+
+    try:
+        params.preprocess.enable = False
+    except AttributeError:
+        pass
+
+    return Simul(params)
+
+
 def load_spatial_means(path, sim=None):
     if sim is None and path:
         if os.path.isdir(path):

### 2019-04-03 Python/make_fig_phys_fields_wave_lap.py

@@ -4,29 +4,23 @@ import h5py
 import numpy as np
 import matplotlib.pyplot as plt
 import fluidsim as fls
-from base import _k_f, set_figsize, matplotlib_rc, set_figsize, _index_where
+from base import (
+    _k_f, set_figsize, matplotlib_rc, set_figsize, _index_where,
+    load_sim as load_sim_from_path
+)
 from paths import paths_lap as paths_sim, exit_if_figure_exists
 from make_fig_phys_fields_wave import fig_phys_subplot
 
 
-def load_sim(short_name):
-    params, Simul = fls.load_for_restart(
-        paths_sim[short_name], merge_missing_params=True)
-    params.oper.type_fft = "default"  # Enforce
-    params.output.HAS_TO_SAVE = False
-    params.output.ONLINE_PLOT_OK = False
-    params.ONLY_COARSE_OPER = False
-    return Simul(params)
+load_sim = lambda short_name: load_sim_from_path(paths_sim.get(short_name), coarse=False)
 
-# load_sim = lambda short_name: fls.load_state_phys_file(
-#     paths_sim.get(short_name), merge_missing_params=True)
- 
+
 if __name__ == '__main__':
     matplotlib_rc(fontsize=10)
     path_fig = exit_if_figure_exists(__file__, extension='.pdf')
     set_figsize(6.65, 5.8)
     fig, axes = plt.subplots(2, 2)
-    
+
     short_names = [
           'noise_c10nh960Buinf',   # WL1
           'noise_c10nh3840Buinf',  # WL5

### 2019-04-18 Latex/article.tex
First revision

--- 2018-10-26 Latex/article.tex
@@
 is the separation. Then we carry out a series of forced simulations with
-resolutions up to $7680^2$, varying the Froude number, $F_{f} = \epsilon^{1/3} /
-ck_f^{1/3} $, where $ k_f $ is the forcing wave number and $c$ is the wave
+resolutions up to $7680^2$, varying the Froude number, $F_{f} = (\epsilon L_f)^{1/3}/
+c $, where $ L_f $ is the forcing length scale  and $c$ is the wave
 speed. In all simulations a stationary state is reached in which there is a
@@
 energy in the constant flux range. The third order structure function relation
-is satisfied with a high degree of accuracy. Mean energy is found to scale as $
-E \sim \sqrt{\epsilon c/k_f} $, and is also dependent on resolution, indicating
+is satisfied with a high degree of accuracy. Mean energy is found to scale approximately as $
+E \sim \sqrt{\epsilon  L_f  c} $, and is also dependent on resolution, indicating
 that shallow water wave turbulence does not fit into the paradigm of a
@@
 long thin bands of negative divergence in flow visualisations. The mean
-distance between the shocks is found to scale as $ d \sim F_f^{1/2}/k_f $.
+distance between the shocks is found to scale as $ d \sim F_f^{1/2} L_f $.
 Structure functions of second and higher order are found to scale in good
@@
 %
-The single layer SW equations are very similar to
+The single layer SW equations are very quite to
 the two-dimensional compressible Navier-Stokes equations.  The
@@
 
-For geophysical applications, it is convenient to consider the limit
-for which the linear wave frequency  is much larger than the
-characteristic nonlinear frequency $ U k$, where $U$ is a
-characteristic velocity.  In this limit, one can obtain a quasi-geostrophic
-single layer SW model, i.e. derive self-consistent evolution
-equations for a zero frequency variable, the Charney potential
-vorticity, which is totally decoupled from the fast waves.
-%
-For finite rotation and wave speed, there are slow balanced motions,
-which are associated with relatively weak non-zero linear frequency
-modes and there is only a weak
-interaction between waves and the balanced motions.
 %
@@
 waves by balanced flows \cite[]{FargeSadourny1989,
-LahayeZeitlin2012,Vanneste2013}.
-In this study, we consider the
-same equations in order to address a related but different issue.
-
-Balanced flows have a dynamics which is very similar to
+LahayeZeitlin2012,Vanneste2013}. Balanced flows have a dynamics which is very similar to
 two-dimensional turbulence, with an upscale energy cascade. %
@@
 transferring it to shorter waves \cite[]{Sadourny1975,
-FargeSadourny1989, YuanHamilton1994}.  The mechanism of a wave cascade
-has been proposed to explain the attraction towards the balanced flows
-\cite[]{Sadourny1975}.  \cite{YuanHamilton1994} showed that
+FargeSadourny1989}.   \cite{YuanHamilton1994} showed that
 statistically stationary shallow-water flows can be obtained by forcing
@@
 small scales.
-%
-They propose that the $k^{-5/3}$ spectra that are observed at the
-atmospheric meso-scales  \cite[]{NastromGage1985,LiLindborg2018}
-and reproduced by some atmospheric models based on the primitive
+They suggested that the $ k^{-5/3} $ energy spectrum observed at   atmospheric mesoscales  \cite[]{NastromGage1985,LiLindborg2018} is generated by a downscale cascade of gravity waves which may be captured by the SW equations.
+
+The $ k^{-5/3} $ spectrum has been reproduced 
+ by some General Circulation Models (GCM:s) based on the primitive
 equations \cite[]{KoshykHamilton2001, Skamarock2004,
-Hamilton_etal2008} could be reproduced by the one-layer
-shallow-water model by a downscale energy cascade of waves.
-However, few studies have investigated the dynamics of the downscale
-energy cascade of waves in SW models.
-Most numerical studies have investigated decaying flows and have not
-focused on the cascade \cite[]{FargeSadourny1989,
-LarichevMcWilliams1991, SpallMcWilliams1992,
-PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
-%
-Moreover, there are strong discrepancies between different numerical
-results and between these results and available theoretical results.
-%
-\cite{FargeSadourny1989} reported spectra scaling as $k^{-4}$
-whereas those shown by \cite{LahayeZeitlin2012} scale as $k^{-6}$.
-
-Some predictions are based on the weak wave turbulence formalism
-\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011}. In the case of
+Hamilton_etal2008}.
+\cite{AugierLindborg2013}  formulated a spectral energy budget of kinetic and available potential energy in terms of spherical harmonics and used this formulation to investigated two GCM:s.
+It was found that one of the models -- named the AFES model -- was able to reproduce a downscale energy cascade with realistic $ k^{-5/3} $ mesoscale spectra.
+The result was almost too good, since the AFES model simulation only contained 21 vertical levels, while theoretical arguments based on stratified turbulence theory \cite[]{Lindborg2006} suggest that a much finer vertical resolution would be needed.
+This lead us to ask what number of vertical levels a model needs in order  to reproduce a downscale energy cascade.
+Was \cite{YuanHamilton1994}  right  when they suggested that even a single layer model, such as the SW equations, could do the job?
+The original motivation of this study was to investigate this suggestion.
+A first set of simulations of the SW equations, containing both balanced and gravity wave motions, showed some encouraging results.
+Indeed, gravity waves were transferring energy towards small scales.
+However, after a while it became clear that the cascade was not as strong as in the GCM simulation.
+Moreover, in all the SW simulations we observed shocks with an associated $ k^{-2} $-spectrum rather than a $ k^{-5/3} $-spectrum.
+These observations lead us to dismiss the SW equations as a model for the atmospheric downscale cascade.
+Based on the SW equations we developed another two-dimensional toy model  \cite[]{LindborgMohanan} that is absent of shocks and can reproduce the energy cascade in the GCM quite well, including a $ k^{-5/3}  $-spectrum.
+
+The shocks we observed in the SW simulations left us in a state of curiosity.
+In some simulations they appeared to be pretty strong and in others rather weak.
+In some simulations they were densely packed and in others sparsely distributed.
+In what way  do the input parameters regulate these variations?
+Will there always be shocks or will they disappear in the limit of weak nonlinearities?
+Such questions made us to shift our theoretical focus and pursue the study, despite the fact that the answer to the question that originally motived it turned out to be negative.
+
+Some predictions  based on the weak wave turbulence formalism
+\cite[]{ZakharovLvovFalkovich1992, Nazarenko2011} may be of relevance in the limit of weak nonlinearities. In the case of
 inertia-gravity waves, \cite{FalkovichMedvedev1992} showed that the exact
@@
 \cite{ZakharovSagdeev1970} used weak turbulence formalism to derive a spectrum
-of the form $ E(k) \sim k^{-3/2} $ for acoustic turbulence. This prediction is
-of particular interest, since the acoustic equations and the SW equations are
-identical when a first order expansion is made in density or displacement
-perturbations. It may be questioned, however, that weak turbulence formalism is
+of the form $ E(k) \sim k^{-3/2} $ for three-dimensional acoustic turbulence. This prediction is
+of particular interest, since the acoustic equations and the SW equations are similar 
+to the equations describing acoustic turbulence. It may be questioned, however, that weak turbulence formalism is
 applicable to acoustic and SW wave turbulence, no matter how weak the
-nonlinearities are supposed to be. As pointed out by \cite{KadomtsevPet1970}
-and \cite{FalkovichMeyer1996}, when dispersion is small enough, waves moving in
-the same direction have the same velocity and interact strongly, which leads to
-the formation of shocks. In this case, the weak wave turbulence formalism is
-unable to give valuable results. Such sharp and long structures have been
-observed in many simulations \cite[]{FargeSadourny1989,
-PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012} but their effects are not
-well understood.
-%
-As shown by \cite{Burgers1948} the energy spectrum of a flow dominated by
+nonlinearities are supposed to be.
+\cite{KadomtsevPet1973} argued that shocks always will always develop in acoustic turbulence, also in the limit of weak nonlinearities, due to the fact that acoustic waves are nondispersive.
+
+Shocks have been been observed in many simulations of the SW equations \cite[]{FargeSadourny1989,
+PolvaniMcWilliamsSpallFord1994, LahayeZeitlin2012}.
+As shown by \cite{Burgers1948} in the one-dimensional case and \cite{Kuznetsov2004} in the two- and three-dimensional cases, the energy spectrum of a flow dominated by
 shocks will scale as $ k^{-2} $, a prediction which has been confirmed by a
@@
 direction while \cite{YuanHamilton1994} forced in geostrophic modes
-which severely complicates the interpretation.
-
-The dynamics of waves in complex SW flows is not well
-understood.  Even wave dynamics in absence of a balanced flow is not well
-understood. A statistically stationary wave cascade has never been
-simulated at high resolutions.
-%
-Is it possible to obtain a statistically stationary state in the very
-fast wave regime, and how does the mean energy in this hypothetical
-regime depends on the forcing and the wave speed?
-% What is the slope of
-How do energy spectra scale with the input parameters? From a theoretical point
-of view, the most interesting issue is, perhaps, the nature of the dynamics in
-the limit of weak nonlinearities. Will shocks prevail in this limit?
-%
-Such questions are still open and straightforward simulations may
-provide the answers.
-In this paper, we investigate the dynamics of single layer SW wave turbulence
-forced  at large scales by means of
-simulations with up the  $7680^2$ grid points.
-%
-Before presenting the results of the simulations we develop some theory.
-%
+which severely complicates the interpretation. Clearly, a new study of two-dimensional shock dominated wave turbulence can bring some more light on the problem.
+
+In this paper, we study SW wave turbulence as a generic case of a forced-dissipative wave breaking system.
+Although there may not be any straightforward meteorological or laboratory applications,  we believe that the investigation has interesting implications for a general understanding of wave turbulence and that there may be long term applications in different fields, such as acoustics and cosmology.
+To start with, we present some theory and then we report on a series of simulations of irrotational SW wave turbulence.
 
@@
 \begin{eqnarray} \label{IRR}
-\p_t \uu &=& -\bnabla \cdot (\uu \cdot \uu /2) - c^2 \bnabla h  \\
+\p_t \uu &=& -\bnabla  (\uu \cdot \uu /2) - c^2 \bnabla h  \\
 \p_t \JJ &=& -\p_j (u_j \JJ) - \bnabla E_p,\\
@@
 which gives
-\begin{equation}
+\begin{equation} \label{FluxT}
 2\p_t \meane{ \JJ'\cdot\uu + \JJ\cdot\uu' + 2c^2 h'h }
@@
 We will now use (\ref{eq_Kolmo}) together with straightforward geometrical and statistical arguments to construct a model for velocity and displacement structure functions of any order above a certain minimum.
-The model has some similarities with the one developed by \cite{BouchaudMezardParisi1995} for Burgers equation.
-The main difference is the that the mean dissipation rate, $\epsilon $, enters into the estimate of the shock amplitude and the final expressions of the structure functions in our model, but is absent in the model of \cite{BouchaudMezardParisi1995}.
+Our analysis has some similarities with the analyses by \cite{BouchaudMezardParisi1995}, \cite{WeinanKhaninMazelSinai1997} and \cite{Weinan}
+for Burgers equation. 
 We consider a domain with total area  $ {\mA} $ occupied by shocks which we 
@@
 =  \frac{1}{\mA} \int_{\mA}  d^2\xx |\delta h(\xx)|^p 
- \simeq  \frac{r}{\mA} \int_\shocks ds |\sin\theta| |\Delta h (s)|^p,
+ \simeq  \frac{r}{\mA} \int_\shocks ds |\cos\theta| |\Delta h (s)|^p,
 \end{eqnarray}
-where $\theta$ is the angle between the shock line and the separation
+where $\theta$ is the angle between the shock normal unit vector and the separation
 vector $\rr$ %
@@
 \simeq 
-r \frac{L_s}{\mA} \meant{|\sin\theta|} \means{|\Delta h |^p}
+r \frac{L_s}{\mA} \meant{|\cos\theta|} \means{|\Delta h |^p}
 \simeq  \frac{2}{\pi} \means{|\Delta h |^p} \frac{r}{d} ,
@@
 For velocity increments, we can also use a characteristic of the
-velocity singularities.  The step in velocity is only in the component
+velocity singularities.  The step in velocity is confined to  the component
 perpendicular to the shocks, which implies that the longitudinal and
 transverse increments can be written as  $\delta u_L = \delta u
-\sin\theta$, $\delta u_T = \delta u \cos\theta$.
+\cos\theta$, $\delta u_T = \delta u \sin\theta$.
 %
@@
 \simeq 
-\meant{|\sin\theta|^{1+p}}
+\meant{|\cos\theta|^{1+p}}
 \means{|\Delta u |^p} \frac{r}{d}
@@
 \simeq 
-\meant{|\sin\theta||\cos\theta|^{p}}
+\meant{|\cos\theta||\sin\theta|^{p}}
 \means{|\Delta u |^p} \frac{r}{d},
@@
 R_p(r) \equiv \frac{\meane{|\delta u_L|^p}}{\meane{|\delta u_T|^p}} = 
-\frac{\meant{|\sin\theta|^{1+p}}}{\meant{|\sin\theta||\cos\theta|^p}},
+\frac{\meant{|\cos\theta|^{1+p}}}{\meant{|\cos\theta||\sin\theta|^p}},
 \end{eqnarray}
@@
 \propto 
-\frac{\meant{|\sin\theta|^5}}{\meant{|\sin\theta|^3}^2} \frac{d}{r}   = \frac{9\pi}{15}  \frac{d}{r} \\ \label{FT}
+\frac{\meant{|\cos\theta|^5}}{\meant{|\cos\theta|^3}^2} \frac{d}{r}   = \frac{9\pi}{15}  \frac{d}{r} \\ \label{FT}
 F_T &=&  \frac{\meane{|\delta u_T|^4}}{\meane{|\delta u_T|^2}^2} 
 \propto
-\frac{\meant{|\sin\theta||\cos\theta|^4}}{\meant{|\sin\theta||\cos\theta|^2}^2} =  \frac{9\pi}{10}  \frac{d}{r} 
+\frac{\meant{|\cos\theta||\sin\theta|^4}}{\meant{|\cos\theta||\sin\theta|^2}^2} =  \frac{9\pi}{10}  \frac{d}{r} 
 \end{eqnarray}
@@
 again giving (\ref{Width}). 
-Applying the same averaging method we obtain the following estimates for skewness and flatness of the velocity derivative, $ \partial_x u $,
+Applying the same averaging method we obtain the following estimates for the skewness and flatness of the velocity derivative, $ \partial_x u $,
 \begin{eqnarray}
@@
 
-Finally, we estimate the Mach number of the shocks, that is the ratio between the shock propagation velocity and $ c $.
-According to \cite{Baines1998} the Mach number of a SW shock can be calculated as
+Finally, we estimate the Mach number, $ M = U/c $, where $ U $ is the shock propagation velocity in the frame of reference where the fluid velocity in front of the shock is zero. 
+Mass and momentum conservation give \cite[see][]{Baines1998} 
 \begin{equation}
@@
 \end{equation} 
-where $ h_+ $ and $ h_- $ are the nondimensional layer thickness before and after the shock, respectively.
-Noting that $ h_+ - h_- =  \;  \mid \!\!
-\Delta h | $, expanding in small $ | \Delta h | $ and using (\ref{Strength}) the Mach number can be estimated as
+where $ h_- $ and $ h_+ $ are the nondimensional layer thickness before and after the shock, respectively.
+Noting that $ h_+ - h_- =  \;  \Delta h  $, expanding in small $ \Delta h  $ and using (\ref{Strength}) the Mach number can be estimated as
 \begin{equation} \label{Mach}
@@
 
-The model we have developed is, indeed, very simple.
-As such, it must, of course, have limitations.
+The analysis we have developed has, of course, some limitations.
 First, it is obvious that  the linear scaling of the structure functions only can be valid for separations  that fulfil the condition $ \delta x \ll r \ll d $.
-Second, the model cannot be valid for low order moments or structure functions.
-The minimum order for which the model may be valid is not easily determined.
-According to  \cite{BouchaudMezardParisi1995} structure functions of shock dominated turbulence of all orders $ p  \ge 1 $ scale linearly in $ r $.
+Second, it is obvious that it  cannot be valid for low order moments or structure functions.
+According to arguments given by  \cite{BouchaudMezardParisi1995}  and \cite{Weinan}, it should be valid for structure functions of all orders $ p  \ge 1 $, in the asymptotic limit of large scale separation.
 It is quite easily argued, however, that the shocks can not determine the scaling of the structure functions of order $ p=1 $.
@@
 $ \means{ |\delta u_L | } < \langle | \delta u_L | \rangle _{ns} $, where the left hand side is the mean value over all separations where a shock is crossed and the right hand side is the mean value over separations where no shock is crossed.
-Therefore, the model is not valid for first order moments.
-It may be conjectured that it is valid for
-second and higher order structure functions.
+Therefore, the analysis is not valid for first order moments.
+In the following, we will compare the predictions with structure functions of second and higher orders calculated from simulations.
 
@@
 
-We have carried out a series of twenty forced-dissipative simulations of the SW
+We have carried out a set of twenty forced-dissipative simulations of the SW
 equations in a quadratic domain with periodic boundary conditions using the
 standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
-fluidsim}.
-%
+fluidsim}. In these twenty simulations we used an eight order diffusion operator to act as the agent of dissipation. 
+ On the request from the reviewers we have also carried out a set of thirteen simulation with  Laplacian diffusion.
+The results from the latter set, which are similar to the results from the first set,  are presented in Appendix A.
+
 The simulations were started from zero initial
@@
 reaching the scales where dissipation actually occurs.
+From a numerical point of view it is very beneficial to introduce a direct sink of APE of equal magnitude as the sink of KE.
+The addition of a hyperdiffusion term in (\ref{eq_h}) will provide such a sink without seriously affecting mass conservation, which will be 
+extremely well fulfilled, even when a high order hyperdiffusion term is added.
+
 %
@@
 of the non-quadratic energy and the aliasing errors in the truncated one-layer
-shallow water model, see][]{FargeSadourny1989}. The resolution is characterized
+shallow water model, see][]{FargeSadourny1989}. The resolution is characterised
 by the number of nodes, $n$, in each direction and has been varied from 960
@@
 \delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
-domain. 
+domain.  We define the forcing wave number as $ k_f = 6 \delta k $. To obtain as broad scaling range as possible it is preferable to choose 
+the forcing scale, $ L_f = \pi/k_f $, as large as possible.
+On the other hand, if $ L_f $ is too large, there is a risk that standing waves will be induced by the periodic boundary conditions and also that isotropy will be broken due to alignment of the shocks with the boundaries.
+We have found that $ L_f/L =1/12 $ is sufficient to avoid these two problems. 
 The forcing is white noise in time and designed so that the energy
 injection rate is normalised to unity at each time step. When the flow has reached a stationary state dissipation should therefore be equal to unity. 
-The strength of the stratification is characterized by a
+The strength of the stratification is characterised by a
 Froude number, defined as
 \begin{equation} \label{Fr}
-F_f = \frac{\epsilon^{1/3}}{c k_f^{1/3}} \, ,
+F_f = \frac{(\epsilon L_f)^{1/3}}{c} \, ,
 \end{equation}
@@
 
-\label{Table1}
-\begin{tabular}{lrrrrrrrr}
-
+\begin{tabular}{lrrrrrrr}
 \toprule
-{} &   $n$ &  $c$ &  $\nu_8$ &  $\epsilon$ &  $ k_{d}  / {k_f} $ &   $F_f$ &    $t_{\max}$ \\
+{} &   $n$ &  $c$ &  $\nu_8$ &  $\epsilon$ &  $\frac{k_{diss}}{k_f}$ &   $F_f$ &  $t_{\max}$ \\
 \midrule
-W1  &   960 &   10 & 1.56e-10 &        1.04 &                    28.8 &   0.111 &                49.9 \\
-W2  &  1920 &   10 & 9.68e-13 &        1.06 &                    57.7 &   0.112 &               49.8 \\
-W3  &  3840 &   10 &    6e-15 &         1.10&                     115 &   0.113 &               49.9 \\
-W4  &  7680 &   10 & 3.72e-17 &        1.18 &                     231 &   0.116 &               49.9 \\
-W5  &   960 &   20 & 1.56e-10 &           1.00 &                    28.8 &   0.055 &              49.9 \\
-W6  &  1920 &   20 & 9.69e-13 &        1.02 &                    57.7 &  0.0553 &                120 \\
-W7  &  3840 &   20 & 6.01e-15 &        1.08 &                     115 &  0.0563 &                120 \\
-W8  &  7680 &   20 & 3.72e-17 &        1.21 &                     231 &  0.0585 &                 120 \\
-W9  &   960 &   40 & 1.56e-10 &          1.00 &                    28.8 &  0.0274 &                49.8 \\
-W10 &  1920 &   40 & 9.68e-13 &       1.00 &                    57.7 &  0.0274 &               49.8 \\
-W11 &  3840 &   40 &    6e-15 &        1.06 &                     115 &   0.028 &               49.8 \\
-W12 &   960 &  100 & 1.56e-10 &       1.00 &                    28.8 &   0.011 &                49.8 \\
-W13 &  1920 &  100 & 9.69e-13 &        1.01 &                    57.7 &   0.011 &                 120 \\
-W14 &  3840 &  100 & 6.01e-15 &        1.06 &                     115 &  0.0112 &                 120 \\
-W15 &  7680 &  100 & 3.72e-17 &        1.22 &                     231 &  0.0117 &                95.8 \\
-W16 &   960 &  400 & 1.56e-10 &        1.14 &                    28.8 & 0.00287 &                 120 \\
-W17 &  1920 &  400 & 9.69e-13 &        1.15 &                    57.7 & 0.00288 &                 120 \\
-W18 &  3840 &  400 & 6.01e-15 &        1.12 &                     115 & 0.00286 &                119 \\
-W19 &   960 &  700 & 1.56e-10 &        1.27 &                    28.8 &  0.0017 &                49.8 \\
-W20 &  1920 &  700 & 9.68e-13 &        1.05 &                    57.7 &  0.0016 &                49.8 \\
+W1  &   960 &   10 & 1.56e-10 &        1.04 &                    28.8 &   0.16 &          50.0 \\
+W2  &  1920 &   10 & 9.68e-13 &        1.06 &                    57.7 &   0.16 &        49.9 \\
+W3  &  3840 &   10 &    6e-15 &         1.10 &                     115 &   0.17 &          50.0 \\
+W4  &  7680 &   10 & 3.72e-17 &         1.20 &                     231 &   0.17 &        25.2 \\
+W5  &   960 &   20 & 1.56e-10 &           1.00 &                    28.8 &  0.08 &          50.0 \\
+W6  &  1920 &   20 & 9.69e-13 &        1.02 &                    57.7 &  0.081 &         120 \\
+W7  &  3840 &   20 & 6.01e-15 &        1.08 &                     115 &  0.082 &         120 \\
+W8  &  7680 &   20 & 3.72e-17 &        1.21 &                     231 &  0.086 &         120 \\
+W9  &   960 &   40 & 1.56e-10 &       0.996 &                    28.8 &  0.040 &        49.9 \\
+W10 &  1920 &   40 & 9.68e-13 &       0.998 &                    57.7 &  0.040 &        49.9 \\
+W11 &  3840 &   40 &    6e-15 &        1.06 &                     115 &  0.041 &        49.9 \\
+W12 &   960 &  100 & 1.56e-10 &       0.999 &                    28.8 &  0.016 &        49.9 \\
+W13 &  1920 &  100 & 9.69e-13 &        1.01 &                    57.7 &  0.016 &         120 \\
+W14 &  3840 &  100 & 6.01e-15 &        1.06 &                     115 &  0.016 &         120 \\
+W15 &  7680 &  100 & 3.72e-17 &        1.22 &                     231 &  0.017 &        95.9 \\
+W16 &   960 &  400 & 1.56e-10 &        1.14 &                    28.8 &  0.0042 &         120 \\
+W17 &  1920 &  400 & 9.69e-13 &        1.15 &                    57.7 & 0.0042 &         120 \\
+W18 &  3840 &  400 & 6.01e-15 &        1.12 &                     115 & 0.0042 &         120 \\
+W19 &   960 &  700 & 1.56e-10 &        1.27 &                    28.8 & 0.0025 &        49.9 \\
+W20 &  1920 &  700 & 9.68e-13 &        1.05 &                    57.7 & 0.0023 &        49.9 \\
 \bottomrule
-
 \end{tabular}
+
+\vskip 3mm
 \caption{Parameters for all simulations. $ n $: number of nodes in each
@@
 \begin{equation} \label{MeanEnergy}
-E \sim \sqrt{\epsilon L_f c} \, n^{\alpha}  \, ,
-\end{equation}
-where $ L_f = \pi/k_f $ is the forcing scale. In figure~\ref{MeanE} to the
+E \sim \sqrt{\epsilon L_f c } \, n^{\alpha}  \, .
+\end{equation}
+ In figure~\ref{MeanE} to the
 left, we see $ E/\sqrt{\epsilon} $ as function of $ c $ for different resolutions $
@@
 with increasing values of $ C_n $ for increasing $ n $. In the same figure to
-the right we see $ E/\sqrt{\epsilon L_f c} $ for different values of $ c $. For
+the right we see $ E/\sqrt{\epsilon L_f c } $ for different values of $ c $. For
 each $ c $ the points follow a power law $ n^{\alpha} $, where $ \alpha $ is
@@
 
+That the energy transfer is not local in a system where the agent of dissipation is wave breaking or shock formation may be expected. According to the theory of ocean waves by  \cite{Phillips}, 
+`wave interactions are usually incapable of transferring energy from a given wavenumber
+band as rapidly as it is supplied by the wind'. Instead, energy is fed into each wave mode by the
+wind field and sucked out from the same mode in `intermittent patches of foaming'
+or `white horses'.  This may be a too simplified picture of SW water turbulence, since a broad band energy spectrum develops between the forcing and the dissipation wave numbers. 
+Nevertheless,  shock formation suggests that there is a considerable direct energy transfer from large to very small wave lengths, without any intermediate steps.
+
 The `four-fifths law' for the third order structure function of Kolmogorov
@@
 the divergence, $ \nabla \cdot {\bf u} $, to the left and the velocity
-component in the $ y $-direction, $ u_y $, to the right. The two figures at the
+component in the $ y $-direction, $ u_y $, to the right.
+Note that total area of the computational domain is sixteen times larger than the area of the outcuts shown in the figures, since the side length of the figures is $ 3 L_f $, while the side length of the computational domain is $ 12 L_f $.
+The two figures at the
 top are from run W6 while the two figures at the bottom are from run W17. The
@@
 However, as measured by the Mach number  (\ref{Mach}), the shocks are much weaker in run W17, where $ c $ is larger by a factor of 20 as compared to run W6 and $ d $ also is smaller.
-The shock interaction should therefore be weaker in run W17.
-The observation that the curvature of the shocks is smaller in run W17 than in run W6 may be explained by this fact.
+The shock interaction should therefore be weaker in run W17, which may explain the observation that the curvature of the shocks is smaller in run W17 than in run W6.
 We have calculated  the mean distance, $ d $, between the shocks by counting the number of negative spikes
-of the divergence along two hundred lines parallel to the $ x $-axis and
-equally many parallel to the $ y $-axis and then divided total length of all
-the lines by the number of spikes. Generally, we found that $ d \propto
-c^{-1/2} $, or
+of the divergence along two hundred lines parallel to the $ x $-axis and equally many 
+parallel to the $ y $-axis and then divided total length of all the lines by
+the number of spikes. Generally, we found that $ d \propto c^{-1/2} $, or
 \begin{equation} \label{MeanDistance}
@@
 follow the $ F_f^{1/2} $-curve quite well, although there seems to be a slight
-systematic deviation at the highest $ F_f $, which may be due to the fact that
-$ d $ is rather close to the length of the side of the box for the largest $
-F_f $.
-
+systematic deviation at the highest $ F_f $.
 \begin{figure}
@@
 As expected, we have found that the displacement structure functions scale
-exactly in the same way as the velocity structure functions, and for this
-reason we only plot
+exactly in the same way as the velocity structure functions, and for this reason we only plot
 velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
@@
 $ r $, which is the theoretical single point limit for an irrotational
-isotropic field. In figure~\ref{fig_flatness} we se the flatness factor, $
+isotropic field. In figure~\ref{fig_flatness} we see the flatness factor, $
 F_T $, of the transverse structure functions at the top and the ratio, $
@@
 Finally, we present energy and dissipation spectra. As expected, we found that APE and KE
-spectra were almost identical, why we only plot the
+spectra were almost identical, Therefore, we only plot the
 total spectra. In figure~\ref{fig_spectra_c40} we see  compensated and
@@
 Assuming that $ d \propto c^{-1/2} $ the ratio between the wave numbers at which the maxima are observed should be $ 70^{1/42} \approx 1.1 $, while the observed ratio is equal to $ 1.16 $.
-
-\section{Conclusions}
+In the latter case, there is no exact quantitative agreement between the predicted trend and the numerical results.
+
+\section{Conclusions and discussion}
 
@@
 order structure function above a certain minimum will scale as $ (\epsilon
-d)^{p/3} r/d $. Then, we carried out a series of twenty forced dissipative
+d)^{p/3} r/d $. Then, we carried out a series of  forced dissipative
 simulations, varying the Froude number and the resolution. In all simulations,
@@
 (\ref{Dissipation}) will go to zero both in the limit of small viscosity and
-large wave speed. This is different from three-dimensional Kolmogorov
+large wave speed. A similar observation was made when we used a second order diffusion operator instead of hyper diffusion (see Appendix A).
+This is different from three-dimensional Kolmogorov
 turbulence as well as strongly stratified turbulence, where, in both cases,
@@
 that SW wave turbulence does not fit into the paradigm of a local
-Richardson-Kolmogorov cascade. The second observation we made was that the mean
+Richardson-Kolmogorov cascade.  It remains a theoretical challenge to give a quantitative explanation of the growth of energy with increased Reynolds number. 
+As far as wee can see, such an explanation would require a completely novel theoretical development.
+The second observation we made was that the mean
 distance between the shocks scales as $ c^{-1/2} $, if the other parameters are
@@
 $ F_{f} \rightarrow 0 $ the range will eventually become so narrow so that
-breaking will disappear. Clearly, a necessary condition for wave breaking is 
+breaking will disappear.
+As argued in Appendix A, the condition $ \lambda_b \gg \delta x $ leads to a wave breaking condition involving both the Reynolds number,  $ Re  \equiv \epsilon^{1/3} L_f^{4/3} /  \nu $, and  the Froude number.
+If $ \lambda_b \propto F_f^{m} $ we obtain the condition $ Re F_f^{4m/3} \gg 1 $ and in the special case when $ m = 1/2 $, the condition is
+\begin{equation} \label{WC}
+Re F_f^{2/3} \gg 1 \, .
+\end{equation} 
+Thus,  for a given Reynolds number, no matter how large, wave breaking will be absent provided that $ F_f $ is sufficiently small.
+On the other hand, if (\ref{WC}) not only is a necessary but also a sufficient condition,  wave breaking will be present for any given $ F_f $, no matter how small, provided that $ Re $ is sufficiently large.
+The condition (\ref{WC}) is analogous to the condition for the presence of turbulence in a stratified fluid, also involving both the Reynolds number and a Froude number \cite[]{Brethouwer2007}.
+The horizontal and vertical length scales of stratified turbulence scale as $ l_h \sim u^{3}/\epsilon $ and $ l_v \sim u/N $, respectively, where $ u $ is a characteristic horizontal velocity and $ N $ is the Brunt-V\"ais\"al\"a frequency.
+As stratification becomes stronger ($ N $ is increasing), $ l_v $ is becoming smaller.
+However, in order for turbulence to be present $ l_v $ must be much larger than the Kolmogorov scale, $ \nu^{3/4}/\epsilon^{1/4} $, which leads to the condition $ Re F_h^2 \gg 1 $, where $ F_h = u/(l_h N) $ is a Froude number based on the horizontal length scale.
+
+ The present study makes some advancement of the understanding of compressible turbulence. Previously, energy flux relations  have 
+ been derived  for a compressible and barotropic fluid by \cite{Falkovich2010} and \cite{Galtier2011}.
+Unlike (\ref{FluxT}) these flux relations are not exclusively expressed in terms of third order structure functions, {\em i.
+e.} third order moments of increments of flow variables.
+As is clear from our analysis, in the general case of a compressible and irrotational fluid the KE flux can be expressed in this way.
+It seems to be more of a specific property that the APE flux also can be expressed in terms of a third order structure function, a property that the SW system shares with the Boussinesq system with constant Brunt-V\"ais\"al\"a frequency, in which case APE also is quadratic in buoyancy \cite[]{Augier2012}.
+In this context,  a comparison between our analysis and the analysis  by \cite{Galtier2011} of  isothermal compressible turbulence  is revealing.
+In the latter case, the pressure is linear in density, $ p = c_t^2 \rho $, where $ c_t $ is the isothermal speed of sound, and the internal energy per unit volume is  equal to $ c_t^2 \rho \ln (\rho/ \rho_0) $, where $ \rho_0 $ is an ambient reference density.
+Due to this  logarithmic dependence, the internal energy flux is not expressible in terms of a structure function.
+However, an equation system which is equivalent to the SW equations can be obtained by replacing the pressure term, $ \rho^{-1} \nabla p = \rho^{-1} c_t^{2} \nabla \rho $, in the isothermal momentum equation, by $ \rho_{0}^{-1} c_t^{2} \nabla \rho $, which may be motivated if density fluctuations are small.
+The expression for the internal energy per unit volume of the modified system is  $ c_t^2 \rho^2/2\rho_{0} $, which is equivalent to the SW potential energy.
+\footnote{To see how the logarithmic and quadratic expressions for the internal energy are
+ related, write $ \rho = \rho_0(1+\eta) $, expand in $ \eta $ and keep  terms up to second order: 
+ $ c_t^2\rho \ln(\rho/\rho_0) \approx c_t^2 \rho_0(1+\eta)(\eta - \eta^2/2) \approx   c_t^2 \rho^2/2 \rho_0 - c_t^2 \rho_0/2 $. 
+For small density fluctuations the two expressions only differ by a constant.} As a consequence of this quadratic dependence, the internal energy flux is expressible in terms of a structure function.
+It may be conjectured that the modified equation system is a good model for isothermal acoustic turbulence and that a flux relation which  equivalent to (\ref{FluxT}) also should hold for this case.
+In the three-dimensional case we then obtain
+ \begin{equation}
+\meane{ \delta (\rho u_L)    |\delta \uu|^2  }
++ c_t^2\meane{ \delta u_L(\delta \rho)^2  } /\rho_0 = - \frac{8}{3} \epsilon r \, ,\label{eq_Kolmo3}
+\end{equation}
+where  $ \epsilon $ here is the mean energy dissipation rate per unit volume.
+
+While isothermal acoustic turbulence may have some interesting application for a radiating gas \cite[]{Stein1967}, standard text book acoustics is not isothermal but isentropic.
+The  condition of constant entropy puts us in a dilemma when we analyse an acoustic field as a forced-dissipative system, since dissipation inevitably is associated with entropy production.
+According to arguments of \cite{KadomtsevPet1973}, an acoustic field is always dissipated by weak shocks if the Reynolds number is sufficiently large,  and this should be true in two as well as in three dimensions.
+Given the numerical results of the present study such a hypothesis seems reasonable, since shock waves have similar stability properties
+in two and three dimensions \cite[]{ApazidisEliasson2018, LivertsApazidis2016}.
+The shock wave hypothesis offers an elegant way out of the isentropic dilemma, since it implies that entropy production is concentrated at the shocks, while the rest of the field can be treated as isentropic.
+In a companion paper \cite[]{Lindborg2019}, scaling relations for such an acoustic field are derived, using the weak shock relations and the entropy equation.
+It turns out that these scaling relations are analogous to the relations for shallow water wave turbulence, with the  difference
+that the mean energy dissipation rate, $ \epsilon $, is replaced by $ \epsilon + \chi $, where $ \chi $ is a quantity associated with entropy production due to heat conduction.
+If  the Prandtl number is of the order of unity, $ \chi $ is of the same order as $ \epsilon $.
+The shock amplitude scales as $ \Delta u \sim (\epsilon + \chi)^{1/3} d^{1/3} $, where $ d $ is the characteristic distance between the shocks and the third order longitudinal structure function scales as $ \langle \delta u_L^{3} \rangle = -C (\epsilon + \chi)r $, where $ C $ is a constant of the order of unity, which can be determined exactly in the weak shock limit.
+
+Acoustic turbulence is an example of a wave breaking system where the concepts and methods we have developed to analyse SW water turbulence can be applied in a fruitful way.
+We believe that there may be other such examples.
+
+\vskip 0.5 cm
+
+\noindent The authors would like to thank Gregory Falkovich and Sergey Nazaranko for  fruitful criticism of an early version of the manuscript and three anonymous reviewers for useful comments.
+Financial
+support from the Swedish Research Council (VR) is gratefully
+acknowledged. The simulations were performed
+on resources provided by the Swedish National Infrastructure
+for Computing (SNIC) at PDC.
+
+\appendix
+
+\section{Simulations with Laplacian diffusion}
+%\label{app_comp}
+On the request from the reviewers we have carried out a set of simulations using Laplacian diffusion, $ \nu \nabla^{2} $, to check that similar results are obtained in this case as when we use higher order diffusion $ \nu_8 \nabla^{8} $.
+A number of test simulations with resolution $ n = 960 $ and $ c= 10 $ was first carried out using different values of the viscosity, till we determined a value which was sufficiently large for the shocks to be resolved, but not unnecessarily large.
+This value was then used for all simulations with $ n = 960 $.
+For the higher resolved simulations the viscosity was then set as $ \nu \propto n^{-1} $, in accordance with the prediction  (\ref{Width}) for the shock width.
+We define the Reynolds number as $ Re \equiv \epsilon^{1/3} L_f^{4/3}/\nu $, which is proportional to $ n $, since $ \nu \propto n^{-1} $.
+The simulations are listed in table 2.
+
+\begin{table}
+\begin{center}
+
+\label{Table2}
+
+\begin{tabular}{lrrrrrrrrr}
+\toprule
+{} &  $n$ &  $c$ &  $\nu $ &  $\epsilon$ &  $\frac{k_{diss}}{k_f}$ &   $F_f$ &  $\; Re$ &  $ReF_f^{2/3} $ &  $t_{\max}$ \\
+\midrule
+WL1  &  960 &   10 &   0.0985 &       0.998 &                    22.6 &   0.16 &  68.0 &           20 &          25 \\
+WL2  & 1920 &   10 &   0.0492 &       0.985 &                    45.3 &    0.16 &  136 &           40 &          25 \\
+WL3  & 2880 &   10 &   0.0328 &       0.984 &                    67.9 &    0.16 &    204 &           60 &          25 \\
+WL4  & 3840 &   10 &   0.0246 &       0.993 &                    90.5 &   0.16 &   273 &            80 &          25 \\
+WL5  & 7680 &   10 &   0.0123 &       1.000 &                     181 &   0.16 &   545 &           160 &          25 \\
+WL6  &  960 &   20 &   0.0985 &       0.994 &                    22.6 &  0.08 &  68.1&            13 &          25 \\
+WL7  & 2880 &   20 &   0.0328 &       0.982 &                    67.9 &    0.08 &  204 &           38 &          25 \\
+WL8  &  960 &   40 &   0.0985 &       0.985 &                    22.6 &    0.04 &  68.0 &           8.0 &          25 \\
+WL9  & 2880 &   40 &   0.0328 &       0.981 &                    67.9 &    0.04 &  204 &            24 &          25 \\
+WL10 &  960 &  100 &   0.0985 &       0.976 &                    22.6 &   0.016 &  67.5 &            4.3 &          25 \\
+WL11 & 2880 &  100 &   0.0328 &       0.961 &                    67.9 &  0.016 &  202 &           13 &          25 \\
+WL12 &  960 &  200 &   0.0985 &       0.988 &                    22.6 & 0.0080 &  67.8 &          2.7 &          25 \\
+WL13 & 2880 &  200 &   0.0328 &       0.928 &                    67.9 & 0.0079 &  200 &           7.9&          25 \\
+\bottomrule
+\end{tabular}
+
+\caption{Parameters for all the simulations executed with laplacian viscosity.
+$ n $: number of nodes in each direction, $ c $: wave speed, $ \nu  $:  viscosity, $ \epsilon $: time
+averaged mean energy dissipation in the stationary state, $ k_{d}/ k_f $: ratio
+between dissipation wave number and forcing wave number, $F_f $: Froude
+number, $Re$: Reynolds number, $ t_{max} $: end time of simulation.}
+\end{center}
+\end{table}
+
+\begin{figure}
+\centerline{\includegraphics[width=5.8in]{../Pyfig/fig_energy_lap}}
+\caption{Left: Mean energy in the stationary state versus $ c $ for different
+resolutions. The lines have slope $ 0.5 $, corresponding to $ E \propto c^{1/2}
+$. Right: Normalised mean energy in the stationary state versus resolution $ n
+$ for different $ c $.}
+\label{MeanE2}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=8cm]{../Pyfig/fig_shock_sep_lap.pdf}}
+\caption{Mean distance between the shocks as function of Froude number.  }
+\label{fig_distance_lap}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width= 8cmin]{../Pyfig/fig_flatness_div_norm_nu.pdf}}
+\caption{Flatness of divergence $ \nabla \cdot {\bf u} $ times viscosity $ \nu $, versus $ F_f $. Dotted straight line indicates $ F_f^{2/3} $. }
+\label{FlatnessDiv}
+\end{figure}
+
+\begin{figure}
+\centerline{\includegraphics[width=6.0in]{../Pyfig/fig_phys_fields_wave_lap}}
+\caption{$ \nabla \cdot {\bf u} $ for four different runs.
+Upper left: WL1, $ Re = 68 $, $ F_f = 0.16 $; Upper right: WL4,  $ Re = 273 $, $ F_f = 0.16 $; Lower left: WL12, $ Re = 68 $, $ F_f = 0.008 $; Lower right: WL13,  $ Re = 200 $, $ F_f = 0.008 $.}
+\label{Physical_lap}
+\end{figure}
+
+The dynamics of the runs with Laplacian diffusion were similar to the runs with higher order diffusion.
+In figure \ref{MeanE2} we see mean energy in the stationary state versus $ c $ to the left and versus $ n $ to the right.
+The variation of mean energy with $ c $ seems to be a little bit weaker for these runs as compared to the runs with hyper diffusion.
+However, the series of runs with $ n = 2280 $ (green crosses) is pretty close to approaching the $ c^{1/2} $-scaling.
+The variation of mean energy with resolution, or Reynolds number, is quite similar to what is seen in the corresponding plot \ref{MeanE}.
+For each $ c $ there is a monotonic increase of mean energy with resolution, and the increase is becoming stronger as $ c $ is increased, with comparable but not equal values of the exponent $ \alpha $.
+
+In figure \ref{fig_distance_lap} we see the mean distance between the shocks as a function of $ F_f $, together with a straight line indicating $ F_f^{1/2} $.
+There is a reasonable agreement between $ F_f ^{1/2} $ and each of the two series of simulations at $ Re \approx 70 $ (blue dots) and $ Re \approx 200$ (yellow triangles).
+However, there is a gap between the two series.
+This gap may be explained by the fact that the shock detection algorithm is much more sensitive to the threshold value which is used for $ \nabla \cdot {\bf u} $ in these simulations than in the simulations with hyperviscosity.
+In particular, this is true in the lower Reynolds number runs.
+In figure \ref{FlatnessDiv} we see the flatness of the divergence, multiplied by $ \nu $, versus $ F_f $.
+According to (\ref{FD}) we should have $ F_{\partial u} \nu \propto  d^{4/3} $ and if $ d \propto Fr^{1/2} $, the points should collapse on a single line, $ F_f^{2/3} $.
+The three runs at highest $ Re $ and the lowest value of $ F_f $ fall on top of each other in the upper right corner, supporting the scaling $ \nu^{-1} $ in the high Reynolds number limit.
+For the three highest $ F_f $ there is a reasonable agreement with $ F_f^{2/3} $, although the lower Reynolds number runs (blue dots) fall below the higher Reynolds number runs, which we interpret as a low Reynolds number effect.
+The points corresponding to the two lowest values of $ F_f $ fall below the prediction.
+This can be explained by the fact that the shocks are on the verge of fading away in these runs.
+Clearly, a necessary condition for shocks to be present is that the mean distance between them is much larger than their  width, that is
 \begin{equation} \label{Condition} 
-\frac{\lambda_b}{\delta x} \gg 1 \, .
-\end{equation} 
-It is interesting to note that this condition means that the flatness factor of velocity derivatives (\ref{FD}) should be much larger than unity and that this flatness factor is equal to the longitudinal flatness factor (\ref{FL}) in the limit $ r \rightarrow 0 $.
-Substituting (\ref{Width}) into (\ref{Condition})  and assuming that (\ref{MeanDistance}) is valid also in the case when Navier-Stokes viscosity is used we can formulate
-the condition as
-\begin{equation} 
-Re F_f^{2/3} \gg 1 \, ,
-\end{equation} 
-where we have defined the Reynolds number as $ Re  \equiv \epsilon^{1/3} L_{f}^{4/3} / \nu $. It may be conjectured  that such a condition is sufficient for wave breaking. If this is true, 
-wave breaking will appear for any small $ F_f $ provided that the Reynolds number is sufficiently large.
-
-The question that originally motivated this study was if SW wave turbulence can
-be used as a model for energy dissipation in the atmosphere and the oceans.
-Undoubtedly, the answer to this question is negative and the reason for this is
-not primarily the appearance of shocks and the associated $ k^{-2} $-spectrum
-which is not consistent with the observed $ k^{-5/3} $-spectrum. The main
-reason is that SW wave turbulence is a far too inefficient agent of
-dissipation. Since the Reynolds number of geophysical flows is extremely large
-and the stratification is strong, the relation (\ref{Dissipation}) implies that
-dissipation would be absent in the interior of the atmosphere and the oceans
-with SW turbulence as the responsible agent. This not what we observe. In a companion paper \cite[]{LindborgMohanan}
-we develop a toy model of geophysical turbulence which is similar to the SW equations in the mathematical structure, but is absent of shocks. 
-In this model energy is dissipated through a local cascade involving both vortical and wave modes.
-
-Although the answer to the question that originally motivated this study is
-negative, it may lead us or some other investigators to pursue another
-interesting research direction. As pointed out in the introduction, the
-acoustic equations are to the lowest order expansion in density perturbations
-identical to the SW equations. This study may therefore give important clues to
-the long standing problem of acoustic turbulence, in two and three dimensions.
-A similar shock model as we developed in two dimensions may easily be
-formulated in three dimensions, where the third order structure function law
-will be similar to (\ref{eq_Kolmo}), with the only difference that the constant
-$ 4 $ on the right hand side should be replaced by $ 8/3 $. In three dimensions
-we find
-\begin{equation}
-\meane{ |\delta \uu|^2 \delta J_L }
-+ c^2\meane{ (\delta h)^2 \delta u_L } = - \frac{8}{3} \epsilon r. \label{eq_Kolmo3}
-\end{equation}
-In the case of acoustic turbulence $ \delta h $ should be interpreted as a
-normalised density increment rather than a displacement increment. If shocks in
-three dimensions are assumed to form as smooth surfaces rather than smooth
-lines, then the mean distance between the shocks will appear in the
-model as $ d \sim {\cal{V}}/A_s $, where $ A_{s} $ is the total shock area and
-$ \cal{V} $ is the volume of the domain. The shock amplitude will thus scale as
-$ (\epsilon d)^{1/3} $ and the structure functions will scale as $ (\epsilon
-d)^{p/3} r/d $ also in three dimensions, provided, of course, that shocks will
-form in a similar way as in two dimensions. Generally, shock waves have similar 
-stability properties in two and three dimensions \cite[]{ApazidisEliasson2018, LivertsApazidis2016} and 
-it can therefore be expected that the three-dimensional case should be similar to the two-dimensional case. 
-If it is, the most interesting
-questions are if the mean energy and the mean distance between the shocks scale
-in a similar way in three dimensions as in two dimensions. Simulations or
-experiments of acoustic turbulence may provide answers to these questions --
-answers that will lead to further clues to a theoretical understanding of
-acoustic turbulence. We hope that the present study will stimulate research in
-this direction.
-
-%\appendix
-
-%\section{Kinetic energy dissipation and forcing rates}
-%\label{app_comp}
-%\input{appendix_dissip_forcing}
+\frac{d}{\delta x} \gg  1\, .
+\end{equation} 
+Since $ F_{\partial u} \propto d/\delta x $, this means that the flatness of divergence must be much larger than unity.
+Substituting (\ref{Width}) into (\ref{Condition})  and assuming that (\ref{MeanDistance}) is valid we can formulate the condition as
+\begin{equation}  \label{SCond}
+Re F_f^{2/3} \gg 1 \, .
+\end{equation} 
+If this condition is not fulfilled the shocks will fade away.
+In figure \ref{Physical_lap} we have plotted the divergence for four different runs with different $ Re $ and $ F_f $.
+It should be pointed out again, that the area of the computational domain is sixteen times larger than area of the outcuts shown in the figures.
+The two upper plots are from simulations with  $ F_f = 0.16 $ but different $ Re $ ($ Re = 68 $ to the left and $ Re = 273 $ to the right).
+As can be seen, the shocks are wider in the lower Reynolds number run to the left than in the higher Reynolds number run to the right, as expected.
+The lower left plot is from a simulation with the same $ Re $ as in the upper left plot, but with a much smaller $ F_f $.
+In this simulation we have $ Re F_f^{2/3} = 2.7 $, so the condition (\ref{SCond}) is not fulfilled, and the shocks have almost faded away.
+The lower right plot is from a simulation with the same $ F_f $ as in the lower left plot, but with a higher $ Re $.
+Here, $ Re F_f^{2/3} = 7.8 $ and  the shocks are clearly discernible.
 

### 2019-04-29 Python/base.py
Make table 2 again

@@ -63,6 +63,8 @@ def load_spatial_means(path, sim=None):
             return xr.Dataset.from_dataframe(df)
     else:
         dico = sim.output.spatial_means.load()
+        return dico
+
 
 def get_font(size=10):
     _font = {'family': 'serif',

### 2019-04-29 Python/paths.py

@@ -34,7 +34,7 @@ def get_pathbase():
     else:
         raise ValueError('Unknown hostname')
 
-    pathbase = os.path.abspath(os.path.expandvars(pathbase))
+    pathbase = os.path.abspath(os.path.expandvars(pathbase)).rstrip(os.path.sep)
     if not os.path.exists(pathbase):
         raise ValueError('Path not found ' + pathbase)
 
@@ -134,25 +134,26 @@ def make_paths_dict(glob_pattern='SW1L*'):
     return paths_dict
 
 
-def specific_paths_dict(patterns=('/noise/SW1L*NOISE2*', '/vortex_grid/SW1L*VG*')):
+def specific_paths_dict(patterns=('noise/SW1L*NOISE2*', 'vortex_grid/SW1L*VG*')):
     paths_dict = {}
     pathbase = get_pathbase()
 
     for pattern in patterns:
-        paths_dict.update(make_paths_dict(os.path.join(pathbase, pattern)))
+        glob_pattern = os.path.join(pathbase, pattern)
+        paths_dict.update(make_paths_dict(glob_pattern))
 
     return paths_dict
 
 
 paths_sim = specific_paths_dict()
-paths_sim_old = specific_paths_dict(['/noise/SW1L*NOISE_*'])
-path_pyfig = os.path.join(os.path.dirname(__file__), '../Pyfig/')
+paths_sim_old = specific_paths_dict(['noise/SW1L*NOISE_*'])
+path_pyfig = os.path.join(os.path.dirname(__file__), '../Pyfig_final/')
 paths_lap = specific_paths_dict(['laplacian_nupt1/*'])
 if not os.path.exists(path_pyfig):
     os.mkdir(path_pyfig)
 
 
-def exit_if_figure_exists(scriptname, extension='.png', override_exit=False):
+def exit_if_figure_exists(scriptname, extension='.eps', override_exit=False):
     scriptname = os.path.basename(scriptname)
     figname = os.path.splitext(scriptname)[0].lstrip('make_') + extension
     figpath = os.path.join(path_pyfig, figname)

### 2019-04-29 Python/table_utils.py

@@ -37,10 +37,10 @@ def sort_reindex(df, prefix=None):
 
 from IPython import display
 
-def to_latex(df, strip_cols, filename=None):
+def to_latex(df, strip_cols, filename=None, **kwargs):
     df = df.drop(strip_cols, axis=1)
-            
-    output = df.to_latex(escape=False)
+
+    output = df.to_latex(escape=False, **kwargs)
 
     if filename == '':
         print(output)

### 2019-04-29 Python/make_all_figures.py
Prepare final figures in eps

@@ -1,0 +1,49 @@
+#!/usr/bin/env python
+import runpy
+import os
+import sys
+import shutil
+from pathlib import Path
+
+
+def run(path):
+    """run
+
+    Parameters
+    ----------
+    path : Python script path
+
+    """
+    #  runpy.run_path(path)
+    os.system(f"{sys.executable} {path}")
+
+
+fig_num = 1
+for script in (
+    "make_fig_Emean_time.py",
+    "make_fig_energy_w.py",
+    "make_fig_flux_struct_combined.py",
+    #  "make_fig_spatiotempspectra.py",
+    "make_fig_phys_fields_wave.py",
+        #  "make_fig_shock_sep.py", TODO:
+    "make_fig_struct_order_246.py",
+    "make_fig_ratio_strfct.py",
+    "make_fig_flatness.py",
+    "make_fig_spectra.py",
+    "make_fig_diss_spectra.py",
+    "make_fig_energy_lap.py",
+        #  "make_fig_shock_sep_lap.py", TODO:
+        #  "make_fig_flatness_div_norm_nu.py", TODO:
+    "make_fig_phys_fields_wave_lap.py",
+):
+    print(f"Running {script}")
+    pyfig = Path.cwd() / ".." / "Pyfig_final"
+    figname, _ = os.path.splitext(script.lstrip("make_"))
+    output = os.path.abspath(
+         pyfig / (figname + ".eps")
+    )
+    run(f"./{script}")
+    dest = pyfig / f"fig{fig_num}.eps"
+    if not dest.exists():
+        shutil.copyfile(output, dest)
+    fig_num += 1

### 2019-04-29 Python/make_fig_Emean_time.py

@@ -109,7 +109,7 @@ def get_legend_and_paths(c_list, nh_list):
 
 if __name__ == "__main__":
     matplotlib_rc(fontsize)
-    path_fig = exit_if_figure_exists(__file__, ".png", override_exit=False)
+    path_fig = exit_if_figure_exists(__file__, override_exit=False)
     set_figsize(5.12, 3.0)
     fig1_plot_all(paths_sim)
     pl.savefig(path_fig)

### 2019-04-29 Python/make_fig_diss_spectra.py

@@ -69,7 +69,7 @@ def plot_df(df, fig, ax):
     for run_nb, (idx, row) in enumerate(df.iterrows()):
         short_name = row["short name"]
         tmin = row["$t_{stat}$"]
-        fig7_spectra(paths_sim[short_name], fig, ax, c, 
+        fig7_spectra(paths_sim[short_name], fig, ax,
                      t_start=tmin,
                      run_nb=run_nb)
 

### 2019-04-29 Python/make_fig_energy_lap.py

@@ -4,7 +4,7 @@ from paths import load_df, exit_if_figure_exists
 from base_fig_energy import plot_energy
 
 matplotlib_rc(fontsize=10)
-path_fig = exit_if_figure_exists(__file__, '.png')
+path_fig = exit_if_figure_exists(__file__)
 df_w = load_df("df_lap")
 fig, ax = plt.subplots(1, 2, figsize=(6.5,3))
 plot_energy(df_w, fig, ax, N=[960, 1920, 2880, 3840, 7680], C=[10, 20, 40, 100, 200])

### 2019-04-29 Python/make_fig_energy_w.py

@@ -4,7 +4,7 @@ from paths import load_df, exit_if_figure_exists
 from base_fig_energy import plot_energy
 
 matplotlib_rc(fontsize=10)
-path_fig = exit_if_figure_exists(__file__, '.png')
+path_fig = exit_if_figure_exists(__file__)
 df_w = load_df("df_w")
 fig, ax = plt.subplots(1, 2, figsize=(6.5,3))
 plot_energy(df_w, fig, ax)

### 2019-04-29 Python/make_fig_flatness.py

@@ -27,8 +27,9 @@ def _ax_inset(fig, xlabel, left, bottom=0.6, width=0.35 / 2, height=0.45 / 4):
     return ax_inset
 
 
-def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5, 
-                   key_var=('uy', 'ux'), run_nb=0, ax_inset=None, cache=False):
+def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5,
+                   key_var=('uy', 'ux'), run_nb=0, ax_inset=None, cache=False,
+                   n_colors=10):
     sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     order = [2, 4]
 
@@ -46,7 +47,7 @@ def fig12_flatness(path, fig, ax, tmin=0, tmax=1000, delta_t=0.5,
     _label = {'ux': 'F_L', 'uy': 'F_T'}
     L_f = pl.pi / _k_f(sim.params)
     # color_list = ['r', 'b', 'g', 'c', 'm', 'r', 'b']
-    color_list = sns.color_palette()
+    color_list = sns.color_palette(n_colors=n_colors)
     def get_F(key):
         So_4 = So_var_dict['{0}_{1:.0f}'.format(key, 4)]
         So_2 = So_var_dict['{0}_{1:.0f}'.format(key, 2)]
@@ -91,11 +92,12 @@ def plot_df(df, fig, ax, ax_inset):
         tmin = row["$t_{stat}$"]
         fig12_flatness(
             paths_sim[short_name], fig, ax_a, tmin=tmin, run_nb=run_nb,
-            key_var=('uy',), cache=test_mode
+            key_var=('uy',), cache=test_mode, n_colors=len(df)
         )
         fig12_flatness(
             paths_sim[short_name], fig, ax_b, tmin=tmin, run_nb=run_nb,
-            key_var=('uy', 'ux',), cache=test_mode, ax_inset=ax_inset
+            key_var=('uy', 'ux',), cache=test_mode, ax_inset=ax_inset,
+            n_colors=len(df)
         )
         if test_mode:
             break

### 2019-04-29 Python/make_fig_flux_struct_combined.py

@@ -12,7 +12,7 @@ from make_fig_Kolmo import fig3_struct
 
 if __name__ == '__main__':
     matplotlib_rc(fontsize=9)
-    path_fig = exit_if_figure_exists(__file__, '.png')
+    path_fig = exit_if_figure_exists(__file__)
     fig, ax = pl.subplots(1, 2, figsize=(7, 3))
     run = 'noise_c20nh3840Buinf'
     fig2_seb(paths_sim[run], fig, ax[0], t_start=20)

### 2019-04-29 Python/make_fig_phys_fields_wave.py

@@ -48,7 +48,7 @@ def fig_phys_subplot(sim, fig, ax, key_field, x_slice=None, y_slice=None, cmap='
     
 if __name__ == '__main__':
     matplotlib_rc(fontsize=10)
-    path_fig = exit_if_figure_exists(__file__, extension='.pdf')
+    path_fig = exit_if_figure_exists(__file__)
     set_figsize(6.65, 5.8)
     fig, axes = plt.subplots(2, 2)
     short_names = [

### 2019-04-29 Python/make_fig_phys_fields_wave_lap.py

@@ -17,15 +17,15 @@ load_sim = lambda short_name: load_sim_from_path(paths_sim.get(short_name), coar
 
 if __name__ == '__main__':
     matplotlib_rc(fontsize=10)
-    path_fig = exit_if_figure_exists(__file__, extension='.pdf')
+    path_fig = exit_if_figure_exists(__file__)
     set_figsize(6.65, 5.8)
     fig, axes = plt.subplots(2, 2)
 
     short_names = [
           'noise_c10nh960Buinf',   # WL1
-          'noise_c10nh3840Buinf',  # WL5
-          'noise_c200nh960Buinf',   # WL12
-          'noise_c200nh2880Buinf',  # WL13
+          'noise_c10nh2880Buinf',  # WL3
+          'noise_c200nh960Buinf',   # WL17
+          'noise_c200nh2880Buinf',  # WL18
     ]
 #         'noise_c20nh2880Buinf',  # WL7
 #         'noise_c200nh2880Buinf'  # WL13
@@ -40,9 +40,11 @@ if __name__ == '__main__':
         vmax = 10 if key_field == "div" else 3.5
         vmin = -50 if key_field == "div" else -3.5
         fig_phys_subplot(
-            sim, fig, ax, key_field, x_slice=[0,3], y_slice=[0,3], vmax=vmax, vmin=vmin
+            sim, fig, ax, key_field, x_slice=[0,3.01], y_slice=[0,3.01], vmax=vmax, vmin=vmin
         )
         sim.output.close_files()
+        ax.set_xticks(np.arange(0, 4.))
+        ax.set_yticks(np.arange(0, 4.))
 
     label ={
         'h': 'h',

### 2019-04-29 Python/make_fig_ratio_strfct.py

@@ -52,7 +52,7 @@ def fig11_ratio_struct(path, fig, ax1, order=[2, 3, 4, 5], tmin=0, tmax=1000,
 if __name__ == '__main__':
     sns.set_palette("cubehelix", 5)
     matplotlib_rc(11)
-    path_fig = exit_if_figure_exists(__file__, '.png')
+    path_fig = exit_if_figure_exists(__file__)
     set_figsize(5, 3)
     fig, ax = pl.subplots()
     fig11_ratio_struct(

### 2019-04-29 Python/make_fig_spectra.py

@@ -60,7 +60,7 @@ def _mean_spectra(sim, tmin=0, tmax=1000):
     return kh, E_tot, EK, EA
 
 
-def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb):
+def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb, n_colors=10):
     sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     kh, E_tot, EK, EA = _mean_spectra(sim, t_start)
     eps = _eps(sim, t_start)
@@ -73,7 +73,7 @@ def fig7_spectra(path, fig, ax, Fr, c, t_start, run_nb):
     o = 2
     L_f = pl.pi / k_f
     norm = (L_f * Fr**0.5)**(o / 3 - 1) * eps**(o/3) * kh**-2
-    color_list = sns.color_palette()
+    color_list = sns.color_palette(n_colors=n_colors)
 
     kh_f = kh / k_f
     ax.plot(
@@ -113,7 +113,9 @@ def plot_df(df, fig, ax):
         c = row["$c$"]
         fig7_spectra(paths_sim[short_name], fig, ax, Fr, c, 
                      t_start=tmin,
-                     run_nb=run_nb)
+                     run_nb=run_nb,
+                     n_colors=len(df)
+                     )
 
 
 if __name__ == '__main__':

### 2019-04-29 Python/make_fig_struct_eta_order_46.py

@@ -30,7 +30,7 @@ def _label(key='eta', odr=5):
 if __name__ == '__main__':
     matplotlib_rc(fontsize=9)
 
-    path_fig = exit_if_figure_exists(__file__, '.png')
+    path_fig = exit_if_figure_exists(__file__)
     fig, ax = plt.subplots(2, 2, figsize=(5, 4.2),
                            sharex=True, sharey=False)
 

### 2019-04-29 Python/make_fig_struct_order_246.py

@@ -34,25 +34,26 @@ def _label(key='ux', odr=5):
 def fig_struct_order(
     path, fig, ax, eps, Fr, order=[2, 4, 6], tmin=10, tmax=1000,
     delta_t=0.5, key="ux",
-    run_nb = 0, label_func=None, coeff=1, ylabel=True, test=False
+    run_nb = 0, label_func=None, coeff=1, ylabel=True, test=False,
+    n_colors=10,
 ):
     sim = fls.load_sim_for_plot(path, merge_missing_params=True)
     rxs, So_var_dict, deltax = _rxs_str_func(
         sim, order, tmin, tmax, delta_t, [key],
         cache=test
     )
-    
+
     for ax1 in ax:
         ax1.set_xlabel('$r/L_f$')
         ax1.set_xscale('log')
         ax1.set_yscale('log')
     if label_func is None:
         label_func = _label
-    
+
     L_f = np.pi / _k_f(sim.params)
 
-    #color_list = ['r', 'b', 'g', 'c', 'm', 'y', 'k']
-    color_list = sns.color_palette()
+    #  color_list = ['r', 'b', 'g', 'c', 'm', 'y', 'k']
+    color_list = sns.color_palette(n_colors=n_colors)
     if coeff == "1/c":
        coeff = 1 / sim.params.c2 ** 0.5
     elif coeff == "c":
@@ -72,6 +73,7 @@ def fig_struct_order(
             ax1.set_ylim([1e-1, 8])
         ax1.set_xlim([1e-3, 2])
 
+
 def plot_df(df, fig, ax, **kwargs):
     for run_nb, (idx, values) in enumerate(df.iterrows()):
         run = values["short name"]
@@ -79,7 +81,8 @@ def plot_df(df, fig, ax, **kwargs):
         Fr = values["$F_f$"]
         tmin = values["$t_{stat}$"]
         fig_struct_order(
-            paths_sim[run], fig, ax, eps, Fr, tmin=tmin, run_nb=run_nb, **kwargs)
+            paths_sim[run], fig, ax, eps, Fr, tmin=tmin, run_nb=run_nb,
+            n_colors=len(df), **kwargs)
         if "test" in kwargs and kwargs["test"] and run_nb == 1:
             break
 
@@ -87,7 +90,7 @@ def plot_df(df, fig, ax, **kwargs):
 if __name__ == '__main__':
     matplotlib_rc(fontsize=9)
 
[…]

### 2019-04-29 Python/make_fig_struct_order_5.py

@@ -31,7 +31,7 @@ def _label(key='ux', odr=5):
 
 if __name__ == '__main__':
     matplotlib_rc(fontsize=9)
-    path_fig = exit_if_figure_exists(__file__, '.png')
+    path_fig = exit_if_figure_exists(__file__)
     fig, ax = plt.subplots(1, 2, figsize=(5, 2.2), sharey=True)
 
     df_w = load_df("df_w")
